### 2022-11-05 paper/paper-mainfile.tex
create the template

\def\year{2022}\relax
%File: formatting-instructions-latex-2022.tex
%release 2022.1
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}

%
% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
\usepackage{newfloat}
\usepackage{listings}
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{xcolor}
%
\nocopyright
%
% PDF Info Is REQUIRED.
% For /Title, write your title in Mixed Case.
% Don't use accents or commands. Retain the parentheses.
% For /Author, add all authors within the parentheses,
% separated by commas. No accents, special characters
% or commands are allowed.
% Keep the /TemplateVersion tag as is
\pdfinfo{
/Title (Title)
/Author (Anonymous)
/TemplateVersion (2022.1)
}

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai22.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash

%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
% \iffalse
\title{Title}
\author {
    Submission
}
\affiliations{
    Anonymous
}
% \fi

%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\iffalse
\title{Title}
\author {
    % Authors
    Anonymous

}
\affiliations {
    % Affiliations
    Anonymous
}
\fi

% REMOVE THIS: bibentry
% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
\usepackage{bibentry}
% END REMOVE bibentry

\begin{document}

\maketitle

\begin{abstract}
   abstract  
\end{abstract}

% Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
\bibliography{aaai23}
% \nobibliography{aaai22}

\end{document}

### 2022-11-05 stuff/puk-tex-code/main.tex
create the template

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{floatrow}  
\usepackage{paralist}     % provides compactitem, a more compact itemize
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}

% other packages
\usepackage[noend,linesnumbered]{algorithm2e}
\usepackage{amsmath}
%\usepackage{subfloat}
\usepackage{csquotes}
\usepackage{todonotes}
\usepackage{subcaption}
% other files to include
\input{macros}

% \captionsetup{width=1.5\linewidth} 
% \subcaptionsetup{width=1.5\linewidth}

\begin{document}

\title{Finding Solution Preserving Linearizations For Partially Ordered Hierarchical Planning Problems}
\titlerunning{Solution Preserving Linearizations}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here

% \author{Anonymous}
\author{Ying Xian Wu\inst{1} \and
Songtuan Lin \inst{1} \and
Gregor Behnke\inst{2} \and
Pascal Bercher\inst{1} }

%\authorrunning{Wu. Y et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
	School of Computing, The Australian National University, Canberra, Australia\inst{1}\\
	ILLC, University of Amsterdam, Amsterdam, The Netherlands\inst{2}\\
	\email{ \{yingxian.wu, songtuan.lin, pascal.bercher\}@anu.edu.au, g.behnke@uva.ni}
}

%\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Solving partially ordered hierarchical planning problems is more computationally expensive compared to solving totally ordered ones. Therefore, automatically transforming partially ordered problem domains into totally ordered ones, such that the totally ordered problem still retains at least one solution, would be a desired capability as it would reduce complexity and thus make it easier for planning systems to solve the problem. This is a complex endeavour, because even creating \emph{all} possible linearizations of all methods in the original domain does not guarantee that solutions are preserved. 
It also allows the planner to use algorithms and heuristics specialised for the totally ordered case to solve the transformed problem. 
In this paper, we propose an algorithm for converting partially ordered problems into totally ordered ones and give criterion for when this is possible. We test our techniques on the partially-ordered track of the bench-mark set of the IPC 2020 and solve both the linearized and the original partially-ordered problems using state-of-the-art planning systems. We find that in the majority of problems across a variety of domains, the linearized problem remains solvable, and can always be solved faster than the without our proposed pre-processing technique.

\keywords{Partially ordered HTN planning \and  Hierarchical planning \and Totally ordered HTN planning }
\end{abstract}

\section{Introduction}
Hierarchical Task Network (HTN) planning \cite{HTNSurvey} \cite{IntroGhallab} is a hierarchical approach to planning. Tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound. HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks. A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications. If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.

In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks. In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.

%Existing problems must be modelled in HTN planning formalism in order to be solved by %existing planners, but the order in which tasks can be done is often unknown.
%This observation the forms the basis -- if a partially ordered problem could be quickly and %automatically analysed, then reduced to a decidable form without losing all solutions.

Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space. In some cases, such over-specification may remove all valid solutions. Thus many problems might be \emph{modelled} as POHTN problems. However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.

This paper specifically presents a method to transform a POHTN problem to a TOHTN problem in order to reduce the search space. Converting the problem to a TOHTN problem allows us to exploit the fact that as proven in Erol et al.\ \cite{ErolHTNExpressivity},  TOHTN planning as a class of problems has lower computational complexity, resulting in lower worst-case solving time. 
Thus, transforming a POHTN problem to a TOHTN problem could allow us to solve the problem more quickly and deploy specialised algorithms and heuristics.

The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. For example, Erol et al.\ \cite{ErolHTNExpressivity} proved that HTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages. Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.

% This is beneficial because heuristic design is comparably easy for total-order problems due to the missing interaction between tasks. Also, we get another class of decidable partially ordered problems that's orthogonal to recursive ones.

% Also, the domain model might be more intuitive: if a task is independent of some others it might be counter-intuitive to demand a certain position of it (if artificially made totally ordered). Plan recognition: independent goals can be described in parallel with POHTN planning but not with TOHTN \cite{DanielPlanRecognition}.

%\subsubsection{Contributions}
In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems. We prove that when certain criteria are met, it guarantees that at least one solution will be preserved. 
Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion. Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.

\section{Hierarchical Planning}
We first introduce classical planning, as hierarchical
planning can be considered an extension of classical planning.

\subsection{Planning Problem Formalisation}
Classical planning problems are defined over a \textbf{domain D} = $(F, A)$, where 
$F$ is a finite set of facts, or propositional state variables.
$A$ is a finite set of actions. 
For all $a \in A$,  $a \in 2^F \times 2^F \times 2^F$, which represents the preconditions and add and delete effects of an action. %$\langle pre, add, del \rangle$. 
The preconditions, add, and delete effects, of an action $a$ are referred to as $\Pre(a), \Add(a)$, and $\Del(a)$ respectively.
An action $a$ is executable in a state $s$ if its precondition $pre$ holds in $s$, i.e. $pre \subseteq s$. 
If executable in $s$, its result is the successor state $s'$ = $(s \backslash \Del) \cup \Add$, i.e., variables in $\Del(a)$ get removed and variables in $\Add(a)$ get added.

A \textbf{classical planning problem} is defined as $\textbf{P} = (D, S_I, S_G)$, 
where $D$ is the domain of the problem, 
$S_I \in 2^F$ is the initial state and $S_G \in F$ is the goal description.
Given a state $s \in 2^F$ , a fact is known for certain to be either true or false, i.e. information about the world state is complete at all times (this is called the closed world assumption).

A \textbf{solution} $\bar{a}$ to a problem is any action sequence that is executable in the initial state $S_I$, and leads to a state $s''$ that satisfies all
goals, i.e., $s'' \supseteq S_G$. Any such state $s''$ is called a goal state.

There are many formalisations for hierarchical planning, also known as \textbf{HTN planning}. The following one borrows heavily from Bercher et al.\ \cite{HTNSurvey} and Geier and Bercher \cite{Geier2011TIHTNDecidability}. HTN planning has two variants, Partially Ordered Hierarchical Task Network Planning, also known as POHTN planning, and Totally Ordered Hierarchical Planning, also called TOHTN planning,   % except with the initial task network replaced by a initial compound task.

A POHTN problem \textbf{P} = $(D, S_I, T_I)$
is defined over some domain $D$, 
has an initial state $S_I \in 2^F$, and 
has a initial compound task $T_I$. 
The closed world assumption also holds for HTN planning.

The domain \textbf{D} = $(F, T_P, T_C, \delta, M)$, where
$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.

A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
T, which is a finite set of task identifiers (ids); 
$\singlePrec$, which is a partial order over T; and
$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.

% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
A method $m$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
\begin{align}
tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
\end{align}
In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.

A solution to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ... t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ... \alpha(t_n) \rangle$ in $S_I$ is executable.

In other words, the goal of hierarchical planning is to find an decomposition of the task, then any executable refinement of the resulting decomposition. Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.

\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$. TO planning domains require that $\prec$ must specify a total order between task ids in $T$.
This leads to a difference in expressiveness and decide-ability of TOHTN vs POHTN planning. POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity). As per H\"{o}ller et al.\ \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TO planning is exactly as expressive as context free languages, whereas PO planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
In terms of complexity classes, Erol et al.\ \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas
Alford et al.\ \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.

%\textbf{Tail-recursive problems} are HTN problems where methods can only recurse through the last task in their task network. Problems that don't have recursion are also tail-recursive. \cite{Alford2015TightHTNBounds}

%\todo{maybe rephrase it a little bit? there are a lot of stuffs between decidable and undecidable problems}% Relying on a comparison to the Chomsky hierarchy, H\"{o}ller et al. [2014;2016] conducted an in-depth  showing which problems (i.e., which intended solution sets) can be expressed by various hierarchical and non-hierarchical formalisms.

%\subsubsection{Grammars}
%The following explanation for \cite{ChomskyHeirarchyRogers}
%A grammar $G$ is defined as $(N, \epsilon, P, S)$, where
%$N$ is  a set of non-terminal symbols, 
%$\epsilon$ is a set of terminal symbols,
%$P$ a set of production rules, that maps elements in $N$ to a finite sequence of elements in %$\epsilon$
%$S$ is the start symbol.
%A $Language$, defined by a specific grammar $G$, consists of all strings that can be produced by repeated application, including infinite applications, of the production rules to the start symbol $S$.

%In a context-free grammar, all production rules $\in P$ take the form $A \implies b$ where $A$ is a single non-terminal symbol and $b$ is a string of symbols. CFLs are those languages that %can be defined by a context-free grammar.

%The Chomsky hierarchy defined a relationship between these different classes of grammars, based off whether one grammar can pruduce all possible languages possible using another grammar class. Context-sensitive grammars are more general than context-free grammars, in the sense that there are languages that can be described by CSG but not by context-free grammars.

\section{Linearization Method}

Though this will not always be possible, we want to impose a total order on the task networks, such that for a method $m = (c, (T, \singlePrec, \alpha))$, the decomposition of $t$ will result in an executable sequence. To attempt this, one could analyse what preconditions the execution of sub-tasks in $T$ might need, and what effects they might have. For example, if a sub-task $t$ deletes a fact in the precondition for sub-task $t'$, one could order $t'$ before $t$ to avoid invalidating the precondition for $t'$. So we need a way of estimating preconditions and effects for compound tasks. It was proven by Olz et al.\ \cite{ConnyPreEstimation} that inferring all preconditions and effects of a compound task is as difficult as solving the problem. Therefore, a polynomial-time algorithm to infer the exact set of preconditions and effects of a compound task does not exist. However, using an approximated set, one can analyse the proposed orderings and resolve any conflicts, e.g. cycles. If conflict-resolution is necessary, we refer to this as needing \textbf{\textit{cycle-breaking}}.

The algorithm provided in this paper approximates possible preconditions and effects for all tasks so that this information can be used to linearize methods. 
For a given task $t$, we  call these approximate preconditions and effects as $\PreS(t), \DelS(t), \AddS(t)$.
If t is an action, $\PreS(t), \DelS(t), \AddS(t)$ is the same as $\Pre(t), \Add(t), \Del(t)$. 
If t is a compound task, $\PreS(t)$, $\AddS(t),  \DelS(t)$, are the union of the respective preconditions, add, and delete effects of all actions that $t$ could decompose to, as shown in Figure~\ref{CompoundPreEff}.
This means that for a task $t$ $\PreS(t), \DelS(t), \AddS(t)$ can contain contradictory effects, e.g. $t$ adds \emph{and} deletes a fact. These are essentially the mentioned literals defined by de Silva et al.\ \cite{mentionedliterals}.

Figure~\ref{AddOrderings} shows how the additional orderings for a method are determined. We then attempt to integrate these orderings into the method $m = (t, (T, \singlePrec, \alpha))$. If there exists a cycle after integrating the new orderings into $\singlePrec$, we remove a random one of the new orderings in that cycle, as shown in Figure~\ref{CycleBreak}, until that cycle no longer exists.
We repeat this for all methods in order to linearize them.

\begin{figure}
	\scalebox{0.8} {
	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.2cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (1) {C};
		\node[main node] (2) [below of=1] {D};
		\node[square effect, label=below:{del=\{a\}}] (3) [below of=2, left of=1] {e};
		\node[square effect, label=below:{add=\{b\}}] (4) [below of=2, left of=2] {f};
		\node[square effect, label=below:{del=\{b\}}] (5) [below of=2, right of=2] {g};

		\path[every node/.style={font=\sffamily\small}]
		(1) edge node [right] {} (2)
		(1) edge node [right] {} (3)
		(2) edge node [right] {} (4)	
		(2) edge node [right] {} (5);
		\end{tikzpicture}
	\end{subfigure}
}
	\hspace{1cm}
\scalebox{0.8}{
	\begin{subfigure}{3cm}
		\begin{tikzpicture}[->,auto,node distance=1.2cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node, label={add=\{b\}, del=\{a,b\}} ] (1) {C};
		\node[main node] (2) [below of=1] {D};
		\node[square effect, label=below:{del=\{a\}}] (3) [below of=2, left of=1] {e};
		\node[square effect, label=below:{add=\{b\}}] (4) [below of=2, left of=2] {f};
		\node[square effect, label=below:{del=\{b\}}] (5) [below of=2, right of=2] {g};

		\path[every node/.style={font=\sffamily\small}]
		(1) edge node [right] {} (2)
		(1) edge node [right] {} (3)
		(2) edge node [right] {} (4)	
		(2) edge node [right] {} (5);
		\end{tikzpicture}   
	\end{subfigure} 
}
	\caption{Inferring preconditions and effects for compound tasks}
	\label{CompoundPreEff}
\end{figure}

\begin{figure}
	\scalebox{0.8}{
	\begin{subfigure}{5cm} 
		\begin{tikzpicture}[->,auto,node distance=1.2cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]		
		\node[main node, label={add=\{b\}, del=\{a, b\}}] (3) {C};
		\node[main node, label=below:{add=\{a\}}] (2) [right of=3, below of=3] {B};
		\node[main node, label={pre=\{a\}}] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{The original method}
	\end{subfigure}
}
	\hspace{1cm}	
\scalebox{0.8}{
		\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.2cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node, label={add=\{b\}, del=\{a, b\}}] (3) {C};
		\node[main node, label=below:{add=\{a\}}] (2) [right of=3, below of=3] {B};
		\node[main node, label={pre=\{a\}}] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		 \caption{C deletes a fact (a) that is in preconditions for A  -- so A is ordered before C}
	\end{subfigure}
}
	\vspace{2em}
	\scalebox{0.8}{
	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.2cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node, label={add=\{b\}, del=\{a, b\}}] (3) {C};
		\node[main node, label=below:{add=\{a\}}] (2) [right of=3, below of=3] {B};
		\node[main node, label={pre=\{a\}}] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		(3) edge[dashed] node [right] {} (2)
		(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{B adds a fact (a) that C deletes -- so C is ordered before B}
	\end{subfigure}
}
	\hspace{1cm}
	\scalebox{0.8}{
	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.2cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node, label={add=\{b\}, del=\{a, b\}}] (3) {C};
		\node[main node, label=below:{add=\{a\}}] (2) [right of=3, below of=3] {B};
		\node[main node, label={pre=\{a\}}] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		(2) edge[dashed] node [right] {} (1)
		(3) edge[dashed] node [right] {} (2)
		(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{B adds a fact (a) that is in preconditions for A -- so B is ordered before A}
	\end{subfigure}
}
	\caption{Adding possible orderings to methods}

	\label{AddOrderings} 
\end{figure}

\begin{figure}
	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.5cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (3) {C};
		\node[main node] (2) [right of=3, below of=3] {B};
		\node[main node] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		(2) edge[dashed] node [right] {} (1)
		(3) edge[dashed] node [right] {} (2)
		(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{Perform depth-first search on the modified method}
	\end{subfigure}
	\hspace{1cm}
	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.5cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (3) {C};
		\node[main node] (2) [right of=3, below of=3] {B};
		\node[main node] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		(2) edge[dashed] node [right] {} (1)
		(3) edge[dashed] node [right] {} (2)
		(1) edge[dashed, bend right] node [left] {} (3);
		\end{tikzpicture}
		\caption{Identify cycle (path along which a node is reachable from one of their ancestors)}
	\end{subfigure}

	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.5cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (3) {C};
		\node[main node] (2) [right of=3, below of=3] {B};
		\node[main node] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		%(2) edge[dashed] node [right] {} (1)
		(3) edge[dashed] node [right] {} (2)
		(1) edge[dashed, bend right] node [left] {} (3);
		\end{tikzpicture}
		\caption{Pick an edge not originally in the method (i.e. a dashed line edge) and delete it.}
	\end{subfigure}
	\hspace{1cm}
	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.5cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (3) {C};
		\node[main node] (2) [right of=3, below of=3] {B};
		\node[main node] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		%(2) edge[dashed] node [right] {} (1)
		(3) edge[dashed] node [right] {} (2)
		(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{Repeat as necessary until depth-first search cannot find any path back to a previously visited node}
	\end{subfigure}
	\vspace{2cm}

	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.5cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (3) {C};
		\node[main node] (2) [right of=3, below of=3] {B};
		\node[main node] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		%(2) edge[dashed] node [right] {} (1)
		(3) edge[dashed] node [right] {} (2)
		(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{Perform depth-first search on the modified method (again)}
	\end{subfigure}
	\hspace{1cm}
	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.5cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
		\node[main node] (3) {C};
		\node[main node] (2) [right of=3, below of=3] {B};
		\node[main node] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		%(2) edge[dashed] node [right] {} (1)
		%(3) edge[dashed] node [right] {} (2)
		(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{Identify cycle (path along which a node is reachable from one of their ancestors (again))}
	\end{subfigure}

	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.5cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (3) {C};
		\node[main node] (2) [right of=3, below of=3] {B};
		\node[main node] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		%(2) edge[dashed] node [right] {} (1)
		%(3) edge[dashed] node [right] {} (2)
		%(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{Pick an edge not originally in the method (i.e. a dashed line edge) and delete it (again).}
	\end{subfigure}		
	\hspace{1cm}
	\begin{subfigure}{5cm}
		\begin{tikzpicture}[->,auto,node distance=1.5cm,
		thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
		square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

		\node[main node] (3) {C};
		\node[main node] (2) [right of=3, below of=3] {B};
		\node[main node] (1) [right of=2, above of=2]  {A};

		\path[every node/.style={font=\sffamily\small}]
		%(2) edge[dashed] node [right] {} (1)
		(3) edge[dashed] node [right] {} (2)
		%(1) edge[dashed, bend right] node [left] {} (3)
		(3) edge node [left] {} (1);
		\end{tikzpicture}
		\caption{No more cycles, so perform a topological sort to produce a total ordering that satisfies the above constraints}
	\end{subfigure}	
	\caption{Cycle breaking to make method linearized}
	\label{CycleBreak} 
\end{figure}

\subsection{Code}

\begin{align*}
& \forall t \in T_P : \PreS(t) = \Pre(t)  \land \AddS(t) = \Add(t)  \land \DelS(t) = \Del(t)  \\ %  \land
& \forall t \in T_C : \PreS(t) = \{f  \mid  \exists m \in M : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
& \forall t \in T_C : \AddS(t) = \{f  \mid  \exists m \in M : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
& \forall t \in T_C : \DelS(t) = \{f  \mid  \exists m \in M : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\
%& \forall t \in T_C : \PreS(t) = \{ \PreS(t)  \mid   \exists m \in M (m=(t,tn)) \}   \\
%& \forall t \in T_C : \DelS(t) = \{ \DelS(t)  \mid   \exists m \in M (m=(t,tn)) \}   \\
%& \forall t \in T_C : \AddS(t) = \{ \AddS(t)  \mid  \exists m \in M (m=(t,tn)) \}   \\
\end{align*}

\begin{algorithm}[H]\label{alg:Algorithm1}
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

	%\For {c $\in$ $T_C$} {
	%	\PreS, \AddS, \DelS = GetPreEff($F, T_P, T_C, \delta, M, visited, m$)
	%}

	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$}{  
		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
		$G \gets \singlePrec$ \\
		\For{a $\in$ F}{  
			\For{$t \in T_m$}{
				\For{$t' \in T_m$}{
					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
				}
			} 
		} 
		\While{$G$ has cycles in it}{
			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
		}
		$\prec'$ = Any linearization of $G$ \\
		$m' = (tasks(m), \prec', \alpha(t))$ \\
		$M' = M' \cup  \{m'\}$ \\
	}
	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
	\caption{Calculation of linearized methods}
\end{algorithm}

\subsection{Runtime}

% One of main results is that one can find these linearizations in poly-time and that those remaining/found still solve the problem if it was solvable in the first place.
%I would see this as a theorem that requires two proofs:
%- the preservance of solutions of the technique (soundness)
%- the P-runtime.

%Could also be that this procedure takes exponential time, which would be much less impressive.

\begin{theorem}\label{thm:Runtime}
	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
\end{theorem}
\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
To calculate $\PreS, \AddS, \DelS$ for each task $t$, we can perform breadth-first search on the task decomposition sub-tree (where tasks are nodes, and edges indicate possible decomposition by methods) rooted at $t$. The size of a sub-tree has an upper limit of $T_C + T_P$ nodes. For each primitive task in the sub-tree, we can iterate over each fact to update $\PreS, \AddS, \DelS$ for the root $t$. Thus calculating  $\PreS, \AddS, \DelS$ for a single compound task has an upper limit of $(3 * |F| * |T_p|) + |T_C|$. This inference occurs for each compound task, so inference for all compound tasks takes $((3 * |F| * |T_p|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$, where $|T|$ refers to $|T_P| + |T_C|$.

% Note that actually visiting $T_c$ nodes for each method requires that the domain have the initial task as the only compound task. In practice, most problems are likely to have significant depth, so a method is likely to have significantly less than all tasks to explore.
%For the computation of $\PreS, \AddS, \DelS $, it is trivial to see that exploring the Task %Decomposition Tree (TDT) for all methods that can decompose a compound task $c$ allows you to infer %preconditions and effects of $c$. Let the function for this procedure be called GetPreEff($F, T_P, %T_C, \delta, M, visited, m$). Tasks form the nodes of this TDT, 
%the upper bound is M * log(T) * F
%\todo{define TDT}

Lines 5 to 12 of Algorithm~\ref{alg:Algorithm1} builds a graph to represent each method. This graph's nodes are tasks of the task network produced, and the edges represent orderings between tasks. The code here iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method. Leading to $(M * F * (t_m)^2)$, where $t_m$ is the average number of sub-tasks per method. So it's at most $\mathcal{O}(|M| * |F| * |T|^2)$, since $t_m$ has an upper bound of $T$, where $T=T_p + T_C$.

Lines 12-13 of Algorithm~\ref{alg:Algorithm1} can be done by Depth-First Search (DFS). If a \enquote{back-edge}, defined as the edge that leads back to an already visited node (indicating a loop), then this edge is deleted, providing it was not part of the original domain. If it was part of the original domain, then assuming that the back edge was from node A to B, then a random edge is selected along any path from B to A (i.e. from the other part of the loop) and deleted instead.
DFS is known to be in $\mathcal{O}(|V|)$, and finding a path back can be achieved using Dijkstra's algorithm, which is known to be in $\mathcal{O}(|V|^2)$.

Temporal complexity of removing cycles is therefore $(|M| * ((t_m + t_m^2) * c)) = M * {t_m}^2 * c$, where $t_m$ is the number of sub-tasks produced by a method, and $c$ is the number of cycles.
% In practice, $c$ and $t_m$ will usually be small. 
This is approximately $\mathcal{O}(M * T^2 * c)$, since $t_m$ is upper bounded by $T$, where $T=T_p + T_C$.

Line 14 can be done via topological sort of the graph (which is known to be in $\mathcal{O}(V+E)$ in time and $\mathcal{O}(V)$ in space). In this case, the nodes of the graph are tasks, and the edges are orderings. So that's $M * (t_m+e_m)$, where $e_m$ is the number of \enquote{edges} in the new method, and has an upper bound of $e_m$ to find a topological sort for the sub-tasks of every method. That's approximately $\mathcal{O}(|M| * |T|)$, since both $t_m$ and $t_e$ are upper bounded by $T$, such that $T=T_p + T_C$.

So in total the main algorithm takes: \newline
$(|M| * |F| * |T|))$  +    % GetPreEff
$(|M| * |F| * |T|^2)$ + % Build new Graph
$(|M| * |T|^2 * c)$ +   % remove cycles
$(|M| * |T|))$        % topological sort

The number of times we need to remove an edge in a cycle, $c$, has an upper limit of $|F|$.
Adding an additional ordering (which may cause a cycle) requires interaction, and removing the aforementioned additional ordering will remove the cycle. Thus the maximum run-time of this algorithm is in $\mathcal{O}(M * F * T^2)$, i.e. quadratic time at most.
\end{proof}

\subsection{Theoretical properties}
\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$ is a not necessarily strict subset of that of $P$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
	\qed
\end{proof}

\begin{theorem}\label{thm:notCompleteness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$ may be empty.
\end{theorem}
\begin{proof}
	This algorithm linearizes all the methods to be totally ordered. Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents that are already ordered with respect to each other. This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered. Consider the simple example problem:

	\begin{figure}
		\caption{Diagram showing an example problem and its decomposition.}		
		\begin{subfigure}{3.5cm}
			\begin{align*}
				F   = & \{a, b, c \}           \\
				N_p =  & \{A, B, C\}      \\
				N_c = & \{AC, T_I\}            \\ 
				M   = & \{  (T_I, \{AC, B\}), \\
				       &    (AC, \{A, C\})  \} \\
				 S_I = & \{ a \} 	             \\ 
			\end{align*} 
		\end{subfigure}		
		\scalebox{0.7}{
		\begin{subfigure}{7cm}
			\begin{tikzpicture}[->,auto,node distance=1.5cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
			\node[] (InitState) {}; %{ $\mathbf{S_I = \{a\}}$ };

			\node[main node] (Init) [right=3cm of InitState] {$T_I$};
			\node[main node] (AC) [right=2cm of Init, below of=Init] {$AC$};

			\node[square node] (A) [left=2cm of AC, below of=AC, label=below:{pre=\{a\}, del=\{a\}, add=\{b\} }] {$A$};
			\node[square node] (B) [left=2cm of Init, below of=Init, label=below:{pre=\{b\}, del=\{b\}, add=\{c\} } ]  {$B$};
			\node[square node] (C) [right=2cm of AC, below of=AC, label=below:{pre=\{c\}, del=\{c\}} ]  {$C$};

			\path[every node/.style={font=\sffamily\small}]
			(Init) edge node [left] {} (B)
			(Init) edge node [left] {} (AC)
			(AC) edge node [left] {} (A)
			(AC) edge node [left] {} (C);
			\end{tikzpicture}
		\end{subfigure}	
		}
	\end{figure}

	\begin{figure}
		\scalebox{0.9}{
		\caption{The only possible solution $A, B, C$ for E.g. 1, requires the children of $AC$ and $B$ to be interleaved, meaning we cannot impose an order between them}
			\begin{tikzpicture}[->,auto,node distance=3cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\node[] (Invis) [] {$S_I$};
			\node[square node] (A) [right of=Invis] {$A$};
			\node[square node] (B) [right of=A] {$B$};
			\node[square node] (C) [right of=B] {$C$};

			\path[every node/.style={font=\sffamily\small}]
			(Invis) edge node [left, label=a] {} (A)
			(A) edge node [left, label=b] {} (B)
			(B) edge node [left, label=c] {} (C);
			\end{tikzpicture}		
		}
	\end{figure}

	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$. This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution. 
	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.

	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete. Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecideable problem into a decidable one.
	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
	\qed
\end{proof}

We will now see that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} does not have to break cycles.
\begin{theorem}\label{thm:SpecialCase}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if Algorithm~\ref{alg:Algorithm1} did not have to
	cycle-break, then if the solution set of $P$ is non-empty then the solution set of $P'$ will be non-empty as well.
\end{theorem}
\begin{proof}
	Assume that there exists a solution in the PO domain. By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain. Assume this sequence is $(a_0, a_1, ..., a_n)$. We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state. The action $a_k$ could only be non-executable, if one or more of its preconditions was not met. Assume one of these unmet preconditions is for existence of the state variable $A$.
	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution. So there must exist an action $a_i$, $0 < i < n$, that will add A. Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree. So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.

	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc. We are assuming that all methods linearized without conflict, so $(t_i, t_k)$ should not be required. This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm. In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.

	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution. Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e. the solution.
	\qed
\end{proof}

There are several levels of \enquote{completeness} possible. 
%\begin{enumerate}
	\begin{compactitem}
	\item all solutions remain 
	\item at least one solution remains 
	\item all optimal solutions remain
	\item at least one optimal solution remains 	
	\end{compactitem}
%\end{enumerate}
Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if no cycle-breaking is needed. If cycle-breaking is needed, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions. Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.

\begin{theorem}\label{thm:newClass}
	For any problem $P$ that satisfies the criterion for linearization without cycle-breaking, the problem $P'$ obtained from applying the algorithm to $P$ forms a new class of decidable problems.
\end{theorem}
\begin{proof}
	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable \cite{Alford2015TightHTNBounds}.  
	\qed
\end{proof}

%\begin{theorem}
%	Cycle-breaking is not guaranteed to eliminate solutions.
%\end{theorem}
%\begin{proof}
%	As per proposition 2.1 and 2.2, not all of the preconditions and effects are always needed. Suppose the initial task network consisted of 2 sub-tasks, $t_1, t_2$. If $t_2$ can decompose into an action $a_1$ such that $add(a_1) = A$, and an action $a_2$ such that $del(a_2) = A$,
%	and $t_1$ can decompose into an action $a_3$ with $prec(a_3) = A$
%	$t_2 = {add A, del A}$ and $t_1 = {prec A}$. The rules $\{(add A, prec A), (prec A, del A))\}$ of Algorthm 1
%	require orderings $\{(t_2, t_2), (t_2, t_1), (t_1, t_2)\}$, i.e.
%	Despite a cycle break being needed, this is obviously a solvable problem. Order $t_2$ before $t_1$ for this method.
%	Then when solving decompose $t_2$ to $a_1$ and $t_1$ to $a_3$. This creates a solution. Therefore, it is possible for the algorithm to preserve solutions despite needing cycle-breaking.
%\end{proof}

%%%%  
%\begin{theorem}
%	Given a POHTN planning problem $P = (F, T_P, T_C, \delta, M)$, for a given method $m \in M$, if some task $t \in T_P \cup T_C$ does not have an ordering applied to it by the graph $G$ built in lines 4-11 of Algorithm 1, 
%	then for the TOHTN problem $P'$ obtained from $P$ by using Algorithm 1,
%	the ordering of $t$ will not affect the executability of the final solution.
%	Given a method with all such tasks will cause the solution set of $P$ to equal the solution set of $P'$
%	Or in other words, if a linearization exists at all, it's possible to remove some edges from $G$ in Algorithm 1 to obtain it.
%\end{theorem}
%\begin{proof}
%	Assume that some pair of tasks $t_1, t_2$, Algorithm 1 did not add an ordering between them based off their preconditions and effects. Assume also that the ordering $t_1, t_2$ is executable but $t_2,t_1$ is not, i.e.
%	it matters where they are executed relative to each other.  \newline  \newline
%	This implies that $t_2$ deletes some variable A $t_1$ relies on. But from the definition of Algorithm 1,
%	that would mean that an ordering $(t_1, t_2)$ was created, which contradicts the assumption that there is no ordering between them.
%	Therefore $(t_2, t_1)$ ordering must also be executable. \newline  \newline
%	Thus if some task t has no ordering from the algorithm, it can never matter where it is in relation to any other task.
%	The algorithm will not order it specifically when $(\forall t' \in m, \forall a \in prec(t). a \notin add(t') \land a \notin del(t'))
%	\land  (\forall t' \in m, \forall a \in add(t). a \notin prec(t') \land a \notin del(t')) 
%	\land  (\forall t' \in m, \forall a \in del(t). a \notin add(t') \land a \notin prec(t'))$
%	In other words, the variables that affect t, do not affect other tasks in that method.
%\end{proof}

% \todo{the environments 'definition', 'lemma', 'proposition', 'corollary', 'remark', and 'example' are defined in the LLNCS documentclass as well.}

\section{Empirical Evaluation}
To prove that our technique is beneficial, we conduct a standard empirical evaluation on PO domains and compare the runtime of a state-of-the-art planning system on the original problem vs. the transformed problem. All problems are taken from two benchmark sets prepared for 2020 IPC. The first set\footnote{\url{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order}} was used in the partially ordered track in the 2020 IPC benchmark, while the second set\footnote{\url{https://github.com/panda-planner-dev/domains/tree/master/partial-order}} went un-used for various reasons. However, the second set still contains valid POHTN problems, so we include it here as well. Each problem has the standard IPC time limit of 30 minutes. Where grounding and pre-processing is needed, the time to do this is included as part of the 'solving' time required. Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem.

\subsubsection{Hardware and Planning Systems}
The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM, for a total of 8 GiB RAM.  We use the $panda_{\pi}$ solver \cite{progressionsearchJAIR20} \cite{useClassicalHeuristicIJCAI19} \cite{useClassicalHuristicICAPS18} on the configuration of Greedy best first search with  visited lists. We try this search with 4 different RC-heuristics: FF \cite{FF}, Add \cite{Add}, Filter \cite{useClassicalHuristicICAPS18} and Landmark-cut \cite{LM-Cut}.

We compare the performance of these 4 planner settings on the original problem and the pre-processed problem.
We also try the Lilotane planner \cite{Lilotane}, which is specialised for TOHTN problems. 
%VCPUs  : 4 \newline
%Memory : 8GB, OR 8192(MB) \newline
%Disk   : 30GB \newline
%RAM per VCPU; 2GB \newline
%CPU Shares: 256 \newline

\subsection{Results}

\begin{figure}
	\floatbox[{\capbeside\thisfloatsetup{capbesideposition={left,center},capbesidewidth=6cm}}]{figure}[\FBwidth]
	{\caption{Percentage of problems for which linearized problems is faster to solve, for problems that took at least $\mathit{x}$ seconds to solve, with $\mathit{x}$  being the value on the x-axis. \\ \label{faster}}}
	{\includegraphics[width=5cm]{figures/faster_to_solve_m.jpg}}

\end{figure}

\input{figures/IPC.tex}
\input{figures/coverage.tex}
% 'UM-Translog': 1, 'Monroe-Fully-Observable': 2, 'Woodworking': 2, 'Monroe-Partially-Observable': 2, 'PCP': 17, 'SmartPhone': 1}

\begin{figure}[t]
	\caption{Comparison of time to solve PO and TO problems, for each $panda_{\pi}$ setting} \label{RuntimevsSolved}
	\begin{subfigure}{6cm}
		\includegraphics[width=5cm]{figures/Runtime comparisionRC(Add).jpg}	
		\caption{Using heuristic RC\textsuperscript{add}}	
	\end{subfigure}
	\begin{subfigure}{6cm}
		\includegraphics[width=5cm]{figures/Runtime comparisionRC(Filter).jpg}	
		\caption{Using heuristic RC\textsuperscript{Filter}}
	\end{subfigure}

	\begin{subfigure}{6cm}
		\includegraphics[width=5cm]{figures/Runtime comparisionRC(FF).jpg}	
		\caption{Using heuristic RC\textsuperscript{FF}}	
	\end{subfigure}
	\begin{subfigure}{6cm}
		\includegraphics[width=5cm]{figures/Runtime comparisionRC(LM-Cut).jpg}
		\caption{Using heuristic RC\textsuperscript{LM-Cut}}		
	\end{subfigure}
\end{figure}

\subsection{Analysis}

Table~\ref{tabIPC} and \ref{tabcoverage} shows that the IPC score and coverage when pre-processing is overall significantly better than when not using pre-processing.

However in some domains there is minimal gain, if any at all. This seems to be because some domains are dominated by small problems. E.g.\ 14 of the 17 PCP problems take less than 0.5 seconds to solve. For very small problems, the pre-processing still takes time, but very little improvement can be gained in the actual solving time. In fact, a second of pre-processing time for a problem that only takes a few seconds to solve will worsen IPC score.

On the other hand, big problems experience significant improvement, enough to make problems solvable within the time limit where they were previously too memory or time intensive. We can see that difference in domains like Rover and Barman-BDI, where there is significant space to improve on coverage/speed.

\input{figures/Allows_retry_table.tex}
\input{figures/Forbids_retry_table.tex}

Table~\ref{tabsummary1} and Table~\ref{tabsummary2} summarises the results of our empirical evaluation on the IPC 2020 benchmarks. The \enquote{unsolvable} columns refer to problems that the solver determined to have no solutions. Lilotane \cite{Lilotane}, the runner-up for the totally ordered track in the 2020 IPC competition, cannot prove that a problem is unsolvable, and thus can't use a re-run policy, unlike the $panda_{\pi}$ planner.
Note that Lilotane wants a lifted representation,
but a grounded representation was used here, to its disadvantage.

The PCP domain in particular was rendered unsolvable for all instances.  In Table~\ref{tabIPC} and Table~\ref{tabcoverage}, $\text{PCP}^{17}$ indicates that 17 PCP problems were unsolvable. So all 14 problems \enquote{solved} in the TO context was from re-running the planner on the original problem using the remaining time. Incidentally, the exact same problems were proven unsolvable for all planners.

The PCP domain defines the post-correspondence problem, which is known to be undecidable. Totally ordered HTN planning problems are always decidable \cite{LanguageClassificationPlanning}, meaning it's a direct consequence that these problem instances are unsolvable without task interleaving. In this specific case, the PCP problems designed for the IPC benchmark are known to be unsolvable without interleaving \cite{PCPDomain}. Table~\ref{tabsummary2} shows the results on the default setting, when allowing the planner to try solving the original problem as a back-up plan when the linearized problem fails. Lilotane is excluded from Table~\ref{tabsummary2} as it cannot prove a problem is unsolvable, and so cannot use the re-run policy. instead. Table~\ref{tabsummary1} shows results without the default back-up strategy.  % the planner moves on to the next problem immediately after the linearized approach for a problem fails.
%  This means that if we could convert such that it retained a solution, we would be turning an undecidable problem into a decidable one -- in other words impossible. A totally ordered problem just does not have the expressive power.

From Table ~\ref{tabsummary2} and \ref{tabsummary1} we can see that this processing means that many more problems can be solved in the time limit, where previously they were too computation-intensive, and very few problems (primarily problems for which interleaving is required for all solutions) become unsolvable due to the transformation. Despite the fact that none of the instances can be linearized without cycle-breaking, only 25/274 of linearized problems are unsolvable, 17 of which are from the PCP domain, where a solvable linearization does not exist.

\section{Conclusion}
Though it's impressive performance on a range of domains is good news, the success of this approach on the IPC benchmark ultimately hinges on the relative lack of unsolvable problems --
e.g. PCP problems in the ICAPS benchmark. When the pre-processed domain eliminates all solutions, significant time is wasted in proving this. Fortunately, the IPC benchmark covers a wide variety of domains, so the performance of the pre-processing is hopefully indicative of good performance in other problems as well. Ultimately, it's also an undecidable problem to detect when a problem cannot be converted to TOHTN representation (as that would be solving whether the problem is undecidable), so no perfect solution exists.
% . For example, a simple machine learning model that learns when the pre-processing step could be applied, by analysing some basic features of the problem, such as size of the problem, structure of the Task Decomposition Graph, etc, could further improve, and is of interest in further work.
\section{Further Work}
Given that HyperTensioN \cite{hypertension} and Lilotane \cite{Lilotane}, planning systems that work on \emph{lifted} totally ordered problems, and rely significantly on lifted input for their efficiency, it would be of interest to generalise this technique to produce lifted domains, so that HyperTensioN and Lilotane can solve the linearized problem more efficiently. For another, the success of this solution was, as stated before, in part due to the relatively few undecidable problems in the benchmark set. A heuristic to decide whether or not to pre-process, so that we can reduce the case where the planning system attempts to solve an unsolvable problem might allow this procedure to generalise better in less favourable circumstances.

%A less naive procedure for approximating preconditions and effects for compound tasks, allowing stronger assumptions to be made when linearizing, may also be of interest.

%The additional processing time is within the same order of time as the time needed for grounding and a tiny fraction of the overall time $\sim$   We compare the ratio of (Grounding + Pre-processing time + TO solve time) to (Grounding + PO solve time), as those are the steps needed to solve the respective problems. The average solve time for the TO problem is ?? percent of the PO problem, for all problems. Difference in reduction of total solving time influenced most by ? (e.g. domain, recursiveness of problem, percentage of linearizable methods, etc)

%\subsubsection{Acknowledgements} Please place your acknowledgments at
%the end of the paper, preceded by an unnumbered run-in heading (i.e.
%3rd-level heading).

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{bib}
% %\bibitem{ref_article1}
% %Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% %\bibitem{ref_lncs1}
% %Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% %F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% %Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% %\bibitem{ref_book1}
% %Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% %Location (1999)

% %\bibitem{ref_proc1}
% %Author, A.-B.: Contribution title. In: 9th International Proceedings
% %on Proceedings, pp. 1--2. Publisher, Location (2010)

% %\bibitem{ref_url1}
% %LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% %Oct 2017
% \end{thebibliography}
\end{document}

### 2022-11-08 paper/mainfile.tex
Update template with first dradt

\documentclass[letterpaper]{article}
% DO NOT CHANGE THIS
% \usepackage[submission]{aaai23} % DO NOT CHANGE THIS
\usepackage[submission]{../AuthorKit23/AnonymousSubmission/LaTeX/aaai23}
\usepackage{times} % DO NOT CHANGE THIS
\usepackage{helvet} % DO NOT CHANGE THIS
\usepackage{courier} % DO NOT CHANGE THIS
\usepackage[hyphens]{url} % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm} % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\usepackage{natbib} % DO NOT CHANGE THIS
\usepackage{caption} % DO NOT CHANGE THIS
\frenchspacing % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
%
% Keep the \pdfinfo as shown here. There’s no need
% for you to add the /Title and /Author tags.
\pdfinfo{
	/TemplateVersion (2023.1)
} 
\usepackage{booktabs} 
\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb,amsmath}
\usepackage{todonotes} 
\usepackage{tikz}

\newtheorem{theorem}{Theorem}
\newtheorem{proof}{Proof}

\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)

\newcommand{\Add} {\ensuremath{\mathit{add}}}
\newcommand{\Del} {\ensuremath{\mathit{del}}}
\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}

\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
\newcommand{\PossEffPlus} {\ensuremath{\mathit{poss-eff^{+}_{*}}}}
\newcommand{\PossEffMinus} {\ensuremath{\mathit{poss-eff^{-}_{*}}}}

\newcommand{\RelEffPlus} {\ensuremath{\mathit{eff^{\emptyset +}_{*}}}}
\newcommand{\RelEffMinus} {\ensuremath{\mathit{eff^{\emptyset -}_{*}}}}
\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}

\title{Transforming Partially Ordered HTN Problems to Totally Ordered}
\begin{document}
\maketitle

\begin{abstract}
Solving partially ordered hierarchical planning problems is more computationally expensive compared to solving totally ordered ones. Therefore, automatically transforming partially ordered problem domains into totally ordered ones, such that the totally ordered problem still retains at least one solution, would be a desired capability as it would reduce complexity and thus make it easier for planning systems to solve the problem. It also allows the planner to use algorithms and heuristics specialised for the totally ordered case to solve the transformed problem.

This is a complex endeavour, and not even possible in some cases, because even creating \emph{all} possible linearizations of all methods in the original domain does not guarantee that solutions are preserved.

In this paper, we propose an algorithm for converting partially ordered problems into totally ordered ones and give criterion for when this conversion will retain at least one solution. We test our techniques on the partially-ordered track of the bench-mark set of the IPC 2020 and solve both the linearized and the original partially-ordered problems using state-of-the-art planning systems. We find that in the majority of problems across a variety of domains, the linearized problems remain solvable, and can always be solved faster than the without our proposed pre-processing technique. We can thus conclude our proposed pre-processing technique becomes (part of)
the state of the art for solving partially ordered planning problems.
\end{abstract}

\section{Introduction}

Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound. HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks. A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications. If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.

In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks. In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.

Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space. For some problems, such over-specification may remove all valid solutions. Thus many problems might be \emph{modelled} as POHTN problems. However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions. In particular, TOHTN planning as a class of problems has lower computational complexity than POHTN planning, as proven by \cite{ErolHTNExpressivity}, resulting in lower worst-case solving time. Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.

Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case. Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.

The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages. On the other hand, TOHTN planning is not expressive enough to model undecideable problems. Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.

% Also, we get another class of decidable partially ordered problems that's orthogonal to recursive ones. 
% Also, the domain model might be more intuitive: if a task is independent of some others it might be counter-intuitive to demand a certain position of it (if artificially made totally ordered). Plan recognition: independent goals can be described in parallel with POHTN planning but not with TOHTN, as per \cite{DanielPlanRecognition}.

%\subsubsection{Contributions}
%Gregor Behnke used a similar linearization process to produce the TO benchmark set used for the 2020 International Planning Competition (IPC 2020). That also attempted to linearize the methods by drawing the same links between preconditions and effects as in this paper, and picked a random linearization if that was not possible. However, no attempt was made to analyse if this lead to a easier to solve problem, or if it had any interesting theoretical implications. As Prof. Bercher thought this could be an interesting use for linearization, this paper offers this empirical evaluation and theoretical analysis.

In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems. We prove that when certain criteria are met, it guarantees that at least one solution will be preserved. 
Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion. Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.

\section{Hierarchical Planning Formalism}
Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning. There are many formalisations for HTN planning. The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}. HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning. TOHTN planning is a special case of POHTN planning.  % except with the initial task network replaced by a initial compound task.

A \textbf{Partially Ordered Hierarchical Planning}(POHTN) problem \textbf{P} = $(D, S_I, T_I)$
is defined over some domain $D$, 
has an initial state $S_I \in 2^F$, and 
has a initial compound task $T_I$. 
The closed world assumption also holds for HTN planning.

The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.

A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
T, which is a finite set of task identifiers (ids); 
$\singlePrec$, which is a partial order over T; and
$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.

% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
\begin{align}
tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
\end{align}
In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.

A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ... t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ... \alpha(t_n) \rangle$ in $S_I$ is executable.

In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition. For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired. Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning. Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.

\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$. TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$.
This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning. POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity). As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.

\section{Simple Linearization Procedure}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.

For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
\begin{align*}
& \forall t \in T_P : \PreS(t) := \Pre(t) \\
& \forall t \in T_P : \AddS(t) := \Add(t) \\
& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
								& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
								& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
								& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
\end{align*}

From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.

\begin{algorithm}\label{alg:Algorithm1}
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
	{

		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}

		$G \gets$ calculateTransitiveClosure($\singlePrec$) \\
		\label{alg:StartBuildGraph}
		\For{a $\in$ F}{  
			\For{$t \in T_m$}{
				\For{$t' \in T_m$}{
					if $a \in \AddS(t)$ and $a \in \PreS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$  \\ 
					if $a \in \AddS(t)$ and $a \in \DelS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \PreS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \AddS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$ \\  
				}
			} 
			\label{alg:EndBuildGraph}	
		}	 
		\label{alg:TopSort}
		$\singlePrec'\gets$ any linearization of $G$ \\
		$m' = (tasks(m), \singlePrec', \alpha(t))$ \\
		$M' = M' \cup  \{m'\}$ \\		
	}
	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
	\caption{Calculation of linearized methods}
\end{algorithm}

\subsection{Theoretical Properties of Linearization Result}
\begin{theorem}\label{thm:Runtime}
	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
\end{theorem}
\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
	Let $|T|$ = $|T_P| + |T_C|$.

	The Floyd-warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,

	To calculate $\PreS, \AddS, \DelS$ for each task $t$, we can perform breadth-first search on the task decomposition sub-tree (where tasks are nodes, and edges indicate possible decomposition by methods) rooted at $t$. The size of a sub-tree has an upper limit of $T_C + T_P$ nodes. For each primitive task in the sub-tree, we can iterate over each fact to update $\PreS, \AddS, \DelS$ for the root $t$. Thus calculating  $\PreS, \AddS, \DelS$ for a single compound task has an upper limit of $(3 * |F| * |T_p|) + |T_C|$. This inference occurs for each compound task, so inference for all compound tasks takes $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.

	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method. Leading to $(M * F * (t_m)^2)$, where $t_m$ is the average number of sub-tasks per method. So it's at most $\mathcal{O}(|M| * |F| * |T|^2)$, since $t_m$ has an upper bound of $T$, where $T=T_p + T_C$.

	Line~\ref{alg:TopSort} can be done via topological sort of the graph (which is known to be in $\mathcal{O}(V+E)$ in time and $\mathcal{O}(V)$ in space). In this case, the nodes of the graph are tasks, and the edges are orderings. So that's $M * (t_m+e_m)$, where $e_m$ is the number of \enquote{edges} in the new method, and has an upper bound of $e_m$ to find a topological sort for the sub-tasks of every method. That's approximately $\mathcal{O}(|M| * |T|)$, since both $t_m$ and $t_e$ are upper bounded by $T$, such that $T=T_p + T_C$.

	So in total the main algorithm takes: \newline
	$(|M| * |T|^3)$ +          % Floyd-Warshall
	$(|M| * |F| * |T|)$  +    % GetPreEff
	$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
	$(|M| * |T|)$        % topological sort
\end{proof}

\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

\begin{theorem}\label{thm:notCompleteness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then $sol(P')$ may be empty.
\end{theorem}
\begin{proof}
	This algorithm linearizes all the methods to be totally ordered. Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents that are already ordered with respect to each other. This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered. Consider the simple example problem:

	\begin{figure}
		\caption{Diagram showing an example problem and its decomposition.}		
		\begin{subfigure}{3.5cm}
			\begin{align*}
			F   = & \{a, b, c \}           \\
			N_p = & \{A, B, C\}      \\
			N_c = & \{AC, T_I\}            \\ 
			M   = & \{  (T_I, \{AC, B\}), \\
			&    (AC, \{A, C\})  \} \\
			S_I = & \{ a \} 	             \\ 
			\end{align*} 
		\end{subfigure}		
		\scalebox{0.7}{
			\begin{subfigure}{7cm}
				\begin{tikzpicture}[auto,node distance=1.5cm,
				thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
				square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
				\node[] (InitState) {}; %{ $\mathbf{S_I = \{a\}}$ };

				\node[main node] (Init) [right=3cm of InitState] {$T_I$};
				\node[main node] (AC) [right=2cm of Init, below of=Init] {$AC$};

				\node[main node] (A) [below left = 2em and 2em of AC] {$A$};
				\node[main node] (B) [below left = 2em and 2em of Init] {$B$}; 
				\node[main node] (C) [below right = 2em and 2em of AC] {$C$};

		%		\action{A}{PrimitiveA,
		%			width  = 2.5em, 
		%			height = 2.5em, 
		%			pre length = 2em,
		%			eff length = 2em,
		%			body = {below left = 2em and 2em of AC} 
		%		};

		%		\action{B}{PrimitiveB,
		%			width  = 2.5em, 
		%			height = 2.5em, 
		%			pre length = 2em,
		%			eff length = 2em,
		%			body = {below left = 2em and 2em of Init} 
		%		};

		%		\action{C}{PrimitiveC,
		%			width  = 2.5em, 
		%			height = 2.5em, 
		%			pre length = 2em,
		%			eff length = 2em,
		%			body = {below right = 2em and 2em of AC} 
		%		};

				\path[every node/.style={font=\sffamily\small}]
				(Init) edge [->] node [left] {} (B)
				(Init) edge [->] node [left] {} (AC)
				(AC) edge [->] node [left] {} (A)
				(AC) edge [->] node [left] {} (C);
				\end{tikzpicture}
			\end{subfigure}	
		}
	\end{figure}

	\begin{figure}
		\caption{The only possible solution $A, B, C$ for E.g.\ 1, requires the children of $AC$ and $B$ to be interleaved, meaning we cannot impose an order between them}
		\scalebox{0.9}{
			\begin{tikzpicture}[auto,node distance=3cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\node[] (Invis) [] {$S_I$};
			\node[square node] (A) [right of=Invis] {$A$};
			\node[square node] (B) [right of=A] {$B$};
			\node[square node] (C) [right of=B] {$C$};

			\path[every node/.style={font=\sffamily\small}]
			(Invis) edge [->] node [left, label=a] {} (A)
			(A) edge [->] node [left, label=b] {} (B)
			(B) edge [->] node [left, label=c] {} (C);
			\end{tikzpicture}		
		}
	\end{figure}

	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$. This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution. 
	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.

	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete. Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
\end{proof}

We will now see that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} does not have to break cycles.
\begin{theorem}\label{thm:SpecialCase}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if Algorithm~\ref{alg:Algorithm1} did not have to
	cycle-break, then if $sol(P)$ is non-empty then $sol(P')$, will be non-empty as well.
\end{theorem}
\begin{proof}
	Assume that there exists a solution in the PO domain. By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain. Assume this sequence is $(a_0, a_1, ..., a_n)$. We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state. The action $a_k$ could only be non-executable, if one or more of its preconditions was not met. Assume one of these unmet preconditions is for existence of the state variable $A$.
	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution. So there must exist an action $a_i$, $0 < i < n$, that will add A. Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree. So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.

	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc. We are assuming that all methods linearized without conflict, so $(t_i, t_k)$ should not be required. This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm. In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.

	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution. Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
\end{proof}

There are several possible levels of \enquote{completeness} for a problem compilation.
%\begin{enumerate}
\begin{itemize}
	\item all solutions remain 
	\item at least one solution remains 
	\item all optimal solutions remain
	\item at least one optimal solution remains 	
\end{itemize}
%\end{enumerate}
Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if no cycle-breaking is needed. If cycle-breaking is needed, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions. Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.

\begin{theorem}\label{thm:newClass}
	Problems $P$ that satisfy the criterion for linearization without cycle-breaking form a new class of decidable problems.
\end{theorem}
\begin{proof}
	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.  
\end{proof}

\section{Complex Linearization Procedure}

The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.

\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.

State-independent positive and negative effects (cf. their
Def. 4) of a compound task c are facts that are added or
deleted, resp., by the successful execution of a refinement of
c, independent of the state in which the task is executed, i.e.
$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$

Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
after every refinement of c but after at least one:
$$ \RelPossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
$$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.

The set of executability-enabling states of c is
$E(c) = \{s \in 2F  \mid  \exists \text{t.o. refinement of c applicable in s} \}$.
The set of resulting states of c w.r.t. some state $s \in 2^F$ is
$R_s(c) = \{s' \in 2^F | \exists t.o. refinement appl. in s res. in s' \}$.

So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined
just like the original ones but based on the precondition-
relaxed variant of D.

We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}.

\section{Empirical Evaluation}

To prove that our technique improves the solving time, we compare the runtime of a state-of-the-art planning system on the original problem vs. the transformed problem, for a number of different PO domains. All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020. The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons. Each problem has the standard IPC time limit of 30 minutes. Any grounding and pre-processing time needed is included as part of the 'solving' time. Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.

\subsection{Hardware and Planning Systems}
The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM. Recent work by \cite{HTN2SAS} shows that the partial-order panda$_\pi$, actually achieved similar coverage and slightly lower IPC score than the best specialised TOHTN planner evaluated. %Lilotane by \cite{Lilotane} is an TOHTN solver and the IPC 2020 runner-up. The winner, HyperTensioN by \cite{hypertension} could not be tested due to lack of support for reading in optimisation metrics.

We therefore test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} on the configuration of Greedy best first search with visited lists, and using RC to turn the problem into a classical planning problem. We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}.

We compare the performance of these 4 planner settings on the original problem and the pre-processed problem, HTN2SAS, and the latest version of HyperTensioN and Lilotane. For panda$_{\pi}$, the same setting is used for re-runs. For TOHTN planners, re-runs use panda$_{\pi}$ on the best setting (Add heuristic). The comparison is done for grounded linearization variant and the lifted linearization variant 1.

\subsection{Performance of Simple Linearization}

\begin{table}[h]
	\scalebox{0.45} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
				& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
		\midrule 
		Barman-BDI  \\ 
		Monroe Fully Observ. \\ 
		Monroe Part. Observ. \\ 
		PCP\\ 
		Rover  \\ 
		Satellite  \\ 
		Transport \\ 
		UM-Translog \\ 
		Woodworking \\ 
		\midrule 
		Monroe  \\ 
		SmartPhone \\ 
		Zenotravel \\ 
		\midrule 
		Coverage \\ 
		Norm. coverage  \\ 
		\bottomrule
			\end{tabular} 	
			}
\end{table}

\begin{table}[h]
	\scalebox{0.45} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
			\end{tabular} 	
	}
\end{table}

\subsection{Performance of Complex Linearization}

\begin{table}[h]
	\scalebox{0.45} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }    \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			Coverage \\ 
			Norm. coverage  \\ 
			\bottomrule
			\end{tabular} 	
	}
\end{table}

\begin{table}[h]
	\scalebox{0.45} {
		\begin{tabular}{lccccccccccccccccccccccccl} 
			\toprule 
			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }  \\ 
			\midrule 
			Barman-BDI  \\ 
			Monroe Fully Observ. \\ 
			Monroe Part. Observ. \\ 
			PCP\\ 
			Rover  \\ 
			Satellite  \\ 
			Transport \\ 
			UM-Translog \\ 
			Woodworking \\ 
			\midrule 
			Monroe  \\ 
			SmartPhone \\ 
			Zenotravel \\ 
			\midrule 
			IPC \\
			\bottomrule
		\end{tabular} 	
	}
\end{table}

As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
As we can see, the best planner is ? planner.

\section{Related Work}
% FROM (https://ojs.aaai.org/index.php/ICAPS/article/view/15944/15755) A Closer Look at Causal Links: Complexity Resultsfor Delete-Relaxation in Partial Order Causal Link (POCL) Planning
Our linearization procedure is a pre-processing technique for the search space, is a compilation of an HTN planning problem class to a different class of problems, and can exploit specialised TO planners.

The panda$_\pi$ grounder by \cite{Behnke2020Grounding} also prunes unreachable tasks, methods, etc.\.  Because the panda$_{\pi}$ planner is a grounded planner, we can ground then linearize, or vice-versa to \enquote{stack} the reduction in search space.

The main optimization of HyperTensioN by \cite{hypertension} is via the Pullup extension - which determines additional preconditions of methods and compound tasks by analysing the preconditions of possible child actions. Unlike ours, no approximation of effects are considered.

The HTN2STRIPS planner by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} compiles HTN problems, both totally and partially ordered, to classical problems. The TOAD planner by \cite{HollerTOAD} compiles TOHTN problems into classical planning problems in order to allow the use of classical planning systems. % TOAD over-approximates the set of solutions to the HTN problem. In the empirical evaluation the paper performed, TOAD achieved higher coverage than the base version of HTN2STRIPS, and all systems submitted to the totally ordered track of the 2020 IPC.

There exists totSAT planner by \cite{TOtoSAT} that compiles a totally ordered problem to SAT problem. There also exists 2 planners by \cite{POtoSAT, OptimalPOtoSAT} that compiles a partially ordered problem to a SAT problem. One searches for optimal plans, the other focuses on finding any solution as quickly as possible. Lilotane by \cite{Lilotane} directly encodes a lifted problem representation into a SAT problem.

Another planner by \cite{Behnke_Speck_2021} converts TOHTN into Binary Decision Diagrams (BDDs), then use symbolic search on it.

The BDD planner by \cite{Behnke_Speck_2021}, totSAT planner by \cite{TOtoSAT}, TOAD by \cite{HollerTOAD}, HyperTensioN by \cite{hypertension}, and Lilotane by \cite{Lilotane}, as discussed before, are all specialised TO planners. So are the TFD (Totally Ordered Fast Downward) and PFD (Partially Ordered Fast Downward) hierarchical planners by \cite{PDDL4J}.  Note however that HTN2SAS achieved similar coverage than greedy search with panda$_\pi$, a partial-order planner.

\section{Summary}

The contributions of this paper are as follows:

At least for the POHTN problems in the IPC domain, most of them are not undecideable.
In another way, it is as if the POHTN domains are compressed TO domains - this linearization
separates one back out.

For another, this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here. Furthermore, there is demonstrably much more room for improvement. Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.

We have a method that can increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques. Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems. Then $k+m$ (lifted or grounded) TOHTN problems exist now. And from empirical evaluation, $k$ may be close to $n$.

We can identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all other criteria.

\section{Future Work}

\subsubsection{MAX-SAT Instead of Cycle-Break} 
The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula. MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.

Cycle-breaking considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$. Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, similar to the one described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain. Assuming no negative preconditons, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment). The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.

\subsubsection{Adding a Plan as Additional Input to the Domain}
Adding a plan as additional input to the PO domain having the
semantics that this plan shall be in the solution set of the TO output
model. This reduces the computational complexity of the decision problem from undecidable to something decidable. The specific complexity class of this will have to be proven in further work.  % I assume the resulting problem is PSPACE-complete, but

% References and End of Paper
% These lines must be placed at the end of your paper
\bibliography{bib}
\end{document}

\begin{document}\\
\maketitle\\
...\\
\bibliography{bib}\\
\end{document}\\

\end{document}

### 2022-11-08 paper/paper-mainfile.tex
remove references to cycle-breaking

@@
 % These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-\usepackage{algorithm}
+% \usepackage{algorithm}
 % \usepackage{algorithmic}
-\usepackage[noend]{algpseudocode}
+% \usepackage[noend]{algpseudocode}
 
@@
 	showstringspaces=false,tabsize=2,breaklines=true}
-\floatstyle{ruled}
-\newfloat{listing}{tb}{lst}{}
-\floatname{listing}{Listing}
+%\floatstyle{ruled}
+%\newfloat{listing}{tb}{lst}{}
+%\floatname{listing}{Listing}
 
@@
 \usepackage{xcolor}
-%
+\usepackage{booktabs} 
+\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
+\usepackage{csquotes}
+\usepackage{subcaption}
+\usepackage{amssymb} 
+\usepackage{tikz}
+
 \nocopyright
@@
 \pdfinfo{
-/Title (Title)
+/Title (Transforming Partially Ordered HTN Problems to Totally Ordered)
 /Author (Anonymous)
@@
 % \iffalse
-\title{Title}
+
+\newtheorem{theorem}{Theorem}
+
+\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
+\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
+
+\newcommand{\Add} {\ensuremath{\mathit{add}}}
+\newcommand{\Del} {\ensuremath{\mathit{del}}}
+\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
+\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
+\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
+\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
+\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
+
+\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
+\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
+\newcommand{\PossEffPlus} {\ensuremath{\mathit{poss-eff^{+}_{*}}}}
+\newcommand{\PossEffMinus} {\ensuremath{\mathit{poss-eff^{-}_{*}}}}
+
+\newcommand{\RelEffPlus} {\ensuremath{\mathit{eff^{\emptyset +}_{*}}}}
+\newcommand{\RelEffMinus} {\ensuremath{\mathit{eff^{\emptyset -}_{*}}}}
+\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
+\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
+
 \author {
@@
 \iffalse
-\title{Title}
+\title{Transforming Partially Ordered HTN Problems to Totally Ordered}
 \author {
@@
 
+\title{Transforming Partially Ordered HTN Problems to Totally Ordered}
+
 % REMOVE THIS: bibentry
 % This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
-\usepackage{bibentry}
+% \usepackage{bibentry}
 % END REMOVE bibentry
@@
 \begin{abstract}
-   abstract  
+Solving partially ordered hierarchical planning problems is more computationally expensive compared to solving totally ordered ones.
+Therefore, automatically transforming partially ordered problem domains into totally ordered ones, such that the totally ordered problem still retains at least one solution, would be a desired capability as it would reduce complexity and thus make it easier for planning systems to solve the problem.
+It also allows the planner to use algorithms and heuristics specialised for the totally ordered case to solve the transformed problem.
+
+This is a complex endeavour, and not even possible in some cases, because even creating \emph{all} possible linearizations of all methods in the original domain does not guarantee that solutions are preserved.
+
+In this paper, we propose an algorithm for converting partially ordered problems into totally ordered ones and give criterion for when this conversion will retain at least one solution.
+We test our techniques on the partially-ordered track of the bench-mark set of the IPC 2020 and solve both the linearized and the original partially-ordered problems using state-of-the-art planning systems.
+We find that in the majority of problems across a variety of domains, the linearized problems remain solvable, and can always be solved faster than the without our proposed pre-processing technique.
+We can thus conclude our proposed pre-processing technique becomes (part of) the state of the art for solving partially ordered planning problems.
 \end{abstract}
 
+\section{Introduction}
+Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
+tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
+HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
+A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
+If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
+
+In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
+In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
+
+Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
+For some problems, such over-specification may remove all valid solutions.
+Thus many problems might be \emph{modelled} as POHTN problems.
+However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
+In particular, TOHTN planning as a class of problems has lower computational complexity than POHTN planning, as proven by \cite{ErolHTNExpressivity}, resulting in lower worst-case solving time.
+Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
+
+Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
+Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
+
+The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem.
+For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
+On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
+Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
+
+In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
+We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
+Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
+Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
+
+\section{Hierarchical Planning Formalism}
+Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning.
+There are many formalisations for HTN planning.
+The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}.
+HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning.
+TOHTN planning is a special case of POHTN planning.
+% except with the initial task network replaced by a initial compound task.
+
+A \textbf{Partially Ordered Hierarchical Planning}(POHTN) problem \textbf{P} = $(D, S_I, T_I)$
+is defined over some domain $D$, 
+has an initial state $S_I \in 2^F$, and 
+has a initial compound task $T_I$. 
+The closed world assumption also holds for HTN planning.
+
+The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
+$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
+$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
+$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.
+
+A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
+T, which is a finite set of task identifiers (ids); 
+$\singlePrec$, which is a partial order over T; and
+$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.
+
+% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
+A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
+a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
+\begin{align}
+tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
+\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
+&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
+\end{align}
+In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
+on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.
+
+A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
+tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ...
+t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ...
+\alpha(t_n) \rangle$ in $S_I$ is executable.
+
+In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition.
+For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired.
+Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning.
+Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.
+
+\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
+For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$.
+TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$.
+This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning.
+POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).
+As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
+In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.
+
+\section{Simple Linearization Procedure}
+The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.
+
+For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
+$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
+For a grounded model, $f' = f$.
+The inferred preconditions and effects for a task are then defined as below:
+\begin{align*}
+& \forall t \in T_P : \PreS(t) := \Pre(t) \\
+& \forall t \in T_P : \AddS(t) := \Add(t) \\
+& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
+& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
+& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
+& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
+& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
+& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
+& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
+\end{align*}
+
+From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.
+
+\begin{algorithm}\label{alg:Algorithm1}
+	\KwData{$(F, T_P, T_C, \delta, M)$}
+	\KwResult{$(F, T_P, T_C, \delta, M)$}
+
+	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
+	{
+
+		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}
+
+		$G \gets$ calculateTransitiveClosure($\singlePrec$) \\
+		\label{alg:StartBuildGraph}
+		\For{a $\in$ F}{  
+			\For{$t \in T_m$}{
+				\For{$t' \in T_m$}{
+					if $a \in \AddS(t)$ and $a \in \PreS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$  \\ 
+					if $a \in \AddS(t)$ and $a \in \DelS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
+					if $a \in \DelS(t)$ and $a \in \PreS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
+					if $a \in \DelS(t)$ and $a \in \AddS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$ \\  
+				}
+			} 
+			\label{alg:EndBuildGraph}	
+		}	 
+		\label{alg:TopSort}
+		$\singlePrec'\gets$ any linearization of $G$ \\
+		$m' = (tasks(m), \singlePrec', \alpha(t))$ \\
+		$M' = M' \cup  \{m'\}$ \\		
+	}
+	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
+	\caption{Calculation of linearized methods}
+\end{algorithm}
+
+\subsection{Theoretical Properties of Linearization Result}
+\begin{theorem}\label{thm:Runtime}
+	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
+\end{theorem}
+\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
+	Let $|T|$ = $|T_P| + |T_C|$.
+
+	The Floyd-warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
+
+	To calculate $\PreS, \AddS, \DelS$ for each task $t$, we can perform breadth-first search on the task decomposition sub-tree (where tasks are nodes, and edges indicate possible decomposition by methods) rooted at $t$.
+The size of a sub-tree has an upper limit of $T_C + T_P$ nodes.
+For each primitive task in the sub-tree, we can iterate over each fact to update $\PreS, \AddS, \DelS$ for the root $t$.
+Thus calculating  $\PreS, \AddS, \DelS$ for a single compound task has an upper limit of $(3 * |F| * |T_p|) + |T_C|$.
+This inference occurs for each compound task, so inference for all compound tasks takes $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
+
+	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
+Leading to $(M * F * (t_m)^2)$, where $t_m$ is the average number of sub-tasks per method.
+So it's at most $\mathcal{O}(|M| * |F| * |T|^2)$, since $t_m$ has an upper bound of $T$, where $T=T_p + T_C$.
+
+	Line~\ref{alg:TopSort} can be done via topological sort of the graph (which is known to be in $\mathcal{O}(V+E)$ in time and $\mathcal{O}(V)$ in space).
+In this case, the nodes of the graph are tasks, and the edges are orderings.
+So that's $M * (t_m+e_m)$, where $e_m$ is the number of \enquote{edges} in the new method, and has an upper bound of $e_m$ to find a topological sort for the sub-tasks of every method.
+That's approximately $\mathcal{O}(|M| * |T|)$, since both $t_m$ and $t_e$ are upper bounded by $T$, such that $T=T_p + T_C$.
+
+	So in total the main algorithm takes: \newline
+	$(|M| * |T|^3)$ +          % Floyd-Warshall
+	$(|M| * |F| * |T|)$  +    % GetPreEff
+	$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
+	$(|M| * |T|)$        % topological sort
+\end{proof}
+
+\begin{theorem}\label{thm:Soundness}
+	Given a POHTN planning problem $P$ and TOHTN problem
+	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
+	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
+\end{theorem}
+\begin{proof}
+	The new desired orderings for a method include all of the orderings already required by the method originally.
+The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph.
+This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one.
+Any solution to the linearized problem is then obviously a solution to the original problem.
+\end{proof}
+
+\begin{theorem}\label{thm:notCompleteness}
+	Given a POHTN planning problem $P$ and TOHTN problem
+	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
+	then $sol(P')$ may be empty.
+\end{theorem}
+\begin{proof}
+	This algorithm linearizes all the methods to be totally ordered.
+Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents that are already ordered with respect to each other.
+This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
+Consider the simple example problem:
+
+	\begin{figure}
+		\caption{Diagram showing an example problem and its decomposition.}		
+		\begin{subfigure}{3.5cm}
+			\begin{align*}
+			F   = & \{a, b, c \}           \\
+			N_p = & \{A, B, C\}      \\
+			N_c = & \{AC, T_I\}            \\ 
+			M   = & \{  (T_I, \{AC, B\}), \\
+			&    (AC, \{A, C\})  \} \\
+			S_I = & \{ a \} 	             \\ 
+			\end{align*} 
+		\end{subfigure}		
+		\scalebox{0.7}{
+			\begin{subfigure}{7cm}
+				\begin{tikzpicture}[auto,node distance=1.5cm,
+				thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
+				square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+				\node[] (InitState) {}; %{ $\mathbf{S_I = \{a\}}$ };
+
+				\node[main node] (Init) [right=3cm of InitState] {$T_I$};
+				\node[main node] (AC) [right=2cm of Init, below of=Init] {$AC$};
+
+				\node[main node] (A) [below left = 2em and 2em of AC] {$A$};
+				\node[main node] (B) [below left = 2em and 2em of Init] {$B$}; 
+				\node[main node] (C) [below right = 2em and 2em of AC] {$C$};
+
+				%		\action{A}{PrimitiveA,
+				%			width  = 2.5em, 
+				%			height = 2.5em, 
+				%			pre length = 2em,
+				%			eff length = 2em,
+				%			body = {below left = 2em and 2em of AC} 
+				%		};
+
+				%		\action{B}{PrimitiveB,
+				%			width  = 2.5em, 
+				%			height = 2.5em, 
+				%			pre length = 2em,
+				%			eff length = 2em,
+				%			body = {below left = 2em and 2em of Init} 
+				%		};
+
+				%		\action{C}{PrimitiveC,
+				%			width  = 2.5em, 
+				%			height = 2.5em, 
+				%			pre length = 2em,
+				%			eff length = 2em,
+				%			body = {below right = 2em and 2em of AC} 
+				%		};
+
+				\path[every node/.style={font=\sffamily\small}]
+				(Init) edge [->] node [left] {} (B)
+				(Init) edge [->] node [left] {} (AC)
+				(AC) edge [->] node [left] {} (A)
+				(AC) edge [->] node [left] {} (C);
+				\end{tikzpicture}
+			\end{subfigure}	
+		}
+	\end{figure}
+
+	\begin{figure}
+		\caption{The only possible solution $A, B, C$ for E.g.\ 1, requires the children of $AC$ and $B$ to be interleaved, meaning we cannot impose an order between them}
+		\scalebox{0.9}{
+			\begin{tikzpicture}[auto,node distance=3cm,
+			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
+			square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+
+			\node[] (Invis) [] {$S_I$};
+			\node[square node] (A) [right of=Invis] {$A$};
+			\node[square node] (B) [right of=A] {$B$};
+			\node[square node] (C) [right of=B] {$C$};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(Invis) edge [->] node [left, label=a] {} (A)
+			(A) edge [->] node [left, label=b] {} (B)
+			(B) edge [->] node [left, label=c] {} (C);
+			\end{tikzpicture}		
+		}
+	\end{figure}
+
+	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
+	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$.
+This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution.
+	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
+
+	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
+Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
+	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
+\end{proof}
+
+\begin{description}
+	\item[Linearization Criteria] If the linearization process does not find a desired ordering contradicting the existing ones for some method, that method is said to meet the linearization criteria.
+	If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well. 
+\end{description}
+We will now see that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} this criterion is met.
+
+\begin{theorem}\label{thm:SpecialCase}
+	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if $P$ meets the linearization criteria and $sol(P)$ is non-empty, then $sol(P')$ will be non-empty as well.
+\end{theorem}
+\begin{proof}
+	Assume that there exists a solution in the PO domain.
+By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain.
+Assume this sequence is $(a_0, a_1, ..., a_n)$.
+We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
+	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state.
+The action $a_k$ could only be non-executable, if one or more of its preconditions was not met.
+Assume one of these unmet preconditions is for existence of the state variable $A$.
+	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution.
+So there must exist an action $a_i$, $0 < i < n$, that will add A.
+Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree.
+So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.
+
+	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
+We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required.
+This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
+In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.
+
+	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution.
+Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
+\end{proof}
+
+There are several possible levels of \enquote{completeness} for a problem compilation.
+%\begin{enumerate}
+\begin{itemize}
+	\item all solutions remain 
+	\item at least one solution remains 
+	\item all optimal solutions remain
+	\item at least one optimal solution remains 	
+\end{itemize}
+%\end{enumerate}
+Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if linearization criteria is met.
+Otherwise, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions.
+Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.
+
+\begin{theorem}\label{thm:newClass}
+	Problems $P$ that satisfy the linearization criteria form a new class of decidable problems.
+\end{theorem}
+\begin{proof}
+	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.
+\end{proof}
+
+\section{Complex Linearization Procedure}
+
+The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.
+
+\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
+So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
+if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
+
+State-independent positive and negative effects (cf. their
+Def. 4) of a compound task c are facts that are added or
+deleted, resp., by the successful execution of a refinement of
+c, independent of the state in which the task is executed, i.e.
+$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
+$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
+
+Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
+after every refinement of c but after at least one:
+$$ \RelPossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
+$$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
+if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
+
+The set of executability-enabling states of c is
+$E(c) = \{s \in 2F  \mid  \exists \text{t.o. refinement of c applicable in s} \}$.
+The set of resulting states of c w.r.t. some state $s \in 2^F$ is
+$R_s(c) = \{s' \in 2^F | \exists t.o. refinement appl. in s res. in s' \}$.
+
+So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
+with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
+Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined
+just like the original ones but based on the precondition-
+relaxed variant of D.
+
+We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}.
+
+\section{Empirical Evaluation}
+
+To prove that our technique improves the solving time, we compare the runtime of a state-of-the-art planning system on the original problem vs.
+the transformed problem, for a number of different PO domains.
+All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
+The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
+Each problem has the standard IPC time limit of 30 minutes.
+Any grounding and pre-processing time needed is included as part of the 'solving' time.
+Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
+
+\subsection{Hardware and Planning Systems}
+The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
+Recent work by \cite{HTN2SAS} shows that the partial-order panda$_\pi$, actually achieved similar coverage and slightly lower IPC score than the best specialised TOHTN planner evaluated.
+%Lilotane by \cite{Lilotane} is an TOHTN solver and the IPC 2020 runner-up.
+The winner, HyperTensioN by \cite{hypertension} could not be tested due to lack of support for reading in optimisation metrics.
+
+We therefore test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} on the configuration of Greedy best first search with visited lists, and using RC to turn the problem into a classical planning problem.
+We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}.
+
+We compare the performance of these 4 planner settings on the original problem and the pre-processed problem, HTN2SAS, and the latest version of HyperTensioN and Lilotane.
+For panda$_{\pi}$, the same setting is used for re-runs.
+For TOHTN planners, re-runs use panda$_{\pi}$ on the best setting (Add heuristic).
+The comparison is done for grounded linearization variant and the lifted linearization variant 1.
+
+\subsection{Performance of Simple Linearization}
+
+\begin{table}[h]
+	\scalebox{0.45} {
+		\begin{tabular}{lccccccccccccccccccccccccl} 
+			\toprule 
+			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
+			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
+			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
+			\midrule 
+			Barman-BDI  \\ 
+			Monroe Fully Observ. \\ 
+			Monroe Part. Observ. \\ 
+			PCP\\ 
+			Rover  \\ 
+			Satellite  \\ 
+			Transport \\ 
+			UM-Translog \\ 
+			Woodworking \\ 
+			\midrule 
+			Monroe  \\ 
+			SmartPhone \\ 
+			Zenotravel \\ 
+			\midrule 
+			Coverage \\ 
+			Norm. coverage  \\ 
+			\bottomrule
+		\end{tabular} 	
+	}
+\end{table}
+
+\begin{table}[h]
+	\scalebox{0.45} {
+		\begin{tabular}{lccccccccccccccccccccccccl} 
+			\toprule 
+			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
+			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
+			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
+			\midrule 
+			Barman-BDI  \\ 
+			Monroe Fully Observ. \\ 
+			Monroe Part. Observ. \\ 
+			PCP\\ 
+			Rover  \\ 
+			Satellite  \\ 
+			Transport \\ 
+			UM-Translog \\ 
+			Woodworking \\ 
+			\midrule 
+			Monroe  \\ 
+			SmartPhone \\ 
+			Zenotravel \\ 
+			\midrule 
+			IPC \\
+			\bottomrule
+		\end{tabular} 	
+	}
+\end{table}
+
+\subsection{Performance of Complex Linearization}
+
+\begin{table}[h]
+	\scalebox{0.45} {
+		\begin{tabular}{lccccccccccccccccccccccccl} 
+			\toprule 
+			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
+			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
+			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }    \\ 
+			\midrule 
+			Barman-BDI  \\ 
+			Monroe Fully Observ. \\ 
+			Monroe Part. Observ. \\ 
+			PCP\\ 
+			Rover  \\ 
+			Satellite  \\ 
+			Transport \\ 
+			UM-Translog \\ 
+			Woodworking \\ 
+			\midrule 
+			Monroe  \\ 
+			SmartPhone \\ 
+			Zenotravel \\ 
+			\midrule 
+			Coverage \\ 
+			Norm. coverage  \\ 
+			\bottomrule
+		\end{tabular} 	
+	}
+\end{table}
+
+\begin{table}[h]
+	\scalebox{0.45} {
+		\begin{tabular}{lccccccccccccccccccccccccl} 
+			\toprule 
+			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
+			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
+			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }  \\ 
+			\midrule 
+			Barman-BDI  \\ 
+			Monroe Fully Observ. \\ 
+			Monroe Part. Observ. \\ 
+			PCP\\ 
+			Rover  \\ 
+			Satellite  \\ 
+			Transport \\ 
+			UM-Translog \\ 
+			Woodworking \\ 
+			\midrule 
+			Monroe  \\ 
+			SmartPhone \\ 
+			Zenotravel \\ 
+			\midrule 
+			IPC \\
+			\bottomrule
+		\end{tabular} 	
+	}
+\end{table}
+
+As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
+As we can see, the best planner is ? planner.
+
+\section{Related Work}
+% FROM (https://ojs.aaai.org/index.php/ICAPS/article/view/15944/15755) A Closer Look at Causal Links: Complexity Resultsfor Delete-Relaxation in Partial Order Causal Link (POCL) Planning
+Our linearization procedure is a pre-processing technique for the search space, is a compilation of an HTN planning problem class to a different class of problems, and can exploit specialised TO planners.
+
+The panda$_\pi$ grounder by \cite{Behnke2020Grounding} also prunes unreachable tasks, methods, etc.\.
+Because the panda$_{\pi}$ planner is a grounded planner, we can ground then linearize, or vice-versa to \enquote{stack} the reduction in search space.
+
+The main optimization of HyperTensioN by \cite{hypertension} is via the Pullup extension - which determines additional preconditions of methods and compound tasks by analysing the preconditions of possible child actions.
+Unlike ours, no approximation of effects are considered.
+
+The HTN2STRIPS planner by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} compiles HTN problems, both totally and partially ordered, to classical problems.
+The TOAD planner by \cite{HollerTOAD} compiles TOHTN problems into classical planning problems in order to allow the use of classical planning systems.
+% TOAD over-approximates the set of solutions to the HTN problem.
+In the empirical evaluation the paper performed, TOAD achieved higher coverage than the base version of HTN2STRIPS, and all systems submitted to the totally ordered track of the 2020 IPC.
+
+There exists totSAT planner by \cite{TOtoSAT} that compiles a totally ordered problem to SAT problem.
+There also exists 2 planners by \cite{POtoSAT, OptimalPOtoSAT} that compiles a partially ordered problem to a SAT problem.
+One searches for optimal plans, the other focuses on finding any solution as quickly as possible.
+Lilotane by \cite{Lilotane} directly encodes a lifted problem representation into a SAT problem.
+
+Another planner by \cite{Behnke_Speck_2021} converts TOHTN into Binary Decision Diagrams (BDDs), then use symbolic search on it.
+
+The BDD planner by \cite{Behnke_Speck_2021}, totSAT planner by \cite{TOtoSAT}, TOAD by \cite{HollerTOAD}, HyperTensioN by \cite{hypertension}, and Lilotane by \cite{Lilotane}, as discussed before, are all specialised TO planners.
+So are the TFD (Totally Ordered Fast Downward) and PFD (Partially Ordered Fast Downward) hierarchical planners by \cite{PDDL4J}.
+Note however that HTN2SAS achieved similar coverage than greedy search with panda$_\pi$, a partial-order planner.
+
+\section{Summary}
+
+The contributions of this paper are as follows:
+
+At least for the POHTN problems in the IPC domain, most of them are not undecideable.
+In another way, it is as if the POHTN domains are compressed TO domains - this linearization
+separates one back out.
+
+For another, this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
+Furthermore, there is demonstrably much more room for improvement.
+Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
+
+We have a method that can increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
+Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
+Then $k+m$ (lifted or grounded) TOHTN problems exist now.
+And from empirical evaluation, $k$ may be close to $n$.
+
+We can identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all other criteria.
+
+\section{Future Work}
+
+\subsubsection{Encode Linearization Problem as a MAX-SAT Problem} 
+The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
+MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.
+
+The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
+Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, similar to the one described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
+Assuming no negative preconditons, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
+The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
+
+\subsubsection{Adding a Plan as Additional Input to the Domain}
+Adding a plan as additional input to the PO domain having the
+semantics that this plan shall be in the solution set of the TO output
+model.
+This reduces the computational complexity of the decision problem from undecidable to something decidable.
+The specific complexity class of this will have to be proven in further work.
+% I assume the resulting problem is PSPACE-complete, but this needs to be proven
+
 % Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
-\bibliography{aaai23}
+\bibliography{bib}
 % \nobibliography{aaai22}

### 2022-11-08 paper/paper-mainfile.tex
fix Alg labelling, Complex Linearization called Complex Inference now

@@
 
+\subsection{Simple Inference}
 For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
@@
 
+\subsection{Complex Inference}
+The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.
+
+\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
+So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
+if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
+
+State-independent positive and negative effects (cf. their
+Def. 4) of a compound task c are facts that are added or
+deleted, resp., by the successful execution of a refinement of
+c, independent of the state in which the task is executed, i.e.
+$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
+$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
+
+Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
+after every refinement of c but after at least one:
+$$ \RelPossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
+$$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
+if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
+
+The set of executability-enabling states of c is
+$E(c) = \{s \in 2F  \mid  \exists \text{t.o. refinement of c applicable in s} \}$.
+The set of resulting states of c w.r.t. some state $s \in 2^F$ is
+$R_s(c) = \{s' \in 2^F | \exists t.o. refinement appl. in s res. in s' \}$.
+
+So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
+with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
+Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-
+relaxed variant of D.
+
+There exists a polynomial-time algorithm for inferring the precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
+
+We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}.
+Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
+or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
+
+\subsection{Linearization Using Inferred Preconditions and Effects}
+
 From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.
 
-\begin{algorithm}\label{alg:Algorithm1}
+\begin{algorithm}
+	\caption{Linearization using inferred set of preconditions and effects}
+	\label{alg:Algorithm1}	
 	\KwData{$(F, T_P, T_C, \delta, M)$}
@@
 
-\subsection{Theoretical Properties of Linearization Result}
+\section{Theoretical Properties of Linearization Result}
+
+We now discuss the implications of the above-described linearization procedure.
+
+\subsection{Theoretical Properties If Using Simple Inference}
 \begin{theorem}\label{thm:Runtime}
@@
 
-\section{Complex Linearization Procedure}
-
-The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.
-
-\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
-
-State-independent positive and negative effects (cf. their
-Def. 4) of a compound task c are facts that are added or
-deleted, resp., by the successful execution of a refinement of
-c, independent of the state in which the task is executed, i.e.
-$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-after every refinement of c but after at least one:
-$$ \RelPossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-$$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
-
-The set of executability-enabling states of c is
-$E(c) = \{s \in 2F  \mid  \exists \text{t.o. refinement of c applicable in s} \}$.
-The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-$R_s(c) = \{s' \in 2^F | \exists t.o. refinement appl. in s res. in s' \}$.
-
-So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined
-just like the original ones but based on the precondition-
-relaxed variant of D.
-
-We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}.
+\subsection{Theoretical Properties If Using Complex Inference}
+Unfortunately, no criteria for determining if a solution is guaranteed to exist when using the second inference method, since there may always be unknown preconditions and effects in the precondition-relaxed effects.
 
@@
 \begin{table}[h]
-	\scalebox{0.45} {
+	\scalebox{0.4} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
@@
 
+\newpage
 As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-As we can see, the best planner is ? planner.
+The planner that has achieved the highest overall coverage and IPC score is ? planner.
 

### 2022-11-08 paper/paper-mainfile.tex
shifted table

@@
 \section{Empirical Evaluation}
-
-To prove that our technique improves the solving time, we compare the runtime of a state-of-the-art planning system on the original problem vs.
-the transformed problem, for a number of different PO domains.
+We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems.
 All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
@@
 The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the partial-order panda$_\pi$, actually achieved similar coverage and slightly lower IPC score than the best specialised TOHTN planner evaluated.
+Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than all TO planners tested.
 %Lilotane by \cite{Lilotane} is an TOHTN solver and the IPC 2020 runner-up.
@@
 
-We therefore test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} on the configuration of Greedy best first search with visited lists, and using RC to turn the problem into a classical planning problem.
+We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} configured to use to turn the problem into a classical planning problem (in RC model), and Greedy best first search with visited lists.
 We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}.
-
-We compare the performance of these 4 planner settings on the original problem and the pre-processed problem, HTN2SAS, and the latest version of HyperTensioN and Lilotane.
-For panda$_{\pi}$, the same setting is used for re-runs.
-For TOHTN planners, re-runs use panda$_{\pi}$ on the best setting (Add heuristic).
-The comparison is done for grounded linearization variant and the lifted linearization variant 1.
+We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
+The same setting is used for re-runs.
+We also test the latest version of TOHTN planners HTN2SAS, HyperTensioN and Lilotane on the transformed problems.
+Re-runs use panda$_{\pi}$ with the best heuristic(Add).
+We test both Complex and Simple Inference for linearization. %The comparison is done for grounded linearization variant and the lifted linearization variant 1.
 
@@
 \begin{table}[h]
-	\scalebox{0.4} {
+	\scalebox{0.45} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
@@
 
-\newpage
 As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
@@
 
+\newpage
 \section{Related Work}
@@
 The TOAD planner by \cite{HollerTOAD} compiles TOHTN problems into classical planning problems in order to allow the use of classical planning systems.
+The panda$_\pi$ engine progression search configuration, also uses a compilation to classical problems.
  % TOAD over-approximates the set of solutions to the HTN problem.

### 2022-11-20 paper/paper-mainfile.tex
verticalise table, move Summary, change Conclusion

@@
 \begin{abstract}
-Solving partially ordered hierarchical planning problems is more computationally expensive compared to solving totally ordered ones.
-Therefore, automatically transforming partially ordered problem domains into totally ordered ones, such that the totally ordered problem still retains at least one solution, would be a desired capability as it would reduce complexity and thus make it easier for planning systems to solve the problem.
+Solving partially ordered hierarchical planning problems (POHTN) is more computationally expensive than solving TOHTN ones.
+Therefore, automatically transforming partially ordered problem domains into totally ordered ones, such that the totally ordered problem still retains at least one solution, would be a desired capability as the reduction in complexity could make it easier for planning systems to solve the problem.
 It also allows the planner to use algorithms and heuristics specialised for the totally ordered case to solve the transformed problem.
@@
 In this paper, we propose an algorithm for converting partially ordered problems into totally ordered ones and give criterion for when this conversion will retain at least one solution.
-We test our techniques on the partially-ordered track of the bench-mark set of the IPC 2020 and solve both the linearized and the original partially-ordered problems using state-of-the-art planning systems.
 We find that in the majority of problems across a variety of domains, the linearized problems remain solvable, and can always be solved faster than the without our proposed pre-processing technique.
-We can thus conclude our proposed pre-processing technique becomes (part of) the state of the art for solving partially ordered planning problems.
 \end{abstract}
@@
 
-Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
+% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
 For some problems, such over-specification may remove all valid solutions.
-Thus many problems might be \emph{modelled} as POHTN problems.
+
+Many problems might be naturally more suited to being modelled as POHTN problems.
 However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-In particular, TOHTN planning as a class of problems has lower computational complexity than POHTN planning, as proven by \cite{ErolHTNExpressivity}, resulting in lower worst-case solving time.
+For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
+On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
+Where this is possible, it results in lower worst-case solving time.
 Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
@@
 Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
+% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
 
 The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
+
 Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
+In fact, the state-of-the-art panda$_\pi$ planner and \cite{HTN2SAS} both use a compilation to classical planning, another decidable planning class.
 
@@
 Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
+
+\section{Related Work}
+There exist other planners that also compile POHTN problems to decidable planning classes e.g.
+the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems.
+To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.
+
+\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
+of actions has an executable linearization.
+Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions.
+That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time.
+It can also find a executable linearization for that subset in polynomial time.
+
+\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.
+\cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
+In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
+
+Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
+This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.
+Thus their results are orthogonal to ours.
+
+The paper by \cite{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
+set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
 
@@
 
-A \textbf{Partially Ordered Hierarchical Planning}(POHTN) problem \textbf{P} = $(D, S_I, T_I)$
+A \textbf{Partially Ordered Hierarchical Planning}, also called POHTN, problem P = $(D, S_I, T_I)$
 is defined over some domain $D$, 
@@
 
-In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition.
+%In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition.
 For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired.
@@
 \textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
-For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$.
+%For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$.
 TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$.
@@
 POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).
-As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
+
+% As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
 In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.
 
-\section{Simple Linearization Procedure}
+\section{Linearization Procedure}
 The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.
 
-\subsection{Simple Inference}
+\subsection{Simple Inference of Preconditions and Effects for Compound Tasks}
 For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
@@
 
-\subsection{Complex Inference}
-The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.
+\subsection{Complex Inference of Effects for Compound Tasks}
+The work by~\cite{ConnyPreEstimation}, details a way to infer a subset of the mandatory preconditions and effects.
 
@@
 $$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
+if $E(c) \neq \emptyset$ and $prec(c) := undef$ otherwise.
 
 The set of executability-enabling states of c is
-$E(c) = \{s \in 2F  \mid  \exists \text{t.o. refinement of c applicable in s} \}$.
+$E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
 The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-$R_s(c) = \{s' \in 2^F | \exists t.o. refinement appl. in s res. in s' \}$.
+$R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
 
@@
 
-We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}.
-Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
-or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
-
 \subsection{Linearization Using Inferred Preconditions and Effects}
 
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.
-
 \begin{algorithm}
-	\caption{Linearization using inferred set of preconditions and effects}
+	\caption{Linearization using inferred set of preconditions and effects} %\caption{Calculation of linearized methods}
 	\label{alg:Algorithm1}	
@@
 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-	\caption{Calculation of linearized methods}
 \end{algorithm}
+
+From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.
+
+% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase.
+Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
+% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
 
@@
 
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$, we can perform breadth-first search on the task decomposition sub-tree (where tasks are nodes, and edges indicate possible decomposition by methods) rooted at $t$.
-The size of a sub-tree has an upper limit of $T_C + T_P$ nodes.
-For each primitive task in the sub-tree, we can iterate over each fact to update $\PreS, \AddS, \DelS$ for the root $t$.
-Thus calculating  $\PreS, \AddS, \DelS$ for a single compound task has an upper limit of $(3 * |F| * |T_p|) + |T_C|$.
-This inference occurs for each compound task, so inference for all compound tasks takes $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
+	To calculate $\PreS, \AddS, \DelS$ for each task $t$.
+We explore it's compound sub-tasks until we collect all primitive tasks.
+Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree.
+This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
+This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
+% we explore all poss (at most $|T_C|$)
 
 	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
-Leading to $(M * F * (t_m)^2)$, where $t_m$ is the average number of sub-tasks per method.
-So it's at most $\mathcal{O}(|M| * |F| * |T|^2)$, since $t_m$ has an upper bound of $T$, where $T=T_p + T_C$.
+Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.
 
-	Line~\ref{alg:TopSort} can be done via topological sort of the graph (which is known to be in $\mathcal{O}(V+E)$ in time and $\mathcal{O}(V)$ in space).
-In this case, the nodes of the graph are tasks, and the edges are orderings.
-So that's $M * (t_m+e_m)$, where $e_m$ is the number of \enquote{edges} in the new method, and has an upper bound of $e_m$ to find a topological sort for the sub-tasks of every method.
-That's approximately $\mathcal{O}(|M| * |T|)$, since both $t_m$ and $t_e$ are upper bounded by $T$, such that $T=T_p + T_C$.
+	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
+% and $\mathcal{O}(V)$ in space.
+	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
 
@@
 Consider the simple example problem:
-
-	\begin{figure}
-		\caption{Diagram showing an example problem and its decomposition.}		
-		\begin{subfigure}{3.5cm}
-			\begin{align*}
-			F   = & \{a, b, c \}           \\
-			N_p = & \{A, B, C\}      \\
-			N_c = & \{AC, T_I\}            \\ 
-			M   = & \{  (T_I, \{AC, B\}), \\
-			&    (AC, \{A, C\})  \} \\
-			S_I = & \{ a \} 	             \\ 
-			\end{align*} 
-		\end{subfigure}		
-		\scalebox{0.7}{
-			\begin{subfigure}{7cm}
-				\begin{tikzpicture}[auto,node distance=1.5cm,
-				thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-				square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-				\node[] (InitState) {}; %{ $\mathbf{S_I = \{a\}}$ };
-
-				\node[main node] (Init) [right=3cm of InitState] {$T_I$};
-				\node[main node] (AC) [right=2cm of Init, below of=Init] {$AC$};
-
-				\node[main node] (A) [below left = 2em and 2em of AC] {$A$};
-				\node[main node] (B) [below left = 2em and 2em of Init] {$B$}; 
-				\node[main node] (C) [below right = 2em and 2em of AC] {$C$};
-
-				%		\action{A}{PrimitiveA,
-				%			width  = 2.5em, 
-				%			height = 2.5em, 
-				%			pre length = 2em,
-				%			eff length = 2em,
-				%			body = {below left = 2em and 2em of AC} 
-				%		};
-
-				%		\action{B}{PrimitiveB,
-				%			width  = 2.5em, 
-				%			height = 2.5em, 
-				%			pre length = 2em,
-				%			eff length = 2em,
-				%			body = {below left = 2em and 2em of Init} 
-				%		};
-
-				%		\action{C}{PrimitiveC,
-				%			width  = 2.5em, 
-				%			height = 2.5em, 
-				%			pre length = 2em,
-				%			eff length = 2em,
-				%			body = {below right = 2em and 2em of AC} 
-				%		};
-
-				\path[every node/.style={font=\sffamily\small}]
-				(Init) edge [->] node [left] {} (B)
-				(Init) edge [->] node [left] {} (AC)
-				(AC) edge [->] node [left] {} (A)
-				(AC) edge [->] node [left] {} (C);
-				\end{tikzpicture}
-			\end{subfigure}	
-		}
-	\end{figure}
-
-	\begin{figure}
-		\caption{The only possible solution $A, B, C$ for E.g.\ 1, requires the children of $AC$ and $B$ to be interleaved, meaning we cannot impose an order between them}
-		\scalebox{0.9}{
-			\begin{tikzpicture}[auto,node distance=3cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\node[] (Invis) [] {$S_I$};
-			\node[square node] (A) [right of=Invis] {$A$};
-			\node[square node] (B) [right of=A] {$B$};
-			\node[square node] (C) [right of=B] {$C$};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(Invis) edge [->] node [left, label=a] {} (A)
-			(A) edge [->] node [left, label=b] {} (B)
-			(B) edge [->] node [left, label=c] {} (C);
-			\end{tikzpicture}		
-		}
-	\end{figure}
 
@@
 \begin{table}[h]
-	\scalebox{0.45} {
+	\scalebox{0.64} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
+			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
+			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
+			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
+			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
+			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
+			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
+			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
 			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
+			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
 			\midrule 
@@
 \begin{table}[h]
-	\scalebox{0.45} {
+	\scalebox{0.64} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
+			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
+			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
+			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
+			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}} 
+			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
+			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
+			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
 			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
+			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
 			\midrule 
@@
 \begin{table}[h]
-	\scalebox{0.45} {
+	\scalebox{0.64} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
+			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
+			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
+			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
+			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
+			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
+			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
+			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
 			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }    \\ 
+			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
 			\midrule 
@@
 \begin{table}[h]
-	\scalebox{0.45} {
+	\scalebox{0.64} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
+			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
+			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
+			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
+			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
+			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
+& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
+& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
 			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }  \\ 
+			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
 			\midrule 
@@
 
-\newpage
-\section{Related Work}
-% FROM (https://ojs.aaai.org/index.php/ICAPS/article/view/15944/15755) A Closer Look at Causal Links: Complexity Resultsfor Delete-Relaxation in Partial Order Causal Link (POCL) Planning
-Our linearization procedure is a pre-processing technique for the search space, is a compilation of an HTN planning problem class to a different class of problems, and can exploit specialised TO planners.
-
-The panda$_\pi$ grounder by \cite{Behnke2020Grounding} also prunes unreachable tasks, methods, etc.\.
-Because the panda$_{\pi}$ planner is a grounded planner, we can ground then linearize, or vice-versa to \enquote{stack} the reduction in search space.
-
-The main optimization of HyperTensioN by \cite{hypertension} is via the Pullup extension - which determines additional preconditions of methods and compound tasks by analysing the preconditions of possible child actions.
-Unlike ours, no approximation of effects are considered.
-
-The HTN2STRIPS planner by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} compiles HTN problems, both totally and partially ordered, to classical problems.
-The TOAD planner by \cite{HollerTOAD} compiles TOHTN problems into classical planning problems in order to allow the use of classical planning systems.
-The panda$_\pi$ engine progression search configuration, also uses a compilation to classical problems.
- % TOAD over-approximates the set of solutions to the HTN problem.
-In the empirical evaluation the paper performed, TOAD achieved higher coverage than the base version of HTN2STRIPS, and all systems submitted to the totally ordered track of the 2020 IPC.
-
-There exists totSAT planner by \cite{TOtoSAT} that compiles a totally ordered problem to SAT problem.
-There also exists 2 planners by \cite{POtoSAT, OptimalPOtoSAT} that compiles a partially ordered problem to a SAT problem.
-One searches for optimal plans, the other focuses on finding any solution as quickly as possible.
-Lilotane by \cite{Lilotane} directly encodes a lifted problem representation into a SAT problem.
-
-Another planner by \cite{Behnke_Speck_2021} converts TOHTN into Binary Decision Diagrams (BDDs), then use symbolic search on it.
-
-The BDD planner by \cite{Behnke_Speck_2021}, totSAT planner by \cite{TOtoSAT}, TOAD by \cite{HollerTOAD}, HyperTensioN by \cite{hypertension}, and Lilotane by \cite{Lilotane}, as discussed before, are all specialised TO planners.
-So are the TFD (Totally Ordered Fast Downward) and PFD (Partially Ordered Fast Downward) hierarchical planners by \cite{PDDL4J}.
-Note however that HTN2SAS achieved similar coverage than greedy search with panda$_\pi$, a partial-order planner.
-
-\section{Summary}
-
-The contributions of this paper are as follows:
-
-At least for the POHTN problems in the IPC domain, most of them are not undecideable.
-In another way, it is as if the POHTN domains are compressed TO domains - this linearization
-separates one back out.
-
-For another, this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
-Furthermore, there is demonstrably much more room for improvement.
-Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
-
-We have a method that can increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
-Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
-Then $k+m$ (lifted or grounded) TOHTN problems exist now.
-And from empirical evaluation, $k$ may be close to $n$.
-
-We can identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all other criteria.
-
 \section{Future Work}
-
-\subsubsection{Encode Linearization Problem as a MAX-SAT Problem} 
+%Encode Linearization Problem as a MAX-SAT Problem
 The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
@@
 
-\subsubsection{Adding a Plan as Additional Input to the Domain}
+%Adding a Plan as Additional Input to the Domain
 Adding a plan as additional input to the PO domain having the
@@
 
+\section{Conclusion}
+
+% The contributions of this paper are as follows:
+
+This paper finds that, at least for the POHTN problems in the IPC domain, most of them are not undecidable.
+In other words, it is as if the POHTN domains are compressed TO domains - this linearization separates one of them back out.
+
+We can also see this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
+Furthermore, there is demonstrably much more room for improvement.
+Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
+
+This method can also be used to increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
+Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
+Then $k+m$ (lifted or grounded) TOHTN problems exist now.
+And from empirical evaluation, $k$ may be close to $n$.
+
+Finally, in this paper we identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all others discussed in other works.
+
 % Use \bibliography{yourbibfile} instead or the References section will not appear in your paper

### 2022-11-21 paper/paper-mainfile.tex
adjust table size

@@
 
-\section{Linearization Procedure}
+\section{Inference of Preconditions and Effects}
 The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.
@@
 
-\subsection{Linearization Using Inferred Preconditions and Effects}
+\subsection{Inference of Preconditions and Effects for Lifted Domain}
+In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
+Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
 
+E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
+If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
+This is true for all possible tasks by simple induction over the decomposition process.
+
+Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
+
+Specifically, let $\sigma$ be the set of parameters for the method.
+Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
+Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
+
+Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
+For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
+% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
+
+This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
+The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
+For variant 1, only one linearized lifted method per partially-ordered lifted method is produced.
+
+\section{Linearization Using Inferred Preconditions and Effects}
 \begin{algorithm}
@@
 
-\begin{table}[h]
-	\scalebox{0.64} {
+\begin{table*}[h]
+	\scalebox{1} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
@@
 	}
-\end{table}
+\end{table*}
 
-\begin{table}[h]
-	\scalebox{0.64} {
+\begin{table*}[h]
+	\scalebox{1} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
@@
 	}
-\end{table}
+\end{table*}
 
@@
 	}
-\end{table}
+\end{table*}
 
-\begin{table}[h]
-	\scalebox{0.64} {
+\begin{table*}[h]
+	\scalebox{1} {
 		\begin{tabular}{lccccccccccccccccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
-& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
+			&& \multicolumn{2}{c}{  \rotatebox{80}{rc2(Add)}} & 
+			\multicolumn{2}{c}{   \rotatebox{80}{rc2(Filter)}} & 
+			\multicolumn{2}{c}{  \rotatebox{80}{rc2(FF)}}
+			& \multicolumn{2}{c}{   \rotatebox{80}{rc2(LMC)}}  
+			& \multicolumn{2}{c}{  \rotatebox{80}{HTN2SAS}}
+& \multicolumn{2}{c}{  \rotatebox{80}{HyperTensioN}}
+& \multicolumn{2}{c}{  \rotatebox{80}{Lilotane}} \\ 
 			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    

### 2022-11-22 paper/paper-mainfile.tex
added results

@@
 \begin{abstract} 
-Solving partially ordered hierarchical planning problems (POHTN) is more computationally expensive than solving TOHTN ones.
-Therefore, automatically transforming partially ordered problem domains into totally ordered ones, such that the totally ordered problem still retains at least one solution, would be a desired capability as the reduction in complexity could make it easier for planning systems to solve the problem.
-It also allows the planner to use algorithms and heuristics specialised for the totally ordered case to solve the transformed problem.
-
-This is a complex endeavour, and not even possible in some cases, because even creating \emph{all} possible linearizations of all methods in the original domain does not guarantee that solutions are preserved.
-
-In this paper, we propose an algorithm for converting partially ordered problems into totally ordered ones and give criterion for when this conversion will retain at least one solution.
-We find that in the majority of problems across a variety of domains, the linearized problems remain solvable, and can always be solved faster than the without our proposed pre-processing technique.
+HTN planning is in general undecidable, yet there exist efficient
+planning algorithms. An important subclass is that of totally ordered
+HTN planning problems. Not only is this class decidable, but also easier
+to handle algorithmically since tasks cannot interleave anymore.
+Consequently, several specialized solvers exist, and dedicated tracks at
+the International Planning Competition (IPC) in both 2020 and 2023. We
+were able to show that almost all currently existing partially ordered
+planning benchmarks can be turned into totally ordered ones without
+sacrificing solvability. Establishing totally ordered problems in a
+preprocessing technique thus allows to use planning systems, heuristics,
+pruning techniques (etc.) that are only available for totally ordered
+problems. This allows solving problems more efficiently and with
+better-informed techniques, at the (little) cost of doing a
+preprocessing technique. We show that in only a very few cases
+linearization isn't possible, and in all others establishing a total
+order pays off \emph{significantly}, thus establishing our technique as
+a significant ingredient in the state of the art for solving partially
+ordered HTN problems. As a side contribution, we identify a new class of
+decidable (EXPTIME-complete) HTN problems, namely those where our
+preprocessing technique is guaranteed to be solvability-preserving.
 \end{abstract}
@@
 % Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-
 The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-
 Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
 In fact, the state-of-the-art panda$_\pi$ planner and \cite{HTN2SAS} both use a compilation to classical planning, another decidable planning class.
-
 In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
@@
 Consider the simple example problem:
-
 	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
@@
 	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
-
 	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
@@
 \begin{table*}[h]
+	\centering
+	\subcaption{Coverage achieved, using Simple Inference}
 	\scalebox{1} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
+\begin{tabular}{lccccl} 
 	\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
+	&& \multicolumn{2}{c}{rc2(Add)} \\
+	\cmidrule(lr){3-4}  
+	& max &PO & TO \\ 
 	\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
+	Barman-BDI & 20 & 3.0 &\multicolumn{2}{c}{ \textbf{10.0}  } \\ 
+	Monroe Fully Observ.$^{2}$ & 25 & \textbf{25.0} &\multicolumn{2}{c}{ \textbf{25.0}  } \\ 
+	Monroe Part. Observ.$^{2}$ & 24 & \textbf{14.0} &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
+	PCP$^{11}$ & 17 & \textbf{14.0} &\multicolumn{2}{c}{ 8.0  } \\ 
+	Rover & 20 & 10.0 &\multicolumn{2}{c}{ \textbf{13.0}  } \\ 
+	Satellite & 25 & 24.0 &\multicolumn{2}{c}{ \textbf{25.0}  } \\ 
+	Transport & 40 & 12.0 &\multicolumn{2}{c}{ \textbf{23.0}  } \\ 
+	UM-Translog & 22 & \textbf{22.0} &\multicolumn{2}{c}{ 0.0  } \\ 
+	Woodworking$^{1}$ & 30 & 13.0 &\multicolumn{2}{c}{ \textbf{15.0}  } \\ 
 	\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
+	Monroe & 100 & \textbf{100.0} &\multicolumn{2}{c}{ \textbf{100.0}  } \\ 
+	SmartPhone & 7 & \textbf{5.0} &\multicolumn{2}{c}{ 2.0  } \\ 
+	Zenotravel$^{1}$ & 5 & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
 	\midrule 
-			Coverage \\ 
-			Norm. coverage  \\ 
+	Coverage & 335 & \textbf{247.0} &\multicolumn{2}{c}{ 240.0  } \\ 
+	Norm. coverage & 12 & \textbf{8.46} &\multicolumn{2}{c}{ 7.56  } \\  
+	\bottomrule 
+\end{tabular}
+
+	}
+\end{table*}
+
+		%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
+%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
+%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
+%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
+%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
+%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
+%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
+
+\begin{table*}[h]
+	\centering
+	\caption{IPOC score achieved, using Simple Inference}
+	\scalebox{1} {
+\begin{tabular}{lccccl} 
+	\toprule 
+	&& \multicolumn{2}{c}{rc2(Add)} \\
+	\cmidrule(lr){3-4}  
+	& max &PO &  TO   \\ 
+	\midrule 
+	Barman-BDI & 1 & 0.08 &\multicolumn{2}{c}{ \textbf{0.39}  } \\ 
+	Monroe Fully Observ.$^{2}$ & 1 & \textbf{0.57} &\multicolumn{2}{c}{ 0.45  } \\ 
+	Monroe Part. Observ.$^{2}$ & 1 & \textbf{0.31} &\multicolumn{2}{c}{ 0.25  } \\ 
+	PCP$^{11}$ & 1 & \textbf{0.82} &\multicolumn{2}{c}{ 0.47  } \\ 
+	Rover & 1 & 0.41 &\multicolumn{2}{c}{ \textbf{0.58}  } \\ 
+	Satellite & 1 & 0.91 &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
+	Transport & 1 & 0.24 &\multicolumn{2}{c}{ \textbf{0.47}  } \\ 
+	UM-Translog & 1 & \textbf{1.0} &\multicolumn{2}{c}{ 0.0  } \\ 
+	Woodworking$^{1}$ & 1 & 0.38 &\multicolumn{2}{c}{ \textbf{0.42}  } \\ 
+	\midrule 
+	Monroe & 1 & \textbf{0.83} &\multicolumn{2}{c}{ 0.69  } \\ 
+	SmartPhone & 1 & \textbf{0.71} &\multicolumn{2}{c}{ 0.29  } \\ 
+	Zenotravel$^{1}$ & 1 & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
+	\midrule 
+	IPC score & 12 & \textbf{7.3} &\multicolumn{2}{c}{ 6.0  } \\ 
+	\bottomrule 
+\end{tabular}
+
+	}
+\end{table*}
+
+\subsection{Performance of Complex Linearization}
+
+\begin{table*}[h]
+	\centering
+	\caption{Coverage achieved, using Complex Inference}
+	\scalebox{0.8} {
+\begin{tabular}{lccccccccccccccccl} 
+	\toprule 
+	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
+	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
+	& max &PO & TO & PO & TO & PO & TO & PO &  TO \\ 
+	\midrule 
+	Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 &\multicolumn{2}{c}{ \textbf{8.0}  } \\ 
+	Monroe Fully Observ. & 25 & \textbf{25.0} & \textbf{25.0} & \textbf{18.0} & \textbf{18.0} & \textbf{22.0} & \textbf{22.0} & \textbf{15.0} &\multicolumn{2}{c}{ \textbf{15.0}  } \\ 
+	Monroe Part. Observ. & 24 & \textbf{14.0} & \textbf{14.0} & \textbf{7.0} & \textbf{7.0} & \textbf{14.0} & \textbf{14.0} & \textbf{10.0} &\multicolumn{2}{c}{ \textbf{10.0}  } \\ 
+	PCP$^{11}$ & 17 & \textbf{14.0} & 8.0 & \textbf{14.0} & 8.0 & \textbf{15.0} & 9.0 & \textbf{15.0} &\multicolumn{2}{c}{ 9.0  } \\ 
+	Rover & 20 & 10.0 & \textbf{18.0} & 4.0 & \textbf{15.0} & 4.0 & \textbf{17.0} & 4.0 &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
+	Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 &\multicolumn{2}{c}{ \textbf{25.0}  } \\ 
+	Transport & 40 & 12.0 & \textbf{28.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 &\multicolumn{2}{c}{ \textbf{11.0}  } \\ 
+	UM-Translog & 22 & \textbf{22.0} & 0.0 & \textbf{22.0} & 0.0 & \textbf{22.0} & 0.0 & \textbf{22.0} &\multicolumn{2}{c}{ 0.0  } \\ 
+	Woodworking$^{1}$ & 30 & 13.0 & \textbf{19.0} & 7.0 & \textbf{14.0} & 12.0 & \textbf{18.0} & 9.0 &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
+	\midrule 
+	Monroe & 100 & \textbf{100.0} & \textbf{100.0} & 79.0 & \textbf{88.0} & 92.0 & \textbf{100.0} & 81.0 &\multicolumn{2}{c}{ \textbf{90.0}  } \\ 
+	SmartPhone & 7 & \textbf{5.0} & 4.0 & \textbf{5.0} & 2.0 & \textbf{5.0} & 3.0 & \textbf{5.0} &\multicolumn{2}{c}{ 3.0  } \\ 
+	Zenotravel$^{2}$ & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
+	\midrule 
+	Coverage & 335 & 247.0 & \textbf{256.0} & 188.0 & \textbf{194.0} & 232.0 & \textbf{237.0} & 199.0 &\multicolumn{2}{c}{ \textbf{204.0}  } \\ 
+	Norm. coverage & 12 & \textbf{8.46} & 8.36 & \textbf{6.85} & 6.41 & \textbf{8.01} & 7.69 & \textbf{7.11} &\multicolumn{2}{c}{ 6.69  } \\  
 	\bottomrule 
@@
 \begin{table*}[h]
-	\scalebox{1} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
+	\centering
+	\caption{IPC score achieved, using Complex Inference}
+	\scalebox{0.9} {
+\begin{tabular}{lccccccccccccccccl} 
 	\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}} 
-			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
+	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
+	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
+	& max &PO & TO & PO & TO & PO & TO & PO &  TO   \\ 
 	\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
+	Barman-BDI & 1 & 0.08 & \textbf{0.38} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.36} & 0.05 &\multicolumn{2}{c}{ \textbf{0.22}  } \\ 
+	Monroe Fully Observ. & 1 & \textbf{0.57} & 0.2 & \textbf{0.32} & 0.12 & \textbf{0.47} & 0.16 & \textbf{0.22} &\multicolumn{2}{c}{ 0.08  } \\ 
+	Monroe Part. Observ. & 1 & \textbf{0.31} & 0.11 & \textbf{0.14} & 0.05 & \textbf{0.31} & 0.11 & \textbf{0.17} &\multicolumn{2}{c}{ 0.06  } \\ 
+	PCP$^{11}$ & 1 & \textbf{0.82} & 0.47 & \textbf{0.82} & 0.47 & \textbf{0.83} & 0.5 & \textbf{0.83} &\multicolumn{2}{c}{ 0.5  } \\ 
+	Rover & 1 & 0.41 & \textbf{0.84} & 0.14 & \textbf{0.58} & 0.2 & \textbf{0.69} & 0.17 &\multicolumn{2}{c}{ \textbf{0.47}  } \\ 
+	Satellite & 1 & 0.91 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 &\multicolumn{2}{c}{ \textbf{0.99}  } \\ 
+	Transport & 1 & 0.24 & \textbf{0.64} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.31} & 0.12 &\multicolumn{2}{c}{ \textbf{0.19}  } \\ 
+	UM-Translog & 1 & \textbf{1.0} & 0.0 & \textbf{1.0} & 0.0 & \textbf{1.0} & 0.0 & \textbf{1.0} &\multicolumn{2}{c}{ 0.0  } \\ 
+	Woodworking$^{1}$ & 1 & 0.38 & \textbf{0.53} & 0.2 & \textbf{0.38} & 0.35 & \textbf{0.51} & 0.27 &\multicolumn{2}{c}{ \textbf{0.35}  } \\ 
 	\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
+	Monroe & 1 & \textbf{0.83} & 0.48 & \textbf{0.5} & 0.38 & \textbf{0.76} & 0.48 & \textbf{0.54} &\multicolumn{2}{c}{ 0.41  } \\ 
+	SmartPhone & 1 & \textbf{0.71} & 0.57 & \textbf{0.69} & 0.26 & \textbf{0.71} & 0.4 & \textbf{0.71} &\multicolumn{2}{c}{ 0.38  } \\ 
+	Zenotravel$^{2}$ & 1 & \textbf{1.0} & \textbf{1.0} & 0.63 & \textbf{0.88} & \textbf{1.0} & \textbf{1.0} & 0.83 &\multicolumn{2}{c}{ \textbf{0.96}  } \\ 
 	\midrule 
-			IPC \\
-			\bottomrule
-		\end{tabular} 	
-	}
-\end{table*}
-
-\subsection{Performance of Complex Linearization}
-
-\begin{table*}[h]
-	\scalebox{1} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			Coverage \\ 
-			Norm. coverage  \\ 
-			\bottomrule
-		\end{tabular} 	
-	}
-\end{table*}
-
-\begin{table*}[h]
-	\scalebox{1} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{80}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{80}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{80}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{80}{rc2(LMC)}}  
-			& \multicolumn{2}{c}{  \rotatebox{80}{HTN2SAS}}
-& \multicolumn{2}{c}{  \rotatebox{80}{HyperTensioN}}
-& \multicolumn{2}{c}{  \rotatebox{80}{Lilotane}} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			IPC \\
+	IPC score & 12 & \textbf{7.3} & 6.2 & \textbf{5.3} & 4.5 & \textbf{7.0} & 5.5 & \textbf{5.8} &\multicolumn{2}{c}{ 4.6  } \\ 
 	\bottomrule 

### 2022-11-23 paper/example.tex

--- 2022-11-08 paper/mainfile.tex
@@
-\documentclass[letterpaper]{article}
-% DO NOT CHANGE THIS
-% \usepackage[submission]{aaai23} % DO NOT CHANGE THIS
-\usepackage[submission]{../AuthorKit23/AnonymousSubmission/LaTeX/aaai23}
-\usepackage{times} % DO NOT CHANGE THIS
-\usepackage{helvet} % DO NOT CHANGE THIS
-\usepackage{courier} % DO NOT CHANGE THIS
-\usepackage[hyphens]{url} % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm} % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\usepackage{natbib} % DO NOT CHANGE THIS
-\usepackage{caption} % DO NOT CHANGE THIS
-\frenchspacing % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
-%
-% Keep the \pdfinfo as shown here. There’s no need
-% for you to add the /Title and /Author tags.
-\pdfinfo{
-	/TemplateVersion (2023.1)
-} 
-\usepackage{booktabs} 
-\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
-\usepackage{csquotes}
-\usepackage{subcaption}
-\usepackage{amssymb,amsmath}
-\usepackage{todonotes} 
-\usepackage{tikz}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{proof}{Proof}
-
-\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
-\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
-
-\newcommand{\Add} {\ensuremath{\mathit{add}}}
-\newcommand{\Del} {\ensuremath{\mathit{del}}}
-\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
-\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
-\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
-\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
-\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
-
-\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{poss-eff^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{poss-eff^{-}_{*}}}}
-
-\newcommand{\RelEffPlus} {\ensuremath{\mathit{eff^{\emptyset +}_{*}}}}
-\newcommand{\RelEffMinus} {\ensuremath{\mathit{eff^{\emptyset -}_{*}}}}
-\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
-\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
-
-\title{Transforming Partially Ordered HTN Problems to Totally Ordered}
-\begin{document}
-\maketitle
-
-\begin{abstract}
-Solving partially ordered hierarchical planning problems is more computationally expensive compared to solving totally ordered ones.
-Therefore, automatically transforming partially ordered problem domains into totally ordered ones, such that the totally ordered problem still retains at least one solution, would be a desired capability as it would reduce complexity and thus make it easier for planning systems to solve the problem.
-It also allows the planner to use algorithms and heuristics specialised for the totally ordered case to solve the transformed problem.
-
-This is a complex endeavour, and not even possible in some cases, because even creating \emph{all} possible linearizations of all methods in the original domain does not guarantee that solutions are preserved.
-
-In this paper, we propose an algorithm for converting partially ordered problems into totally ordered ones and give criterion for when this conversion will retain at least one solution.
-We test our techniques on the partially-ordered track of the bench-mark set of the IPC 2020 and solve both the linearized and the original partially-ordered problems using state-of-the-art planning systems.
-We find that in the majority of problems across a variety of domains, the linearized problems remain solvable, and can always be solved faster than the without our proposed pre-processing technique.
-We can thus conclude our proposed pre-processing technique becomes (part of)
-the state of the art for solving partially ordered planning problems.
-\end{abstract}
-
-\section{Introduction}
-
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
-
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-Thus many problems might be \emph{modelled} as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-In particular, TOHTN planning as a class of problems has lower computational complexity than POHTN planning, as proven by \cite{ErolHTNExpressivity}, resulting in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-
-% Also, we get another class of decidable partially ordered problems that's orthogonal to recursive ones. 
-% Also, the domain model might be more intuitive: if a task is independent of some others it might be counter-intuitive to demand a certain position of it (if artificially made totally ordered).
-Plan recognition: independent goals can be described in parallel with POHTN planning but not with TOHTN, as per \cite{DanielPlanRecognition}.
-
-%\subsubsection{Contributions}
-%Gregor Behnke used a similar linearization process to produce the TO benchmark set used for the 2020 International Planning Competition (IPC 2020).
-That also attempted to linearize the methods by drawing the same links between preconditions and effects as in this paper, and picked a random linearization if that was not possible.
-However, no attempt was made to analyse if this lead to a easier to solve problem, or if it had any interesting theoretical implications.
-As Prof.
-Bercher thought this could be an interesting use for linearization, this paper offers this empirical evaluation and theoretical analysis.
-
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
-
-\section{Hierarchical Planning Formalism}
-Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning.
-There are many formalisations for HTN planning.
-The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}.
-HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning.
-TOHTN planning is a special case of POHTN planning.
-% except with the initial task network replaced by a initial compound task.
-
-A \textbf{Partially Ordered Hierarchical Planning}(POHTN) problem \textbf{P} = $(D, S_I, T_I)$
-is defined over some domain $D$, 
-has an initial state $S_I \in 2^F$, and 
-has a initial compound task $T_I$. 
-The closed world assumption also holds for HTN planning.
-
-The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
-$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
-$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
-$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.
-
-A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
-T, which is a finite set of task identifiers (ids); 
-$\singlePrec$, which is a partial order over T; and
-$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.
-
-% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
-A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
-a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
-\begin{align}
-tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
-\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
-&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
-\end{align}
-In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
-on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.
-
-A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
-tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ...
-t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ...
-\alpha(t_n) \rangle$ in $S_I$ is executable.
-
-In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition.
-For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired.
-Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning.
-Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.
-
-\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
-For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$.
-TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$.
-This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning.
-POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).
-As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
-In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.
-
-\section{Simple Linearization Procedure}
-The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.
-
-For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
-For a grounded model, $f' = f$.
-The inferred preconditions and effects for a task are then defined as below:
-\begin{align*}
-& \forall t \in T_P : \PreS(t) := \Pre(t) \\
-& \forall t \in T_P : \AddS(t) := \Add(t) \\
-& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-								& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-								& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-								& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-\end{align*}
-
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.
-
-\begin{algorithm}\label{alg:Algorithm1}
-	\KwData{$(F, T_P, T_C, \delta, M)$}
-	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-	{
-
-		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}
-
-		$G \gets$ calculateTransitiveClosure($\singlePrec$) \\
-		\label{alg:StartBuildGraph}
-		\For{a $\in$ F}{  
-			\For{$t \in T_m$}{
-				\For{$t' \in T_m$}{
-					if $a \in \AddS(t)$ and $a \in \PreS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$  \\ 
-					if $a \in \AddS(t)$ and $a \in \DelS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \PreS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \AddS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$ \\  
-				}
-			} 
-			\label{alg:EndBuildGraph}	
-		}	 
-		\label{alg:TopSort}
-		$\singlePrec'\gets$ any linearization of $G$ \\
-		$m' = (tasks(m), \singlePrec', \alpha(t))$ \\
-		$M' = M' \cup  \{m'\}$ \\		
-	}
-	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-	\caption{Calculation of linearized methods}
-\end{algorithm}
-
-\subsection{Theoretical Properties of Linearization Result}
-\begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
-\end{theorem}
-\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
-	Let $|T|$ = $|T_P| + |T_C|$.
-
-	The Floyd-warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
-
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$, we can perform breadth-first search on the task decomposition sub-tree (where tasks are nodes, and edges indicate possible decomposition by methods) rooted at $t$.
-The size of a sub-tree has an upper limit of $T_C + T_P$ nodes.
-For each primitive task in the sub-tree, we can iterate over each fact to update $\PreS, \AddS, \DelS$ for the root $t$.
-Thus calculating  $\PreS, \AddS, \DelS$ for a single compound task has an upper limit of $(3 * |F| * |T_p|) + |T_C|$.
-This inference occurs for each compound task, so inference for all compound tasks takes $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
-
-	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
-Leading to $(M * F * (t_m)^2)$, where $t_m$ is the average number of sub-tasks per method.
-So it's at most $\mathcal{O}(|M| * |F| * |T|^2)$, since $t_m$ has an upper bound of $T$, where $T=T_p + T_C$.
-
-	Line~\ref{alg:TopSort} can be done via topological sort of the graph (which is known to be in $\mathcal{O}(V+E)$ in time and $\mathcal{O}(V)$ in space).
-In this case, the nodes of the graph are tasks, and the edges are orderings.
-So that's $M * (t_m+e_m)$, where $e_m$ is the number of \enquote{edges} in the new method, and has an upper bound of $e_m$ to find a topological sort for the sub-tasks of every method.
-That's approximately $\mathcal{O}(|M| * |T|)$, since both $t_m$ and $t_e$ are upper bounded by $T$, such that $T=T_p + T_C$.
-
-	So in total the main algorithm takes: \newline
-	$(|M| * |T|^3)$ +          % Floyd-Warshall
-	$(|M| * |F| * |T|)$  +    % GetPreEff
-	$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
-	$(|M| * |T|)$        % topological sort
-\end{proof}
-
-\begin{theorem}\label{thm:Soundness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
-\end{theorem}
-\begin{proof}
-	The new desired orderings for a method include all of the orderings already required by the method originally.
-The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph.
-This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one.
-Any solution to the linearized problem is then obviously a solution to the original problem.
-\end{proof}
-
-\begin{theorem}\label{thm:notCompleteness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then $sol(P')$ may be empty.
-\end{theorem}
-\begin{proof}
-	This algorithm linearizes all the methods to be totally ordered.
-Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents that are already ordered with respect to each other.
-This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
-Consider the simple example problem:
-
 	\begin{figure}	
-		\caption{Diagram showing an example problem and its decomposition.}		
 		\begin{subfigure}{3.5cm}
@@
 		\end{subfigure}		
-		\scalebox{0.7}{
+		\scalebox{0.6}{
 			\begin{subfigure}{7cm}
@@
 
-		%		\action{A}{PrimitiveA,
-		%			width  = 2.5em, 
-		%			height = 2.5em, 
-		%			pre length = 2em,
-		%			eff length = 2em,
-		%			body = {below left = 2em and 2em of AC} 
-		%		};
-
-		%		\action{B}{PrimitiveB,
-		%			width  = 2.5em, 
-		%			height = 2.5em, 
-		%			pre length = 2em,
-		%			eff length = 2em,
-		%			body = {below left = 2em and 2em of Init} 
-		%		};
-
-		%		\action{C}{PrimitiveC,
-		%			width  = 2.5em, 
-		%			height = 2.5em, 
-		%			pre length = 2em,
-		%			eff length = 2em,
-		%			body = {below right = 2em and 2em of AC} 
-		%		};
-
 				\path[every node/.style={font=\sffamily\small}]
@@
 		}	
+		\caption{Diagram showing an example problem and its decomposition.}	
 	\end{figure}
@@
 	\begin{figure}
-		\caption{The only possible solution $A, B, C$ for E.g.\ 1, requires the children of $AC$ and $B$ to be interleaved, meaning we cannot impose an order between them}
-		\scalebox{0.9}{
+		\scalebox{0.8}{
 			\begin{tikzpicture}[auto,node distance=3cm,
@@
 		}
+			\caption{The only possible solution $A, B, C$ for E.g.\ 1, requires the children of $AC$ and $B$ to be interleaved, meaning we cannot impose an order between them}
 	\end{figure}
-
-	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
-	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$.
-This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution.
-	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
-
-	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
-Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
-	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
-\end{proof}
-
-We will now see that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} does not have to break cycles.
-\begin{theorem}\label{thm:SpecialCase}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if Algorithm~\ref{alg:Algorithm1} did not have to
-	cycle-break, then if $sol(P)$ is non-empty then $sol(P')$, will be non-empty as well.
-\end{theorem}
-\begin{proof}
-	Assume that there exists a solution in the PO domain.
-By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain.
-Assume this sequence is $(a_0, a_1, ..., a_n)$.
-We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
-	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state.
-The action $a_k$ could only be non-executable, if one or more of its preconditions was not met.
-Assume one of these unmet preconditions is for existence of the state variable $A$.
-	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution.
-So there must exist an action $a_i$, $0 < i < n$, that will add A.
-Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree.
-So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.
-
-	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
-We are assuming that all methods linearized without conflict, so $(t_i, t_k)$ should not be required.
-This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
-In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.
-
-	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution.
-Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
-\end{proof}
-
-There are several possible levels of \enquote{completeness} for a problem compilation.
-%\begin{enumerate}
-\begin{itemize}
-	\item all solutions remain 
-	\item at least one solution remains 
-	\item all optimal solutions remain
-	\item at least one optimal solution remains 	
-\end{itemize}
-%\end{enumerate}
-Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if no cycle-breaking is needed.
-If cycle-breaking is needed, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions.
-Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.
-
-\begin{theorem}\label{thm:newClass}
-	Problems $P$ that satisfy the criterion for linearization without cycle-breaking form a new class of decidable problems.
-\end{theorem}
-\begin{proof}
-	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.
-\end{proof}
-
-\section{Complex Linearization Procedure}
-
-The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.
-
-\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
-
-State-independent positive and negative effects (cf. their
-Def. 4) of a compound task c are facts that are added or
-deleted, resp., by the successful execution of a refinement of
-c, independent of the state in which the task is executed, i.e.
-$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-after every refinement of c but after at least one:
-$$ \RelPossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-$$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
-
-The set of executability-enabling states of c is
-$E(c) = \{s \in 2F  \mid  \exists \text{t.o. refinement of c applicable in s} \}$.
-The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-$R_s(c) = \{s' \in 2^F | \exists t.o. refinement appl. in s res. in s' \}$.
-
-So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined
-just like the original ones but based on the precondition-
-relaxed variant of D.
-
-We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}.
-
-\section{Empirical Evaluation}
-
-To prove that our technique improves the solving time, we compare the runtime of a state-of-the-art planning system on the original problem vs.
-the transformed problem, for a number of different PO domains.
-All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
-The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
-Each problem has the standard IPC time limit of 30 minutes.
-Any grounding and pre-processing time needed is included as part of the 'solving' time.
-Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
-
-\subsection{Hardware and Planning Systems}
-The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the partial-order panda$_\pi$, actually achieved similar coverage and slightly lower IPC score than the best specialised TOHTN planner evaluated.
-%Lilotane by \cite{Lilotane} is an TOHTN solver and the IPC 2020 runner-up.
-The winner, HyperTensioN by \cite{hypertension} could not be tested due to lack of support for reading in optimisation metrics.
-
-We therefore test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} on the configuration of Greedy best first search with visited lists, and using RC to turn the problem into a classical planning problem.
-We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}.
-
-We compare the performance of these 4 planner settings on the original problem and the pre-processed problem, HTN2SAS, and the latest version of HyperTensioN and Lilotane.
-For panda$_{\pi}$, the same setting is used for re-runs.
-For TOHTN planners, re-runs use panda$_{\pi}$ on the best setting (Add heuristic).
-The comparison is done for grounded linearization variant and the lifted linearization variant 1.
-
-\subsection{Performance of Simple Linearization}
-
-\begin{table}[h]
-	\scalebox{0.45} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-				& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
-		\midrule 
-		Barman-BDI  \\ 
-		Monroe Fully Observ. \\ 
-		Monroe Part. Observ. \\ 
-		PCP\\ 
-		Rover  \\ 
-		Satellite  \\ 
-		Transport \\ 
-		UM-Translog \\ 
-		Woodworking \\ 
-		\midrule 
-		Monroe  \\ 
-		SmartPhone \\ 
-		Zenotravel \\ 
-		\midrule 
-		Coverage \\ 
-		Norm. coverage  \\ 
-		\bottomrule
-			\end{tabular} 	
-			}
-\end{table}
-
-\begin{table}[h]
-	\scalebox{0.45} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			IPC \\
-			\bottomrule
-			\end{tabular} 	
-	}
-\end{table}
-
-\subsection{Performance of Complex Linearization}
-
-\begin{table}[h]
-	\scalebox{0.45} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }    \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			Coverage \\ 
-			Norm. coverage  \\ 
-			\bottomrule
-			\end{tabular} 	
-	}
-\end{table}
-
-\begin{table}[h]
-	\scalebox{0.45} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }  \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			IPC \\
-			\bottomrule
-		\end{tabular} 	
-	}
-\end{table}
-
-As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-As we can see, the best planner is ? planner.
 
@@
 The TOAD planner by \cite{HollerTOAD} compiles TOHTN problems into classical planning problems in order to allow the use of classical planning systems.
+The panda$_\pi$ engine progression search configuration, also uses a compilation to classical problems.
 % TOAD over-approximates the set of solutions to the HTN problem.
@@
 Note however that HTN2SAS achieved similar coverage than greedy search with panda$_\pi$, a partial-order planner.
-
-\section{Summary}
-
-The contributions of this paper are as follows:
-
-At least for the POHTN problems in the IPC domain, most of them are not undecideable.
-In another way, it is as if the POHTN domains are compressed TO domains - this linearization
-separates one back out.
-
-For another, this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
-Furthermore, there is demonstrably much more room for improvement.
-Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
-
-We have a method that can increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
-Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
-Then $k+m$ (lifted or grounded) TOHTN problems exist now.
-And from empirical evaluation, $k$ may be close to $n$.
-
-We can identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all other criteria.
-
-\section{Future Work}
-
-\subsubsection{MAX-SAT Instead of Cycle-Break} 
-The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
-MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.
-
-Cycle-breaking considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, similar to the one described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-Assuming no negative preconditons, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
-The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
-
-\subsubsection{Adding a Plan as Additional Input to the Domain}
-Adding a plan as additional input to the PO domain having the
-semantics that this plan shall be in the solution set of the TO output
-model.
-This reduces the computational complexity of the decision problem from undecidable to something decidable.
-The specific complexity class of this will have to be proven in further work.
-% I assume the resulting problem is PSPACE-complete, but
-
-% References and End of Paper
-% These lines must be placed at the end of your paper
-\bibliography{bib}
-\end{document}
-
-\begin{document}\\
-\maketitle\\
-...\\
-\bibliography{bib}\\
-\end{document}\\
-
-\end{document}

### 2022-11-23 paper/paper-mainfile.tex

@@
 \pdfinfo{
-/Title (Transforming Partially Ordered HTN Problems to Totally Ordered)
+/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
+Planning Problems is Half the Job (to Getting them Solved More Efficiently))
 /Author (Anonymous)
@@
 \iffalse
-\title{Transforming Partially Ordered HTN Problems to Totally Ordered}
+\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
+	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
 \author {
@@
 
-\title{Transforming Partially Ordered HTN Problems to Totally Ordered}
+\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
+	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
 

### 2022-11-24 paper/paper-mainfile.tex
back to cycle-break

--- 2022-11-21 paper/paper-mainfile.tex
@@
 \section{Inference of Preconditions and Effects}
-The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.
+The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
+We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
 
-\subsection{Simple Inference of Preconditions and Effects for Compound Tasks}
-For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
+\subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
+In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
+Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
+
+E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
+If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
+This is true for all possible tasks by simple induction over the decomposition process.
+
+Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
+
+Specifically, let $\sigma$ be the set of parameters for the method.
+Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
+Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
+
+Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
+For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
+% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
+
+This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
+The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
+Only one linearized lifted method per partially-ordered lifted method is produced.
+
+For a grounded method, there are no parameters in a task or method.
+Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
+We can then use these to produce a linearized grounded method per grounded method.
+
+In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
 $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
@@
 
-\subsection{Complex Inference of Effects for Compound Tasks}
+\subsection{Complex Inference of Effects for Compound Tasks (for Grounded Domain) }
 The work by~\cite{ConnyPreEstimation}, details a way to infer a subset of the mandatory preconditions and effects.
@@
 So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
+if $E(c) \neq \emptyset$ and $prec(c) := undef$ otherwise.
 
@@
 with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-
-relaxed variant of D.
+Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
 
 There exists a polynomial-time algorithm for inferring the precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
+In this paper, we will be utilizing the precondition-relaxed possible effects, which guaranteed to hold after at least one refinement of c.
 
-\subsection{Inference of Preconditions and Effects for Lifted Domain}
-In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
-Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
+%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
+%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
+%f ∈ prec(ai) and there does not exist an action aj with
+%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
+%The exploitation of the relaxed preconditions and effects
+%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates
 
-E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
-If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
-This is true for all possible tasks by simple induction over the decomposition process.
+\section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}
 
-Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-Specifically, let $\sigma$ be the set of parameters for the method.
-Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
-Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
-
-Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
-For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
-% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
-
-This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
-The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
-For variant 1, only one linearized lifted method per partially-ordered lifted method is produced.
-
-\section{Linearization Using Inferred Preconditions and Effects}
-\begin{algorithm}
-	\caption{Linearization using inferred set of preconditions and effects} %\caption{Calculation of linearized methods}
+\begin{algorithm}[h]
+	\caption{Calculation of linearized methods}
 	\label{alg:Algorithm1}
@@
 	{
-
 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-
-		$G \gets$ calculateTransitiveClosure($\singlePrec$) \\
+		$G \gets \singlePrec$ \\
 		\label{alg:StartBuildGraph}
@@
 				\For{$t' \in T_m$}{
-					if $a \in \AddS(t)$ and $a \in \PreS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$  \\ 
-					if $a \in \AddS(t)$ and $a \in \DelS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \PreS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \AddS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$ \\  
+					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
+					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
+					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
+					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
 				}
@@
 		}	
+		\label{alg:StartCycleBreak}
+		\While{$G$ has cycles in it}{
+			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
+		}
+		\label{alg:EndCycleBreak}
+		$\prec'$ = Any linearization of $G$ \\
 		\label{alg:TopSort}
-		$\singlePrec'\gets$ any linearization of $G$ \\
-		$m' = (tasks(m), \singlePrec', \alpha(t))$ \\
+		$m' = (tasks(m), \prec', \alpha(t))$ \\
 		$M' = M' \cup  \{m'\}$ \\
+
 	}
@@
 
-\subsection{Theoretical Properties If Using Simple Inference}
 \begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
+	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
 \end{theorem}
@@
 
-	The Floyd-warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
+	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
 
@@
 Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree.
-This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
+This is obviously polynomial in terms of $|T|$.
+%This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
 This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
@@
 
+	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.
+
 	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
@@
 
-	So in total the main algorithm takes: \newline
-	$(|M| * |T|^3)$ +          % Floyd-Warshall
-	$(|M| * |F| * |T|)$  +    % GetPreEff
-	$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
-	$(|M| * |T|)$        % topological sort
+	So the algorithm takes polynomial time.
+	%So in total the main algorithm takes: \newline
+	%$(|M| * |T|^3)$ +          % Floyd-Warshall
+	%$(|M| * |F| * |T|)$  +    % GetPreEff
+	%$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
+	%$(|M| * |T|)$        % topological sort
 \end{proof}
 
+\subsection{Theoretical Properties If Using Simple Inference (for Grounded Or Lifted)}
 \begin{theorem}\label{thm:Soundness}
@@
 
-\subsection{Performance of Simple Linearization}
+\begin{table*}[h]
+	\centering
+	\subcaption{Coverage achieved, using Simple Inference on Grounded (Linearized) Problem}
+	\scalebox{1} {
+	\begin{tabular}{lccccccccccccccccl} 
+	\toprule 
+	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
+	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
+	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
+	\midrule 
+	Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 &\multicolumn{2}{c}{ \textbf{9.0}  } \\ 
+	Monroe Fully Observ.$^{2}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & 15.0 &\multicolumn{2}{c}{ \textbf{16.0}  } \\ 
+	Monroe Part. Observ.$^{2}$ & 24 & \textbf{14.0} & \textbf{14.0} & \textbf{7.0} & \textbf{7.0} & 14.0 & \textbf{15.0} & \textbf{10.0} &\multicolumn{2}{c}{ \textbf{10.0}  } \\ 
+	PCP$^{17}$ & 17 & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
+	Rover & 20 & 6.0 & \textbf{20.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{19.0} & 4.0 &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
+	Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 &\multicolumn{2}{c}{ \textbf{25.0}  } \\  
+	Transport & 40 & 12.0 & \textbf{28.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 &\multicolumn{2}{c}{ \textbf{12.0}  } \\ 
+	UM-Translog$^{1}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ \textbf{22.0}  } \\ 
+	Woodworking$^{2}$ & 30 & 13.0 & \textbf{19.0} & 7.0 & \textbf{15.0} & 12.0 & \textbf{20.0} & 9.0 &\multicolumn{2}{c}{ \textbf{15.0}  } \\ 
+	\midrule 
+	Monroe & 100 & 96.0 & \textbf{100.0} & 79.0 & \textbf{88.0} & 92.0 & \textbf{100.0} & 81.0 &\multicolumn{2}{c}{ \textbf{90.0}  } \\ 
+	SmartPhone$^{1}$ & 7 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
+	Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
+	\midrule 
+	Coverage & 335 & 239.0 & \textbf{287.0} & 188.0 & \textbf{232.0} & 231.0 & \textbf{274.0} & 198.0 &\multicolumn{2}{c}{ \textbf{237.0}  } \\ 
+	Norm. coverage & 12 & 8.22 & \textbf{9.95} & 6.85 & \textbf{8.46} & 8.0 & \textbf{9.63} & 7.1 &\multicolumn{2}{c}{ \textbf{8.44}  } \\ 
+	\bottomrule 
+	\end{tabular}
+	}
+\end{table*}
+
+		%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
+%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
+%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
+%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
+%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
+%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
+%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
 
 \begin{table*}[h]
+	\centering
+	\caption{IPC score achieved, using Simple Inference, on Grounded Problems}
 	\scalebox{1} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
+\begin{tabular}{lccccccccccccccccl} 
 	\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
+	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
+	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
+	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
 	\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
+	Barman-BDI & 1 & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.36} & 0.05 &\multicolumn{2}{c}{ \textbf{0.22}  } \\ 
+	Monroe Fully Observ.$^{2}$ & 1 & \textbf{0.56} & 0.45 & \textbf{0.31} & 0.3 & \textbf{0.46} & 0.41 & \textbf{0.22} &\multicolumn{2}{c}{ 0.18  } \\ 
+	Monroe Part. Observ.$^{2}$ & 1 & \textbf{0.31} & 0.25 & \textbf{0.13} & 0.11 & \textbf{0.31} & 0.26 & \textbf{0.17} &\multicolumn{2}{c}{ 0.14  } \\ 
+	PCP$^{17}$ & 1 & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ \textbf{0.82}  } \\ 
+	Rover & 1 & 0.29 & \textbf{0.95} & 0.14 & \textbf{0.52} & 0.2 & \textbf{0.78} & 0.16 &\multicolumn{2}{c}{ \textbf{0.48}  } \\ 
+	Satellite & 1 & 0.91 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 &\multicolumn{2}{c}{ \textbf{0.99}  } \\ 
+	Transport & 1 & 0.24 & \textbf{0.61} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 &\multicolumn{2}{c}{ \textbf{0.2}  } \\ 
+	UM-Translog$^{1}$ & 1 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
+	Woodworking$^{2}$ & 1 & 0.38 & \textbf{0.58} & 0.2 & \textbf{0.41} & 0.36 & \textbf{0.57} & 0.27 &\multicolumn{2}{c}{ \textbf{0.39}  } \\ 
 	\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
+	Monroe & 1 & \textbf{0.77} & 0.69 & \textbf{0.5} & 0.47 & \textbf{0.75} & 0.71 & \textbf{0.53} &\multicolumn{2}{c}{ \textbf{0.53}  } \\ 
+	SmartPhone$^{1}$ & 1 & \textbf{0.71} & \textbf{0.71} & 0.69 & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} &\multicolumn{2}{c}{ \textbf{0.71}  } \\ 
+	Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.63 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
 	\midrule 
-			Coverage \\ 
-			Norm. coverage  \\ 
+	IPC score & 12 & 7.1 & \textbf{8.4} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.9} & 5.8 &\multicolumn{2}{c}{ \textbf{6.7}  } \\
 	\bottomrule 
@@
 \begin{table*}[h]
-	\scalebox{1} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
+	\centering
+	\caption{Coverage achieved, using Simple Inference, Lifted Problems}
+\begin{tabular}{lccccccccccccccccccl} 
 	\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}} 
-			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
+	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane}\\ 
+	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  
+	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
 	\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
+	Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 & \textbf{9.0} &\multicolumn{2}{c}{ \textbf{17.0}  } \\ 
+	Monroe Fully Observ.$^{7,7,7,5,0}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{22.0} & 22.0 & \textbf{23.0} & \textbf{15.0} & \textbf{15.0} &\multicolumn{2}{c}{ 18.0  } \\ 
+	Monroe Part. Observ.$^{2,2,2,2,0}$ & 24 & \textbf{14.0} & 13.0 & \textbf{7.0} & 6.0 & \textbf{14.0} & 13.0 & \textbf{11.0} & 9.0 &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
+	PCP$^{18,18,17,17}$ & 18 & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ 0.0  } \\ 
+	Rover & 20 & 6.0 & \textbf{15.0} & 4.0 & \textbf{13.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{13.0} &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
+	Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 & \textbf{25.0} &\multicolumn{2}{c}{ \textbf{25.0}  } \\ 
+	Transport & 40 & 12.0 & \textbf{27.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 & \textbf{12.0} &\multicolumn{2}{c}{ \textbf{35.0}  } \\ 
+	UM-Translog$^{1,1,1,1,0}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ 21.0  } \\ 
+	Woodworking & 30 & \textbf{13.0} & 7.0 & \textbf{8.0} & 7.0 & \textbf{12.0} & 7.0 & \textbf{9.0} & 7.0 &\multicolumn{2}{c}{ 6.0  } \\ 
 	\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
+	Monroe & 100 & \textbf{96.0} & 92.0 & 79.0 & \textbf{87.0} & \textbf{92.0} & 90.0 & 81.0 & \textbf{89.0} &\multicolumn{2}{c}{ \textbf{100.0}  } \\ 
+	SmartPhone$^{3,3,3,3,0}$ & 7 & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} &\multicolumn{2}{c}{ 1.0  } \\ 
+	Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
 	\midrule 
-			IPC \\
+	Coverage & 336 & 240.0 & \textbf{263.0} & 190.0 & \textbf{220.0} & 231.0 & \textbf{243.0} & 199.0 & \textbf{226.0} &\multicolumn{2}{c}{ \textbf{268.0}  } \\ 
+	Norm. coverage & 12 & 8.23 & \textbf{9.45} & 6.9 & \textbf{8.12} & 8.0 & \textbf{8.83} & 7.14 & \textbf{8.18} &\multicolumn{2}{c}{ 8.58  } \\ 
 	\bottomrule 
 \end{tabular} 
-	}
 \end{table*}
 
-\subsection{Performance of Complex Linearization}
+\begin{table*}[h]
+	\centering
+	\caption{IPC score achieved, using Simple Inference, Lifted Problems}
+\begin{tabular}{lccccccccccccccccccl} 
+	\toprule 
+	&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} \\ 
+	\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  
+	& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
+	\midrule 
+	Barman-BDI & 1 & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.35} & 0.05 & \textbf{0.23} &\multicolumn{2}{c}{ \textbf{0.72}  } \\ 
+	Monroe Fully Observ.$^{7,7,7,5,0}$ & 1 & \textbf{0.56} & 0.52 & 0.32 & \textbf{0.33} & \textbf{0.47} & 0.45 & \textbf{0.22} & 0.21 &\multicolumn{2}{c}{ 0.54  } \\ 
+	Monroe Part. Observ.$^{2,2,2,2,0}$ & 1 & \textbf{0.31} & 0.28 & \textbf{0.14} & 0.13 & \textbf{0.31} & 0.29 & \textbf{0.17} & 0.16 &\multicolumn{2}{c}{ \textbf{0.63}  } \\ 
+	PCP$^{18,18,17,17}$ & 1 & \textbf{0.83} & \textbf{0.83} & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ 0.0  } \\ 
+	Rover & 1 & 0.28 & \textbf{0.61} & 0.14 & \textbf{0.49} & 0.2 & \textbf{0.56} & 0.17 & \textbf{0.42} &\multicolumn{2}{c}{ \textbf{0.97}  } \\ 
+	Satellite & 1 & 0.9 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 & \textbf{0.99} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
+	Transport & 1 & 0.24 & \textbf{0.6} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 & \textbf{0.2} &\multicolumn{2}{c}{ \textbf{0.78}  } \\ 
+	UM-Translog$^{1,1,1,1,0}$ & 1 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ 0.92  } \\ 
+	Woodworking & 1 & \textbf{0.38} & 0.23 & 0.2 & \textbf{0.23} & \textbf{0.36} & 0.23 & \textbf{0.27} & 0.23 &\multicolumn{2}{c}{ 0.2  } \\ 
+	\midrule 
+	Monroe & 1 & \textbf{0.77} & 0.74 & \textbf{0.5} & 0.47 & \textbf{0.76} & 0.73 & \textbf{0.54} & 0.51 &\multicolumn{2}{c}{ \textbf{0.96}  } \\ 
+	SmartPhone$^{3,3,3,3,0}$ & 1 & 0.71 & \textbf{1.0} & 0.69 & \textbf{0.85} & 0.71 & \textbf{0.86} & 0.71 & \textbf{0.83} &\multicolumn{2}{c}{ 0.14  } \\  
+	Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.64 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
+	\midrule 
+	IPC score & 12 & 7.1 & \textbf{8.2} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.6} & 5.8 & \textbf{6.6} &\multicolumn{2}{c}{ 7.9  } \\ 
+	\bottomrule 
+\end{tabular} 
+\end{table*}
 
 \begin{table*}[h]
-	\scalebox{1} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
+	\centering
+	\caption{Coverage achieved, using Complex Inference}
+	\scalebox{0.8} {
+\begin{tabular}{lccccccccccccccccl} 
 	\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-			& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-			& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			Coverage \\ 
-			Norm. coverage  \\ 
-			\bottomrule
 \end{tabular}  
@@
 \begin{table*}[h]
-	\scalebox{1} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
+	\centering
+	\caption{IPC score achieved, using Complex Inference}
+	\scalebox{0.9} {
+\begin{tabular}{lccccccccccccccccl} 
 	\toprule 
-			&& \multicolumn{2}{c}{  \rotatebox{80}{rc2(Add)}} & 
-			\multicolumn{2}{c}{   \rotatebox{80}{rc2(Filter)}} & 
-			\multicolumn{2}{c}{  \rotatebox{80}{rc2(FF)}}
-			& \multicolumn{2}{c}{   \rotatebox{80}{rc2(LMC)}}  
-			& \multicolumn{2}{c}{  \rotatebox{80}{HTN2SAS}}
-& \multicolumn{2}{c}{  \rotatebox{80}{HyperTensioN}}
-& \multicolumn{2}{c}{  \rotatebox{80}{Lilotane}} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			IPC \\
-			\bottomrule
 \end{tabular}

### 2022-11-25 paper/paper-mainfile.tex
Added (partial) literal comparision, re-arranged tables, proof incl. poss eff, removed guaranteed effects definition

@@
 
-\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{poss-eff^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{poss-eff^{-}_{*}}}}
+%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
+%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
+\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
+\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}
 
-\newcommand{\RelEffPlus} {\ensuremath{\mathit{eff^{\emptyset +}_{*}}}}
-\newcommand{\RelEffMinus} {\ensuremath{\mathit{eff^{\emptyset -}_{*}}}}
+%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
+%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
 \newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
@@
 We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
+This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.
 
@@
 So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-if $E(c) \neq \emptyset$ and $prec(c) := undef$ otherwise.
+if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
 
-State-independent positive and negative effects (cf. their
-Def. 4) of a compound task c are facts that are added or
-deleted, resp., by the successful execution of a refinement of
-c, independent of the state in which the task is executed, i.e.
-$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
+%State-independent positive and negative effects (cf.
+their Def.
+4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
+%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
+%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
 
@@
 after every refinement of c but after at least one:
-$$ \RelPossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-$$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-if $E(c) \neq \emptyset$ and $prec(c) := undef$ otherwise.
+$$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
+$$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
+if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
 
@@
 with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
 
-There exists a polynomial-time algorithm for inferring the precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
-In this paper, we will be utilizing the precondition-relaxed possible effects, which guaranteed to hold after at least one refinement of c.
+Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
+This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
+the precondition relaxation can make further refinements executable that produce
+effects that can not be achieved in the non-relaxed domain. 
+In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
+
+There exists a polynomial-time algorithm for inferring the mandatory preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
+In this paper, we will be utilising both of these, as seen in the next section.
+%the precondition-relaxed possible effects, which may hold after at least one refinement of c.
 
@@
 
-\subsection{Theoretical Properties If Using Simple Inference (for Grounded Or Lifted)}
 \begin{theorem}\label{thm:Soundness}
@@
 
+% The exploitation of the relaxed preconditions and effects
+% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.
+
 \begin{description}
-	\item[Linearization Criteria] If the linearization process does not find a desired ordering contradicting the existing ones for some method, that method is said to meet the linearization criteria.
+	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, (i.e.\ nothing needs to be removed when cycle-breaking) that method is said to meet the linearization criteria.
 	If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well. 
 \end{description}
-We will now see that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} this criterion is met.
+
+We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.
+
+%\textit{Note that this criteria does not apply if using preconditions and guaranteed effects from complex inference}, as those are a \emph{subset} of possible preconditions and effects -- and thus there may be other, unknown effects that impact the executability of the sequence produced by Algorithm~\ref{alg:Algorithm1}.
+
+%Specifically, unknown mandatory delete effects may render the chose linearization un-executable. Otherwise, it is notable that mandatory effects all occur in the state.
+
+%On the other hand possible preconditions and effects - if they never occur, that's also a problem the PO version has to deal with.
 
@@
 Re-runs use panda$_{\pi}$ with the best heuristic(Add).
-We test both Complex and Simple Inference for linearization. %The comparison is done for grounded linearization variant and the lifted linearization variant 1.
+We test both Complex and Simple Inference for linearization.
 
-\begin{table*}[h]
+The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
+As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
+The planner that has achieved the highest overall coverage and IPC score is ? planner.
+
+%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}
+
+Unfortunately, when using simple inference, there are very few problems for which all partially ordered methods are linearized without conflict.
+Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
+Figure~\ref{fig:ProblemsLinearizedWOCycleBreak} shows the comparison between the two.
+
+%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
+%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
+%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
+%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
+%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
+%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
+%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
+
+\begin{table*}
 	\centering
-	\subcaption{Coverage achieved, using Simple Inference on Grounded (Linearized) Problem}
-	\scalebox{1} {
+	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
+	\label{table:GroundedSimpleCoverage}
+	\scalebox{0.8} {
 		\begin{tabular}{lccccccccccccccccl} 
@@
 
-		%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
-
-\begin{table*}[h]
+\begin{table*}
 	\centering
-	\caption{IPC score achieved, using Simple Inference, on Grounded Problems}
-	\scalebox{1} {
+	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
+	\label{table:GroundedSimpleIPC}
+	\scalebox{0.85} {
 		\begin{tabular}{lccccccccccccccccl} 
@@
 
-\begin{table*}[h]
+\begin{table*}
 	\centering
-	\caption{Coverage achieved, using Simple Inference, Lifted Problems}
+	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
+	\label{table:LiftedSimpleCoverage}
+	\scalebox{0.7} {
 		\begin{tabular}{lccccccccccccccccccl} 
@@
 		\end{tabular} 
+	}
 \end{table*}
 
-\begin{table*}[h]
+\begin{table*}
 	\centering
-	\caption{IPC score achieved, using Simple Inference, Lifted Problems}
+	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
+	\label{table:LiftedSimpleIPC}
+	\scalebox{0.7} {
 		\begin{tabular}{lccccccccccccccccccl} 
@@
 		\end{tabular} 
+	}
 \end{table*}
 
-\begin{table*}[h]
+\begin{table*}
 	\centering
 	\caption{Coverage achieved, using Complex Inference}
+	\label{table:GroundedComplexCoverage}.
 	\scalebox{0.8} {
@@
 
-\begin{table*}[h]
+\begin{table*}
 	\centering
 	\caption{IPC score achieved, using Complex Inference}
+	\label{table:GroundedComplexIPC}.
 	\scalebox{0.9} {
@@
 
-As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-The planner that has achieved the highest overall coverage and IPC score is ? planner.
+\begin{figure*}
+	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
+	\label{fig:ProblemsLinearizedWOCycleBreak}
+	\centering
+	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
+\end{figure*}
 

### 2022-11-26 paper/paper-mainfile.tex
semi-final draft?

@@
 
-\subsection{Complex Inference of Effects for Compound Tasks (for Grounded Domain) }
-The work by~\cite{ConnyPreEstimation}, details a way to infer a subset of the mandatory preconditions and effects.
-
-\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
+\subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
+The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
+Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
 
@@
 
-There exists a polynomial-time algorithm for inferring the mandatory preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
+\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
+So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
+if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
+
+A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
+refinements (ignoring executability of the refinement) $\langle a_0 ...
+a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.
+
+There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
 In this paper, we will be utilising both of these, as seen in the next section.
@@
 
+%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.
+
+\begin{theorem} \label{thm:RelaxedPreconditions}
+	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, \emph{only if $P$, the entire problem meets the linearization criteria},
+	then we know executability-relaxed preconditions for any $c$ are indeed the only ones needed to execute any refinement of $c$.
+\end{theorem}
+\begin{proof}
+	At least in our special case, we can be assured that the executability-relaxed preconditions actually work for us.
+
+	For some method with at least two sub-tasks, $a$ and $b$,
+	the desired orderings are to put $a$ with $f \in \Add(a)$ before $a_i$ with $f \in \Pre(a_i)$.
+We're assuming no cycle-breaking, so this was actually achieved.
+If such a precondition can't be met this way, (such an $a_j$ does not exist, or the method already enforces that $b$ executes after $a_i$) by definition it must be in the executability-relaxed preconditions calculated.
+
+	Therefore, any precondition of $c$'s children that can't be met by other placing $c$'s children before it is part - \emph{so it is indeed a super-set of actual preconditions}(assuming no cycle-breaking was needed).
+
+	If even one partially ordered method did need cycle-breaking, than of course it means nothing - we may indeed need other preconditions to make refinements of $c$ executable.
+Then those results no longer hold.
+\end{proof}
+
+We use Theorem~\ref{thm:RelaxedPreconditions} as support for the following main result.
 We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.
-
-%\textit{Note that this criteria does not apply if using preconditions and guaranteed effects from complex inference}, as those are a \emph{subset} of possible preconditions and effects -- and thus there may be other, unknown effects that impact the executability of the sequence produced by Algorithm~\ref{alg:Algorithm1}.
-
-%Specifically, unknown mandatory delete effects may render the chose linearization un-executable. Otherwise, it is notable that mandatory effects all occur in the state.
-
-%On the other hand possible preconditions and effects - if they never occur, that's also a problem the PO version has to deal with.
 
@@
 	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
-We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required.
+We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required, either directly or via inheritance from parent tasks.
 This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
@@
 
-\subsection{Theoretical Properties If Using Complex Inference}
-Unfortunately, no criteria for determining if a solution is guaranteed to exist when using the second inference method, since there may always be unknown preconditions and effects in the precondition-relaxed effects.
-
 \section{Empirical Evaluation}
@@
 The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than all TO planners tested.
-%Lilotane by \cite{Lilotane} is an TOHTN solver and the IPC 2020 runner-up.
-The winner, HyperTensioN by \cite{hypertension} could not be tested due to lack of support for reading in optimisation metrics.
+Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested.
+Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.
 
@@
 Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
-Figure~\ref{fig:ProblemsLinearizedWOCycleBreak} shows the comparison between the two.
+Figure~\ref{ffig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
 
@@
 	\label{table:LiftedSimpleCoverage}
-	\scalebox{0.7} {
+	\scalebox{0.6} {
 		\begin{tabular}{lccccccccccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane}\\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
+			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} & \multicolumn{2}{c}{HyperTensioN} \\
+			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}   \cmidrule(lr){13-14} 
+			& max &PO & TO & PO & TO & PO & TO & PO &  TO  \\ 
 			\midrule 
@@
 	\label{table:LiftedSimpleIPC}
-	\scalebox{0.7} {
+	\scalebox{0.6} {
 		\begin{tabular}{lccccccccccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
+			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} & \multicolumn{2}{c}{HyperTensioN} \\ 
+			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}   \cmidrule(lr){13-14} 
+			& max &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
 			\midrule 
@@
 			\toprule 
+			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
+			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}     \cmidrule(lr){11-12} \cmidrule(lr){13-14}  
+			& max &PO & TO & PO & TO & PO & TO & PO & TO \\ 
+			\midrule 
+			Barman-BDI  \\ 
+			Monroe Fully Observ.$^{2}$   \\ 
+			Monroe Part. Observ.$^{2}$  \\ 
+			PCP$^{17}$  \\ 
+			Rover  \\ 
+			Satellite   \\  
+			Transport   \\ 
+			UM-Translog$^{1}$  \\ 
+			Woodworking$^{2}$  \\ 
+			\midrule 
+			Monroe   \\ 
+			SmartPhone$^{1}$   \\ 
+			Zenotravel   \\ 
+			\midrule 
+			Coverage  \\ 
+			Norm. coverage  \\ 
+			\bottomrule 
 		\end{tabular}  
@@
 	\label{table:GroundedComplexIPC}.
-	\scalebox{0.9} {
+	\scalebox{0.8} {
 		\begin{tabular}{lccccccccccccccccl} 
 			\toprule 
+&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
+\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}   \cmidrule(lr){11-12} \cmidrule(lr){13-14}  
+& max &PO & TO & PO & TO & PO & TO & PO & TO \\ 
+\midrule 
+Barman-BDI  \\ 
+Monroe Fully Observ.$^{2}$   \\ 
+Monroe Part. Observ.$^{2}$  \\ 
+PCP$^{17}$  \\ 
+Rover  \\ 
+Satellite   \\  
+Transport   \\ 
+UM-Translog$^{1}$  \\ 
+Woodworking$^{2}$  \\ 
+\midrule 
+Monroe   \\ 
+SmartPhone$^{1}$   \\ 
+Zenotravel   \\ 
+\midrule 
+IPC score \\
+\bottomrule 
 \end{tabular}  
@@
 
+%\begin{figure*}
+%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
+%	\label{fig:ProblemsLinearizedWOCycleBreak}
+%	\centering
+%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
+%\end{figure*}
+
 \begin{figure*}
-	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
-	\label{fig:ProblemsLinearizedWOCycleBreak}
+	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without Cycle-break for Each Domain and for Each Inference Method}
+	\label{fig:MethodsLinearizedWOCycleBreak}
 	\centering
-	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
+	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
 \end{figure*}

### 2022-11-26 paper/paper-mainfile.tex
adjust proof

@@
 \begin{description}
-	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, (i.e.\ nothing needs to be removed when cycle-breaking) that method is said to meet the linearization criteria.
+	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, or in other words, \emph{cycle-breaking} did not occur, that method is said to meet the linearization criteria.
 If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well.
@@
 \begin{proof}
-	At least in our special case, we can be assured that the executability-relaxed preconditions actually work for us.
+%	At least in the case where the linearization criteria is met for all methods, we can be assured that the executability-relaxed preconditions actually work for us.
 
 	For some method with at least two sub-tasks, $a$ and $b$,
-	the desired orderings are to put $a$ with $f \in \Add(a)$ before $a_i$ with $f \in \Pre(a_i)$.
+	the desired orderings are to put $a$ with $f \in \Add(a)$ before $b$ with $f \in \Pre(b)$.
 We're assuming no cycle-breaking, so this was actually achieved.
-If such a precondition can't be met this way, (such an $a_j$ does not exist, or the method already enforces that $b$ executes after $a_i$) by definition it must be in the executability-relaxed preconditions calculated.
+If such a precondition can't be met this way, (such an $a$ does not exist, or the method already enforces that $b$ executes before $a$) by definition it must be in the executability-relaxed preconditions calculated.
 
-	Therefore, any precondition of $c$'s children that can't be met by other placing $c$'s children before it is part - \emph{so it is indeed a super-set of actual preconditions}(assuming no cycle-breaking was needed).
+	Therefore, any precondition of $c$'s children that can't be met by placing  other children of $c$ before it is part - so it is indeed a super-set of actual preconditions, assuming no cycle-breaking was needed.
 

### 2022-11-26 paper/paper-mainfile.tex

@@
 
-\section{Related Work}
-There exist other planners that also compile POHTN problems to decidable planning classes e.g.
-the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems.
-To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.
-
-\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
-of actions has an executable linearization.
-Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions.
-That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time.
-It can also find a executable linearization for that subset in polynomial time.
-
-\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.
-\cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
-In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
-
-Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
-This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.
-Thus their results are orthogonal to ours.
-
-The paper by \cite{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
-set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
-
 \section{Hierarchical Planning Formalism}
@@
 	So the algorithm takes polynomial time. 
-	%So in total the main algorithm takes: \newline
-	%$(|M| * |T|^3)$ +          % Floyd-Warshall
-	%$(|M| * |F| * |T|)$  +    % GetPreEff
-	%$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
-	%$(|M| * |T|)$        % topological sort
 \end{proof}
@@
 	This algorithm linearizes all the methods to be totally ordered.
-Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents that are already ordered with respect to each other.
+Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents are already ordered with respect to each other.
 This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
@@
 
+\section{Related Work}
+There exist other planners that also compile POHTN problems to decidable planning classes e.g.
+the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems.
+To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.
+
+\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
+of actions has an executable linearization.
+Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions.
+That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time.
+It can also find a executable linearization for that subset in polynomial time.
+
+\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.
+\cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
+In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
+
+Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
+This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.
+Thus their results are orthogonal to ours.
+
+The paper by \cite{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
+set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
+
 \section{Future Work}

### 2022-11-27 paper/paper-mainfile.tex

@@
 \usepackage{tikz}
+\usetikzlibrary{aiplans}
+
+\scheme{SinglePrec}{0}{
+	text = {\textbf{A}},
+	pre  = {a}
+}
+
+\scheme{SingleAdd}{0}{
+	text = {\textbf{B}},
+	effs = { a}
+}
+
+\scheme{SingleDelete}{0}{
+	text = {\textbf{C}},
+	effs = { {{$\neg$}a} }
+}
+
+\scheme{PrimitiveA}{0}{
+	text = {\textbf{A}},
+	pre  = {a},
+	effs = { {{$\neg$}a}, {b} }
+}
+
+\scheme{PrimitiveB}{0}{
+	text = {\textbf{B}},
+	pre = {b},
+	effs = {{{$\neg$}b}, {c}}
+}
+
+\scheme{PrimitiveC}{0}{
+	text = {\textbf{C}},
+	pre = {c},
+	eff = {{$\neg$}c}
+}
 
@@
 
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.
+From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
+For an visual demonstration of what this algorithm is doing:
+
+ \begin{figure}[h]
+	\scalebox{0.75}{
+		\begin{subfigure}{4.5cm} 
+			\begin{tikzpicture}[auto,node distance=1.2cm,
+			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
+			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+
+			\action{first}{SingleAdd,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em 
+			};
+
+			\action{second}{SinglePrec,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {right = 4em of first} 		
+			};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(first) edge [->,bend right] node [left]  {} (second);
+			\end{tikzpicture}
+
+			\caption{B adds a fact in preconditions of A -- so B before A}
+
+		\end{subfigure}
+	}  
+	\scalebox{0.75}{
+		\begin{subfigure}{4.5cm} 
+			\begin{tikzpicture}[auto,node distance=1.2cm,
+			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
+			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+
+			\action{A}{SingleDelete,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em
+				%body = {below left = 2em and 2em of } 
+			};
+
+			\action{B}{SinglePrec,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {left = 4em of A} 
+			};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(B) edge [->,bend right] node [left]  {} (A);
+			\end{tikzpicture}
+			\caption{C deletes a fact in preconditions of A  -- so A before C}	
+		\end{subfigure}
+	}
+
+	\scalebox{0.75}{
+		\begin{subfigure}{4.5cm} 
+			\begin{tikzpicture}[auto,node distance=1.2cm,
+			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
+			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+
+			\action{A}{SingleAdd,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em
+				%body = {below left = 2em and 2em of } 
+			};
+
+			\action{B}{SingleDelete,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {left = 4em of A} 
+			};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(B) edge [->, bend right] node [left]  {} (A);
+			\end{tikzpicture}
+			\caption{B adds a fact that C deletes -- so C before B}
+		\end{subfigure}
+	} 
+\end{figure}
+
+\begin{figure}[h]
+	\scalebox{0.75}{
+		\begin{subfigure}{7cm} 
+			\begin{tikzpicture}[auto,node distance=1.2cm,
+			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
+			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+
+			\action{B}{SingleAdd,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em 
+			};
+
+			\action{A}{SinglePrec,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {right = 4em of first} 		
+			};
+
+			\action{C}{SingleDelete,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {right = 4em of second} 	
+				%body = {below left = 2em and 2em of } 
+			};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(B) edge [->,bend right] node [left]  {} (A)
+			(A) edge [->,bend right] node [left]  {} (C)
+			(C) edge [->,bend right] node [left]  {} (B);
+			\end{tikzpicture}
+
+			\caption{Resulting method ordering has a cycle}
+
+		\end{subfigure}
+	}
+
+	\scalebox{0.75}{
+		\begin{subfigure}{6cm} 
+			\begin{tikzpicture}[auto,node distance=1.2cm,
+			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
+			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+
+			\action{B}{SingleAdd,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em 
+			};
+
+			\action{A}{SinglePrec,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {right = 4em of first} 		
+			};
+
+			\action{C}{SingleDelete,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {right = 4em of second} 	
+				%body = {below left = 2em and 2em of } 
+			};
+
+			\path[every node/.style={font=\sffamily\small}]
+			(B) edge [->,bend right] node [left]  {} (A)
+		%	(A) edge [->,bend right] node [left]  {} (C)
+			(C) edge [->,bend right] node [left]  {} (B);
+			\end{tikzpicture}
+
+			\caption{Delete any random ordering to break it}
+		\end{subfigure}
+	}  
+\end{figure}
 
@@
 	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
+	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
 \end{theorem}
@@
 
-We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} configured to use to turn the problem into a classical planning problem (in RC model), and Greedy best first search with visited lists.
-We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}.
+We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
+This is when it's configured to turn the problem into a classical planning problem (in RC model), and Greedy best first search, using FF by \cite{FF}, and using visited lists.
+The visited lists use task sequence hashing, visited checking with task sequences which makes totally-ordered visited lists incomplete (with order), layer hashing, order pairs hashing, no optimisation for parallel sequences,  GI-complete equivalence checking for
+partially ordered task networks (with GI-complete checking).
+
+\todo{Most notably, note that TO problems allow for other visited list
+	configurations than PO problems. So we should also use a TO
+	configuration there (this is however not reported)}
+
+We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
+%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
 We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
 The same setting is used for re-runs.
+For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
 We also test the latest version of TOHTN planners HTN2SAS, HyperTensioN and Lilotane on the transformed problems.
@@
 As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-The planner that has achieved the highest overall coverage and IPC score is ? planner.
+
+The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.
+
+For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
+the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem.
+For each total-order planner, the column beneath it shows performance on the linearized problem.
+The IPC score has a maximum of 1 per domain, for the 12 domains in total.
 
@@
 Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
-Figure~\ref{ffig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
+%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
 
@@
 %		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
-
-\begin{table*}
+\begin{table}
 	\centering
@@
 	\scalebox{0.8} {
-		\begin{tabular}{lccccccccccccccccl} 
+\begin{tabular}{lccccccl} 
 	\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
+	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
+	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
+	&PO & TO &PO & TO\\  
 	\midrule 
-			Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 &\multicolumn{2}{c}{ \textbf{9.0}  } \\ 
-			Monroe Fully Observ.$^{2}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & 15.0 &\multicolumn{2}{c}{ \textbf{16.0}  } \\ 
-			Monroe Part. Observ.$^{2}$ & 24 & \textbf{14.0} & \textbf{14.0} & \textbf{7.0} & \textbf{7.0} & 14.0 & \textbf{15.0} & \textbf{10.0} &\multicolumn{2}{c}{ \textbf{10.0}  } \\ 
-			PCP$^{17}$ & 17 & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
-			Rover & 20 & 6.0 & \textbf{20.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{19.0} & 4.0 &\multicolumn{2}{c}{ \textbf{14.0}  } \\ 
-			Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 &\multicolumn{2}{c}{ \textbf{25.0}  } \\  
-			Transport & 40 & 12.0 & \textbf{28.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 &\multicolumn{2}{c}{ \textbf{12.0}  } \\ 
-			UM-Translog$^{1}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ \textbf{22.0}  } \\ 
-			Woodworking$^{2}$ & 30 & 13.0 & \textbf{19.0} & 7.0 & \textbf{15.0} & 12.0 & \textbf{20.0} & 9.0 &\multicolumn{2}{c}{ \textbf{15.0}  } \\ 
+	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
+	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
+	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
+	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
+	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
+	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
+	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
+	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
+	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
 			\midrule 
-			Monroe & 100 & 96.0 & \textbf{100.0} & 79.0 & \textbf{88.0} & 92.0 & \textbf{100.0} & 81.0 &\multicolumn{2}{c}{ \textbf{90.0}  } \\ 
-			SmartPhone$^{1}$ & 7 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
-			Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
+	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
+	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
+	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
 			\midrule 
-			Coverage & 335 & 239.0 & \textbf{287.0} & 188.0 & \textbf{232.0} & 231.0 & \textbf{274.0} & 198.0 &\multicolumn{2}{c}{ \textbf{237.0}  } \\ 
-			Norm. coverage & 12 & 8.22 & \textbf{9.95} & 6.85 & \textbf{8.46} & 8.0 & \textbf{9.63} & 7.1 &\multicolumn{2}{c}{ \textbf{8.44}  } \\ 
+	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
+	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
 	\bottomrule 
@@
 	}
-\end{table*}
+\end{table}
 
-\begin{table*}
+\begin{table}
 	\centering
@@
 	\scalebox{0.85} {
-		\begin{tabular}{lccccccccccccccccl} 
+	\begin{tabular}{lccccccccl} 
 	\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}  
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  } \\ 
+	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
+	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
+	& PO & TO & PO & TO  \\ 
 	\midrule 
-			Barman-BDI & 1 & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.36} & 0.05 &\multicolumn{2}{c}{ \textbf{0.22}  } \\ 
-			Monroe Fully Observ.$^{2}$ & 1 & \textbf{0.56} & 0.45 & \textbf{0.31} & 0.3 & \textbf{0.46} & 0.41 & \textbf{0.22} &\multicolumn{2}{c}{ 0.18  } \\ 
-			Monroe Part. Observ.$^{2}$ & 1 & \textbf{0.31} & 0.25 & \textbf{0.13} & 0.11 & \textbf{0.31} & 0.26 & \textbf{0.17} &\multicolumn{2}{c}{ 0.14  } \\ 
-			PCP$^{17}$ & 1 & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ \textbf{0.82}  } \\ 
-			Rover & 1 & 0.29 & \textbf{0.95} & 0.14 & \textbf{0.52} & 0.2 & \textbf{0.78} & 0.16 &\multicolumn{2}{c}{ \textbf{0.48}  } \\ 
-			Satellite & 1 & 0.91 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 &\multicolumn{2}{c}{ \textbf{0.99}  } \\ 
-			Transport & 1 & 0.24 & \textbf{0.61} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 &\multicolumn{2}{c}{ \textbf{0.2}  } \\ 
-			UM-Translog$^{1}$ & 1 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
-			Woodworking$^{2}$ & 1 & 0.38 & \textbf{0.58} & 0.2 & \textbf{0.41} & 0.36 & \textbf{0.57} & 0.27 &\multicolumn{2}{c}{ \textbf{0.39}  } \\ 
+	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\
+
+	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
+	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
+	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
+	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
+	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\
+
+	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
+	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
+	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
 	\midrule 
-			Monroe & 1 & \textbf{0.77} & 0.69 & \textbf{0.5} & 0.47 & \textbf{0.75} & 0.71 & \textbf{0.53} &\multicolumn{2}{c}{ \textbf{0.53}  } \\ 
-			SmartPhone$^{1}$ & 1 & \textbf{0.71} & \textbf{0.71} & 0.69 & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} &\multicolumn{2}{c}{ \textbf{0.71}  } \\ 
-			Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.63 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
+	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
+	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
+	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\
+
 	\midrule 
-			IPC score & 12 & 7.1 & \textbf{8.4} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.9} & 5.8 &\multicolumn{2}{c}{ \textbf{6.7}  } \\
+	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\
+
 	\bottomrule 
@@
 	\label{table:LiftedSimpleCoverage}
-	\scalebox{0.6} {
-		\begin{tabular}{lccccccccccccccccccl} 
+	\scalebox{0.65} {
+		\begin{tabular}{lccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} & \multicolumn{2}{c}{HyperTensioN} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}   \cmidrule(lr){13-14} 
-			& max &PO & TO & PO & TO & PO & TO & PO &  TO  \\ 
+			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
+			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
+			&PO & TO & PO & TO  \\ 
 			\midrule 
-			Barman-BDI & 20 & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 2.0 & \textbf{9.0} &\multicolumn{2}{c}{ \textbf{17.0}  } \\ 
-			Monroe Fully Observ.$^{7,7,7,5,0}$ & 25 & \textbf{25.0} & \textbf{25.0} & 18.0 & \textbf{22.0} & 22.0 & \textbf{23.0} & \textbf{15.0} & \textbf{15.0} &\multicolumn{2}{c}{ 18.0  } \\ 
-			Monroe Part. Observ.$^{2,2,2,2,0}$ & 24 & \textbf{14.0} & 13.0 & \textbf{7.0} & 6.0 & \textbf{14.0} & 13.0 & \textbf{11.0} & 9.0 &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
-			PCP$^{18,18,17,17}$ & 18 & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} &\multicolumn{2}{c}{ 0.0  } \\ 
-			Rover & 20 & 6.0 & \textbf{15.0} & 4.0 & \textbf{13.0} & 4.0 & \textbf{14.0} & 4.0 & \textbf{13.0} &\multicolumn{2}{c}{ \textbf{20.0}  } \\ 
-			Satellite & 25 & 24.0 & \textbf{25.0} & 22.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 24.0 & \textbf{25.0} &\multicolumn{2}{c}{ \textbf{25.0}  } \\ 
-			Transport & 40 & 12.0 & \textbf{27.0} & \textbf{2.0} & \textbf{2.0} & 13.0 & \textbf{14.0} & 7.0 & \textbf{12.0} &\multicolumn{2}{c}{ \textbf{35.0}  } \\ 
-			UM-Translog$^{1,1,1,1,0}$ & 22 & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} &\multicolumn{2}{c}{ 21.0  } \\ 
-			Woodworking & 30 & \textbf{13.0} & 7.0 & \textbf{8.0} & 7.0 & \textbf{12.0} & 7.0 & \textbf{9.0} & 7.0 &\multicolumn{2}{c}{ 6.0  } \\ 
+			Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 0.0 & \textbf{17.0}  \\ 
+			Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & 0.0 & \textbf{18.0}   \\ 
+			Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}   \\ 
+			PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 0.0 & 0.0   \\ 
+			Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & 0.0 & 20.0   \\ 
+			Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 0.0 & \textbf{25.0}   \\ 
+			Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 2.0 & \textbf{35.0}   \\ 
+			UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 0.0 & \textbf{21.0}   \\ 
+			Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
 			\midrule
-			Monroe & 100 & \textbf{96.0} & 92.0 & 79.0 & \textbf{87.0} & \textbf{92.0} & 90.0 & 81.0 & \textbf{89.0} &\multicolumn{2}{c}{ \textbf{100.0}  } \\ 
-			SmartPhone$^{3,3,3,3,0}$ & 7 & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} & 5.0 & \textbf{6.0} &\multicolumn{2}{c}{ 1.0  } \\ 
-			Zenotravel & 5 & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} &\multicolumn{2}{c}{ \textbf{5.0}  } \\ 
+			Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
+			SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 0.0 & 1.0  \\ 
+			Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & 0.0 & 5.0  \\ 
 			\midrule 
-			Coverage & 336 & 240.0 & \textbf{263.0} & 190.0 & \textbf{220.0} & 231.0 & \textbf{243.0} & 199.0 & \textbf{226.0} &\multicolumn{2}{c}{ \textbf{268.0}  } \\ 
-			Norm. coverage & 12 & 8.23 & \textbf{9.45} & 6.9 & \textbf{8.12} & 8.0 & \textbf{8.83} & 7.14 & \textbf{8.18} &\multicolumn{2}{c}{ 8.58  } \\ 
+			Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{114.0} & \textbf{268.0}  \\ 
+			Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & 1.65 & 8.58  \\ 
+			\bottomrule 
+		\end{tabular}
+
+	}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
+	\label{table:LiftedSimpleIPC}
+	\scalebox{0.7} {
+\begin{tabular}{lccccccccccl} 
+	\toprule 
+	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
+	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
+	&PO & TO & PO & TO  \\  
+	\midrule 
+	Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & 0.0 & \textbf{0.72}  \\
+
+	Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & 0.0 & 0.54   \\ 
+	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & 0.63   \\ 
+	PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.0 & 0.0   \\ 
+	Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & 0.0 & \textbf{0.97}  \\ 
+	Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.0 & \textbf{1.0}   \\ 
+	Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.22 & 0.78   \\ 
+	UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & 0.0 & 0.92   \\ 
+	Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
+	\midrule 
+	Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
+	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.0 & 0.14   \\ 
+	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.0 & 1.0   \\ 
+	\midrule 
+	IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{1.6} & \textbf{7.9}   \\ 
 	\bottomrule 
@@
 	}
-\end{table*}
+\end{table}
 
-\begin{table*}
+\begin{table}
 	\centering
-	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleIPC}
-	\scalebox{0.6} {
-		\begin{tabular}{lccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{Lilotane} & \multicolumn{2}{c}{HyperTensioN} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}   \cmidrule(lr){13-14} 
-			& max &PO & TO & PO & TO & PO & TO & PO & TO   \\ 
-			\midrule 
-			Barman-BDI & 1 & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.34} & 0.07 & \textbf{0.35} & 0.05 & \textbf{0.23} &\multicolumn{2}{c}{ \textbf{0.72}  } \\ 
-			Monroe Fully Observ.$^{7,7,7,5,0}$ & 1 & \textbf{0.56} & 0.52 & 0.32 & \textbf{0.33} & \textbf{0.47} & 0.45 & \textbf{0.22} & 0.21 &\multicolumn{2}{c}{ 0.54  } \\ 
-			Monroe Part. Observ.$^{2,2,2,2,0}$ & 1 & \textbf{0.31} & 0.28 & \textbf{0.14} & 0.13 & \textbf{0.31} & 0.29 & \textbf{0.17} & 0.16 &\multicolumn{2}{c}{ \textbf{0.63}  } \\ 
-			PCP$^{18,18,17,17}$ & 1 & \textbf{0.83} & \textbf{0.83} & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} &\multicolumn{2}{c}{ 0.0  } \\ 
-			Rover & 1 & 0.28 & \textbf{0.61} & 0.14 & \textbf{0.49} & 0.2 & \textbf{0.56} & 0.17 & \textbf{0.42} &\multicolumn{2}{c}{ \textbf{0.97}  } \\ 
-			Satellite & 1 & 0.9 & \textbf{1.0} & 0.76 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.89 & \textbf{0.99} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
-			Transport & 1 & 0.24 & \textbf{0.6} & 0.04 & \textbf{0.05} & 0.27 & \textbf{0.32} & 0.12 & \textbf{0.2} &\multicolumn{2}{c}{ \textbf{0.78}  } \\ 
-			UM-Translog$^{1,1,1,1,0}$ & 1 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} &\multicolumn{2}{c}{ 0.92  } \\ 
-			Woodworking & 1 & \textbf{0.38} & 0.23 & 0.2 & \textbf{0.23} & \textbf{0.36} & 0.23 & \textbf{0.27} & 0.23 &\multicolumn{2}{c}{ 0.2  } \\ 
-			\midrule 
-			Monroe & 1 & \textbf{0.77} & 0.74 & \textbf{0.5} & 0.47 & \textbf{0.76} & 0.73 & \textbf{0.54} & 0.51 &\multicolumn{2}{c}{ \textbf{0.96}  } \\ 
-			SmartPhone$^{3,3,3,3,0}$ & 1 & 0.71 & \textbf{1.0} & 0.69 & \textbf{0.85} & 0.71 & \textbf{0.86} & 0.71 & \textbf{0.83} &\multicolumn{2}{c}{ 0.14  } \\  
-			Zenotravel & 1 & \textbf{1.0} & \textbf{1.0} & 0.64 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.83 & \textbf{1.0} &\multicolumn{2}{c}{ \textbf{1.0}  } \\ 
-			\midrule 
-			IPC score & 12 & 7.1 & \textbf{8.2} & 5.3 & \textbf{6.7} & 7.0 & \textbf{7.6} & 5.8 & \textbf{6.6} &\multicolumn{2}{c}{ 7.9  } \\ 
-			\bottomrule 
-		\end{tabular} 
-	}
-\end{table*}
-
-\begin{table*}
-	\centering
-	\caption{Coverage achieved, using Complex Inference}
+	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
 	\label{table:GroundedComplexCoverage}.
-	\scalebox{0.8} {
+	\scalebox{0.7} {
 		\begin{tabular}{lccccccccccccccccl} 
 			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}     \cmidrule(lr){11-12} \cmidrule(lr){13-14}  
-			& max &PO & TO & PO & TO & PO & TO & PO & TO \\ 
+	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
+\cmidrule(lr){2-3} \cmidrule(lr){4-5}   
+			&PO & TO & PO & TO \\
 			\midrule 
@@
 	}
-\end{table*}
+\end{table}
 
-\begin{table*}
+\begin{table}
 	\centering
-	\caption{IPC score achieved, using Complex Inference}
+	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
 	\label{table:GroundedComplexIPC}.
-	\scalebox{0.8} {
+	\scalebox{0.7} {
 		\begin{tabular}{lccccccccccccccccl} 
 			\toprule 
-&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\ 
-\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10}   \cmidrule(lr){11-12} \cmidrule(lr){13-14}  
-& max &PO & TO & PO & TO & PO & TO & PO & TO \\ 
+	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
+\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
+ &PO & TO & PO & TO \\
 \midrule 
@@
 	}
-\end{table*}
+\end{table}
 
@@
 
-\begin{figure*}
-	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without Cycle-break for Each Domain and for Each Inference Method}
-	\label{fig:MethodsLinearizedWOCycleBreak}
-	\centering
-	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
-\end{figure*}
+%\begin{figure*}
+%	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without %Cycle-break for Each Domain and for Each Inference Method}
+%	\label{fig:MethodsLinearizedWOCycleBreak}
+%	\centering
+%	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
+%\end{figure*}
 
@@
 
-The paper by \cite{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
+The paper by \citet{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
 set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
@@
 The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, similar to the one described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-Assuming no negative preconditons, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
+Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
+% Assuming no negative preconditions, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
 The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
@@
 %Adding a Plan as Additional Input to the Domain
-Adding a plan as additional input to the PO domain having the
-semantics that this plan shall be in the solution set of the TO output
-model.
-This reduces the computational complexity of the decision problem from undecidable to something decidable.
-The specific complexity class of this will have to be proven in further work.
+%Adding a plan as additional input to the PO domain having the semantics that this plan shall be in the solution set of the TO output model.
+This reduces the computational complexity of the decision problem from undecidable.
 % I assume the resulting problem is PSPACE-complete, but this needs to be proven

### 2022-11-28 paper/paper-mainfile.tex
Conny panda results

@@
 	\scalebox{0.7} {
-		\begin{tabular}{lccccccccccccccccl} 
+
+\begin{tabular}{lccccccl} 
 	\toprule 
@@
 	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-			&PO & TO & PO & TO \\
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ.$^{2}$   \\ 
-			Monroe Part. Observ.$^{2}$  \\ 
-			PCP$^{17}$  \\ 
-			Rover  \\ 
-			Satellite   \\  
-			Transport   \\ 
-			UM-Translog$^{1}$  \\ 
-			Woodworking$^{2}$  \\ 
-			\midrule 
-			Monroe   \\ 
-			SmartPhone$^{1}$   \\ 
-			Zenotravel   \\ 
-			\midrule 
-			Coverage  \\ 
-			Norm. coverage  \\ 
+	&PO & TO &PO & TO  \\ 
+	\midrule 
+	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
+	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
+	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
+	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
+	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
+	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
+	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
+	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
+	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
+	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\
+
+	\midrule 
+	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
+	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
+	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\
+
+		\midrule 
+	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
+	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
 	\bottomrule 
@@
 	\scalebox{0.7} { 
-		\begin{tabular}{lccccccccccccccccl} 
+\begin{tabular}{lccccccl} 
 			\toprule 
@@
 		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
- &PO & TO & PO & TO \\
-\midrule 
-Barman-BDI  \\ 
-Monroe Fully Observ.$^{2}$   \\ 
-Monroe Part. Observ.$^{2}$  \\ 
-PCP$^{17}$  \\ 
-Rover  \\ 
-Satellite   \\  
-Transport   \\ 
-UM-Translog$^{1}$  \\ 
-Woodworking$^{2}$  \\ 
-\midrule 
-Monroe   \\ 
-SmartPhone$^{1}$   \\ 
-Zenotravel   \\ 
-\midrule 
-IPC score \\
+	&PO & TO  &PO & TO  \\ 
+	\midrule 
+	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\
+
+	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
+	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
+	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
+	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
+	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
+	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
+	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
+	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
+	\midrule 
+	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
+	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
+	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
+		\midrule 
+	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
 	\bottomrule 

### 2022-11-28 paper/paper-mainfile.tex
Remove all grounded problem eval on lifted planners

@@
 
-\todo{Most notably, note that TO problems allow for other visited list
-	configurations than PO problems. So we should also use a TO
-	configuration there (this is however not reported)}
+%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}
 
@@
 %The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}
+
+The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
+achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}.
+This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average.
+However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains.
+E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.
 
@@
 	\label{table:GroundedComplexCoverage}.
-	\scalebox{0.7} {
+	\scalebox{0.8} {
 
@@
 	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
+	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
 	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
@@
 	\label{table:GroundedComplexIPC}.
-	\scalebox{0.7} { 
+	\scalebox{0.8} { 
 \begin{tabular}{lccccccl} 
 			\toprule 
-		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
+		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
 		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
@@
 
+\begin{table} 
+	\centering
+	\caption{These results are from using Simple Inference.
+Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
+	\label{table:SimpleLinearizable} 
+		\scalebox{0.75} { 
+	\begin{tabular}{lcccl} 
+		\toprule 
+		&$>$ 1 subtasks & Cycle-breaking & Percentage &  \\ 
+		\midrule
+Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
+Monroe & 12127.3 & 3447.8 & 72.4  \\ 
+Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
+Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
+PCP & 12.3 & 12.3 & 0.0  \\ 
+Rover & 509.4 & 355.2 & 32.3  \\ 
+Satellite & 70.6 & 36.1 & 50.9  \\ 
+SmartPhone & 6.3 & 4.0 & 21.8  \\ 
+Transport & 1144.9 & 1144.9 & 0.0  \\ 
+UM-Translog & 1.5 & 1.5 & 0.0  \\ 
+Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
+Zenotravel & 190.2 & 99.4 & 47.0  \\ 
+		\bottomrule 
+	\end{tabular} 
+}
+\end{table}
+
+\begin{table} 
+	\centering
+	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
+	\label{table:ComplexLinearizable} 
+	\scalebox{0.75} { 
+	\begin{tabular}{lcccl} 
+		\toprule 
+		&$>$ 1 subtasks & Cycle-breaking & Percentage &  \\ 
+		\midrule
+			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
+			Monroe & 12127.3 & 216.9 & 98.2  \\ 
+			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
+			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
+			PCP & 12.3 & 4.9 & 59.8  \\ 
+			Rover & 509.4 & 134.8 & 72.4  \\ 
+			Satellite & 70.6 & 10.7 & 77.9  \\ 
+			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
+			Transport & 1144.9 & 0.0 & 100.0  \\ 
+			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
+			Woodworking & 1927.3 & 476.0 & 85.5  \\
+			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
+			\bottomrule 
+		\end{tabular} 
+		}
+\end{table}
+
 %\begin{figure*}

### 2022-11-28 paper/paper-mainfile.tex
Add lin statistics

@@
 
-Unfortunately, when using simple inference, there are very few problems for which all partially ordered methods are linearized without conflict.
-Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
+Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
+When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
 %Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
@@
 	\centering  
+	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
+	\scalebox{0.75} { 
+	\begin{tabular}{lcccl} 
+		\toprule
+		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
+		\midrule
+		SmartPhone  & 4.0                   &  1     \\
+		Transport   & 1144.9                & 40       \\
+		UM-Translog & 1.1                    & 17   \\
+		Woodworking & 2035              &   21    \\
+				\bottomrule 
+	\end{tabular} 
+	}
+\end{table}
+
+\begin{table} 
+	\centering
 	\caption{These results are from using Simple Inference.
@@
 	\label{table:SimpleLinearizable} 
-		\scalebox{0.75} { 
+		\scalebox{0.65} { 
 	\begin{tabular}{lcccl} 
 		\toprule 
-		&$>$ 1 subtasks & Cycle-breaking & Percentage &  \\ 
+		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
 		\midrule
@@
 	\label{table:ComplexLinearizable} 
-	\scalebox{0.75} { 
+	\scalebox{0.65} { 
 	\begin{tabular}{lcccl} 
 		\toprule 
-		&$>$ 1 subtasks & Cycle-breaking & Percentage &  \\ 
+		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
 		\midrule

### 2022-11-28 paper/paper-mainfile.tex

@@
 We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
-This is when it's configured to turn the problem into a classical planning problem (in RC model), and Greedy best first search, using FF by \cite{FF}, and using visited lists.
-The visited lists use task sequence hashing, visited checking with task sequences which makes totally-ordered visited lists incomplete (with order), layer hashing, order pairs hashing, no optimisation for parallel sequences,  GI-complete equivalence checking for
-partially ordered task networks (with GI-complete checking).
+This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
+The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
+
+% visited checking with task sequences makes totally-ordered visited lists incomplete (with order)
 
@@
 
+While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
+(Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
+\begin{table} 
+	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain.
+Shows Results for Both Inference Methods.}\label{}
+	\begin{tabular}{lccl} 
+		\toprule 
+		Domain & Complex & Simple &  \\ 
+		\midrule
+		Transport & 1.0 & 0.0  \\ 
+		UM-Translog & 0.8 & 0.0  \\ 
+		Satellite & 1.0 & 0.0  \\ 
+		Monroe Fully Observ. & 1.0 & 0.0  \\ 
+		Rover & 1.0 & 0.0  \\ 
+		Woodworking & 0.9 & 0.0  \\ 
+		Monroe Part. Observ. & 1.0 & 0.0  \\ 
+		PCP & 0.0 & 0.0  \\ 
+		Barman-BDI & 1.0 & 0.0  \\ 
+		SmartPhone & 0.1 & 0.1  \\ 
+		Monroe & 0.8 & 0.0  \\ 
+		Zenotravel & 1.0 & 0.0  \\ 
+		\bottomrule 
+	\end{tabular} 
+\end{table}
+
 %\begin{figure*}

### 2022-11-29 paper/02--htn.tex
some changes

For the purpose of illustrating our approach, we first present the HTN planning formalism used throughout the paper, including the grounded one and the lifted one. % The grounded HTN formalism is based on the one by \shortCite{HTNSurvey}.

\paragraph{Grounded HTN Planning} The grounded HTN planning formalism presented is based on the one by \shortCite{HTNSurvey}. A grounded HTN planning problem is a tuple $\groundProb{} = (\domain{}, tn_{I}, s_{I})$ with $\domain{} = (\lit{}, \pTasks{}, \cTasks{}, \delta, \methods{})$ being its \emph{domain}. $\lit{}$ is a set of \emph{propositions}. $\pTasks{}$ and $\cTasks{}$ are the set of \emph{primitive tasks} (also called \emph{actions}) and of \emph{compound tasks}, respectively. $\delta: \pTasks{} \to \powerSet{\lit{}} \times \powerSet{\lit{}} \times \powerSet{\lit{}}$ is a function mapping each primitive task $a \in \pTasks{}$ to its \emph{precondition}, \emph{positive effects}, and \emph{negative effects}, written $\delta(a) = (\preCond{a}, \effPos{a}, \effNeg{a})$. In particular, applying an action $a$ in some \emph{state} $s \in \powerSet{\lit{}}$ will result in a new state $s'$ with $s' = (s \setminus \effNeg{a}) \cup \effPos{a}$, written $s \to_{a} s'$, and $a$ is said to be applicable in $s$ \emph{iff} $\preCond{a} \subseteq s$. Furthermore, we say that a state $s'$ is obtained from another one $s$ by applying an action sequence $\pi = \langle a_{1} \cdots a_{n} \rangle$ in $s$, written $s \to^{\ast}_{\pi} s'$, \emph{iff} there exists a state sequence $\langle s_{0} \cdots s_{n} \rangle$ such that $s = s_{0}$, $s' = s_{n}$, and for each $1 \leq i \leq n$, $a_{i}$ is applicable in the state $s_{i - 1}$ and $s_{i - 1} \to_{a_{i}} s_{i}$.

Each compound task $c \in \cTasks{}$ is \emph{decomposed} (refined) into a \emph{task network} $tn$, which is essentially a partial order \emph{multiset} of tasks, by a \emph{method} $m = (c, tn)$. Formally speaking, a task network $tn$ is a triple $(T, \parOrd{}, \alpha)$ where $T$ is a set of identifier, $\parOrd{} \subseteq T \times T$ is a partial order defined over $T$, and $\alpha: T \to \pTasks{} \cup \cTasks{}$ is a function mapping each identifier to a task. $\methods{}$ in the domain is the set of methods. $tn_{I}$ and $s_{I} \in \powerSet{\lit{}}$ are the initial task network and the initial state, respectively.

%TODO: decomposition

A \emph{solution} to an HTN planning problem is a sequence of actions $\pi = \langle a_{1} \cdots a_{n} \rangle$ such that $s_{I} \to^{\ast}_{\pi} s$ for some state $s$, and there exists a task network $tn = (T, \parOrd{}, \alpha)$ such that $tn_{I} \Rightarrow^{\ast}_{\overline{m}} tn$ for some method sequence $\overline{m}$, and $tn$ possesses a linearization $\langle t_{1} \cdots t_{n} \rangle$ with $\alpha(t_{i}) = a_{i}$ for each $1 \leq i \leq n$. A linearization of $tn$ is a total order of $T$ that respects $\parOrd{}$.

As a special case of

### 2022-11-29 paper/paper-mainfile.tex
some changes

@@
 \begin{document}
-
+\input{00--macro.tex}
 \maketitle
@@
 \section{Introduction}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
-
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-
-Many problems might be naturally more suited to being modelled as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Where this is possible, it results in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In fact, the state-of-the-art panda$_\pi$ planner and \cite{HTN2SAS} both use a compilation to classical planning, another decidable planning class.
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
+\input{01--intro.tex}
 
 \section{Hierarchical Planning Formalism}
+\input{02--htn.tex}
+
 Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning.

### 2022-11-29 paper/paper-mainfile.tex
update hyptn

--- 2022-11-28 paper/paper-mainfile.tex
@@
 
-% visited checking with task sequences makes totally-ordered visited lists incomplete (with order)
+% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
 
@@
 %		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
+
+\todo{proven unsolvable should not be in superscripts}
+
 \begin{table}
@@
 \midrule 
-			Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 0.0 & \textbf{17.0}  \\ 
-			Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & 0.0 & \textbf{18.0}   \\ 
+Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
+Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
 Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
-			PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 0.0 & 0.0   \\ 
-			Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & 0.0 & 20.0   \\ 
-			Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 0.0 & \textbf{25.0}   \\ 
-			Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 2.0 & \textbf{35.0}   \\ 
-			UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 0.0 & \textbf{21.0}   \\ 
+PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
+Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
+Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
+Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
+UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
 Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
@@
 Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
-			SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 0.0 & 1.0  \\ 
-			Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & 0.0 & 5.0  \\ 
-			\midrule 
-			Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{114.0} & \textbf{268.0}  \\ 
-			Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & 1.65 & 8.58  \\ 
+SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
+Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
+\midrule 
+Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
+Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
 \bottomrule 
@@
 \midrule 
-	Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & 0.0 & \textbf{0.72}  \\
-
-	Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & 0.0 & 0.54   \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & 0.63   \\ 
-	PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.0 & 0.0   \\ 
-	Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & 0.0 & \textbf{0.97}  \\ 
-	Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.0 & \textbf{1.0}   \\ 
-	Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.22 & 0.78   \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & 0.0 & 0.92   \\ 
+Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
+Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
+Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
+PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
+Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
+Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
+Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
+UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
 Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
@@
 Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
-	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.0 & 0.14   \\ 
-	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.0 & 1.0   \\ 
-	\midrule 
-	IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{1.6} & \textbf{7.9}   \\ 
+SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
+Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
+\midrule 
+IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
 \bottomrule 

### 2022-11-29 paper/paper-mainfile.tex
remove unnecessary reference to HTN2SAS

@@
 Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In fact, the state-of-the-art panda$_\pi$ planner and \cite{HTN2SAS} both use a compilation to classical planning, another decidable planning class.
 In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
@@
 For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
-We also test the latest version of TOHTN planners HTN2SAS, HyperTensioN and Lilotane on the transformed problems.
+We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems.
 Re-runs use panda$_{\pi}$ with the best heuristic(Add).
 We test both Complex and Simple Inference for linearization.
+Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
 
@@
 %		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HTN2SAS}}
 %		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
@@
 
-\todo{proven unsolvable should not be in superscripts}
+%\todo{proven unsolvable should not be in superscripts}
 

### 2022-11-29 paper/paper-mainfile.tex
Update paper title

@@
 \pdfinfo{
-/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
+/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
 Planning Problems is Half the Job (to Getting them Solved More Efficiently))
+%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
+%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
 /Author (Anonymous)
@@
 \iffalse 
-\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
+%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
+%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
 \author {
@@
 
-\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
+\title{Ordering is half the battle -- Establishing Totally Ordered HTN
 	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
+
+%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
+%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
 

### 2022-11-29 paper/03--linearization-ground.tex
some high level introduction

We now introduce how to transform a general (i.e., partially ordered) grounded HTN planning problem into a totally ordered one. Given a grounded HTN planning problem, our goal is to linearize every method's task network by adding ordering constraints to them. In particular, in order to decide which ordering constraints are to be added to a task network, we want to \emph{infer} the precondition and effects of each compound task in the task network from all primitive tasks into which it can be decomposed.

The reason for doing such inference is that our intent is to let every linearized task network be able to be decomposed into at least one executable action sequence (though it is not always possible), and hence, we want to capture the state transition information about the action sequences that can be obtained from the task network. % which can be loosely acquired by inferring the preconditions and the effects of the compound tasks.

Thus, generally speaking, our linearization approach consists of two phases. The first one is to infer preconditions and effects of compound tasks, and the second one is to add ordering constraints to each method's task network according to those inferred preconditions and effects. We now elaborate these two phases in detail as follows.

\subsection{Inferring Preconditions and Effects}

### 2022-11-29 paper/paper-mainfile.tex
some high level introduction

--- 2022-11-29 paper/paper-mainfile.tex
@@
 \section{Introduction}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
-
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-
-Many problems might be naturally more suited to being modelled as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Where this is possible, it results in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In fact, the state-of-the-art panda$_\pi$ planner and \cite{HTN2SAS} both use a compilation to classical planning, another decidable planning class.
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
+\input{01--intro.tex}
 
 \section{Hierarchical Planning Formalism}
-Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning.
-There are many formalisations for HTN planning.
-The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}.
-HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning.
-TOHTN planning is a special case of POHTN planning.
-% except with the initial task network replaced by a initial compound task.
-
-A \textbf{Partially Ordered Hierarchical Planning}, also called POHTN, problem P = $(D, S_I, T_I)$
-is defined over some domain $D$, 
-has an initial state $S_I \in 2^F$, and 
-has a initial compound task $T_I$. 
-The closed world assumption also holds for HTN planning.
-
-The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
-$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
-$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
-$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.
-
-A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
-T, which is a finite set of task identifiers (ids); 
-$\singlePrec$, which is a partial order over T; and
-$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.
-
-% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
-A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
-a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
-\begin{align}
-tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
-\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
-&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
-\end{align}
-In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
-on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.
-
-A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
-tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ...
-t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ...
-\alpha(t_n) \rangle$ in $S_I$ is executable.
-
-%In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition.
-For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired.
-Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning.
-Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.
-
-\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
-%For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$.
-TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$.
-This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning.
-POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).
-
-% As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
-In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.
+\input{02--htn.tex}
 
 \section{Inference of Preconditions and Effects}
+\input{03--linearization-ground.tex}
+
 The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
@@
 \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
+
 In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
@@
 
-% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
+% visited checking with task sequences makes totally-ordered visited lists incomplete (with order)
 
@@
 %		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\ 
-
-\todo{proven unsolvable should not be in superscripts}
-
 \begin{table}
@@
 			\midrule 
-Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
+			Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & 0.0 & \textbf{17.0}  \\ 
+			Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & 0.0 & \textbf{18.0}   \\ 
 			Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}   \\ 
-PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
-Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
-Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
-UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
+			PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 0.0 & 0.0   \\ 
+			Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & 0.0 & 20.0   \\ 
+			Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & 0.0 & \textbf{25.0}   \\ 
+			Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 2.0 & \textbf{35.0}   \\ 
+			UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 0.0 & \textbf{21.0}   \\ 
 			Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
@@
 			Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
-SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
-Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
-\midrule 
-Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
-Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
+			SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 0.0 & 1.0  \\ 
+			Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & 0.0 & 5.0  \\ 
+			\midrule 
+			Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{114.0} & \textbf{268.0}  \\ 
+			Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & 1.65 & 8.58  \\ 
 			\bottomrule 
@@
 	\midrule 
-Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
-PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
-Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
-Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
-UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
+	Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & 0.0 & \textbf{0.72}  \\
+
+	Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & 0.0 & 0.54   \\ 
+	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & 0.63   \\ 
+	PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.0 & 0.0   \\ 
+	Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & 0.0 & \textbf{0.97}  \\ 
+	Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & 0.0 & \textbf{1.0}   \\ 
+	Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.22 & 0.78   \\ 
+	UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & 0.0 & 0.92   \\ 
 	Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
@@
 	Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
-SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
-Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-\midrule 
-IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
+	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.0 & 0.14   \\ 
+	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.0 & 1.0   \\ 
+	\midrule 
+	IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{1.6} & \textbf{7.9}   \\ 
 	\bottomrule 

### 2022-11-30 paper/03--linearization-ground.tex
some changes

@@
 Given a grounded HTN planning problem, our goal is to linearize every method's task network by adding ordering constraints to them.
-In particular, in order to decide which ordering constraints are to be added to a task network, we want to \emph{infer} the precondition and effects of each compound task in the task network from all primitive tasks into which it can be decomposed.
+In particular, in order to decide which ordering constraints are to be added to a task network, we want to \emph{infer} the precondition and effects of each compound task in the task network.
+% from all primitive tasks into which it can be decomposed.
 
-The reason for doing such inference is that our intent is to let every linearized task network be able to be decomposed into at least one executable action sequence (though it is not always possible), and hence, we want to capture the state transition information about the action sequences that can be obtained from the task network.
+The reason for doing such inference is that our intent is to let every linearized task network be able to be decomposed into at least one executable action sequence (though it is not always possible), and we thus want to capture the state transition information about the action sequences that can be obtained from the task network.
+In other words, we want to acquire the knowledge that for each compound task $c$ in the task network, which propositions are required so that there is an action sequence $\pi \in \seqSet{c}$ this is executable (i.e., the precondition of $c$), and which propositions will be obtained (or deleted) by applying such a $\pi$ (i.e., the effects of $c$).
 % which can be loosely acquired by inferring the preconditions and the effects of the compound tasks.
@@
 \subsection{Inferring Preconditions and Effects}
+We present two approaches for inferring preconditions and effects of compound tasks.
+The first one is a polynomial time procedure that overly \emph{approximates} a compound task $c$'s precondition and effects by collecting all propositions that are in some action's precondition (or effects) into which can be decomposed from $c$.
+The second inference approach is developed by \shortCite{ConnyPreEstimation} which can extract more precise preconditions and effects but also has higher computational complexity.
+
+For the purpose of simplicity, for every $t \in \pTasks{} \cup \cTasks{}$, we extend the previous notations to let $\preCondExt{t}$, $\effPosExt{t}$, $\effNegExt{t}$ refer to the (inferred) precondition, positive effects, and negative effects of the task $t$, respectively.
+
+\paragraph{Simple Inference} For a compound task $c$, our simple inference approach collects a proposition into $c$'s precondition (or effects) if it is in some action's precondition (or effects) into which can be decomposed from $c$.
+% In other words, the approach collects all \emph{possible} propositions that can be in the precondition and effects of a compound task. %
+Concretely, for a task $t \in \pTasks{} \cup \cTasks{}$, the inference is done inductively as follows:
+\begin{description}
+    \item[Basis:] If $t \in \pTasks{}$, $\preCondExt{t} = \preCond{t}$, $\effPosExt{t} = \effPos{t}$, and $\effNegExt{t} = \effNeg{t}$.
+    \item[Induction:] If $t \in \cTasks{}$, for each $X \in \left\{\mathtt{prec}, \mathtt{eff}^{+}, \mathtt{eff}^{-}\right\}$,
+    \begin{displaymath}
+        X(t) = \bigcup_{\substack{(t, (T, \parOrd{}, \alpha)) \in \methods{}\\t' \in T}}X(t')
+    \end{displaymath}
+\end{description}
+
+One can easily recognize that the inductive procedure can be done in polynomial time because it will terminate after visiting all methods in $\methods{}$.
+
+\paragraph{Complex Inference} Compared with the simple inference approach, the one by \shortCite{ConnyPreEstimation} extracts more accurate precondition and effects for each compound task.
+
+% TODO: maybe define a notation for the set of action sequences obtained from a compound tasks.
+In particular, while inferring the effects (positive or negative) of a compound task $c$, the approach by \shortCite{ConnyPreEstimation} can further rule out some propositions that are \emph{impossible} to occur in \emph{any} state resulting from executing an action sequence into which can be decomposed from $c$.
+That is, the effects $\effPosExt{c}$ or $\effNegExt{c}$ found by this complex approach will form a \emph{subset} of the one found by the simple inference approach described above.
+For more technical details about this approach, we refer to the authors' original work.
+
+\subsection{Linearizing Methods}
+
+Having presented the approaches for inferring preconditions and effects of compound tasks, we move on to introduce how to linearize a method's task network on top of this information.
+In particular, we could now view each compound task in the task network to be linearized as an ``action'' (because it is equipped with the inferred precondition and effects just as an action), and thus we could interpret the linearization problem as the problem of finding an executable linearization of a task network consisting solely of actions.

### 2022-11-30 paper/paper-mainfile.tex
some changes
change title

--- 2022-11-29 paper/paper-mainfile.tex
@@
 
-\title{Ordering is half the battle -- Establishing Totally Ordered HTN
+\title{Order is half of life -- Establishing Totally Ordered HTN
 	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
@@
 	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
+	\label{table:FullyLinearizedProblems}
 	\scalebox{0.75} { 
@@
 (Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
+
 \begin{table} 
 	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain.
-Shows Results for Both Inference Methods.}\label{}
+Shows Results for Both Inference Methods.}\label{table:POMethodBreak}
 	\begin{tabular}{lccl} 

### 2022-11-30 paper/03--linearization-ground.tex
some changes

@@
 
-Having presented the approaches for inferring preconditions and effects of compound tasks, we move on to introduce how to linearize a method's task network on top of this information.
-In particular, we could now view each compound task in the task network to be linearized as an ``action'' (because it is equipped with the inferred precondition and effects just as an action), and thus we could interpret the linearization problem as the problem of finding an executable linearization of a task network consisting solely of actions.
+We now move on to introduce how to linearize a method's task network.
+Bearing the inferred preconditions and effects of the compound tasks in a task network, we could phrase this task as follows.
+Given a task network $tn = (T, \parOrd{}, \alpha)$, we want to find a linearization $\langle t_{1} \cdots t_{|T|} \rangle$ of $tn$ respecting $\parOrd{}$ such that there exists a state sequence $\langle s_{1} \cdots s_{|T| - 1} \rangle$ in which $s_{1} = \effPosExt{\alpha(t_{1})}$, and for each $1 \leq i \leq |T| - 1$, $\preCondExt{t_{i + 1}} \subseteq s_{i}$ and $s_{i} \to_{\alpha(t_{i + 1})} s_{i + 1}$, namely we can view each compound task as an ``action'' and interpret the linearization problem as the problem of finding an \emph{executable} linearization of a task network consisting solely of actions.

### 2022-12-01 paper/03--linearization-ground.tex
again some changes

--- 2022-11-30 paper/03--linearization-ground.tex
@@
 
-Having presented the approaches for inferring preconditions and effects of compound tasks, we move on to introduce how to linearize a method's task network on top of this information.
-In particular, we could now view each compound task in the task network to be linearized as an ``action'' (because it is equipped with the inferred precondition and effects just as an action), and thus we could interpret the linearization problem as the problem of finding an executable linearization of a task network consisting solely of actions.
+We now move on to introduce how to linearize a method's task network.
+Bearing the inferred preconditions and effects of the compound tasks in a task network, we could formulate this task as follows.
+Given a task network $tn = (T, \parOrd{}, \alpha)$, we want to find a linearization $\langle t_{1} \cdots t_{|T|} \rangle$ of $tn$ respecting $\parOrd{}$ such that there exists a state sequence $\langle s_{1} \cdots s_{|T| - 1} \rangle$ in which $s_{1} = \effPosExt{\alpha(t_{1})}$, and for each $1 \leq i \leq |T| - 1$, $\preCondExt{t_{i + 1}} \subseteq s_{i}$ and $s_{i} \to_{\alpha(t_{i + 1})} s_{i + 1}$, namely we can view each compound task as an ``action'' and interpret linearizing a task network as the problem of finding an \emph{executable} linearization of the task network consisting solely of actions.
+
+This task is \NP{}-complete, as proved by \shortCite{Erol1996HTNComplexity}.
+Thus, under the conjecture that $\PTIME{} \neq \NP{}$, no polynomial time algorithms exist that can solve this problem precisely.
+In order to avoid high computational cost, we present here a poly-time procedure which approximates a linearization which is \emph{most likely} to be executable.
+
+One essential observation for making such an approximation is that in any executable linearization, the precondition of every task except the first one must be satisfied, i.e., in any such linearizations, the following criteria must be satisfied:
+\begin{compactenum}[1)]
+    \item if $t$ is a task that is not at the beginning of the sequence, and there is a proposition $p \in \preCondExt{t}$, then there must be a task $t'$ with $p \in \effPosExt{t'}$ placed before $t$ (because otherwise $t$'s precondition cannot be satisfied), and
+    \item for any task $t^{\ast}$ with $p \in \effNegExt{t^{\ast}}$, either
+    \begin{compactenum}[a)]
+        \item $t^{\ast}$ is placed after $t$, or
+        \item $t^{\ast}$ is ordered before some $t'$ with $p \in \effPosExt{t'}$ so that after $t^{\ast}$ deletes $p$, it can be added back by $t'$ and thus satisfies $t$'s precondition.
+% i.e., there must be a task $t'$ adding back $p$ that is placed somewhere between $t^{\ast}$ and $t$.
+    \end{compactenum}
+\end{compactenum}
+
+Thus, for linearizing a task network, we would like to add ordering constraints to enforce that the above criteria hold.
+More concretely, given a task network $tn = (T, \parOrd{}, \alpha)$ with $\parOrd{}^{+}$ being the transitive closure of $\parOrd{}$, we will add an ordering constraint $(t, t')$ with $t, t' \in T$, provided that $(t' ,t ) \notin \parOrd{}^{+}$, if there exists a proposition $p$ such that one of the following conditions holds:
+\begin{inparaenum}[1)]
+    \item $p \in \preCondExt{t}$ and $p \in \effPosExt{t'}$,
+    \item $p \in \effPosExt{t}$ and $p \in \effNegExt{t'}$, or
+    \item $p \in \effNegExt{t}$ and $p \in \preCondExt{t'}$. 
+\end{inparaenum}
+After adding all ordering constraints, we could view the tasks together with the \emph{extended} set of ordering constraints as a graph $G$ where each task is a vertex and each ordering constraint is an edge.
+A linearization can then be obtained by ordering $G$ in a \emph{topological} order.
+
+Notably, the graph $G$ might \emph{not} have a topological order because it may contain cycles.
+That is, some ordering constraints we add might conflict with each other.
+If this is the case, we \emph{randomly} remove some edges $(t, t')$ from $G$ with $(t, t') \notin \parOrd{}^{+}$ (because we \emph{cannot} violate the original ordering constraints in $tn$) until there exist no cycles.
+We call this step \emph{cycle-breaking}.
+The entire procedure is shown in Alg.~\ref{alg:Algorithm1}.
+
+% Thus, when finding such a linearization, for every task $t'$ which is not placed at the beginning and every proposition $p \in \preCondExt{t'}$, there is supposed to be another task $t$ with $p \in \effPosExt{t}$ placed before it, i.e., an ordering constraint $(t, t')$ should be added.
+Similarly, consider a task $t^{\ast}$ with $p \in \effNegExt{t^{\ast}}$ (i.e., $t^{\ast}$ deletes $p$), we would like to place it before $t$ so that after $t^{\ast}$ deletes $p$, it can be added back by $t$ which thus satisfies the precondition of $t'$.

### 2022-12-01 paper/paper-mainfile.tex
label tikz figures
some changes

--- 2022-11-29 paper/paper-mainfile.tex
@@
 \usepackage{varwidth}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 \usepackage{xcolor}
 \usepackage{booktabs} 
-\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
+% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
 \usepackage{csquotes}
@@
 \usepackage{amssymb} 
+\usepackage{mathbbol}
 \usepackage{tikz}
@@
 
-\section{Inference of Preconditions and Effects}
+\section{Linearizing Grounded HTN Problems}
 \input{03--linearization-ground.tex}
@@
 
-\begin{algorithm}[h]
-	\caption{Calculation of linearized methods}
+\begin{algorithm}
+	\input{alg-linearization.tex}
+	\caption{Lineraizing a method.}
 	\label{alg:Algorithm1}
-	\KwData{$(F, T_P, T_C, \delta, M)$}
-	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-	{
-		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-		$G \gets \singlePrec$ \\
-		\label{alg:StartBuildGraph}
-		\For{a $\in$ F}{  
-			\For{$t \in T_m$}{
-				\For{$t' \in T_m$}{
-					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-				}
-			} 
-			\label{alg:EndBuildGraph}	
-		}	
-		\label{alg:StartCycleBreak}
-		\While{$G$ has cycles in it}{
-			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-		}
-		\label{alg:EndCycleBreak}
-		$\prec'$ = Any linearization of $G$ \\
-		\label{alg:TopSort}
-		$m' = (tasks(m), \prec', \alpha(t))$ \\
-		$M' = M' \cup  \{m'\}$ \\
-
-	}
-	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
 \end{algorithm}
+
+% \begin{algorithm}[h]
+% 	\caption{Calculation of linearized methods}
+% 	\label{alg:Algorithm1}
+% 	\KwData{$(F, T_P, T_C, \delta, M)$}
+% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
+
+% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
+% 	{
+% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
+% 		$G \gets \singlePrec$ \\
+% 		\label{alg:StartBuildGraph}
+% 		\For{a $\in$ F}{  
+% 			\For{$t \in T_m$}{
+% 				\For{$t' \in T_m$}{
+% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
+% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
+% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
+% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
+% 				}
+% 			} 
+% 			\label{alg:EndBuildGraph}	
+% 		}	
+% 		\label{alg:StartCycleBreak}
+% 		\While{$G$ has cycles in it}{
+% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
+% 		}
+% 		\label{alg:EndCycleBreak}
+% 		$\prec'$ = Any linearization of $G$ \\
+% 		\label{alg:TopSort}
+% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
+% 		$M' = M' \cup  \{m'\}$ \\
+
+% 	}
+% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
+% \end{algorithm}
 

### 2022-12-02 paper/03--linearization-ground.tex
some changes

@@
 That is, some ordering constraints we add might conflict with each other.
-If this is the case, we \emph{randomly} remove some edges $(t, t')$ from $G$ with $(t, t') \notin \parOrd{}^{+}$ (because we \emph{cannot} violate the original ordering constraints in $tn$) until there exist no cycles.
+If this is the case, we \emph{randomly} remove some edges $(t, t')$ from $G$ with $(t, t') \notin \parOrd{}^{+}$ (because we must \emph{not} contradict the original ordering constraints in $tn$) until there exist no cycles.
 We call this step \emph{cycle-breaking}.
-The entire procedure is shown in Alg.~\ref{alg:Algorithm1}.
+The entire procedure for linearizing a method is summarized in Alg.~\ref{alg:Algorithm1}.
+
+\begin{algorithm}[t]
+	\input{alg-linearization.tex}
+	\caption{Lineraizing a method.}
+	\label{alg:Algorithm1}
+\end{algorithm}
+
+Lastly, in order to transform a partially ordered HTN planning problem into a totally ordered one, we could call Alg.~\ref{alg:Algorithm1} on every method in the input problem.
 

### 2022-12-15 paper/paper-mainfile.tex
some changes

--- 2022-11-30 paper/paper-mainfile.tex
@@
 	effs = { {{$\neg$}a} }
+}
+
+\scheme{SinglePrecAlt}{0}{
+	text = {\textbf{D}},
+	pre  = {a}
+}
+
+\scheme{SingleAddAlt}{0}{
+	text = {\textbf{E}},
+	effs = { a}
 }
@@
 \section{Introduction}
+\input{01--intro.tex}
 Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
@@
 \section{Hierarchical Planning Formalism}
-Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning.
-There are many formalisations for HTN planning.
-The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}.
-HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning.
-TOHTN planning is a special case of POHTN planning.
-% except with the initial task network replaced by a initial compound task.
-
-A \textbf{Partially Ordered Hierarchical Planning}, also called POHTN, problem P = $(D, S_I, T_I)$
-is defined over some domain $D$, 
-has an initial state $S_I \in 2^F$, and 
-has a initial compound task $T_I$. 
-The closed world assumption also holds for HTN planning.
-
-The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
-$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
-$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
-$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.
-
-A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
-T, which is a finite set of task identifiers (ids); 
-$\singlePrec$, which is a partial order over T; and
-$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.
-
-% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
-A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
-a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
-\begin{align}
-tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
-\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
-&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
-\end{align}
-In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
-on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.
-
-A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
-tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ...
-t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ...
-\alpha(t_n) \rangle$ in $S_I$ is executable.
-
-%In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition.
-For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired.
-Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning.
-Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.
-
-\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
-%For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$.
-TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$.
-This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning.
-POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).
-
-% As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
-In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.
-
-\section{Inference of Preconditions and Effects}
-The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
+\input{02--htn.tex}
+
+\section{Linearizing Grounded HTN Problems}
+\input{03--linearization-ground.tex}
+
+% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
 We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
@@
 
-\subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
-In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
+% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
+
+% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
 Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
 
-E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
+% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
 If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
@@
 
-Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-Specifically, let $\sigma$ be the set of parameters for the method.
+% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
+
+% Specifically, let $\sigma$ be the set of parameters for the method.
 Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
@@
 
-Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
+% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
 For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
@@
 
-This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
+% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
 The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
@@
 
-For a grounded method, there are no parameters in a task or method.
+% For a grounded method, there are no parameters in a task or method.
 Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
@@
 
-In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
+% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
+% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
 For a grounded model, $f' = f$.
 The inferred preconditions and effects for a task are then defined as below:
-\begin{align*}
-& \forall t \in T_P : \PreS(t) := \Pre(t) \\
-& \forall t \in T_P : \AddS(t) := \Add(t) \\
-& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-\end{align*}
-
-\subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
-The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
+% \begin{align*}
+% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
+% & \forall t \in T_P : \AddS(t) := \Add(t) \\
+% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
+% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
+% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
+% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
+% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
+% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
+% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
+% \end{align*}
+
+% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
+% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
 Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
@@
 
-\begin{algorithm}[h]
-	\caption{Calculation of linearized methods}
-	\label{alg:Algorithm1}
-	\KwData{$(F, T_P, T_C, \delta, M)$}
-	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-	{
-		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-		$G \gets \singlePrec$ \\
-		\label{alg:StartBuildGraph}
-		\For{a $\in$ F}{  
-			\For{$t \in T_m$}{
-				\For{$t' \in T_m$}{
-					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-				}
-			} 
-			\label{alg:EndBuildGraph}	
-		}	
-		\label{alg:StartCycleBreak}
-		\While{$G$ has cycles in it}{
-			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-		}
-		\label{alg:EndCycleBreak}
-		$\prec'$ = Any linearization of $G$ \\
-		\label{alg:TopSort}
-		$m' = (tasks(m), \prec', \alpha(t))$ \\
-		$M' = M' \cup  \{m'\}$ \\
-
-	}
-	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-\end{algorithm}
+% \begin{algorithm}[h]
+% 	\caption{Calculation of linearized methods}
+% 	\label{alg:Algorithm1}
+% 	\KwData{$(F, T_P, T_C, \delta, M)$}
+% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
+
+% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
+% 	{
+% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
+% 		$G \gets \singlePrec$ \\
+% 		\label{alg:StartBuildGraph}
+% 		\For{a $\in$ F}{  
+% 			\For{$t \in T_m$}{
+% 				\For{$t' \in T_m$}{
+% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
+% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
+% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
+% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
+% 				}
+% 			} 
+% 			\label{alg:EndBuildGraph}	
+% 		}	
+% 		\label{alg:StartCycleBreak}
+% 		\While{$G$ has cycles in it}{
+% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
+% 		}
+% 		\label{alg:EndCycleBreak}
+% 		$\prec'$ = Any linearization of $G$ \\
+% 		\label{alg:TopSort}
+% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
+% 		$M' = M' \cup  \{m'\}$ \\
+
+% 	}
+% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
+% \end{algorithm}
 
 From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
-For an visual demonstration of what this algorithm is doing:
+For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:
 
  \begin{figure}[h]
+ 	\caption{Example of Desired Additional Orderings}
+ 	\label{fig:OrderingRules}
 	\scalebox{0.75}{
@@
 \begin{figure}[h]
+	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
+	\label{fig:CycleBreaking}
 	\scalebox{0.75}{
 		\begin{subfigure}{7cm} 
+		 	\centering
+			\caption{Resulting method ordering has a cycle}
+			\label{fig:CycleBreaking1}
 			\begin{tikzpicture}[auto,node distance=1.2cm,
@@
 
-			\caption{Resulting method ordering has a cycle}
-
 		\end{subfigure}
@@
 		\begin{subfigure}{6cm} 
+		 %	\centering
+			\caption{Delete any random ordering to break it}
+			\label{fig:CycleBreaking2}
 			\begin{tikzpicture}[auto,node distance=1.2cm,
@@
 
-			\caption{Delete any random ordering to break it}
 		\end{subfigure}
 	}
+
+%	\scalebox{0.75}{
+%		\begin{subfigure}{7cm} 
+%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
+%			\label{fig:NotCycleBreaking}
+%			\begin{tikzpicture}[auto,node distance=1.2cm,
+%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
+%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
+
+%			\action{B}{SingleAddAlt,
+%				width  = 2.5em, 
+%				height = 2.5em, 
+%				pre length = 1em,
+%				eff length = 1em 
+%			};
+
+%			\action{A}{SinglePrecAlt,
+%				width  = 2.5em, 
+%				height = 2.5em, 
+%				pre length = 1em,
+%				eff length = 1em,
+%				body = {right = 4em of first} 		
+%			};
+
+%			\path[every node/.style={font=\sffamily\small}]
+%			(B) edge [->,bend right] node [left]  {} (A);
+%			\end{tikzpicture}
+
+%			\caption{Resulting method ordering has no cycle}
+%			
+%		\end{subfigure}
+%	}   
 \end{figure}

### 2022-12-15 paper/paper-mainfile.tex
some changes

@@
 
-Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-after every refinement of c but after at least one:
-$$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-$$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-The set of executability-enabling states of c is
-$E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
-The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-$R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
-
-So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-
-Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
-This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
-the precondition relaxation can make further refinements executable that produce
-effects that can not be achieved in the non-relaxed domain. 
-In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
-
-\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
+% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
+% after every refinement of c but after at least one:
+% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
+% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
+% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
+
+% The set of executability-enabling states of c is
+% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
+% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
+% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
+
+% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
+% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
+
+% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
+% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
+% the precondition relaxation can make further refinements executable that produce
+% effects that can not be achieved in the non-relaxed domain. 
+% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
+
+% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
 So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
+% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
+
+% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
 refinements (ignoring executability of the refinement) $\langle a_0 ...
@@
 
-There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
-In this paper, we will be utilising both of these, as seen in the next section.
+% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
+% In this paper, we will be utilising both of these, as seen in the next section.
 %the precondition-relaxed possible effects, which may hold after at least one refinement of c.

### 2022-12-16 paper/paper-mainfile.tex
comment intro
update TO=GBFS and PO=WA*  -- unknown weights

--- 2022-12-15 paper/paper-mainfile.tex
@@
 \usepackage{varwidth}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
 \usepackage{xcolor}
 \usepackage{booktabs} 
-% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
+\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
 \usepackage{csquotes}
@@
 \usepackage{amssymb} 
-\usepackage{mathbbol}
 \usepackage{tikz}
@@
 \begin{document}
-\input{00--macro.tex}
+
 \maketitle
@@
 \section{Introduction}
-\input{01--intro.tex}
 Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
@@
 \section{Hierarchical Planning Formalism}
-\input{02--htn.tex}
-
-\section{Linearizing Grounded HTN Problems}
-\input{03--linearization-ground.tex}
-
-% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
+Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning.
+There are many formalisations for HTN planning.
+The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}.
+HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning.
+TOHTN planning is a special case of POHTN planning.
+% except with the initial task network replaced by a initial compound task.
+
+A \textbf{Partially Ordered Hierarchical Planning}, also called POHTN, problem P = $(D, S_I, T_I)$
+is defined over some domain $D$, 
+has an initial state $S_I \in 2^F$, and 
+has a initial compound task $T_I$. 
+The closed world assumption also holds for HTN planning.
+
+The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
+$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
+$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
+$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.
+
+A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
+T, which is a finite set of task identifiers (ids); 
+$\singlePrec$, which is a partial order over T; and
+$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.
+
+% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
+A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
+a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
+\begin{align}
+tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
+\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
+&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
+\end{align}
+In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
+on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.
+
+A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
+tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ...
+t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ...
+\alpha(t_n) \rangle$ in $S_I$ is executable.
+
+%In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition.
+For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired.
+Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning.
+Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.
+
+\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
+%For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$.
+TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$.
+This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning.
+POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).
+
+% As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
+In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.
+
+\section{Inference of Preconditions and Effects}
+The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
 We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
@@
 
-% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
-
-% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
+\subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
+In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
 Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
 
-% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
+E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
 If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
@@
 
-% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-% Specifically, let $\sigma$ be the set of parameters for the method.
+Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
+
+Specifically, let $\sigma$ be the set of parameters for the method.
 Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
@@
 
-% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
+Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
 For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
@@
 
-% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
+This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
 The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
@@
 
-% For a grounded method, there are no parameters in a task or method.
+For a grounded method, there are no parameters in a task or method.
 Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
@@
 
-% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
+In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
+$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
 For a grounded model, $f' = f$.
 The inferred preconditions and effects for a task are then defined as below:
-% \begin{align*}
-% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
-% & \forall t \in T_P : \AddS(t) := \Add(t) \\
-% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-% \end{align*}
-
-% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
-% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
+\begin{align*}
+& \forall t \in T_P : \PreS(t) := \Pre(t) \\
+& \forall t \in T_P : \AddS(t) := \Add(t) \\
+& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
+& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
+& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
+& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
+& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
+& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
+& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
+\end{align*}
+
+\subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
+The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
 Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
@@
 
-% \begin{algorithm}[h]
-% 	\caption{Calculation of linearized methods}
-% 	\label{alg:Algorithm1}
-% 	\KwData{$(F, T_P, T_C, \delta, M)$}
-% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-% 	{
-% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-% 		$G \gets \singlePrec$ \\
-% 		\label{alg:StartBuildGraph}
-% 		\For{a $\in$ F}{  
-% 			\For{$t \in T_m$}{
-% 				\For{$t' \in T_m$}{
-% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-% 				}
-% 			} 
-% 			\label{alg:EndBuildGraph}	
-% 		}	
-% 		\label{alg:StartCycleBreak}
-% 		\While{$G$ has cycles in it}{
-% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-% 		}
-% 		\label{alg:EndCycleBreak}
-% 		$\prec'$ = Any linearization of $G$ \\
-% 		\label{alg:TopSort}
-% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
-% 		$M' = M' \cup  \{m'\}$ \\
-
-% 	}
-% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-% \end{algorithm}
+\begin{algorithm}[h]
+	\caption{Calculation of linearized methods}
+	\label{alg:Algorithm1}
+	\KwData{$(F, T_P, T_C, \delta, M)$}
+	\KwResult{$(F, T_P, T_C, \delta, M)$}
+
+	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
+	{
+		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
+		$G \gets \singlePrec$ \\
+		\label{alg:StartBuildGraph}
+		\For{a $\in$ F}{  
+			\For{$t \in T_m$}{
+				\For{$t' \in T_m$}{
+					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
+					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
+					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
+					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
+				}
+			} 
+			\label{alg:EndBuildGraph}	
+		}	
+		\label{alg:StartCycleBreak}
+		\While{$G$ has cycles in it}{
+			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
+		}
+		\label{alg:EndCycleBreak}
+		$\prec'$ = Any linearization of $G$ \\
+		\label{alg:TopSort}
+		$m' = (tasks(m), \prec', \alpha(t))$ \\
+		$M' = M' \cup  \{m'\}$ \\
+
+	}
+	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
+\end{algorithm}
 
@@
 	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
+		\begin{subfigure}{7cm} 
 			\begin{tikzpicture}[auto,node distance=1.2cm,
@@
 
+			\action{Del}{SingleDelete,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em 
+			};
+
 			\action{first}{SingleAdd,
@@
 				pre length = 1em,
-				eff length = 1em 
+				eff length = 1em ,
+					body = {right = 4em of Del} 
 			};
@@
 	}
+
 	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
+		\begin{subfigure}{7cm} 
 			\begin{tikzpicture}[auto,node distance=1.2cm,
@@
 
-			\action{A}{SingleDelete,
+			\action{Del}{SingleDelete,
 				width  = 2.5em, 
@@
 
-			\action{B}{SinglePrec,
+			\action{Prec}{SinglePrec,
 				width  = 2.5em, 
@@
 				eff length = 1em,
-				body = {left = 4em of A} 
+				body = {left = 4em of Del} 
+			};
+
+			\action{Add}{SingleAdd,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {left = 4em of Prec} 
 		};
@@
 			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A);
+			(Prec) edge [->,bend right] node [left]  {} (Del);
 			\end{tikzpicture}
@@
 
-			\action{A}{SingleAdd,
+			\action{Add}{SingleAdd,
 				width  = 2.5em, 
@@
 				eff length = 1em 
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SingleDelete,
+			};
+
+			\action{Prec}{SinglePrec,
 			width  = 2.5em, 
@@
 			eff length = 1em,
-				body = {left = 4em of A} 
+			body = {left = 4em of Add} 
+			};
+
+			\action{Del}{SingleDelete,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em,
+				body = {left = 4em of Prec} 
 			};
@@
 			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->, bend right] node [left]  {} (A);
+			(Del) edge [->, bend right] node [left]  {} (Add);
 			\end{tikzpicture}
@@
 
-We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
-This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
-The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
-
-% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
-
-%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}
-
-We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
-%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
+We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} on both the original and the linearized problems.
+According to \cite{holler2021loop} the best setting for solving partial-order problems is \textit{GA* FF th+gi}, and the best setting for total-order is \textit{GBFS Add th+s}.
+Both turn the problem into a classical planning problem (in RC model).
+The former uses weighted A* search \todo{confirm weight}, the FF heuristic by \cite{FF}, and visited lists.
+The latter uses Greedy best first search, Add heuristic by \cite{Add}, and visited lists.
+
+Hashing is used to speed up checks to the visited list.
+Both approaches use \textit{th}, i.e.
+uses task hash approximation (computes  a  hash  value  that  only  incorporates  information  on which task is how often in a given TN) to replace tests for task network isomorphism.
+For \textit{th+s} first hash with taskhash and then use the exact test on all TNs in the hash bucket.
+When \textit{+gi} follows, the exact test is performed in case of a hash collision.
+
+%incomplete: (GA* FF th)
+%/pandaPIengine -H "rc2(ff)" -w 2  --noLayers --noGIcheck (GA* FF oh)
+%/pandaPIengine -H "rc2(ff)" -w 2  --noLayers  (GA* FF oh+gi)
+
+%incomplete: ./pandaPIengine -H "rc2(add)" -g "none" -Q  --noLayers   --noOrderPairs   --noGIcheck  (GBFS Add th)
+%./pandaPIengine -H "rc2(add)" -g "none"  -T   --noLayers   --noOrderPairs   --noGIcheck  (GBFS Add s)
+%./pandaPIengine -H "rc2(add)" -g "none"  --noLayers   --noOrderPairs  --noGIcheck  (GBFS Add th+s)
+
 We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.

### 2022-12-16 paper/paper-mainfile.tex

--- 2022-12-15 paper/paper-mainfile.tex
@@
 
-\title{Order is half of life -- Establishing Totally Ordered HTN
-	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
+\title{``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)}
 
@@
 \section{Introduction}
-\input{01--intro.tex}
+% \input{01--intro.tex}
 Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},

### 2022-12-20 paper/04--otherLinearization.tex
...

--- 2022-12-15 paper/paper-mainfile.tex
@@
-\def\year{2022}\relax
-%File: formatting-instructions-latex-2022.tex
-%release 2022.1
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%
-% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-% \usepackage{algorithm}
-% \usepackage{algorithmic}
-% \usepackage[noend]{algpseudocode}
-
-%
-% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
-\usepackage{newfloat}
-\usepackage{listings}
-\lstset{%
-	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
-	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
-	aboveskip=0pt,belowskip=0pt,%
-	showstringspaces=false,tabsize=2,breaklines=true}
-%\floatstyle{ruled}
-%\newfloat{listing}{tb}{lst}{}
-%\floatname{listing}{Listing}
-
-%
-% user import packages
-\usepackage{amsfonts}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{paralist}
-\usepackage{todonotes}
-\usepackage{booktabs}
-\usepackage{varwidth}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{xcolor}
-\usepackage{booktabs} 
-% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
-\usepackage{csquotes}
-\usepackage{subcaption}
-\usepackage{amssymb} 
-\usepackage{mathbbol}
-\usepackage{tikz}
-\usetikzlibrary{aiplans}
-
-\scheme{SinglePrec}{0}{
-	text = {\textbf{A}},
-	pre  = {a}
-}
-
-\scheme{SingleAdd}{0}{
-	text = {\textbf{B}},
-	effs = { a}
-}
-
-\scheme{SingleDelete}{0}{
-	text = {\textbf{C}},
-	effs = { {{$\neg$}a} }
-}
-
-\scheme{SinglePrecAlt}{0}{
-	text = {\textbf{D}},
-	pre  = {a}
-}
-
-\scheme{SingleAddAlt}{0}{
-	text = {\textbf{E}},
-	effs = { a}
-}
-
-\scheme{PrimitiveA}{0}{
-	text = {\textbf{A}},
-	pre  = {a},
-	effs = { {{$\neg$}a}, {b} }
-}
-
-\scheme{PrimitiveB}{0}{
-	text = {\textbf{B}},
-	pre = {b},
-	effs = {{{$\neg$}b}, {c}}
-}
-
-\scheme{PrimitiveC}{0}{
-	text = {\textbf{C}},
-	pre = {c},
-	eff = {{$\neg$}c}
-}
-
-\nocopyright
-%
-% PDF Info Is REQUIRED.
-% For /Title, write your title in Mixed Case.
-% Don't use accents or commands. Retain the parentheses.
-% For /Author, add all authors within the parentheses,
-% separated by commas. No accents, special characters
-% or commands are allowed.
-% Keep the /TemplateVersion tag as is
-\pdfinfo{
-/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
-Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-/Author (Anonymous)
-/TemplateVersion (2022.1)
-}
-
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-% The file aaai22.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
-% Title
-
-% Your title must be in mixed case, not sentence case.
-% That means all verbs (including short verbs like be, is, using,and go),
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-% \iffalse
-
-\newtheorem{theorem}{Theorem}
-
-\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
-\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
-
-\newcommand{\Add} {\ensuremath{\mathit{add}}}
-\newcommand{\Del} {\ensuremath{\mathit{del}}}
-\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
-\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
-\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
-\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
-\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
-
-%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}
-
-%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
-%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
-\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
-\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
-
-\author {
-    Submission
-}
-\affiliations{
-    Anonymous
-}
-% \fi
-
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\iffalse 
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-\author {
-    % Authors
-    Anonymous
-
-}
-\affiliations {
-    % Affiliations
-    Anonymous
-}
-\fi
-
-\title{Order is half of life -- Establishing Totally Ordered HTN
-	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-% REMOVE THIS: bibentry
-% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
-% \usepackage{bibentry}
-% END REMOVE bibentry
-
-\begin{document}
-\input{00--macro.tex}
-\maketitle
-
-\begin{abstract} 
-HTN planning is in general undecidable, yet there exist efficient
-planning algorithms. An important subclass is that of totally ordered
-HTN planning problems. Not only is this class decidable, but also easier
-to handle algorithmically since tasks cannot interleave anymore.
-Consequently, several specialized solvers exist, and dedicated tracks at
-the International Planning Competition (IPC) in both 2020 and 2023. We
-were able to show that almost all currently existing partially ordered
-planning benchmarks can be turned into totally ordered ones without
-sacrificing solvability. Establishing totally ordered problems in a
-preprocessing technique thus allows to use planning systems, heuristics,
-pruning techniques (etc.) that are only available for totally ordered
-problems. This allows solving problems more efficiently and with
-better-informed techniques, at the (little) cost of doing a
-preprocessing technique. We show that in only a very few cases
-linearization isn't possible, and in all others establishing a total
-order pays off \emph{significantly}, thus establishing our technique as
-a significant ingredient in the state of the art for solving partially
-ordered HTN problems. As a side contribution, we identify a new class of
-decidable (EXPTIME-complete) HTN problems, namely those where our
-preprocessing technique is guaranteed to be solvability-preserving.
-\end{abstract}
-
-\section{Introduction}
-\input{01--intro.tex}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
-
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-
-Many problems might be naturally more suited to being modelled as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Where this is possible, it results in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
-
-\section{Hierarchical Planning Formalism}
-\input{02--htn.tex}
-
-\section{Linearizing Grounded HTN Problems}
-\input{03--linearization-ground.tex}
-
-% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
-We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
-This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.
-
-% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
-
-% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
-Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
-
-% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
-If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
-This is true for all possible tasks by simple induction over the decomposition process.
-
-% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-% Specifically, let $\sigma$ be the set of parameters for the method.
-Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
-Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
-
-% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
-For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
-% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
-
-% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
-The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
-Only one linearized lifted method per partially-ordered lifted method is produced.
-
-% For a grounded method, there are no parameters in a task or method.
-Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
-We can then use these to produce a linearized grounded method per grounded method.
-
-% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
-For a grounded model, $f' = f$.
-The inferred preconditions and effects for a task are then defined as below:
-% \begin{align*}
-% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
-% & \forall t \in T_P : \AddS(t) := \Add(t) \\
-% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-% \end{align*}
-
-% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
-% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
-Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
-
-%State-independent positive and negative effects (cf.
-their Def.
-4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
-%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-% after every refinement of c but after at least one:
-% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% The set of executability-enabling states of c is
-% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
-% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
-
-% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-
-% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
-% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
-% the precondition relaxation can make further refinements executable that produce
-% effects that can not be achieved in the non-relaxed domain. 
-% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
-
-% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
-refinements (ignoring executability of the refinement) $\langle a_0 ...
-a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.
-
-% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
-% In this paper, we will be utilising both of these, as seen in the next section.
-%the precondition-relaxed possible effects, which may hold after at least one refinement of c.
-
-%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
-%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
-%f ∈ prec(ai) and there does not exist an action aj with
-%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
-%The exploitation of the relaxed preconditions and effects
-%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates
-
 \section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}
 
-% \begin{algorithm}[h]
-% 	\caption{Calculation of linearized methods}
-% 	\label{alg:Algorithm1}
-% 	\KwData{$(F, T_P, T_C, \delta, M)$}
-% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-% 	{
-% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-% 		$G \gets \singlePrec$ \\
-% 		\label{alg:StartBuildGraph}
-% 		\For{a $\in$ F}{  
-% 			\For{$t \in T_m$}{
-% 				\For{$t' \in T_m$}{
-% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-% 				}
-% 			} 
-% 			\label{alg:EndBuildGraph}	
-% 		}	
-% 		\label{alg:StartCycleBreak}
-% 		\While{$G$ has cycles in it}{
-% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-% 		}
-% 		\label{alg:EndCycleBreak}
-% 		$\prec'$ = Any linearization of $G$ \\
-% 		\label{alg:TopSort}
-% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
-% 		$M' = M' \cup  \{m'\}$ \\
-
-% 	}
-% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-% \end{algorithm}
-
 From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
-For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:
+For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.
 
@@
 				eff length = 1em
-				%body = {below left = 2em and 2em of } 
 			};
@@
 				body = {right = 4em of second}
-				%body = {below left = 2em and 2em of } 
 			};
@@
 			(B) edge [->,bend right] node [left]  {} (A)
-		%	(A) edge [->,bend right] node [left]  {} (C)
 			(C) edge [->,bend right] node [left]  {} (B);
@@
 	}
-
-%	\scalebox{0.75}{
-%		\begin{subfigure}{7cm} 
-%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
-%			\label{fig:NotCycleBreaking}
-%			\begin{tikzpicture}[auto,node distance=1.2cm,
-%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-%			\action{B}{SingleAddAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em 
-%			};
-
-%			\action{A}{SinglePrecAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em,
-%				body = {right = 4em of first} 		
-%			};
-
-%			\path[every node/.style={font=\sffamily\small}]
-%			(B) edge [->,bend right] node [left]  {} (A);
-%			\end{tikzpicture}
-
-%			\caption{Resulting method ordering has no cycle}
-%			
-%		\end{subfigure}
-%	}   
 \end{figure}
-
-% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase.
-Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
-% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
-
-\section{Theoretical Properties of Linearization Result}
-
-We now discuss the implications of the above-described linearization procedure.
-
-\begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
-\end{theorem}
-\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
-	Let $|T|$ = $|T_P| + |T_C|$.
-
-	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
-
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$.
-We explore it's compound sub-tasks until we collect all primitive tasks.
-Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree.
-This is obviously polynomial in terms of $|T|$.
-%This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
-This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
-% we explore all poss (at most $|T_C|$)
-
-	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
-Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.
-
-	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.
-
-	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
-% and $\mathcal{O}(V)$ in space.
-	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
-
-	So the algorithm takes polynomial time. 
-\end{proof}
-
-\begin{theorem}\label{thm:Soundness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
-\end{theorem}
-\begin{proof}
-	The new desired orderings for a method include all of the orderings already required by the method originally.
-The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph.
-This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one.
-Any solution to the linearized problem is then obviously a solution to the original problem.
-\end{proof}
-
-\begin{theorem}\label{thm:notCompleteness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then $sol(P')$ may be empty.
-\end{theorem}
-\begin{proof}
-	This algorithm linearizes all the methods to be totally ordered.
-Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents are already ordered with respect to each other.
-This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
-Consider the simple example problem:
-	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
-	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$.
-This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution.
-	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
-	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
-Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
-	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
-\end{proof}
-
-% The exploitation of the relaxed preconditions and effects
-% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.
-
-\begin{description}
-	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, or in other words, \emph{cycle-breaking} did not occur, that method is said to meet the linearization criteria.
-If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well.
-\end{description}
-
-%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.
-
-\begin{theorem} \label{thm:RelaxedPreconditions}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, \emph{only if $P$, the entire problem meets the linearization criteria},
-	then we know executability-relaxed preconditions for any $c$ are indeed the only ones needed to execute any refinement of $c$.
-\end{theorem}
-\begin{proof}
-%	At least in the case where the linearization criteria is met for all methods, we can be assured that the executability-relaxed preconditions actually work for us.
-
-	For some method with at least two sub-tasks, $a$ and $b$,
-	the desired orderings are to put $a$ with $f \in \Add(a)$ before $b$ with $f \in \Pre(b)$.
-We're assuming no cycle-breaking, so this was actually achieved.
-If such a precondition can't be met this way, (such an $a$ does not exist, or the method already enforces that $b$ executes before $a$) by definition it must be in the executability-relaxed preconditions calculated.
-
-	Therefore, any precondition of $c$'s children that can't be met by placing other children of $c$ before it is part - so it is indeed a super-set of actual preconditions, assuming no cycle-breaking was needed.
-
-	If even one partially ordered method did need cycle-breaking, than of course it means nothing - we may indeed need other preconditions to make refinements of $c$ executable.
-Then those results no longer hold.
-\end{proof}
-
-We use Theorem~\ref{thm:RelaxedPreconditions} as support for the following main result.
-We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.
-
-\begin{theorem}\label{thm:SpecialCase}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if $P$ meets the linearization criteria and $sol(P)$ is non-empty, then $sol(P')$ will be non-empty as well.
-\end{theorem}
-\begin{proof}	
-	Assume that there exists a solution in the PO domain.
-By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain.
-Assume this sequence is $(a_0, a_1, ..., a_n)$.
-We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
-	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state.
-The action $a_k$ could only be non-executable, if one or more of its preconditions was not met.
-Assume one of these unmet preconditions is for existence of the state variable $A$.
-	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution.
-So there must exist an action $a_i$, $0 < i < n$, that will add A.
-Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree.
-So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.
-
-	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
-We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required, either directly or via inheritance from parent tasks.
-This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
-In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.
-
-	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution.
-Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
-\end{proof}
-
-There are several possible levels of \enquote{completeness} for a problem compilation.
-%\begin{enumerate}
-\begin{itemize}
-	\item all solutions remain 
-	\item at least one solution remains 
-	\item all optimal solutions remain
-	\item at least one optimal solution remains 	
-\end{itemize}
-%\end{enumerate}
-Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if linearization criteria is met.
-Otherwise, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions.
-Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.
-
-\begin{theorem}\label{thm:newClass}
-	Problems $P$ that satisfy the linearization criteria form a new class of decidable problems.
-\end{theorem}
-\begin{proof}
-	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.
-\end{proof}
-
-\section{Empirical Evaluation}
-We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems.
-All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
-The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
-Each problem has the standard IPC time limit of 30 minutes.
-Any grounding and pre-processing time needed is included as part of the 'solving' time.
-Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
-
-\subsection{Hardware and Planning Systems}
-The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested.
-Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.
-
-We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
-This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
-The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
-
-% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
-
-%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}
-
-We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
-%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
-We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
-The same setting is used for re-runs.
-For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
-We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems.
-Re-runs use panda$_{\pi}$ with the best heuristic(Add).
-We test both Complex and Simple Inference for linearization.
-Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
-
-The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
-As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-
-The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.
-
-For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
-the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem.
-For each total-order planner, the column beneath it shows performance on the linearized problem.
-The IPC score has a maximum of 1 per domain, for the 12 domains in total.
-
-%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}
-
-The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
-achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}.
-This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average.
-However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains.
-E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.
-
-Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
-When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
-%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
-
-%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
-
-%\todo{proven unsolvable should not be in superscripts}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleCoverage}
-	\scalebox{0.8} {
-\begin{tabular}{lccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO\\  
-	\midrule 
-	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
-	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
-	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
-	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
-			\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-			\midrule 
-	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
-	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleIPC}
-	\scalebox{0.85} {
-	\begin{tabular}{lccccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	& PO & TO & PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\
-
-	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
-	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\
-
-	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
-	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
-	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
-	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\
-
-	\midrule 
-	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\
-
-	\bottomrule 
-		\end{tabular} 		
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleCoverage}
-	\scalebox{0.65} {
-		\begin{tabular}{lccccccccccl} 
-			\toprule 
-			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-			&PO & TO & PO & TO  \\ 
-\midrule 
-Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
-PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
-Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
-Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
-UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
-Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
-\midrule 
-Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
-SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
-Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
-\midrule 
-Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
-Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
-\bottomrule 
-		\end{tabular}
-
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleIPC}
-	\scalebox{0.7} {
-\begin{tabular}{lccccccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
-	&PO & TO & PO & TO  \\  
-\midrule 
-Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
-PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
-Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
-Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
-UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
-Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
-\midrule 
-Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
-SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
-Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-\midrule 
-IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
-\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexCoverage}.
-	\scalebox{0.8} {
-
-\begin{tabular}{lccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
-	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
-	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\
-
-	\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
-	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\
-
-		\midrule 
-	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexIPC}.
-	\scalebox{0.8} { 
-\begin{tabular}{lccccccl} 
-			\toprule 
-		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO  &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\
-
-	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
-	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
-	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
-	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
-	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
-	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-		\midrule 
-	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
-	\bottomrule 
-\end{tabular}  
-	}
-\end{table}
-
-\begin{table} 
-	\centering  
-	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
-	\label{table:FullyLinearizedProblems}
-	\scalebox{0.75} { 
-	\begin{tabular}{lcccl} 
-		\toprule
-		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
-		\midrule
-		SmartPhone  & 4.0                   &  1     \\
-		Transport   & 1144.9                & 40       \\
-		UM-Translog & 1.1                    & 17   \\
-		Woodworking & 2035              &   21    \\
-				\bottomrule 
-	\end{tabular} 
-	}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are from using Simple Inference.
-Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
-	\label{table:SimpleLinearizable} 
-		\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
-		\midrule
-Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
-Monroe & 12127.3 & 3447.8 & 72.4  \\ 
-Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
-Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
-PCP & 12.3 & 12.3 & 0.0  \\ 
-Rover & 509.4 & 355.2 & 32.3  \\ 
-Satellite & 70.6 & 36.1 & 50.9  \\ 
-SmartPhone & 6.3 & 4.0 & 21.8  \\ 
-Transport & 1144.9 & 1144.9 & 0.0  \\ 
-UM-Translog & 1.5 & 1.5 & 0.0  \\ 
-Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
-Zenotravel & 190.2 & 99.4 & 47.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
-	\label{table:ComplexLinearizable} 
-	\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
-		\midrule
-			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
-			Monroe & 12127.3 & 216.9 & 98.2  \\ 
-			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
-			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
-			PCP & 12.3 & 4.9 & 59.8  \\ 
-			Rover & 509.4 & 134.8 & 72.4  \\ 
-			Satellite & 70.6 & 10.7 & 77.9  \\ 
-			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
-			Transport & 1144.9 & 0.0 & 100.0  \\ 
-			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
-			Woodworking & 1927.3 & 476.0 & 85.5  \\
-			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
-			\bottomrule 
-		\end{tabular} 
-		}
-\end{table}
-
-While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
-(Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
-
-\begin{table} 
-	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain.
-Shows Results for Both Inference Methods.}\label{table:POMethodBreak}
-	\begin{tabular}{lccl} 
-		\toprule 
-		Domain & Complex & Simple &  \\ 
-		\midrule
-		Transport & 1.0 & 0.0  \\ 
-		UM-Translog & 0.8 & 0.0  \\ 
-		Satellite & 1.0 & 0.0  \\ 
-		Monroe Fully Observ. & 1.0 & 0.0  \\ 
-		Rover & 1.0 & 0.0  \\ 
-		Woodworking & 0.9 & 0.0  \\ 
-		Monroe Part. Observ. & 1.0 & 0.0  \\ 
-		PCP & 0.0 & 0.0  \\ 
-		Barman-BDI & 1.0 & 0.0  \\ 
-		SmartPhone & 0.1 & 0.1  \\ 
-		Monroe & 0.8 & 0.0  \\ 
-		Zenotravel & 1.0 & 0.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-\end{table}
-
-%\begin{figure*}
-%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
-%	\label{fig:ProblemsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
-%\end{figure*}
-
-%\begin{figure*}
-%	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without %Cycle-break for Each Domain and for Each Inference Method}
-%	\label{fig:MethodsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
-%\end{figure*}
-
-\section{Related Work}
-There exist other planners that also compile POHTN problems to decidable planning classes e.g.
-the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems.
-To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.
-
-\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
-of actions has an executable linearization.
-Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions.
-That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time.
-It can also find a executable linearization for that subset in polynomial time.
-
-\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.
-\cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
-In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
-
-Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
-This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.
-Thus their results are orthogonal to ours.
-
-The paper by \citet{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
-set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
-
-\section{Future Work}
-%Encode Linearization Problem as a MAX-SAT Problem
-The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
-MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.
-
-The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-% Assuming no negative preconditions, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
-The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
-
-%Adding a Plan as Additional Input to the Domain
-%Adding a plan as additional input to the PO domain having the semantics that this plan shall be in the solution set of the TO output model.
-This reduces the computational complexity of the decision problem from undecidable.
-% I assume the resulting problem is PSPACE-complete, but this needs to be proven
-
-\section{Conclusion}
-
-% The contributions of this paper are as follows:
-
-This paper finds that, at least for the POHTN problems in the IPC domain, most of them are not undecidable.
-In other words, it is as if the POHTN domains are compressed TO domains - this linearization separates one of them back out.
-
-We can also see this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
-Furthermore, there is demonstrably much more room for improvement.
-Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
-
-This method can also be used to increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
-Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
-Then $k+m$ (lifted or grounded) TOHTN problems exist now.
-And from empirical evaluation, $k$ may be close to $n$.
-
-Finally, in this paper we identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all others discussed in other works.
-
-% Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
-\bibliography{bib}
-% \nobibliography{aaai22}
-
-\end{document}

### 2022-12-20 paper/05--theory.tex
...

--- 2022-12-15 paper/paper-mainfile.tex
@@
-\def\year{2022}\relax
-%File: formatting-instructions-latex-2022.tex
-%release 2022.1
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%
-% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-% \usepackage{algorithm}
-% \usepackage{algorithmic}
-% \usepackage[noend]{algpseudocode}
-
-%
-% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
-\usepackage{newfloat}
-\usepackage{listings}
-\lstset{%
-	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
-	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
-	aboveskip=0pt,belowskip=0pt,%
-	showstringspaces=false,tabsize=2,breaklines=true}
-%\floatstyle{ruled}
-%\newfloat{listing}{tb}{lst}{}
-%\floatname{listing}{Listing}
-
-%
-% user import packages
-\usepackage{amsfonts}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{paralist}
-\usepackage{todonotes}
-\usepackage{booktabs}
-\usepackage{varwidth}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{xcolor}
-\usepackage{booktabs} 
-% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
-\usepackage{csquotes}
-\usepackage{subcaption}
-\usepackage{amssymb} 
-\usepackage{mathbbol}
-\usepackage{tikz}
-\usetikzlibrary{aiplans}
-
-\scheme{SinglePrec}{0}{
-	text = {\textbf{A}},
-	pre  = {a}
-}
-
-\scheme{SingleAdd}{0}{
-	text = {\textbf{B}},
-	effs = { a}
-}
-
-\scheme{SingleDelete}{0}{
-	text = {\textbf{C}},
-	effs = { {{$\neg$}a} }
-}
-
-\scheme{SinglePrecAlt}{0}{
-	text = {\textbf{D}},
-	pre  = {a}
-}
-
-\scheme{SingleAddAlt}{0}{
-	text = {\textbf{E}},
-	effs = { a}
-}
-
-\scheme{PrimitiveA}{0}{
-	text = {\textbf{A}},
-	pre  = {a},
-	effs = { {{$\neg$}a}, {b} }
-}
-
-\scheme{PrimitiveB}{0}{
-	text = {\textbf{B}},
-	pre = {b},
-	effs = {{{$\neg$}b}, {c}}
-}
-
-\scheme{PrimitiveC}{0}{
-	text = {\textbf{C}},
-	pre = {c},
-	eff = {{$\neg$}c}
-}
-
-\nocopyright
-%
-% PDF Info Is REQUIRED.
-% For /Title, write your title in Mixed Case.
-% Don't use accents or commands. Retain the parentheses.
-% For /Author, add all authors within the parentheses,
-% separated by commas. No accents, special characters
-% or commands are allowed.
-% Keep the /TemplateVersion tag as is
-\pdfinfo{
-/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
-Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-/Author (Anonymous)
-/TemplateVersion (2022.1)
-}
-
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-% The file aaai22.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
-% Title
-
-% Your title must be in mixed case, not sentence case.
-% That means all verbs (including short verbs like be, is, using,and go),
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-% \iffalse
-
-\newtheorem{theorem}{Theorem}
-
-\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
-\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
-
-\newcommand{\Add} {\ensuremath{\mathit{add}}}
-\newcommand{\Del} {\ensuremath{\mathit{del}}}
-\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
-\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
-\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
-\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
-\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
-
-%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}
-
-%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
-%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
-\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
-\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
-
-\author {
-    Submission
-}
-\affiliations{
-    Anonymous
-}
-% \fi
-
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\iffalse 
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-\author {
-    % Authors
-    Anonymous
-
-}
-\affiliations {
-    % Affiliations
-    Anonymous
-}
-\fi
-
-\title{Order is half of life -- Establishing Totally Ordered HTN
-	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-% REMOVE THIS: bibentry
-% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
-% \usepackage{bibentry}
-% END REMOVE bibentry
-
-\begin{document}
-\input{00--macro.tex}
-\maketitle
-
-\begin{abstract} 
-HTN planning is in general undecidable, yet there exist efficient
-planning algorithms. An important subclass is that of totally ordered
-HTN planning problems. Not only is this class decidable, but also easier
-to handle algorithmically since tasks cannot interleave anymore.
-Consequently, several specialized solvers exist, and dedicated tracks at
-the International Planning Competition (IPC) in both 2020 and 2023. We
-were able to show that almost all currently existing partially ordered
-planning benchmarks can be turned into totally ordered ones without
-sacrificing solvability. Establishing totally ordered problems in a
-preprocessing technique thus allows to use planning systems, heuristics,
-pruning techniques (etc.) that are only available for totally ordered
-problems. This allows solving problems more efficiently and with
-better-informed techniques, at the (little) cost of doing a
-preprocessing technique. We show that in only a very few cases
-linearization isn't possible, and in all others establishing a total
-order pays off \emph{significantly}, thus establishing our technique as
-a significant ingredient in the state of the art for solving partially
-ordered HTN problems. As a side contribution, we identify a new class of
-decidable (EXPTIME-complete) HTN problems, namely those where our
-preprocessing technique is guaranteed to be solvability-preserving.
-\end{abstract}
-
-\section{Introduction}
-\input{01--intro.tex}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
-
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-
-Many problems might be naturally more suited to being modelled as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Where this is possible, it results in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
-
-\section{Hierarchical Planning Formalism}
-\input{02--htn.tex}
-
-\section{Linearizing Grounded HTN Problems}
-\input{03--linearization-ground.tex}
-
-% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
-We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
-This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.
-
-% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
-
-% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
-Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
-
-% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
-If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
-This is true for all possible tasks by simple induction over the decomposition process.
-
-% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-% Specifically, let $\sigma$ be the set of parameters for the method.
-Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
-Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
-
-% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
-For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
-% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
-
-% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
-The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
-Only one linearized lifted method per partially-ordered lifted method is produced.
-
-% For a grounded method, there are no parameters in a task or method.
-Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
-We can then use these to produce a linearized grounded method per grounded method.
-
-% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
-For a grounded model, $f' = f$.
-The inferred preconditions and effects for a task are then defined as below:
-% \begin{align*}
-% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
-% & \forall t \in T_P : \AddS(t) := \Add(t) \\
-% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-% \end{align*}
-
-% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
-% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
-Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
-
-%State-independent positive and negative effects (cf.
-their Def.
-4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
-%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-% after every refinement of c but after at least one:
-% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% The set of executability-enabling states of c is
-% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
-% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
-
-% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-
-% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
-% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
-% the precondition relaxation can make further refinements executable that produce
-% effects that can not be achieved in the non-relaxed domain. 
-% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
-
-% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
-refinements (ignoring executability of the refinement) $\langle a_0 ...
-a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.
-
-% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
-% In this paper, we will be utilising both of these, as seen in the next section.
-%the precondition-relaxed possible effects, which may hold after at least one refinement of c.
-
-%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
-%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
-%f ∈ prec(ai) and there does not exist an action aj with
-%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
-%The exploitation of the relaxed preconditions and effects
-%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates
-
-\section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}
-
-% \begin{algorithm}[h]
-% 	\caption{Calculation of linearized methods}
-% 	\label{alg:Algorithm1}
-% 	\KwData{$(F, T_P, T_C, \delta, M)$}
-% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-% 	{
-% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-% 		$G \gets \singlePrec$ \\
-% 		\label{alg:StartBuildGraph}
-% 		\For{a $\in$ F}{  
-% 			\For{$t \in T_m$}{
-% 				\For{$t' \in T_m$}{
-% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-% 				}
-% 			} 
-% 			\label{alg:EndBuildGraph}	
-% 		}	
-% 		\label{alg:StartCycleBreak}
-% 		\While{$G$ has cycles in it}{
-% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-% 		}
-% 		\label{alg:EndCycleBreak}
-% 		$\prec'$ = Any linearization of $G$ \\
-% 		\label{alg:TopSort}
-% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
-% 		$M' = M' \cup  \{m'\}$ \\
-
-% 	}
-% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-% \end{algorithm}
-
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
-For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:
-
- \begin{figure}[h]
- 	\caption{Example of Desired Additional Orderings}
- 	\label{fig:OrderingRules}
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{first}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{second}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(first) edge [->,bend right] node [left]  {} (second);
-			\end{tikzpicture}
-
-			\caption{B adds a fact in preconditions of A -- so B before A}
-
-		\end{subfigure}
-	}  
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{C deletes a fact in preconditions of A  -- so A before C}	
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->, bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{B adds a fact that C deletes -- so C before B}
-		\end{subfigure}
-	} 
-\end{figure}
-
-\begin{figure}[h]
-	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
-	\label{fig:CycleBreaking}
-	\scalebox{0.75}{
-		\begin{subfigure}{7cm} 
-		 	\centering
-			\caption{Resulting method ordering has a cycle}
-			\label{fig:CycleBreaking1}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-			(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{6cm} 
-		 %	\centering
-			\caption{Delete any random ordering to break it}
-			\label{fig:CycleBreaking2}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-		%	(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-%	\scalebox{0.75}{
-%		\begin{subfigure}{7cm} 
-%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
-%			\label{fig:NotCycleBreaking}
-%			\begin{tikzpicture}[auto,node distance=1.2cm,
-%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-%			\action{B}{SingleAddAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em 
-%			};
-
-%			\action{A}{SinglePrecAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em,
-%				body = {right = 4em of first} 		
-%			};
-
-%			\path[every node/.style={font=\sffamily\small}]
-%			(B) edge [->,bend right] node [left]  {} (A);
-%			\end{tikzpicture}
-
-%			\caption{Resulting method ordering has no cycle}
-%			
-%		\end{subfigure}
-%	}   
-\end{figure}
-
-% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase.
-Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
-% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
-
 \section{Theoretical Properties of Linearization Result}
@@
 \end{theorem}
-\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
+\begin{proof}
 	Let $|T|$ = $|T_P| + |T_C|$.
-
-	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
 
@@
 This is obviously polynomial in terms of $|T|$.
-%This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
-This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
-% we explore all poss (at most $|T_C|$)
 
@@
 	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
-% and $\mathcal{O}(V)$ in space.
 	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
@@
 
-% The exploitation of the relaxed preconditions and effects
-% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.
-
 \begin{description}
@@
 \end{description}
-
-%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.
 
@@
 \begin{proof}
-%	At least in the case where the linearization criteria is met for all methods, we can be assured that the executability-relaxed preconditions actually work for us.
 
@@
 
-There are several possible levels of \enquote{completeness} for a problem compilation.
-%\begin{enumerate}
+There are several possible levels of \emph{completeness} for a problem compilation.
 \begin{itemize}
@@
 \end{itemize}
-%\end{enumerate}
 Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if linearization criteria is met.
@@
 \end{proof}
-
-\section{Empirical Evaluation}
-We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems.
-All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
-The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
-Each problem has the standard IPC time limit of 30 minutes.
-Any grounding and pre-processing time needed is included as part of the 'solving' time.
-Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
-
-\subsection{Hardware and Planning Systems}
-The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested.
-Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.
-
-We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
-This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
-The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
-
-% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
-
-%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}
-
-We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
-%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
-We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
-The same setting is used for re-runs.
-For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
-We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems.
-Re-runs use panda$_{\pi}$ with the best heuristic(Add).
-We test both Complex and Simple Inference for linearization.
-Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
-
-The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
-As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-
-The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.
-
-For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
-the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem.
-For each total-order planner, the column beneath it shows performance on the linearized problem.
-The IPC score has a maximum of 1 per domain, for the 12 domains in total.
-
-%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}
-
-The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
-achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}.
-This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average.
-However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains.
-E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.
-
-Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
-When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
-%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
-
-%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
-
-%\todo{proven unsolvable should not be in superscripts}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleCoverage}
-	\scalebox{0.8} {
-\begin{tabular}{lccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO\\  
-	\midrule 
-	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
-	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
-	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
-	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
-			\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-			\midrule 
-	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
-	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleIPC}
-	\scalebox{0.85} {
-	\begin{tabular}{lccccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	& PO & TO & PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\
-
-	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
-	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\
-
-	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
-	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
-	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
-	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\
-
-	\midrule 
-	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\
-
-	\bottomrule 
-		\end{tabular} 		
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleCoverage}
-	\scalebox{0.65} {
-		\begin{tabular}{lccccccccccl} 
-			\toprule 
-			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-			&PO & TO & PO & TO  \\ 
-\midrule 
-Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
-PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
-Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
-Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
-UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
-Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
-\midrule 
-Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
-SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
-Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
-\midrule 
-Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
-Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
-\bottomrule 
-		\end{tabular}
-
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleIPC}
-	\scalebox{0.7} {
-\begin{tabular}{lccccccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
-	&PO & TO & PO & TO  \\  
-\midrule 
-Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
-PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
-Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
-Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
-UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
-Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
-\midrule 
-Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
-SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
-Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-\midrule 
-IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
-\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexCoverage}.
-	\scalebox{0.8} {
-
-\begin{tabular}{lccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
-	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
-	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\
-
-	\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
-	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\
-
-		\midrule 
-	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexIPC}.
-	\scalebox{0.8} { 
-\begin{tabular}{lccccccl} 
-			\toprule 
-		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO  &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\
-
-	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
-	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
-	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
-	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
-	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
-	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-		\midrule 
-	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
-	\bottomrule 
-\end{tabular}  
-	}
-\end{table}
-
-\begin{table} 
-	\centering  
-	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
-	\label{table:FullyLinearizedProblems}
-	\scalebox{0.75} { 
-	\begin{tabular}{lcccl} 
-		\toprule
-		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
-		\midrule
-		SmartPhone  & 4.0                   &  1     \\
-		Transport   & 1144.9                & 40       \\
-		UM-Translog & 1.1                    & 17   \\
-		Woodworking & 2035              &   21    \\
-				\bottomrule 
-	\end{tabular} 
-	}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are from using Simple Inference.
-Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
-	\label{table:SimpleLinearizable} 
-		\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
-		\midrule
-Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
-Monroe & 12127.3 & 3447.8 & 72.4  \\ 
-Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
-Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
-PCP & 12.3 & 12.3 & 0.0  \\ 
-Rover & 509.4 & 355.2 & 32.3  \\ 
-Satellite & 70.6 & 36.1 & 50.9  \\ 
-SmartPhone & 6.3 & 4.0 & 21.8  \\ 
-Transport & 1144.9 & 1144.9 & 0.0  \\ 
-UM-Translog & 1.5 & 1.5 & 0.0  \\ 
-Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
-Zenotravel & 190.2 & 99.4 & 47.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
-	\label{table:ComplexLinearizable} 
-	\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
-		\midrule
-			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
-			Monroe & 12127.3 & 216.9 & 98.2  \\ 
-			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
-			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
-			PCP & 12.3 & 4.9 & 59.8  \\ 
-			Rover & 509.4 & 134.8 & 72.4  \\ 
-			Satellite & 70.6 & 10.7 & 77.9  \\ 
-			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
-			Transport & 1144.9 & 0.0 & 100.0  \\ 
-			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
-			Woodworking & 1927.3 & 476.0 & 85.5  \\
-			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
-			\bottomrule 
-		\end{tabular} 
-		}
-\end{table}
-
-While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
-(Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
-
-\begin{table} 
-	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain.
-Shows Results for Both Inference Methods.}\label{table:POMethodBreak}
-	\begin{tabular}{lccl} 
-		\toprule 
-		Domain & Complex & Simple &  \\ 
-		\midrule
-		Transport & 1.0 & 0.0  \\ 
-		UM-Translog & 0.8 & 0.0  \\ 
-		Satellite & 1.0 & 0.0  \\ 
-		Monroe Fully Observ. & 1.0 & 0.0  \\ 
-		Rover & 1.0 & 0.0  \\ 
-		Woodworking & 0.9 & 0.0  \\ 
-		Monroe Part. Observ. & 1.0 & 0.0  \\ 
-		PCP & 0.0 & 0.0  \\ 
-		Barman-BDI & 1.0 & 0.0  \\ 
-		SmartPhone & 0.1 & 0.1  \\ 
-		Monroe & 0.8 & 0.0  \\ 
-		Zenotravel & 1.0 & 0.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-\end{table}
-
-%\begin{figure*}
-%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
-%	\label{fig:ProblemsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
-%\end{figure*}
-
-%\begin{figure*}
-%	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without %Cycle-break for Each Domain and for Each Inference Method}
-%	\label{fig:MethodsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
-%\end{figure*}
-
-\section{Related Work}
-There exist other planners that also compile POHTN problems to decidable planning classes e.g.
-the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems.
-To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.
-
-\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
-of actions has an executable linearization.
-Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions.
-That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time.
-It can also find a executable linearization for that subset in polynomial time.
-
-\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.
-\cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
-In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
-
-Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
-This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.
-Thus their results are orthogonal to ours.
-
-The paper by \citet{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
-set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
-
-\section{Future Work}
-%Encode Linearization Problem as a MAX-SAT Problem
-The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
-MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.
-
-The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-% Assuming no negative preconditions, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
-The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
-
-%Adding a Plan as Additional Input to the Domain
-%Adding a plan as additional input to the PO domain having the semantics that this plan shall be in the solution set of the TO output model.
-This reduces the computational complexity of the decision problem from undecidable.
-% I assume the resulting problem is PSPACE-complete, but this needs to be proven
-
-\section{Conclusion}
-
-% The contributions of this paper are as follows:
-
-This paper finds that, at least for the POHTN problems in the IPC domain, most of them are not undecidable.
-In other words, it is as if the POHTN domains are compressed TO domains - this linearization separates one of them back out.
-
-We can also see this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
-Furthermore, there is demonstrably much more room for improvement.
-Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
-
-This method can also be used to increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
-Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
-Then $k+m$ (lifted or grounded) TOHTN problems exist now.
-And from empirical evaluation, $k$ may be close to $n$.
-
-Finally, in this paper we identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all others discussed in other works.
-
-% Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
-\bibliography{bib}
-% \nobibliography{aaai22}
-
-\end{document}

### 2022-12-20 paper/07--relatedWork.tex
...

--- 2022-12-15 paper/paper-mainfile.tex
@@
-\def\year{2022}\relax
-%File: formatting-instructions-latex-2022.tex
-%release 2022.1
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%
-% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-% \usepackage{algorithm}
-% \usepackage{algorithmic}
-% \usepackage[noend]{algpseudocode}
+\section{Related Work}
 
-%
-% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
-\usepackage{newfloat}
-\usepackage{listings}
-\lstset{%
-	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
-	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
-	aboveskip=0pt,belowskip=0pt,%
-	showstringspaces=false,tabsize=2,breaklines=true}
-%\floatstyle{ruled}
-%\newfloat{listing}{tb}{lst}{}
-%\floatname{listing}{Listing}
-
-%
-% user import packages
-\usepackage{amsfonts}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{paralist}
-\usepackage{todonotes}
-\usepackage{booktabs}
-\usepackage{varwidth}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{xcolor}
-\usepackage{booktabs} 
-% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
-\usepackage{csquotes}
-\usepackage{subcaption}
-\usepackage{amssymb} 
-\usepackage{mathbbol}
-\usepackage{tikz}
-\usetikzlibrary{aiplans}
-
-\scheme{SinglePrec}{0}{
-	text = {\textbf{A}},
-	pre  = {a}
-}
-
-\scheme{SingleAdd}{0}{
-	text = {\textbf{B}},
-	effs = { a}
-}
-
-\scheme{SingleDelete}{0}{
-	text = {\textbf{C}},
-	effs = { {{$\neg$}a} }
-}
-
-\scheme{SinglePrecAlt}{0}{
-	text = {\textbf{D}},
-	pre  = {a}
-}
-
-\scheme{SingleAddAlt}{0}{
-	text = {\textbf{E}},
-	effs = { a}
-}
-
-\scheme{PrimitiveA}{0}{
-	text = {\textbf{A}},
-	pre  = {a},
-	effs = { {{$\neg$}a}, {b} }
-}
-
-\scheme{PrimitiveB}{0}{
-	text = {\textbf{B}},
-	pre = {b},
-	effs = {{{$\neg$}b}, {c}}
-}
-
-\scheme{PrimitiveC}{0}{
-	text = {\textbf{C}},
-	pre = {c},
-	eff = {{$\neg$}c}
-}
-
-\nocopyright
-%
-% PDF Info Is REQUIRED.
-% For /Title, write your title in Mixed Case.
-% Don't use accents or commands. Retain the parentheses.
-% For /Author, add all authors within the parentheses,
-% separated by commas. No accents, special characters
-% or commands are allowed.
-% Keep the /TemplateVersion tag as is
-\pdfinfo{
-/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
-Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-/Author (Anonymous)
-/TemplateVersion (2022.1)
-}
-
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-% The file aaai22.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
-% Title
-
-% Your title must be in mixed case, not sentence case.
-% That means all verbs (including short verbs like be, is, using,and go),
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-% \iffalse
-
-\newtheorem{theorem}{Theorem}
-
-\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
-\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
-
-\newcommand{\Add} {\ensuremath{\mathit{add}}}
-\newcommand{\Del} {\ensuremath{\mathit{del}}}
-\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
-\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
-\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
-\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
-\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
-
-%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}
-
-%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
-%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
-\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
-\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
-
-\author {
-    Submission
-}
-\affiliations{
-    Anonymous
-}
-% \fi
-
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\iffalse 
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-\author {
-    % Authors
-    Anonymous
-
-}
-\affiliations {
-    % Affiliations
-    Anonymous
-}
-\fi
-
-\title{Order is half of life -- Establishing Totally Ordered HTN
-	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-% REMOVE THIS: bibentry
-% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
-% \usepackage{bibentry}
-% END REMOVE bibentry
-
-\begin{document}
-\input{00--macro.tex}
-\maketitle
-
-\begin{abstract} 
-HTN planning is in general undecidable, yet there exist efficient
-planning algorithms. An important subclass is that of totally ordered
-HTN planning problems. Not only is this class decidable, but also easier
-to handle algorithmically since tasks cannot interleave anymore.
-Consequently, several specialized solvers exist, and dedicated tracks at
-the International Planning Competition (IPC) in both 2020 and 2023. We
-were able to show that almost all currently existing partially ordered
-planning benchmarks can be turned into totally ordered ones without
-sacrificing solvability. Establishing totally ordered problems in a
-preprocessing technique thus allows to use planning systems, heuristics,
-pruning techniques (etc.) that are only available for totally ordered
-problems. This allows solving problems more efficiently and with
-better-informed techniques, at the (little) cost of doing a
-preprocessing technique. We show that in only a very few cases
-linearization isn't possible, and in all others establishing a total
-order pays off \emph{significantly}, thus establishing our technique as
-a significant ingredient in the state of the art for solving partially
-ordered HTN problems. As a side contribution, we identify a new class of
-decidable (EXPTIME-complete) HTN problems, namely those where our
-preprocessing technique is guaranteed to be solvability-preserving.
-\end{abstract}
-
-\section{Introduction}
-\input{01--intro.tex}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
-
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-
-Many problems might be naturally more suited to being modelled as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Where this is possible, it results in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
-
-\section{Hierarchical Planning Formalism}
-\input{02--htn.tex}
-
-\section{Linearizing Grounded HTN Problems}
-\input{03--linearization-ground.tex}
-
-% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
-We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
-This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.
-
-% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
-
-% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
-Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
-
-% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
-If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
-This is true for all possible tasks by simple induction over the decomposition process.
-
-% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-% Specifically, let $\sigma$ be the set of parameters for the method.
-Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
-Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
-
-% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
-For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
-% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
-
-% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
-The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
-Only one linearized lifted method per partially-ordered lifted method is produced.
-
-% For a grounded method, there are no parameters in a task or method.
-Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
-We can then use these to produce a linearized grounded method per grounded method.
-
-% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
-For a grounded model, $f' = f$.
-The inferred preconditions and effects for a task are then defined as below:
-% \begin{align*}
-% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
-% & \forall t \in T_P : \AddS(t) := \Add(t) \\
-% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-% \end{align*}
-
-% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
-% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
-Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
-
-%State-independent positive and negative effects (cf.
-their Def.
-4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
-%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-% after every refinement of c but after at least one:
-% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% The set of executability-enabling states of c is
-% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
-% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
-
-% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-
-% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
-% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
-% the precondition relaxation can make further refinements executable that produce
-% effects that can not be achieved in the non-relaxed domain. 
-% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
-
-% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
-refinements (ignoring executability of the refinement) $\langle a_0 ...
-a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.
-
-% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
-% In this paper, we will be utilising both of these, as seen in the next section.
-%the precondition-relaxed possible effects, which may hold after at least one refinement of c.
-
-%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
-%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
-%f ∈ prec(ai) and there does not exist an action aj with
-%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
-%The exploitation of the relaxed preconditions and effects
-%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates
-
-\section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}
-
-% \begin{algorithm}[h]
-% 	\caption{Calculation of linearized methods}
-% 	\label{alg:Algorithm1}
-% 	\KwData{$(F, T_P, T_C, \delta, M)$}
-% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-% 	{
-% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-% 		$G \gets \singlePrec$ \\
-% 		\label{alg:StartBuildGraph}
-% 		\For{a $\in$ F}{  
-% 			\For{$t \in T_m$}{
-% 				\For{$t' \in T_m$}{
-% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-% 				}
-% 			} 
-% 			\label{alg:EndBuildGraph}	
-% 		}	
-% 		\label{alg:StartCycleBreak}
-% 		\While{$G$ has cycles in it}{
-% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-% 		}
-% 		\label{alg:EndCycleBreak}
-% 		$\prec'$ = Any linearization of $G$ \\
-% 		\label{alg:TopSort}
-% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
-% 		$M' = M' \cup  \{m'\}$ \\
-
-% 	}
-% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-% \end{algorithm}
-
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
-For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:
-
- \begin{figure}[h]
- 	\caption{Example of Desired Additional Orderings}
- 	\label{fig:OrderingRules}
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{first}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{second}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(first) edge [->,bend right] node [left]  {} (second);
-			\end{tikzpicture}
-
-			\caption{B adds a fact in preconditions of A -- so B before A}
-
-		\end{subfigure}
-	}  
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{C deletes a fact in preconditions of A  -- so A before C}	
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->, bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{B adds a fact that C deletes -- so C before B}
-		\end{subfigure}
-	} 
-\end{figure}
-
-\begin{figure}[h]
-	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
-	\label{fig:CycleBreaking}
-	\scalebox{0.75}{
-		\begin{subfigure}{7cm} 
-		 	\centering
-			\caption{Resulting method ordering has a cycle}
-			\label{fig:CycleBreaking1}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-			(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{6cm} 
-		 %	\centering
-			\caption{Delete any random ordering to break it}
-			\label{fig:CycleBreaking2}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-		%	(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-%	\scalebox{0.75}{
-%		\begin{subfigure}{7cm} 
-%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
-%			\label{fig:NotCycleBreaking}
-%			\begin{tikzpicture}[auto,node distance=1.2cm,
-%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-%			\action{B}{SingleAddAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em 
-%			};
-
-%			\action{A}{SinglePrecAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em,
-%				body = {right = 4em of first} 		
-%			};
-
-%			\path[every node/.style={font=\sffamily\small}]
-%			(B) edge [->,bend right] node [left]  {} (A);
-%			\end{tikzpicture}
-
-%			\caption{Resulting method ordering has no cycle}
-%			
-%		\end{subfigure}
-%	}   
-\end{figure}
-
-% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase.
-Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
-% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
-
-\section{Theoretical Properties of Linearization Result}
-
-We now discuss the implications of the above-described linearization procedure.
-
-\begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
-\end{theorem}
-\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
-	Let $|T|$ = $|T_P| + |T_C|$.
-
-	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
-
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$.
-We explore it's compound sub-tasks until we collect all primitive tasks.
-Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree.
-This is obviously polynomial in terms of $|T|$.
-%This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
-This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
-% we explore all poss (at most $|T_C|$)
-
-	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
-Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.
-
-	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.
-
-	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
-% and $\mathcal{O}(V)$ in space.
-	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
-
-	So the algorithm takes polynomial time. 
-\end{proof}
-
-\begin{theorem}\label{thm:Soundness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
-\end{theorem}
-\begin{proof}
-	The new desired orderings for a method include all of the orderings already required by the method originally.
-The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph.
-This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one.
-Any solution to the linearized problem is then obviously a solution to the original problem.
-\end{proof}
-
-\begin{theorem}\label{thm:notCompleteness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then $sol(P')$ may be empty.
-\end{theorem}
-\begin{proof}
-	This algorithm linearizes all the methods to be totally ordered.
-Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents are already ordered with respect to each other.
-This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
-Consider the simple example problem:
-	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
-	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$.
-This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution.
-	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
-	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
-Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
-	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
-\end{proof}
-
-% The exploitation of the relaxed preconditions and effects
-% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.
-
-\begin{description}
-	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, or in other words, \emph{cycle-breaking} did not occur, that method is said to meet the linearization criteria.
-If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well.
-\end{description}
-
-%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.
-
-\begin{theorem} \label{thm:RelaxedPreconditions}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, \emph{only if $P$, the entire problem meets the linearization criteria},
-	then we know executability-relaxed preconditions for any $c$ are indeed the only ones needed to execute any refinement of $c$.
-\end{theorem}
-\begin{proof}
-%	At least in the case where the linearization criteria is met for all methods, we can be assured that the executability-relaxed preconditions actually work for us.
-
-	For some method with at least two sub-tasks, $a$ and $b$,
-	the desired orderings are to put $a$ with $f \in \Add(a)$ before $b$ with $f \in \Pre(b)$.
-We're assuming no cycle-breaking, so this was actually achieved.
-If such a precondition can't be met this way, (such an $a$ does not exist, or the method already enforces that $b$ executes before $a$) by definition it must be in the executability-relaxed preconditions calculated.
-
-	Therefore, any precondition of $c$'s children that can't be met by placing other children of $c$ before it is part - so it is indeed a super-set of actual preconditions, assuming no cycle-breaking was needed.
-
-	If even one partially ordered method did need cycle-breaking, than of course it means nothing - we may indeed need other preconditions to make refinements of $c$ executable.
-Then those results no longer hold.
-\end{proof}
-
-We use Theorem~\ref{thm:RelaxedPreconditions} as support for the following main result.
-We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.
-
-\begin{theorem}\label{thm:SpecialCase}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if $P$ meets the linearization criteria and $sol(P)$ is non-empty, then $sol(P')$ will be non-empty as well.
-\end{theorem}
-\begin{proof}	
-	Assume that there exists a solution in the PO domain.
-By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain.
-Assume this sequence is $(a_0, a_1, ..., a_n)$.
-We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
-	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state.
-The action $a_k$ could only be non-executable, if one or more of its preconditions was not met.
-Assume one of these unmet preconditions is for existence of the state variable $A$.
-	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution.
-So there must exist an action $a_i$, $0 < i < n$, that will add A.
-Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree.
-So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.
-
-	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
-We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required, either directly or via inheritance from parent tasks.
-This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
-In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.
-
-	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution.
-Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
-\end{proof}
-
-There are several possible levels of \enquote{completeness} for a problem compilation.
-%\begin{enumerate}
-\begin{itemize}
-	\item all solutions remain 
-	\item at least one solution remains 
-	\item all optimal solutions remain
-	\item at least one optimal solution remains 	
-\end{itemize}
-%\end{enumerate}
-Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if linearization criteria is met.
-Otherwise, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions.
-Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.
-
-\begin{theorem}\label{thm:newClass}
-	Problems $P$ that satisfy the linearization criteria form a new class of decidable problems.
-\end{theorem}
-\begin{proof}
-	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.
-\end{proof}
-
-\section{Empirical Evaluation}
-We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems.
-All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
-The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
-Each problem has the standard IPC time limit of 30 minutes.
-Any grounding and pre-processing time needed is included as part of the 'solving' time.
-Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
-
-\subsection{Hardware and Planning Systems}
-The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested.
-Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.
-
-We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
-This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
-The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
-
-% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
-
-%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}
-
-We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
-%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
-We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
-The same setting is used for re-runs.
-For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
-We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems.
-Re-runs use panda$_{\pi}$ with the best heuristic(Add).
-We test both Complex and Simple Inference for linearization.
-Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
-
-The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
-As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-
-The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.
-
-For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
-the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem.
-For each total-order planner, the column beneath it shows performance on the linearized problem.
-The IPC score has a maximum of 1 per domain, for the 12 domains in total.
-
-%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}
-
-The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
-achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}.
-This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average.
-However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains.
-E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.
-
-Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
-When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
-%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
-
-%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
-
-%\todo{proven unsolvable should not be in superscripts}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleCoverage}
-	\scalebox{0.8} {
-\begin{tabular}{lccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO\\  
-	\midrule 
-	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
-	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
-	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
-	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
-			\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-			\midrule 
-	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
-	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleIPC}
-	\scalebox{0.85} {
-	\begin{tabular}{lccccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	& PO & TO & PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\
-
-	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
-	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\
-
-	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
-	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
-	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
-	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\
-
-	\midrule 
-	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\
-
-	\bottomrule 
-		\end{tabular} 		
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleCoverage}
-	\scalebox{0.65} {
-		\begin{tabular}{lccccccccccl} 
-			\toprule 
-			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-			&PO & TO & PO & TO  \\ 
-\midrule 
-Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
-PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
-Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
-Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
-UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
-Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
-\midrule 
-Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
-SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
-Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
-\midrule 
-Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
-Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
-\bottomrule 
-		\end{tabular}
-
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleIPC}
-	\scalebox{0.7} {
-\begin{tabular}{lccccccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
-	&PO & TO & PO & TO  \\  
-\midrule 
-Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
-PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
-Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
-Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
-UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
-Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
-\midrule 
-Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
-SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
-Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-\midrule 
-IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
-\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexCoverage}.
-	\scalebox{0.8} {
-
-\begin{tabular}{lccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
-	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
-	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\
-
-	\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
-	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\
-
-		\midrule 
-	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexIPC}.
-	\scalebox{0.8} { 
-\begin{tabular}{lccccccl} 
-			\toprule 
-		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO  &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\
-
-	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
-	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
-	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
-	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
-	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
-	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-		\midrule 
-	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
-	\bottomrule 
-\end{tabular}  
-	}
-\end{table}
-
-\begin{table} 
-	\centering  
-	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
-	\label{table:FullyLinearizedProblems}
-	\scalebox{0.75} { 
-	\begin{tabular}{lcccl} 
-		\toprule
-		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
-		\midrule
-		SmartPhone  & 4.0                   &  1     \\
-		Transport   & 1144.9                & 40       \\
-		UM-Translog & 1.1                    & 17   \\
-		Woodworking & 2035              &   21    \\
-				\bottomrule 
-	\end{tabular} 
-	}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are from using Simple Inference.
-Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
-	\label{table:SimpleLinearizable} 
-		\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
-		\midrule
-Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
-Monroe & 12127.3 & 3447.8 & 72.4  \\ 
-Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
-Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
-PCP & 12.3 & 12.3 & 0.0  \\ 
-Rover & 509.4 & 355.2 & 32.3  \\ 
-Satellite & 70.6 & 36.1 & 50.9  \\ 
-SmartPhone & 6.3 & 4.0 & 21.8  \\ 
-Transport & 1144.9 & 1144.9 & 0.0  \\ 
-UM-Translog & 1.5 & 1.5 & 0.0  \\ 
-Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
-Zenotravel & 190.2 & 99.4 & 47.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
-	\label{table:ComplexLinearizable} 
-	\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
-		\midrule
-			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
-			Monroe & 12127.3 & 216.9 & 98.2  \\ 
-			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
-			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
-			PCP & 12.3 & 4.9 & 59.8  \\ 
-			Rover & 509.4 & 134.8 & 72.4  \\ 
-			Satellite & 70.6 & 10.7 & 77.9  \\ 
-			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
-			Transport & 1144.9 & 0.0 & 100.0  \\ 
-			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
-			Woodworking & 1927.3 & 476.0 & 85.5  \\
-			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
-			\bottomrule 
-		\end{tabular} 
-		}
-\end{table}
-
-While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
-(Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
-
-\begin{table} 
-	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain.
-Shows Results for Both Inference Methods.}\label{table:POMethodBreak}
-	\begin{tabular}{lccl} 
-		\toprule 
-		Domain & Complex & Simple &  \\ 
-		\midrule
-		Transport & 1.0 & 0.0  \\ 
-		UM-Translog & 0.8 & 0.0  \\ 
-		Satellite & 1.0 & 0.0  \\ 
-		Monroe Fully Observ. & 1.0 & 0.0  \\ 
-		Rover & 1.0 & 0.0  \\ 
-		Woodworking & 0.9 & 0.0  \\ 
-		Monroe Part. Observ. & 1.0 & 0.0  \\ 
-		PCP & 0.0 & 0.0  \\ 
-		Barman-BDI & 1.0 & 0.0  \\ 
-		SmartPhone & 0.1 & 0.1  \\ 
-		Monroe & 0.8 & 0.0  \\ 
-		Zenotravel & 1.0 & 0.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-\end{table}
-
-%\begin{figure*}
-%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
-%	\label{fig:ProblemsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
-%\end{figure*}
-
-%\begin{figure*}
-%	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without %Cycle-break for Each Domain and for Each Inference Method}
-%	\label{fig:MethodsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
-%\end{figure*}
-
-\section{Related Work}
 There exist other planners that also compile POHTN problems to decidable planning classes e.g.
@@
 
-The paper by \citet{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
+The paper by \shortCite{DeleteRelaxation,Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
 set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
-
-\section{Future Work}
-%Encode Linearization Problem as a MAX-SAT Problem
-The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
-MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.
-
-The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-% Assuming no negative preconditions, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
-The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
-
-%Adding a Plan as Additional Input to the Domain
-%Adding a plan as additional input to the PO domain having the semantics that this plan shall be in the solution set of the TO output model.
-This reduces the computational complexity of the decision problem from undecidable.
-% I assume the resulting problem is PSPACE-complete, but this needs to be proven
-
-\section{Conclusion}
-
-% The contributions of this paper are as follows:
-
-This paper finds that, at least for the POHTN problems in the IPC domain, most of them are not undecidable.
-In other words, it is as if the POHTN domains are compressed TO domains - this linearization separates one of them back out.
-
-We can also see this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
-Furthermore, there is demonstrably much more room for improvement.
-Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
-
-This method can also be used to increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
-Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
-Then $k+m$ (lifted or grounded) TOHTN problems exist now.
-And from empirical evaluation, $k$ may be close to $n$.
-
-Finally, in this paper we identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all others discussed in other works.
-
-% Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
-\bibliography{bib}
-% \nobibliography{aaai22}
-
-\end{document}

### 2022-12-20 paper/08--futureWork.tex
...

--- 2022-12-15 paper/paper-mainfile.tex
@@
-\def\year{2022}\relax
-%File: formatting-instructions-latex-2022.tex
-%release 2022.1
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%
-% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-% \usepackage{algorithm}
-% \usepackage{algorithmic}
-% \usepackage[noend]{algpseudocode}
+\section{Future Work}
 
-%
-% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
-\usepackage{newfloat}
-\usepackage{listings}
-\lstset{%
-	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
-	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
-	aboveskip=0pt,belowskip=0pt,%
-	showstringspaces=false,tabsize=2,breaklines=true}
-%\floatstyle{ruled}
-%\newfloat{listing}{tb}{lst}{}
-%\floatname{listing}{Listing}
-
-%
-% user import packages
-\usepackage{amsfonts}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{paralist}
-\usepackage{todonotes}
-\usepackage{booktabs}
-\usepackage{varwidth}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{xcolor}
-\usepackage{booktabs} 
-% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
-\usepackage{csquotes}
-\usepackage{subcaption}
-\usepackage{amssymb} 
-\usepackage{mathbbol}
-\usepackage{tikz}
-\usetikzlibrary{aiplans}
-
-\scheme{SinglePrec}{0}{
-	text = {\textbf{A}},
-	pre  = {a}
-}
-
-\scheme{SingleAdd}{0}{
-	text = {\textbf{B}},
-	effs = { a}
-}
-
-\scheme{SingleDelete}{0}{
-	text = {\textbf{C}},
-	effs = { {{$\neg$}a} }
-}
-
-\scheme{SinglePrecAlt}{0}{
-	text = {\textbf{D}},
-	pre  = {a}
-}
-
-\scheme{SingleAddAlt}{0}{
-	text = {\textbf{E}},
-	effs = { a}
-}
-
-\scheme{PrimitiveA}{0}{
-	text = {\textbf{A}},
-	pre  = {a},
-	effs = { {{$\neg$}a}, {b} }
-}
-
-\scheme{PrimitiveB}{0}{
-	text = {\textbf{B}},
-	pre = {b},
-	effs = {{{$\neg$}b}, {c}}
-}
-
-\scheme{PrimitiveC}{0}{
-	text = {\textbf{C}},
-	pre = {c},
-	eff = {{$\neg$}c}
-}
-
-\nocopyright
-%
-% PDF Info Is REQUIRED.
-% For /Title, write your title in Mixed Case.
-% Don't use accents or commands. Retain the parentheses.
-% For /Author, add all authors within the parentheses,
-% separated by commas. No accents, special characters
-% or commands are allowed.
-% Keep the /TemplateVersion tag as is
-\pdfinfo{
-/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
-Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-/Author (Anonymous)
-/TemplateVersion (2022.1)
-}
-
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-% The file aaai22.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
-% Title
-
-% Your title must be in mixed case, not sentence case.
-% That means all verbs (including short verbs like be, is, using,and go),
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-% \iffalse
-
-\newtheorem{theorem}{Theorem}
-
-\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
-\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
-
-\newcommand{\Add} {\ensuremath{\mathit{add}}}
-\newcommand{\Del} {\ensuremath{\mathit{del}}}
-\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
-\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
-\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
-\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
-\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
-
-%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}
-
-%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
-%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
-\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
-\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
-
-\author {
-    Submission
-}
-\affiliations{
-    Anonymous
-}
-% \fi
-
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\iffalse 
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-\author {
-    % Authors
-    Anonymous
-
-}
-\affiliations {
-    % Affiliations
-    Anonymous
-}
-\fi
-
-\title{Order is half of life -- Establishing Totally Ordered HTN
-	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-% REMOVE THIS: bibentry
-% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
-% \usepackage{bibentry}
-% END REMOVE bibentry
-
-\begin{document}
-\input{00--macro.tex}
-\maketitle
-
-\begin{abstract} 
-HTN planning is in general undecidable, yet there exist efficient
-planning algorithms. An important subclass is that of totally ordered
-HTN planning problems. Not only is this class decidable, but also easier
-to handle algorithmically since tasks cannot interleave anymore.
-Consequently, several specialized solvers exist, and dedicated tracks at
-the International Planning Competition (IPC) in both 2020 and 2023. We
-were able to show that almost all currently existing partially ordered
-planning benchmarks can be turned into totally ordered ones without
-sacrificing solvability. Establishing totally ordered problems in a
-preprocessing technique thus allows to use planning systems, heuristics,
-pruning techniques (etc.) that are only available for totally ordered
-problems. This allows solving problems more efficiently and with
-better-informed techniques, at the (little) cost of doing a
-preprocessing technique. We show that in only a very few cases
-linearization isn't possible, and in all others establishing a total
-order pays off \emph{significantly}, thus establishing our technique as
-a significant ingredient in the state of the art for solving partially
-ordered HTN problems. As a side contribution, we identify a new class of
-decidable (EXPTIME-complete) HTN problems, namely those where our
-preprocessing technique is guaranteed to be solvability-preserving.
-\end{abstract}
-
-\section{Introduction}
-\input{01--intro.tex}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
-
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-
-Many problems might be naturally more suited to being modelled as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Where this is possible, it results in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
-
-\section{Hierarchical Planning Formalism}
-\input{02--htn.tex}
-
-\section{Linearizing Grounded HTN Problems}
-\input{03--linearization-ground.tex}
-
-% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
-We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
-This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.
-
-% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
-
-% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
-Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
-
-% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
-If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
-This is true for all possible tasks by simple induction over the decomposition process.
-
-% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-% Specifically, let $\sigma$ be the set of parameters for the method.
-Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
-Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
-
-% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
-For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
-% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
-
-% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
-The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
-Only one linearized lifted method per partially-ordered lifted method is produced.
-
-% For a grounded method, there are no parameters in a task or method.
-Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
-We can then use these to produce a linearized grounded method per grounded method.
-
-% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
-For a grounded model, $f' = f$.
-The inferred preconditions and effects for a task are then defined as below:
-% \begin{align*}
-% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
-% & \forall t \in T_P : \AddS(t) := \Add(t) \\
-% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-% \end{align*}
-
-% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
-% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
-Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
-
-%State-independent positive and negative effects (cf.
-their Def.
-4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
-%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-% after every refinement of c but after at least one:
-% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% The set of executability-enabling states of c is
-% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
-% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
-
-% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-
-% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
-% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
-% the precondition relaxation can make further refinements executable that produce
-% effects that can not be achieved in the non-relaxed domain. 
-% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
-
-% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
-refinements (ignoring executability of the refinement) $\langle a_0 ...
-a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.
-
-% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
-% In this paper, we will be utilising both of these, as seen in the next section.
-%the precondition-relaxed possible effects, which may hold after at least one refinement of c.
-
-%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
-%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
-%f ∈ prec(ai) and there does not exist an action aj with
-%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
-%The exploitation of the relaxed preconditions and effects
-%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates
-
-\section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}
-
-% \begin{algorithm}[h]
-% 	\caption{Calculation of linearized methods}
-% 	\label{alg:Algorithm1}
-% 	\KwData{$(F, T_P, T_C, \delta, M)$}
-% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-% 	{
-% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-% 		$G \gets \singlePrec$ \\
-% 		\label{alg:StartBuildGraph}
-% 		\For{a $\in$ F}{  
-% 			\For{$t \in T_m$}{
-% 				\For{$t' \in T_m$}{
-% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-% 				}
-% 			} 
-% 			\label{alg:EndBuildGraph}	
-% 		}	
-% 		\label{alg:StartCycleBreak}
-% 		\While{$G$ has cycles in it}{
-% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-% 		}
-% 		\label{alg:EndCycleBreak}
-% 		$\prec'$ = Any linearization of $G$ \\
-% 		\label{alg:TopSort}
-% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
-% 		$M' = M' \cup  \{m'\}$ \\
-
-% 	}
-% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-% \end{algorithm}
-
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
-For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:
-
- \begin{figure}[h]
- 	\caption{Example of Desired Additional Orderings}
- 	\label{fig:OrderingRules}
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{first}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{second}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(first) edge [->,bend right] node [left]  {} (second);
-			\end{tikzpicture}
-
-			\caption{B adds a fact in preconditions of A -- so B before A}
-
-		\end{subfigure}
-	}  
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{C deletes a fact in preconditions of A  -- so A before C}	
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->, bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{B adds a fact that C deletes -- so C before B}
-		\end{subfigure}
-	} 
-\end{figure}
-
-\begin{figure}[h]
-	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
-	\label{fig:CycleBreaking}
-	\scalebox{0.75}{
-		\begin{subfigure}{7cm} 
-		 	\centering
-			\caption{Resulting method ordering has a cycle}
-			\label{fig:CycleBreaking1}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-			(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{6cm} 
-		 %	\centering
-			\caption{Delete any random ordering to break it}
-			\label{fig:CycleBreaking2}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-		%	(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-%	\scalebox{0.75}{
-%		\begin{subfigure}{7cm} 
-%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
-%			\label{fig:NotCycleBreaking}
-%			\begin{tikzpicture}[auto,node distance=1.2cm,
-%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-%			\action{B}{SingleAddAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em 
-%			};
-
-%			\action{A}{SinglePrecAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em,
-%				body = {right = 4em of first} 		
-%			};
-
-%			\path[every node/.style={font=\sffamily\small}]
-%			(B) edge [->,bend right] node [left]  {} (A);
-%			\end{tikzpicture}
-
-%			\caption{Resulting method ordering has no cycle}
-%			
-%		\end{subfigure}
-%	}   
-\end{figure}
-
-% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase.
-Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
-% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
-
-\section{Theoretical Properties of Linearization Result}
-
-We now discuss the implications of the above-described linearization procedure.
-
-\begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
-\end{theorem}
-\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
-	Let $|T|$ = $|T_P| + |T_C|$.
-
-	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
-
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$.
-We explore it's compound sub-tasks until we collect all primitive tasks.
-Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree.
-This is obviously polynomial in terms of $|T|$.
-%This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
-This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
-% we explore all poss (at most $|T_C|$)
-
-	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
-Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.
-
-	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.
-
-	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
-% and $\mathcal{O}(V)$ in space.
-	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
-
-	So the algorithm takes polynomial time. 
-\end{proof}
-
-\begin{theorem}\label{thm:Soundness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
-\end{theorem}
-\begin{proof}
-	The new desired orderings for a method include all of the orderings already required by the method originally.
-The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph.
-This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one.
-Any solution to the linearized problem is then obviously a solution to the original problem.
-\end{proof}
-
-\begin{theorem}\label{thm:notCompleteness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then $sol(P')$ may be empty.
-\end{theorem}
-\begin{proof}
-	This algorithm linearizes all the methods to be totally ordered.
-Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents are already ordered with respect to each other.
-This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
-Consider the simple example problem:
-	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
-	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$.
-This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution.
-	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
-	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
-Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
-	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
-\end{proof}
-
-% The exploitation of the relaxed preconditions and effects
-% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.
-
-\begin{description}
-	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, or in other words, \emph{cycle-breaking} did not occur, that method is said to meet the linearization criteria.
-If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well.
-\end{description}
-
-%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.
-
-\begin{theorem} \label{thm:RelaxedPreconditions}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, \emph{only if $P$, the entire problem meets the linearization criteria},
-	then we know executability-relaxed preconditions for any $c$ are indeed the only ones needed to execute any refinement of $c$.
-\end{theorem}
-\begin{proof}
-%	At least in the case where the linearization criteria is met for all methods, we can be assured that the executability-relaxed preconditions actually work for us.
-
-	For some method with at least two sub-tasks, $a$ and $b$,
-	the desired orderings are to put $a$ with $f \in \Add(a)$ before $b$ with $f \in \Pre(b)$.
-We're assuming no cycle-breaking, so this was actually achieved.
-If such a precondition can't be met this way, (such an $a$ does not exist, or the method already enforces that $b$ executes before $a$) by definition it must be in the executability-relaxed preconditions calculated.
-
-	Therefore, any precondition of $c$'s children that can't be met by placing other children of $c$ before it is part - so it is indeed a super-set of actual preconditions, assuming no cycle-breaking was needed.
-
-	If even one partially ordered method did need cycle-breaking, than of course it means nothing - we may indeed need other preconditions to make refinements of $c$ executable.
-Then those results no longer hold.
-\end{proof}
-
-We use Theorem~\ref{thm:RelaxedPreconditions} as support for the following main result.
-We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.
-
-\begin{theorem}\label{thm:SpecialCase}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if $P$ meets the linearization criteria and $sol(P)$ is non-empty, then $sol(P')$ will be non-empty as well.
-\end{theorem}
-\begin{proof}	
-	Assume that there exists a solution in the PO domain.
-By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain.
-Assume this sequence is $(a_0, a_1, ..., a_n)$.
-We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
-	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state.
-The action $a_k$ could only be non-executable, if one or more of its preconditions was not met.
-Assume one of these unmet preconditions is for existence of the state variable $A$.
-	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution.
-So there must exist an action $a_i$, $0 < i < n$, that will add A.
-Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree.
-So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.
-
-	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
-We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required, either directly or via inheritance from parent tasks.
-This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
-In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.
-
-	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution.
-Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
-\end{proof}
-
-There are several possible levels of \enquote{completeness} for a problem compilation.
-%\begin{enumerate}
-\begin{itemize}
-	\item all solutions remain 
-	\item at least one solution remains 
-	\item all optimal solutions remain
-	\item at least one optimal solution remains 	
-\end{itemize}
-%\end{enumerate}
-Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if linearization criteria is met.
-Otherwise, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions.
-Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.
-
-\begin{theorem}\label{thm:newClass}
-	Problems $P$ that satisfy the linearization criteria form a new class of decidable problems.
-\end{theorem}
-\begin{proof}
-	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.
-\end{proof}
-
-\section{Empirical Evaluation}
-We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems.
-All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
-The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
-Each problem has the standard IPC time limit of 30 minutes.
-Any grounding and pre-processing time needed is included as part of the 'solving' time.
-Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
-
-\subsection{Hardware and Planning Systems}
-The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested.
-Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.
-
-We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
-This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
-The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
-
-% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
-
-%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}
-
-We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
-%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
-We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
-The same setting is used for re-runs.
-For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
-We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems.
-Re-runs use panda$_{\pi}$ with the best heuristic(Add).
-We test both Complex and Simple Inference for linearization.
-Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
-
-The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
-As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-
-The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.
-
-For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
-the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem.
-For each total-order planner, the column beneath it shows performance on the linearized problem.
-The IPC score has a maximum of 1 per domain, for the 12 domains in total.
-
-%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}
-
-The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
-achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}.
-This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average.
-However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains.
-E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.
-
-Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
-When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
-%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
-
-%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
-
-%\todo{proven unsolvable should not be in superscripts}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleCoverage}
-	\scalebox{0.8} {
-\begin{tabular}{lccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO\\  
-	\midrule 
-	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
-	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
-	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
-	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
-			\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-			\midrule 
-	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
-	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleIPC}
-	\scalebox{0.85} {
-	\begin{tabular}{lccccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	& PO & TO & PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\
-
-	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
-	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\
-
-	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
-	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
-	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
-	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\
-
-	\midrule 
-	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\
-
-	\bottomrule 
-		\end{tabular} 		
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleCoverage}
-	\scalebox{0.65} {
-		\begin{tabular}{lccccccccccl} 
-			\toprule 
-			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-			&PO & TO & PO & TO  \\ 
-\midrule 
-Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
-PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
-Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
-Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
-UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
-Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
-\midrule 
-Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
-SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
-Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
-\midrule 
-Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
-Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
-\bottomrule 
-		\end{tabular}
-
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleIPC}
-	\scalebox{0.7} {
-\begin{tabular}{lccccccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
-	&PO & TO & PO & TO  \\  
-\midrule 
-Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
-PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
-Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
-Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
-UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
-Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
-\midrule 
-Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
-SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
-Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-\midrule 
-IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
-\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexCoverage}.
-	\scalebox{0.8} {
-
-\begin{tabular}{lccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
-	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
-	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\
-
-	\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
-	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\
-
-		\midrule 
-	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexIPC}.
-	\scalebox{0.8} { 
-\begin{tabular}{lccccccl} 
-			\toprule 
-		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO  &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\
-
-	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
-	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
-	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
-	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
-	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
-	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-		\midrule 
-	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
-	\bottomrule 
-\end{tabular}  
-	}
-\end{table}
-
-\begin{table} 
-	\centering  
-	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
-	\label{table:FullyLinearizedProblems}
-	\scalebox{0.75} { 
-	\begin{tabular}{lcccl} 
-		\toprule
-		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
-		\midrule
-		SmartPhone  & 4.0                   &  1     \\
-		Transport   & 1144.9                & 40       \\
-		UM-Translog & 1.1                    & 17   \\
-		Woodworking & 2035              &   21    \\
-				\bottomrule 
-	\end{tabular} 
-	}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are from using Simple Inference.
-Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
-	\label{table:SimpleLinearizable} 
-		\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
-		\midrule
-Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
-Monroe & 12127.3 & 3447.8 & 72.4  \\ 
-Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
-Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
-PCP & 12.3 & 12.3 & 0.0  \\ 
-Rover & 509.4 & 355.2 & 32.3  \\ 
-Satellite & 70.6 & 36.1 & 50.9  \\ 
-SmartPhone & 6.3 & 4.0 & 21.8  \\ 
-Transport & 1144.9 & 1144.9 & 0.0  \\ 
-UM-Translog & 1.5 & 1.5 & 0.0  \\ 
-Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
-Zenotravel & 190.2 & 99.4 & 47.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
-	\label{table:ComplexLinearizable} 
-	\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
-		\midrule
-			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
-			Monroe & 12127.3 & 216.9 & 98.2  \\ 
-			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
-			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
-			PCP & 12.3 & 4.9 & 59.8  \\ 
-			Rover & 509.4 & 134.8 & 72.4  \\ 
-			Satellite & 70.6 & 10.7 & 77.9  \\ 
-			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
-			Transport & 1144.9 & 0.0 & 100.0  \\ 
-			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
-			Woodworking & 1927.3 & 476.0 & 85.5  \\
-			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
-			\bottomrule 
-		\end{tabular} 
-		}
-\end{table}
-
-While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
-(Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
-
-\begin{table} 
-	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain.
-Shows Results for Both Inference Methods.}\label{table:POMethodBreak}
-	\begin{tabular}{lccl} 
-		\toprule 
-		Domain & Complex & Simple &  \\ 
-		\midrule
-		Transport & 1.0 & 0.0  \\ 
-		UM-Translog & 0.8 & 0.0  \\ 
-		Satellite & 1.0 & 0.0  \\ 
-		Monroe Fully Observ. & 1.0 & 0.0  \\ 
-		Rover & 1.0 & 0.0  \\ 
-		Woodworking & 0.9 & 0.0  \\ 
-		Monroe Part. Observ. & 1.0 & 0.0  \\ 
-		PCP & 0.0 & 0.0  \\ 
-		Barman-BDI & 1.0 & 0.0  \\ 
-		SmartPhone & 0.1 & 0.1  \\ 
-		Monroe & 0.8 & 0.0  \\ 
-		Zenotravel & 1.0 & 0.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-\end{table}
-
-%\begin{figure*}
-%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
-%	\label{fig:ProblemsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
-%\end{figure*}
-
-%\begin{figure*}
-%	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without %Cycle-break for Each Domain and for Each Inference Method}
-%	\label{fig:MethodsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
-%\end{figure*}
-
-\section{Related Work}
-There exist other planners that also compile POHTN problems to decidable planning classes e.g.
-the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems.
-To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.
-
-\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
-of actions has an executable linearization.
-Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions.
-That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time.
-It can also find a executable linearization for that subset in polynomial time.
-
-\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.
-\cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
-In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
-
-Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
-This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.
-Thus their results are orthogonal to ours.
-
-The paper by \citet{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
-set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
-
-\section{Future Work}
-%Encode Linearization Problem as a MAX-SAT Problem
 The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
@@
 The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-% Assuming no negative preconditions, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
-The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
-
-%Adding a Plan as Additional Input to the Domain
-%Adding a plan as additional input to the PO domain having the semantics that this plan shall be in the solution set of the TO output model.
-This reduces the computational complexity of the decision problem from undecidable.
-% I assume the resulting problem is PSPACE-complete, but this needs to be proven
-
-\section{Conclusion}
-
-% The contributions of this paper are as follows:
-
-This paper finds that, at least for the POHTN problems in the IPC domain, most of them are not undecidable.
-In other words, it is as if the POHTN domains are compressed TO domains - this linearization separates one of them back out.
-
-We can also see this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
-Furthermore, there is demonstrably much more room for improvement.
-Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
-
-This method can also be used to increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
-Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
-Then $k+m$ (lifted or grounded) TOHTN problems exist now.
-And from empirical evaluation, $k$ may be close to $n$.
-
-Finally, in this paper we identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all others discussed in other works.
-
-% Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
-\bibliography{bib}
-% \nobibliography{aaai22}
-
-\end{document}
+Thus we can treat each sub-task as a \emph{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \emph{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.

### 2022-12-20 paper/09--conclusion.tex
...

--- 2022-12-15 paper/paper-mainfile.tex
@@
-\def\year{2022}\relax
-%File: formatting-instructions-latex-2022.tex
-%release 2022.1
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%
-% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-% \usepackage{algorithm}
-% \usepackage{algorithmic}
-% \usepackage[noend]{algpseudocode}
-
-%
-% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
-\usepackage{newfloat}
-\usepackage{listings}
-\lstset{%
-	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
-	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
-	aboveskip=0pt,belowskip=0pt,%
-	showstringspaces=false,tabsize=2,breaklines=true}
-%\floatstyle{ruled}
-%\newfloat{listing}{tb}{lst}{}
-%\floatname{listing}{Listing}
-
-%
-% user import packages
-\usepackage{amsfonts}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{paralist}
-\usepackage{todonotes}
-\usepackage{booktabs}
-\usepackage{varwidth}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{xcolor}
-\usepackage{booktabs} 
-% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
-\usepackage{csquotes}
-\usepackage{subcaption}
-\usepackage{amssymb} 
-\usepackage{mathbbol}
-\usepackage{tikz}
-\usetikzlibrary{aiplans}
-
-\scheme{SinglePrec}{0}{
-	text = {\textbf{A}},
-	pre  = {a}
-}
-
-\scheme{SingleAdd}{0}{
-	text = {\textbf{B}},
-	effs = { a}
-}
-
-\scheme{SingleDelete}{0}{
-	text = {\textbf{C}},
-	effs = { {{$\neg$}a} }
-}
-
-\scheme{SinglePrecAlt}{0}{
-	text = {\textbf{D}},
-	pre  = {a}
-}
-
-\scheme{SingleAddAlt}{0}{
-	text = {\textbf{E}},
-	effs = { a}
-}
-
-\scheme{PrimitiveA}{0}{
-	text = {\textbf{A}},
-	pre  = {a},
-	effs = { {{$\neg$}a}, {b} }
-}
-
-\scheme{PrimitiveB}{0}{
-	text = {\textbf{B}},
-	pre = {b},
-	effs = {{{$\neg$}b}, {c}}
-}
-
-\scheme{PrimitiveC}{0}{
-	text = {\textbf{C}},
-	pre = {c},
-	eff = {{$\neg$}c}
-}
-
-\nocopyright
-%
-% PDF Info Is REQUIRED.
-% For /Title, write your title in Mixed Case.
-% Don't use accents or commands. Retain the parentheses.
-% For /Author, add all authors within the parentheses,
-% separated by commas. No accents, special characters
-% or commands are allowed.
-% Keep the /TemplateVersion tag as is
-\pdfinfo{
-/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
-Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-/Author (Anonymous)
-/TemplateVersion (2022.1)
-}
-
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-% The file aaai22.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
-% Title
-
-% Your title must be in mixed case, not sentence case.
-% That means all verbs (including short verbs like be, is, using,and go),
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-% \iffalse
-
-\newtheorem{theorem}{Theorem}
-
-\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
-\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
-
-\newcommand{\Add} {\ensuremath{\mathit{add}}}
-\newcommand{\Del} {\ensuremath{\mathit{del}}}
-\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
-\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
-\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
-\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
-\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
-
-%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}
-
-%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
-%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
-\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
-\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
-
-\author {
-    Submission
-}
-\affiliations{
-    Anonymous
-}
-% \fi
-
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-\iffalse 
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-\author {
-    % Authors
-    Anonymous
-
-}
-\affiliations {
-    % Affiliations
-    Anonymous
-}
-\fi
-
-\title{Order is half of life -- Establishing Totally Ordered HTN
-	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-% REMOVE THIS: bibentry
-% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
-% \usepackage{bibentry}
-% END REMOVE bibentry
-
-\begin{document}
-\input{00--macro.tex}
-\maketitle
-
-\begin{abstract} 
-HTN planning is in general undecidable, yet there exist efficient
-planning algorithms. An important subclass is that of totally ordered
-HTN planning problems. Not only is this class decidable, but also easier
-to handle algorithmically since tasks cannot interleave anymore.
-Consequently, several specialized solvers exist, and dedicated tracks at
-the International Planning Competition (IPC) in both 2020 and 2023. We
-were able to show that almost all currently existing partially ordered
-planning benchmarks can be turned into totally ordered ones without
-sacrificing solvability. Establishing totally ordered problems in a
-preprocessing technique thus allows to use planning systems, heuristics,
-pruning techniques (etc.) that are only available for totally ordered
-problems. This allows solving problems more efficiently and with
-better-informed techniques, at the (little) cost of doing a
-preprocessing technique. We show that in only a very few cases
-linearization isn't possible, and in all others establishing a total
-order pays off \emph{significantly}, thus establishing our technique as
-a significant ingredient in the state of the art for solving partially
-ordered HTN problems. As a side contribution, we identify a new class of
-decidable (EXPTIME-complete) HTN problems, namely those where our
-preprocessing technique is guaranteed to be solvability-preserving.
-\end{abstract}
-
-\section{Introduction}
-\input{01--intro.tex}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
-
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-
-Many problems might be naturally more suited to being modelled as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Where this is possible, it results in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
-
-\section{Hierarchical Planning Formalism}
-\input{02--htn.tex}
-
-\section{Linearizing Grounded HTN Problems}
-\input{03--linearization-ground.tex}
-
-% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
-We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
-This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.
-
-% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
-
-% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
-Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
-
-% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
-If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
-This is true for all possible tasks by simple induction over the decomposition process.
-
-% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-% Specifically, let $\sigma$ be the set of parameters for the method.
-Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
-Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
-
-% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
-For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
-% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
-
-% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
-The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
-Only one linearized lifted method per partially-ordered lifted method is produced.
-
-% For a grounded method, there are no parameters in a task or method.
-Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
-We can then use these to produce a linearized grounded method per grounded method.
-
-% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
-For a grounded model, $f' = f$.
-The inferred preconditions and effects for a task are then defined as below:
-% \begin{align*}
-% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
-% & \forall t \in T_P : \AddS(t) := \Add(t) \\
-% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-% \end{align*}
-
-% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
-% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
-Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
-
-%State-independent positive and negative effects (cf.
-their Def.
-4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
-%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-% after every refinement of c but after at least one:
-% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% The set of executability-enabling states of c is
-% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
-% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
-
-% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-
-% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
-% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
-% the precondition relaxation can make further refinements executable that produce
-% effects that can not be achieved in the non-relaxed domain. 
-% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
-
-% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
-refinements (ignoring executability of the refinement) $\langle a_0 ...
-a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.
-
-% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
-% In this paper, we will be utilising both of these, as seen in the next section.
-%the precondition-relaxed possible effects, which may hold after at least one refinement of c.
-
-%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
-%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
-%f ∈ prec(ai) and there does not exist an action aj with
-%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
-%The exploitation of the relaxed preconditions and effects
-%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates
-
-\section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}
-
-% \begin{algorithm}[h]
-% 	\caption{Calculation of linearized methods}
-% 	\label{alg:Algorithm1}
-% 	\KwData{$(F, T_P, T_C, \delta, M)$}
-% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-% 	{
-% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-% 		$G \gets \singlePrec$ \\
-% 		\label{alg:StartBuildGraph}
-% 		\For{a $\in$ F}{  
-% 			\For{$t \in T_m$}{
-% 				\For{$t' \in T_m$}{
-% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-% 				}
-% 			} 
-% 			\label{alg:EndBuildGraph}	
-% 		}	
-% 		\label{alg:StartCycleBreak}
-% 		\While{$G$ has cycles in it}{
-% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-% 		}
-% 		\label{alg:EndCycleBreak}
-% 		$\prec'$ = Any linearization of $G$ \\
-% 		\label{alg:TopSort}
-% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
-% 		$M' = M' \cup  \{m'\}$ \\
-
-% 	}
-% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-% \end{algorithm}
-
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
-For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:
-
- \begin{figure}[h]
- 	\caption{Example of Desired Additional Orderings}
- 	\label{fig:OrderingRules}
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{first}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{second}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(first) edge [->,bend right] node [left]  {} (second);
-			\end{tikzpicture}
-
-			\caption{B adds a fact in preconditions of A -- so B before A}
-
-		\end{subfigure}
-	}  
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{C deletes a fact in preconditions of A  -- so A before C}	
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->, bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{B adds a fact that C deletes -- so C before B}
-		\end{subfigure}
-	} 
-\end{figure}
-
-\begin{figure}[h]
-	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
-	\label{fig:CycleBreaking}
-	\scalebox{0.75}{
-		\begin{subfigure}{7cm} 
-		 	\centering
-			\caption{Resulting method ordering has a cycle}
-			\label{fig:CycleBreaking1}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-			(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{6cm} 
-		 %	\centering
-			\caption{Delete any random ordering to break it}
-			\label{fig:CycleBreaking2}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-		%	(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-%	\scalebox{0.75}{
-%		\begin{subfigure}{7cm} 
-%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
-%			\label{fig:NotCycleBreaking}
-%			\begin{tikzpicture}[auto,node distance=1.2cm,
-%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-%			\action{B}{SingleAddAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em 
-%			};
-
-%			\action{A}{SinglePrecAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em,
-%				body = {right = 4em of first} 		
-%			};
-
-%			\path[every node/.style={font=\sffamily\small}]
-%			(B) edge [->,bend right] node [left]  {} (A);
-%			\end{tikzpicture}
-
-%			\caption{Resulting method ordering has no cycle}
-%			
-%		\end{subfigure}
-%	}   
-\end{figure}
-
-% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase.
-Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
-% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
-
-\section{Theoretical Properties of Linearization Result}
-
-We now discuss the implications of the above-described linearization procedure.
-
-\begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
-\end{theorem}
-\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
-	Let $|T|$ = $|T_P| + |T_C|$.
-
-	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
-
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$.
-We explore it's compound sub-tasks until we collect all primitive tasks.
-Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree.
-This is obviously polynomial in terms of $|T|$.
-%This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
-This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
-% we explore all poss (at most $|T_C|$)
-
-	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
-Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.
-
-	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.
-
-	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
-% and $\mathcal{O}(V)$ in space.
-	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
-
-	So the algorithm takes polynomial time. 
-\end{proof}
-
-\begin{theorem}\label{thm:Soundness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
-\end{theorem}
-\begin{proof}
-	The new desired orderings for a method include all of the orderings already required by the method originally.
-The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph.
-This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one.
-Any solution to the linearized problem is then obviously a solution to the original problem.
-\end{proof}
-
-\begin{theorem}\label{thm:notCompleteness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then $sol(P')$ may be empty.
-\end{theorem}
-\begin{proof}
-	This algorithm linearizes all the methods to be totally ordered.
-Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents are already ordered with respect to each other.
-This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
-Consider the simple example problem:
-	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
-	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$.
-This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution.
-	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
-	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
-Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
-	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
-\end{proof}
-
-% The exploitation of the relaxed preconditions and effects
-% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.
-
-\begin{description}
-	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, or in other words, \emph{cycle-breaking} did not occur, that method is said to meet the linearization criteria.
-If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well.
-\end{description}
-
-%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.
-
-\begin{theorem} \label{thm:RelaxedPreconditions}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, \emph{only if $P$, the entire problem meets the linearization criteria},
-	then we know executability-relaxed preconditions for any $c$ are indeed the only ones needed to execute any refinement of $c$.
-\end{theorem}
-\begin{proof}
-%	At least in the case where the linearization criteria is met for all methods, we can be assured that the executability-relaxed preconditions actually work for us.
-
-	For some method with at least two sub-tasks, $a$ and $b$,
-	the desired orderings are to put $a$ with $f \in \Add(a)$ before $b$ with $f \in \Pre(b)$.
-We're assuming no cycle-breaking, so this was actually achieved.
-If such a precondition can't be met this way, (such an $a$ does not exist, or the method already enforces that $b$ executes before $a$) by definition it must be in the executability-relaxed preconditions calculated.
-
-	Therefore, any precondition of $c$'s children that can't be met by placing other children of $c$ before it is part - so it is indeed a super-set of actual preconditions, assuming no cycle-breaking was needed.
-
-	If even one partially ordered method did need cycle-breaking, than of course it means nothing - we may indeed need other preconditions to make refinements of $c$ executable.
-Then those results no longer hold.
-\end{proof}
-
-We use Theorem~\ref{thm:RelaxedPreconditions} as support for the following main result.
-We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.
-
-\begin{theorem}\label{thm:SpecialCase}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if $P$ meets the linearization criteria and $sol(P)$ is non-empty, then $sol(P')$ will be non-empty as well.
-\end{theorem}
-\begin{proof}	
-	Assume that there exists a solution in the PO domain.
-By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain.
-Assume this sequence is $(a_0, a_1, ..., a_n)$.
-We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
-	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state.
-The action $a_k$ could only be non-executable, if one or more of its preconditions was not met.
-Assume one of these unmet preconditions is for existence of the state variable $A$.
-	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution.
-So there must exist an action $a_i$, $0 < i < n$, that will add A.
-Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree.
-So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.
-
-	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
-We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required, either directly or via inheritance from parent tasks.
-This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
-In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.
-
-	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution.
-Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
-\end{proof}
-
-There are several possible levels of \enquote{completeness} for a problem compilation.
-%\begin{enumerate}
-\begin{itemize}
-	\item all solutions remain 
-	\item at least one solution remains 
-	\item all optimal solutions remain
-	\item at least one optimal solution remains 	
-\end{itemize}
-%\end{enumerate}
-Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if linearization criteria is met.
-Otherwise, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions.
-Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.
-
-\begin{theorem}\label{thm:newClass}
-	Problems $P$ that satisfy the linearization criteria form a new class of decidable problems.
-\end{theorem}
-\begin{proof}
-	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.
-\end{proof}
-
-\section{Empirical Evaluation}
-We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems.
-All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
-The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
-Each problem has the standard IPC time limit of 30 minutes.
-Any grounding and pre-processing time needed is included as part of the 'solving' time.
-Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
-
-\subsection{Hardware and Planning Systems}
-The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested.
-Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.
-
-We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
-This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
-The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
-
-% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
-
-%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}
-
-We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
-%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
-We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
-The same setting is used for re-runs.
-For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
-We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems.
-Re-runs use panda$_{\pi}$ with the best heuristic(Add).
-We test both Complex and Simple Inference for linearization.
-Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
-
-The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
-As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-
-The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.
-
-For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
-the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem.
-For each total-order planner, the column beneath it shows performance on the linearized problem.
-The IPC score has a maximum of 1 per domain, for the 12 domains in total.
-
-%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}
-
-The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
-achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}.
-This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average.
-However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains.
-E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.
-
-Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
-When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
-%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
-
-%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
-
-%\todo{proven unsolvable should not be in superscripts}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleCoverage}
-	\scalebox{0.8} {
-\begin{tabular}{lccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO\\  
-	\midrule 
-	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
-	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
-	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
-	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
-			\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-			\midrule 
-	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
-	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleIPC}
-	\scalebox{0.85} {
-	\begin{tabular}{lccccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	& PO & TO & PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\
-
-	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
-	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\
-
-	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
-	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
-	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
-	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\
-
-	\midrule 
-	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\
-
-	\bottomrule 
-		\end{tabular} 		
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleCoverage}
-	\scalebox{0.65} {
-		\begin{tabular}{lccccccccccl} 
-			\toprule 
-			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-			&PO & TO & PO & TO  \\ 
-\midrule 
-Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
-PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
-Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
-Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
-UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
-Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
-\midrule 
-Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
-SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
-Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
-\midrule 
-Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
-Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
-\bottomrule 
-		\end{tabular}
-
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleIPC}
-	\scalebox{0.7} {
-\begin{tabular}{lccccccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
-	&PO & TO & PO & TO  \\  
-\midrule 
-Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
-PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
-Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
-Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
-UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
-Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
-\midrule 
-Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
-SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
-Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-\midrule 
-IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
-\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexCoverage}.
-	\scalebox{0.8} {
-
-\begin{tabular}{lccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
-	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
-	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\
-
-	\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
-	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\
-
-		\midrule 
-	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexIPC}.
-	\scalebox{0.8} { 
-\begin{tabular}{lccccccl} 
-			\toprule 
-		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO  &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\
-
-	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
-	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
-	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
-	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
-	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
-	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-		\midrule 
-	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
-	\bottomrule 
-\end{tabular}  
-	}
-\end{table}
-
-\begin{table} 
-	\centering  
-	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
-	\label{table:FullyLinearizedProblems}
-	\scalebox{0.75} { 
-	\begin{tabular}{lcccl} 
-		\toprule
-		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
-		\midrule
-		SmartPhone  & 4.0                   &  1     \\
-		Transport   & 1144.9                & 40       \\
-		UM-Translog & 1.1                    & 17   \\
-		Woodworking & 2035              &   21    \\
-				\bottomrule 
-	\end{tabular} 
-	}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are from using Simple Inference.
-Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
-	\label{table:SimpleLinearizable} 
-		\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
-		\midrule
-Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
-Monroe & 12127.3 & 3447.8 & 72.4  \\ 
-Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
-Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
-PCP & 12.3 & 12.3 & 0.0  \\ 
-Rover & 509.4 & 355.2 & 32.3  \\ 
-Satellite & 70.6 & 36.1 & 50.9  \\ 
-SmartPhone & 6.3 & 4.0 & 21.8  \\ 
-Transport & 1144.9 & 1144.9 & 0.0  \\ 
-UM-Translog & 1.5 & 1.5 & 0.0  \\ 
-Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
-Zenotravel & 190.2 & 99.4 & 47.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
-	\label{table:ComplexLinearizable} 
-	\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
-		\midrule
-			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
-			Monroe & 12127.3 & 216.9 & 98.2  \\ 
-			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
-			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
-			PCP & 12.3 & 4.9 & 59.8  \\ 
-			Rover & 509.4 & 134.8 & 72.4  \\ 
-			Satellite & 70.6 & 10.7 & 77.9  \\ 
-			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
-			Transport & 1144.9 & 0.0 & 100.0  \\ 
-			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
-			Woodworking & 1927.3 & 476.0 & 85.5  \\
-			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
-			\bottomrule 
-		\end{tabular} 
-		}
-\end{table}
-
-While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
-(Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
-
-\begin{table} 
-	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain.
-Shows Results for Both Inference Methods.}\label{table:POMethodBreak}
-	\begin{tabular}{lccl} 
-		\toprule 
-		Domain & Complex & Simple &  \\ 
-		\midrule
-		Transport & 1.0 & 0.0  \\ 
-		UM-Translog & 0.8 & 0.0  \\ 
-		Satellite & 1.0 & 0.0  \\ 
-		Monroe Fully Observ. & 1.0 & 0.0  \\ 
-		Rover & 1.0 & 0.0  \\ 
-		Woodworking & 0.9 & 0.0  \\ 
-		Monroe Part. Observ. & 1.0 & 0.0  \\ 
-		PCP & 0.0 & 0.0  \\ 
-		Barman-BDI & 1.0 & 0.0  \\ 
-		SmartPhone & 0.1 & 0.1  \\ 
-		Monroe & 0.8 & 0.0  \\ 
-		Zenotravel & 1.0 & 0.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-\end{table}
-
-%\begin{figure*}
-%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
-%	\label{fig:ProblemsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
-%\end{figure*}
-
-%\begin{figure*}
-%	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without %Cycle-break for Each Domain and for Each Inference Method}
-%	\label{fig:MethodsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
-%\end{figure*}
-
-\section{Related Work}
-There exist other planners that also compile POHTN problems to decidable planning classes e.g.
-the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems.
-To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.
-
-\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
-of actions has an executable linearization.
-Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions.
-That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time.
-It can also find a executable linearization for that subset in polynomial time.
-
-\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.
-\cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
-In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
-
-Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
-This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.
-Thus their results are orthogonal to ours.
-
-The paper by \citet{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
-set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
-
-\section{Future Work}
-%Encode Linearization Problem as a MAX-SAT Problem
-The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
-MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.
-
-The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-% Assuming no negative preconditions, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
-The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
-
-%Adding a Plan as Additional Input to the Domain
-%Adding a plan as additional input to the PO domain having the semantics that this plan shall be in the solution set of the TO output model.
-This reduces the computational complexity of the decision problem from undecidable.
-% I assume the resulting problem is PSPACE-complete, but this needs to be proven
-
 \section{Conclusion}
-
-% The contributions of this paper are as follows:
 
@@
 Finally, in this paper we identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all others discussed in other works.
-
-% Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
-\bibliography{bib}
-% \nobibliography{aaai22}
-
-\end{document}

### 2022-12-20 paper/paper-mainfile.tex
...

--- 2022-12-15 paper/paper-mainfile.tex
@@
-\def\year{2022}\relax
-%File: formatting-instructions-latex-2022.tex
-%release 2022.1
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
-%
-% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
-% \usepackage{algorithm}
+%%%% ijcai22.tex
+
+\typeout{IJCAI--22 Instructions for Authors}
+
+% These are the instructions for authors for IJCAI-22.
+
+\documentclass{article}
+\pdfpagewidth=8.5in
+\pdfpageheight=11in
+% The file ijcai22.sty is NOT the same as previous years'
+\usepackage{ijcai22}
+
+% Use the postscript times font!
+\usepackage{times}
+\usepackage{soul}
+\usepackage{url}
+\usepackage[hidelinks]{hyperref}
+\usepackage[utf8]{inputenc}
+\usepackage[small]{caption}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{booktabs}
+\usepackage{algorithm}
 % \usepackage{algorithmic}
-% \usepackage[noend]{algpseudocode}
+\urlstyle{same}
 
-%
-% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
-\usepackage{newfloat}
-\usepackage{listings}
-\lstset{%
-	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
-	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
-	aboveskip=0pt,belowskip=0pt,%
-	showstringspaces=false,tabsize=2,breaklines=true}
-%\floatstyle{ruled}
-%\newfloat{listing}{tb}{lst}{}
-%\floatname{listing}{Listing}
+% the following package is optional:
+%\usepackage{latexsym}
 
-%
-% user import packages
+% See https://www.overleaf.com/learn/latex/theorems_and_proofs
+% for a nice explanation of how to define new theorems, but keep
+% in mind that the amsthm package is already included in this
+% template and that you must *not* alter the styling.
+\newtheorem{example}{Example}
+\newtheorem{theorem}{Theorem}
+
+% % % % % PACKAGES IMPORTED BY US % % % % %
 \usepackage{amsfonts}
@@
 \usepackage{amsmath}
-\usepackage{paralist}
-\usepackage{todonotes}
-\usepackage{booktabs}
-\usepackage{varwidth}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{xcolor}
-\usepackage{booktabs} 
-% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
-\usepackage{csquotes}
-\usepackage{subcaption}
 \usepackage{amssymb}
 \usepackage{mathbbol}
+\usepackage[noend]{algpseudocode}
+\usepackage{paralist}
+\usepackage{booktabs}
+\usepackage{xcolor}
+\usepackage{subcaption}
 \usepackage{tikz}
@@
 
-\scheme{SinglePrec}{0}{
-	text = {\textbf{A}},
-	pre  = {a}
+% Following comment is from ijcai97-submit.tex:
+% The preparation of these files was supported by Schlumberger Palo Alto
+% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
+% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
+% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
+% preparation.
+
+% These instructions can be modified and used in other conferences as long
+% as credit to the authors and supporting agencies is retained, this notice
+% is not changed, and further modification or reuse is not restricted.
+% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
+% contacts for providing assistance without their prior permission.
+
+% To use for other conferences, change references to files and the
+% conference appropriate and use other authors, contacts, publishers, and
+% organizations.
+% Also change the deadline and address for returning papers and the length and
+% page charge instructions.
+% Put where the files are available in the appropriate places.
+
+% PDF Info Is REQUIRED.
+% Please **do not** include Title and Author information
+\pdfinfo{
+/TemplateVersion (IJCAI.2022.0)
 }
 
-\scheme{SingleAdd}{0}{
-	text = {\textbf{B}},
-	effs = { a}
-}
+\title{``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)}
 
-\scheme{SingleDelete}{0}{
-	text = {\textbf{C}},
-	effs = { {{$\neg$}a} }
-}
+\author{Anonymous}
 
-\scheme{SinglePrecAlt}{0}{
-	text = {\textbf{D}},
-	pre  = {a}
-}
+% Single author syntax
+% \author{
+%     Author Name
+%     \affiliations
+%     Affiliation
+%     \emails
+%     pcchair@ijcai-22.org
+% }
 
-\scheme{SingleAddAlt}{0}{
-	text = {\textbf{E}},
-	effs = { a}
-}
-
-\scheme{PrimitiveA}{0}{
-	text = {\textbf{A}},
-	pre  = {a},
-	effs = { {{$\neg$}a}, {b} }
-}
-
-\scheme{PrimitiveB}{0}{
-	text = {\textbf{B}},
-	pre = {b},
-	effs = {{{$\neg$}b}, {c}}
-}
-
-\scheme{PrimitiveC}{0}{
-	text = {\textbf{C}},
-	pre = {c},
-	eff = {{$\neg$}c}
-}
-
-\nocopyright
-%
-% PDF Info Is REQUIRED.
-% For /Title, write your title in Mixed Case.
-% Don't use accents or commands. Retain the parentheses.
-% For /Author, add all authors within the parentheses,
-% separated by commas. No accents, special characters
-% or commands are allowed.
-% Keep the /TemplateVersion tag as is
-\pdfinfo{
-/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
-Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
-/Author (Anonymous)
-/TemplateVersion (2022.1)
-}
-
-% DISALLOWED PACKAGES
-% \usepackage{authblk} -- This package is specifically forbidden
-% \usepackage{balance} -- This package is specifically forbidden
-% \usepackage{color (if used in text)
-% \usepackage{CJK} -- This package is specifically forbidden
-% \usepackage{float} -- This package is specifically forbidden
-% \usepackage{flushend} -- This package is specifically forbidden
-% \usepackage{fontenc} -- This package is specifically forbidden
-% \usepackage{fullpage} -- This package is specifically forbidden
-% \usepackage{geometry} -- This package is specifically forbidden
-% \usepackage{grffile} -- This package is specifically forbidden
-% \usepackage{hyperref} -- This package is specifically forbidden
-% \usepackage{navigator} -- This package is specifically forbidden
-% (or any other package that embeds links such as navigator or hyperref)
-% \indentfirst} -- This package is specifically forbidden
-% \layout} -- This package is specifically forbidden
-% \multicol} -- This package is specifically forbidden
-% \nameref} -- This package is specifically forbidden
-% \usepackage{savetrees} -- This package is specifically forbidden
-% \usepackage{setspace} -- This package is specifically forbidden
-% \usepackage{stfloats} -- This package is specifically forbidden
-% \usepackage{tabu} -- This package is specifically forbidden
-% \usepackage{titlesec} -- This package is specifically forbidden
-% \usepackage{tocbibind} -- This package is specifically forbidden
-% \usepackage{ulem} -- This package is specifically forbidden
-% \usepackage{wrapfig} -- This package is specifically forbidden
-% DISALLOWED COMMANDS
-% \nocopyright -- Your paper will not be published if you use this command
-% \addtolength -- This command may not be used
-% \balance -- This command may not be used
-% \baselinestretch -- Your paper will not be published if you use this command
-% \clearpage -- No page breaks of any kind may be used for the final version of your paper
-% \columnsep -- This command may not be used
-% \newpage -- No page breaks of any kind may be used for the final version of your paper
-% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
-% \pagestyle -- This command may not be used
-% \tiny -- This is not an acceptable font size.
-% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
-% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference
-
-\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.
-
-% The file aaai22.sty is the style file for AAAI Press
-% proceedings, working notes, and technical reports.
-%
-
-% Title
-
-% Your title must be in mixed case, not sentence case.
-% That means all verbs (including short verbs like be, is, using,and go),
-% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
-% articles, conjunctions, and prepositions are lower case unless they
-% directly follow a colon or long dash
-
-%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
-% \iffalse
-
-\newtheorem{theorem}{Theorem}
-
-\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
-\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
-
-\newcommand{\Add} {\ensuremath{\mathit{add}}}
-\newcommand{\Del} {\ensuremath{\mathit{del}}}
-\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
-\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
-\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
-\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
-\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
-
-%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}
-
-%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
-%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
-\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
-\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
-
-\author {
-    Submission
-}
-\affiliations{
-    Anonymous
-}
-% \fi
-
-%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
+% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
 \iffalse
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-\author {
-    % Authors
-    Anonymous
-
-}
-\affiliations {
-    % Affiliations
-    Anonymous
+\author{
+First Author$^1$
+\and
+Second Author$^2$\and
+Third Author$^{2,3}$\And
+Fourth Author$^4$
+\affiliations
+$^1$First Affiliation\\
+$^2$Second Affiliation\\
+$^3$Third Affiliation\\
+$^4$Fourth Affiliation
+\emails
+\{first, second\}@example.com,
+third@other.example.com,
+fourth@example.com
 }
@@
 
-\title{Order is half of life -- Establishing Totally Ordered HTN
-	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
+\begin{document}
 
-%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
-%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
-
-% REMOVE THIS: bibentry
-% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
-% \usepackage{bibentry}
-% END REMOVE bibentry
-
-\begin{document}
-\input{00--macro.tex}
 \maketitle
@@
 \begin{abstract}
-HTN planning is in general undecidable, yet there exist efficient
-planning algorithms. An important subclass is that of totally ordered
-HTN planning problems. Not only is this class decidable, but also easier
-to handle algorithmically since tasks cannot interleave anymore.
-Consequently, several specialized solvers exist, and dedicated tracks at
-the International Planning Competition (IPC) in both 2020 and 2023. We
-were able to show that almost all currently existing partially ordered
-planning benchmarks can be turned into totally ordered ones without
-sacrificing solvability. Establishing totally ordered problems in a
-preprocessing technique thus allows to use planning systems, heuristics,
-pruning techniques (etc.) that are only available for totally ordered
-problems. This allows solving problems more efficiently and with
-better-informed techniques, at the (little) cost of doing a
-preprocessing technique. We show that in only a very few cases
-linearization isn't possible, and in all others establishing a total
-order pays off \emph{significantly}, thus establishing our technique as
-a significant ingredient in the state of the art for solving partially
-ordered HTN problems. As a side contribution, we identify a new class of
-decidable (EXPTIME-complete) HTN problems, namely those where our
-preprocessing technique is guaranteed to be solvability-preserving.
+HTN planning is in general undecidable, yet there exist efficient planning algorithms.
+An important subclass is that of totally ordered HTN planning problems.
+Not only is this class decidable, but also easier to handle algorithmically since tasks cannot interleave anymore.
+Consequently, several specialized solvers exist, and dedicated tracks at the International Planning Competition (IPC) in both 2020 and 2023.
+We were able to show that almost all currently existing partially ordered planning benchmarks can be turned into totally ordered ones without sacrificing solvability.
+Establishing totally ordered problems in a preprocessing technique thus allows to use planning systems, heuristics, pruning techniques (etc.) that are only available for totally ordered problems.
+This allows solving problems more efficiently and with better-informed techniques, at the (little) cost of doing a preprocessing technique.
+We show that in only a very few cases linearization isn't possible, and in all others establishing a total order pays off \emph{significantly}, thus establishing our technique as a significant ingredient in the state of the art for solving partially ordered HTN problems.
+As a side contribution, we identify a new class of decidable (EXPTIME-complete) HTN problems, namely those where our preprocessing technique is guaranteed to be solvability-preserving.
 \end{abstract}
 
-\section{Introduction}
-\input{01--intro.tex}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
-tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
-HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks.
-A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
+\input{00--macros}
 
-In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks.
-In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
+\input{01--introduction}
+\input{02--formalism}
+\input{03--linearization-ground}
+\input{04--otherLinearization}
+\input{05--theory}
+\input{06--evaluation}
+\input{07--relatedWork}
+\input{08--futureWork}
+\input{09--conclusion}
 
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
-
-Many problems might be naturally more suited to being modelled as POHTN problems.
-However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
-Where this is possible, it results in lower worst-case solving time.
-Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.
-
-Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
-Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
-We prove that when certain criteria are met, it guarantees that at least one solution will be preserved.
-Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion.
-Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
-
-\section{Hierarchical Planning Formalism}
-\input{02--htn.tex}
-
-\section{Linearizing Grounded HTN Problems}
-\input{03--linearization-ground.tex}
-
-% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks.
-We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other.
-This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.
-
-% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
-
-% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type.
-Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.
-
-% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed.
-If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$.
-This is true for all possible tasks by simple induction over the decomposition process.
-
-% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.
-
-% Specifically, let $\sigma$ be the set of parameters for the method.
-Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$.
-Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.
-
-% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects.
-For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects.
-% This is illustrated in Figure~\ref{CompoundPreEffForLifted}.
-
-% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$.
-The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded.
-Only one linearized lifted method per partially-ordered lifted method is produced.
-
-% For a grounded method, there are no parameters in a task or method.
-Methods decompose to specific actions, actions have preconditions and effects on specific state variables.
-We can then use these to produce a linearized grounded method per grounded method.
-
-% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
-For a grounded model, $f' = f$.
-The inferred preconditions and effects for a task are then defined as below:
-% \begin{align*}
-% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
-% & \forall t \in T_P : \AddS(t) := \Add(t) \\
-% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-% \end{align*}
-
-% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
-% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects.
-Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.
-
-%State-independent positive and negative effects (cf.
-their Def.
-4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
-%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-% after every refinement of c but after at least one:
-% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% The set of executability-enabling states of c is
-% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
-% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.
-
-% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-
-% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
-% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
-% the precondition relaxation can make further refinements executable that produce
-% effects that can not be achieved in the non-relaxed domain. 
-% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.
-
-% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.
-
-% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o.
-refinements (ignoring executability of the refinement) $\langle a_0 ...
-a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.
-
-% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
-% In this paper, we will be utilising both of these, as seen in the next section.
-%the precondition-relaxed possible effects, which may hold after at least one refinement of c.
-
-%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
-%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
-%f ∈ prec(ai) and there does not exist an action aj with
-%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
-%The exploitation of the relaxed preconditions and effects
-%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates
-
-\section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}
-
-% \begin{algorithm}[h]
-% 	\caption{Calculation of linearized methods}
-% 	\label{alg:Algorithm1}
-% 	\KwData{$(F, T_P, T_C, \delta, M)$}
-% 	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-% 	{
-% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
-% 		$G \gets \singlePrec$ \\
-% 		\label{alg:StartBuildGraph}
-% 		\For{a $\in$ F}{  
-% 			\For{$t \in T_m$}{
-% 				\For{$t' \in T_m$}{
-% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
-% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
-% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
-% 				}
-% 			} 
-% 			\label{alg:EndBuildGraph}	
-% 		}	
-% 		\label{alg:StartCycleBreak}
-% 		\While{$G$ has cycles in it}{
-% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
-% 		}
-% 		\label{alg:EndCycleBreak}
-% 		$\prec'$ = Any linearization of $G$ \\
-% 		\label{alg:TopSort}
-% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
-% 		$M' = M' \cup  \{m'\}$ \\
-
-% 	}
-% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-% \end{algorithm}
-
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
-For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:
-
- \begin{figure}[h]
- 	\caption{Example of Desired Additional Orderings}
- 	\label{fig:OrderingRules}
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{first}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{second}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(first) edge [->,bend right] node [left]  {} (second);
-			\end{tikzpicture}
-
-			\caption{B adds a fact in preconditions of A -- so B before A}
-
-		\end{subfigure}
-	}  
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{C deletes a fact in preconditions of A  -- so A before C}	
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm} 
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{A}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\action{B}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of A} 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->, bend right] node [left]  {} (A);
-			\end{tikzpicture}
-			\caption{B adds a fact that C deletes -- so C before B}
-		\end{subfigure}
-	} 
-\end{figure}
-
-\begin{figure}[h]
-	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
-	\label{fig:CycleBreaking}
-	\scalebox{0.75}{
-		\begin{subfigure}{7cm} 
-		 	\centering
-			\caption{Resulting method ordering has a cycle}
-			\label{fig:CycleBreaking1}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-			(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-	\scalebox{0.75}{
-		\begin{subfigure}{6cm} 
-		 %	\centering
-			\caption{Delete any random ordering to break it}
-			\label{fig:CycleBreaking2}
-			\begin{tikzpicture}[auto,node distance=1.2cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\action{B}{SingleAdd,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{A}{SinglePrec,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of first} 		
-			};
-
-			\action{C}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
-			};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(B) edge [->,bend right] node [left]  {} (A)
-		%	(A) edge [->,bend right] node [left]  {} (C)
-			(C) edge [->,bend right] node [left]  {} (B);
-			\end{tikzpicture}
-
-		\end{subfigure}
-	}
-
-%	\scalebox{0.75}{
-%		\begin{subfigure}{7cm} 
-%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
-%			\label{fig:NotCycleBreaking}
-%			\begin{tikzpicture}[auto,node distance=1.2cm,
-%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-%			\action{B}{SingleAddAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em 
-%			};
-
-%			\action{A}{SinglePrecAlt,
-%				width  = 2.5em, 
-%				height = 2.5em, 
-%				pre length = 1em,
-%				eff length = 1em,
-%				body = {right = 4em of first} 		
-%			};
-
-%			\path[every node/.style={font=\sffamily\small}]
-%			(B) edge [->,bend right] node [left]  {} (A);
-%			\end{tikzpicture}
-
-%			\caption{Resulting method ordering has no cycle}
-%			
-%		\end{subfigure}
-%	}   
-\end{figure}
-
-% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase.
-Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
-% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.
-
-\section{Theoretical Properties of Linearization Result}
-
-We now discuss the implications of the above-described linearization procedure.
-
-\begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
-\end{theorem}
-\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
-	Let $|T|$ = $|T_P| + |T_C|$.
-
-	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
-
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$.
-We explore it's compound sub-tasks until we collect all primitive tasks.
-Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree.
-This is obviously polynomial in terms of $|T|$.
-%This provides an upper limit of $(3 * |F| * |T_p|) + T_C$.
-This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
-% we explore all poss (at most $|T_C|$)
-
-	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
-Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.
-
-	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.
-
-	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
-% and $\mathcal{O}(V)$ in space.
-	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
-
-	So the algorithm takes polynomial time. 
-\end{proof}
-
-\begin{theorem}\label{thm:Soundness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
-\end{theorem}
-\begin{proof}
-	The new desired orderings for a method include all of the orderings already required by the method originally.
-The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph.
-This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one.
-Any solution to the linearized problem is then obviously a solution to the original problem.
-\end{proof}
-
-\begin{theorem}\label{thm:notCompleteness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then $sol(P')$ may be empty.
-\end{theorem}
-\begin{proof}
-	This algorithm linearizes all the methods to be totally ordered.
-Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents are already ordered with respect to each other.
-This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
-Consider the simple example problem:
-	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
-	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$.
-This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution.
-	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
-	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
-Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
-	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
-\end{proof}
-
-% The exploitation of the relaxed preconditions and effects
-% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.
-
-\begin{description}
-	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, or in other words, \emph{cycle-breaking} did not occur, that method is said to meet the linearization criteria.
-If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well.
-\end{description}
-
-%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.
-
-\begin{theorem} \label{thm:RelaxedPreconditions}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, \emph{only if $P$, the entire problem meets the linearization criteria},
-	then we know executability-relaxed preconditions for any $c$ are indeed the only ones needed to execute any refinement of $c$.
-\end{theorem}
-\begin{proof}
-%	At least in the case where the linearization criteria is met for all methods, we can be assured that the executability-relaxed preconditions actually work for us.
-
-	For some method with at least two sub-tasks, $a$ and $b$,
-	the desired orderings are to put $a$ with $f \in \Add(a)$ before $b$ with $f \in \Pre(b)$.
-We're assuming no cycle-breaking, so this was actually achieved.
-If such a precondition can't be met this way, (such an $a$ does not exist, or the method already enforces that $b$ executes before $a$) by definition it must be in the executability-relaxed preconditions calculated.
-
-	Therefore, any precondition of $c$'s children that can't be met by placing other children of $c$ before it is part - so it is indeed a super-set of actual preconditions, assuming no cycle-breaking was needed.
-
-	If even one partially ordered method did need cycle-breaking, than of course it means nothing - we may indeed need other preconditions to make refinements of $c$ executable.
-Then those results no longer hold.
-\end{proof}
-
-We use Theorem~\ref{thm:RelaxedPreconditions} as support for the following main result.
-We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.
-
-\begin{theorem}\label{thm:SpecialCase}
-	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if $P$ meets the linearization criteria and $sol(P)$ is non-empty, then $sol(P')$ will be non-empty as well.
-\end{theorem}
-\begin{proof}	
-	Assume that there exists a solution in the PO domain.
-By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain.
-Assume this sequence is $(a_0, a_1, ..., a_n)$.
-We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
-	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state.
-The action $a_k$ could only be non-executable, if one or more of its preconditions was not met.
-Assume one of these unmet preconditions is for existence of the state variable $A$.
-	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution.
-So there must exist an action $a_i$, $0 < i < n$, that will add A.
-Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree.
-So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.
-
-	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
-We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required, either directly or via inheritance from parent tasks.
-This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
-In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.
-
-	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution.
-Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
-\end{proof}
-
-There are several possible levels of \enquote{completeness} for a problem compilation.
-%\begin{enumerate}
-\begin{itemize}
-	\item all solutions remain 
-	\item at least one solution remains 
-	\item all optimal solutions remain
-	\item at least one optimal solution remains 	
-\end{itemize}
-%\end{enumerate}
-Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if linearization criteria is met.
-Otherwise, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions.
-Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.
-
-\begin{theorem}\label{thm:newClass}
-	Problems $P$ that satisfy the linearization criteria form a new class of decidable problems.
-\end{theorem}
-\begin{proof}
-	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.
-\end{proof}
-
-\section{Empirical Evaluation}
-We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems.
-All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
-The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
-Each problem has the standard IPC time limit of 30 minutes.
-Any grounding and pre-processing time needed is included as part of the 'solving' time.
-Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
-
-\subsection{Hardware and Planning Systems}
-The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested.
-Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.
-
-We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
-This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
-The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
-
-% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }
-
-%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}
-
-We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
-%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
-We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
-The same setting is used for re-runs.
-For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
-We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems.
-Re-runs use panda$_{\pi}$ with the best heuristic(Add).
-We test both Complex and Simple Inference for linearization.
-Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
-
-The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
-As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-
-The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.
-
-For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
-the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem.
-For each total-order planner, the column beneath it shows performance on the linearized problem.
-The IPC score has a maximum of 1 per domain, for the 12 domains in total.
-
-%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}
-
-The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
-achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}.
-This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average.
-However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains.
-E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.
-
-Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
-When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
-%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.
-
-%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
-%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
-%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
-%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
-%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
-%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\
-
-%\todo{proven unsolvable should not be in superscripts}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleCoverage}
-	\scalebox{0.8} {
-\begin{tabular}{lccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO\\  
-	\midrule 
-	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
-	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
-	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
-	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
-			\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
-			\midrule 
-	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
-	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
-	\label{table:GroundedSimpleIPC}
-	\scalebox{0.85} {
-	\begin{tabular}{lccccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	& PO & TO & PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\
-
-	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
-	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
-	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\
-
-	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
-	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
-	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
-	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\
-
-	\midrule 
-	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\
-
-	\bottomrule 
-		\end{tabular} 		
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleCoverage}
-	\scalebox{0.65} {
-		\begin{tabular}{lccccccccccl} 
-			\toprule 
-			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-			&PO & TO & PO & TO  \\ 
-\midrule 
-Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
-PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
-Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
-Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
-UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
-Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
-\midrule 
-Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
-SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
-Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
-\midrule 
-Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
-Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
-\bottomrule 
-		\end{tabular}
-
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
-	\label{table:LiftedSimpleIPC}
-	\scalebox{0.7} {
-\begin{tabular}{lccccccccccl} 
-	\toprule 
-	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
-	&PO & TO & PO & TO  \\  
-\midrule 
-Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
-Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
-Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
-PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
-Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
-Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
-UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
-Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
-\midrule 
-Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
-SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
-Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-\midrule 
-IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
-\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexCoverage}.
-	\scalebox{0.8} {
-
-\begin{tabular}{lccccccl} 
-	\toprule 
-	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
-	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
-	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
-	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
-	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
-	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
-	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\
-
-	\midrule 
-	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
-	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
-	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\
-
-		\midrule 
-	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
-	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
-	\bottomrule 
-\end{tabular} 
-	}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
-	\label{table:GroundedComplexIPC}.
-	\scalebox{0.8} { 
-\begin{tabular}{lccccccl} 
-			\toprule 
-		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
-	&PO & TO  &PO & TO  \\ 
-	\midrule 
-	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\
-
-	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
-	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
-	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
-	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
-	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
-	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
-	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
-	\midrule 
-	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
-	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
-	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
-		\midrule 
-	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
-	\bottomrule 
-\end{tabular}  
-	}
-\end{table}
-
-\begin{table} 
-	\centering  
-	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
-	\label{table:FullyLinearizedProblems}
-	\scalebox{0.75} { 
-	\begin{tabular}{lcccl} 
-		\toprule
-		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
-		\midrule
-		SmartPhone  & 4.0                   &  1     \\
-		Transport   & 1144.9                & 40       \\
-		UM-Translog & 1.1                    & 17   \\
-		Woodworking & 2035              &   21    \\
-				\bottomrule 
-	\end{tabular} 
-	}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are from using Simple Inference.
-Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
-	\label{table:SimpleLinearizable} 
-		\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
-		\midrule
-Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
-Monroe & 12127.3 & 3447.8 & 72.4  \\ 
-Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
-Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
-PCP & 12.3 & 12.3 & 0.0  \\ 
-Rover & 509.4 & 355.2 & 32.3  \\ 
-Satellite & 70.6 & 36.1 & 50.9  \\ 
-SmartPhone & 6.3 & 4.0 & 21.8  \\ 
-Transport & 1144.9 & 1144.9 & 0.0  \\ 
-UM-Translog & 1.5 & 1.5 & 0.0  \\ 
-Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
-Zenotravel & 190.2 & 99.4 & 47.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-}
-\end{table}
-
-\begin{table} 
-	\centering
-	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
-	\label{table:ComplexLinearizable} 
-	\scalebox{0.65} { 
-	\begin{tabular}{lcccl} 
-		\toprule 
-		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
-		\midrule
-			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
-			Monroe & 12127.3 & 216.9 & 98.2  \\ 
-			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
-			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
-			PCP & 12.3 & 4.9 & 59.8  \\ 
-			Rover & 509.4 & 134.8 & 72.4  \\ 
-			Satellite & 70.6 & 10.7 & 77.9  \\ 
-			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
-			Transport & 1144.9 & 0.0 & 100.0  \\ 
-			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
-			Woodworking & 1927.3 & 476.0 & 85.5  \\
-			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
-			\bottomrule 
-		\end{tabular} 
-		}
-\end{table}
-
-While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
-(Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
-
-\begin{table} 
-	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain.
-Shows Results for Both Inference Methods.}\label{table:POMethodBreak}
-	\begin{tabular}{lccl} 
-		\toprule 
-		Domain & Complex & Simple &  \\ 
-		\midrule
-		Transport & 1.0 & 0.0  \\ 
-		UM-Translog & 0.8 & 0.0  \\ 
-		Satellite & 1.0 & 0.0  \\ 
-		Monroe Fully Observ. & 1.0 & 0.0  \\ 
-		Rover & 1.0 & 0.0  \\ 
-		Woodworking & 0.9 & 0.0  \\ 
-		Monroe Part. Observ. & 1.0 & 0.0  \\ 
-		PCP & 0.0 & 0.0  \\ 
-		Barman-BDI & 1.0 & 0.0  \\ 
-		SmartPhone & 0.1 & 0.1  \\ 
-		Monroe & 0.8 & 0.0  \\ 
-		Zenotravel & 1.0 & 0.0  \\ 
-		\bottomrule 
-	\end{tabular} 
-\end{table}
-
-%\begin{figure*}
-%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
-%	\label{fig:ProblemsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
-%\end{figure*}
-
-%\begin{figure*}
-%	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without %Cycle-break for Each Domain and for Each Inference Method}
-%	\label{fig:MethodsLinearizedWOCycleBreak}
-%	\centering
-%	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
-%\end{figure*}
-
-\section{Related Work}
-There exist other planners that also compile POHTN problems to decidable planning classes e.g.
-the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems.
-To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.
-
-\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
-of actions has an executable linearization.
-Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions.
-That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time.
-It can also find a executable linearization for that subset in polynomial time.
-
-\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.
-\cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
-In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
-
-Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
-This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.
-Thus their results are orthogonal to ours.
-
-The paper by \citet{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
-set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.
-
-\section{Future Work}
-%Encode Linearization Problem as a MAX-SAT Problem
-The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
-MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.
-
-The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-% Assuming no negative preconditions, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
-The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
-
-%Adding a Plan as Additional Input to the Domain
-%Adding a plan as additional input to the PO domain having the semantics that this plan shall be in the solution set of the TO output model.
-This reduces the computational complexity of the decision problem from undecidable.
-% I assume the resulting problem is PSPACE-complete, but this needs to be proven
-
-\section{Conclusion}
-
-% The contributions of this paper are as follows:
-
-This paper finds that, at least for the POHTN problems in the IPC domain, most of them are not undecidable.
-In other words, it is as if the POHTN domains are compressed TO domains - this linearization separates one of them back out.
-
-We can also see this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
-Furthermore, there is demonstrably much more room for improvement.
-Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
-
-This method can also be used to increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
-Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
-Then $k+m$ (lifted or grounded) TOHTN problems exist now.
-And from empirical evaluation, $k$ may be close to $n$.
-
-Finally, in this paper we identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all others discussed in other works.
-
-% Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
+%% The file named.bst is a bibliography style file for BibTeX 0.99c
+\bibliographystyle{named}
 \bibliography{bib}
-% \nobibliography{aaai22}
 

### 2022-12-20 stuff/old-stuff/01-intro-inText.tex
...

--- 2022-11-08 paper/mainfile.tex
@@
-\documentclass[letterpaper]{article}
-% DO NOT CHANGE THIS
-% \usepackage[submission]{aaai23} % DO NOT CHANGE THIS
-\usepackage[submission]{../AuthorKit23/AnonymousSubmission/LaTeX/aaai23}
-\usepackage{times} % DO NOT CHANGE THIS
-\usepackage{helvet} % DO NOT CHANGE THIS
-\usepackage{courier} % DO NOT CHANGE THIS
-\usepackage[hyphens]{url} % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm} % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\usepackage{natbib} % DO NOT CHANGE THIS
-\usepackage{caption} % DO NOT CHANGE THIS
-\frenchspacing % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
-%
-% Keep the \pdfinfo as shown here. There’s no need
-% for you to add the /Title and /Author tags.
-\pdfinfo{
-	/TemplateVersion (2023.1)
-} 
-\usepackage{booktabs} 
-\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
-\usepackage{csquotes}
-\usepackage{subcaption}
-\usepackage{amssymb,amsmath}
-\usepackage{todonotes} 
-\usepackage{tikz}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{proof}{Proof}
-
-\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
-\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)
-
-\newcommand{\Add} {\ensuremath{\mathit{add}}}
-\newcommand{\Del} {\ensuremath{\mathit{del}}}
-\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
-\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
-\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
-\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
-\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}
-
-\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
-\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
-\newcommand{\PossEffPlus} {\ensuremath{\mathit{poss-eff^{+}_{*}}}}
-\newcommand{\PossEffMinus} {\ensuremath{\mathit{poss-eff^{-}_{*}}}}
-
-\newcommand{\RelEffPlus} {\ensuremath{\mathit{eff^{\emptyset +}_{*}}}}
-\newcommand{\RelEffMinus} {\ensuremath{\mathit{eff^{\emptyset -}_{*}}}}
-\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
-\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}
-
-\title{Transforming Partially Ordered HTN Problems to Totally Ordered}
-\begin{document}
-\maketitle
-
-\begin{abstract}
-Solving partially ordered hierarchical planning problems is more computationally expensive compared to solving totally ordered ones.
-Therefore, automatically transforming partially ordered problem domains into totally ordered ones, such that the totally ordered problem still retains at least one solution, would be a desired capability as it would reduce complexity and thus make it easier for planning systems to solve the problem.
-It also allows the planner to use algorithms and heuristics specialised for the totally ordered case to solve the transformed problem.
-
-This is a complex endeavour, and not even possible in some cases, because even creating \emph{all} possible linearizations of all methods in the original domain does not guarantee that solutions are preserved.
-
-In this paper, we propose an algorithm for converting partially ordered problems into totally ordered ones and give criterion for when this conversion will retain at least one solution.
-We test our techniques on the partially-ordered track of the bench-mark set of the IPC 2020 and solve both the linearized and the original partially-ordered problems using state-of-the-art planning systems.
-We find that in the majority of problems across a variety of domains, the linearized problems remain solvable, and can always be solved faster than the without our proposed pre-processing technique.
-We can thus conclude our proposed pre-processing technique becomes (part of)
-the state of the art for solving partially ordered planning problems.
-\end{abstract}
-
 \section{Introduction}
-
+% \input{01--intro.tex}
 Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
@@
 Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
-
+% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
 The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem.
-For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages.
-On the other hand, TOHTN planning is not expressive enough to model undecideable problems.
 Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
-
-% Also, we get another class of decidable partially ordered problems that's orthogonal to recursive ones. 
-% Also, the domain model might be more intuitive: if a task is independent of some others it might be counter-intuitive to demand a certain position of it (if artificially made totally ordered).
-Plan recognition: independent goals can be described in parallel with POHTN planning but not with TOHTN, as per \cite{DanielPlanRecognition}.
-
-%\subsubsection{Contributions}
-%Gregor Behnke used a similar linearization process to produce the TO benchmark set used for the 2020 International Planning Competition (IPC 2020).
-That also attempted to linearize the methods by drawing the same links between preconditions and effects as in this paper, and picked a random linearization if that was not possible.
-However, no attempt was made to analyse if this lead to a easier to solve problem, or if it had any interesting theoretical implications.
-As Prof.
-Bercher thought this could be an interesting use for linearization, this paper offers this empirical evaluation and theoretical analysis.
-
 In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems.
@@
 Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.
-
-\section{Hierarchical Planning Formalism}
-Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning.
-There are many formalisations for HTN planning.
-The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}.
-HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning.
-TOHTN planning is a special case of POHTN planning.
-% except with the initial task network replaced by a initial compound task.
-
-A \textbf{Partially Ordered Hierarchical Planning}(POHTN) problem \textbf{P} = $(D, S_I, T_I)$
-is defined over some domain $D$, 
-has an initial state $S_I \in 2^F$, and 
-has a initial compound task $T_I$. 
-The closed world assumption also holds for HTN planning.
-
-The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
-$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
-$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
-$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.
-
-A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
-T, which is a finite set of task identifiers (ids); 
-$\singlePrec$, which is a partial order over T; and
-$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.
-
-% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
-A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
-a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
-\begin{align}
-tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
-\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
-&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
-\end{align}
-In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
-on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.
-
-A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
-tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ...
-t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ...
-\alpha(t_n) \rangle$ in $S_I$ is executable.
-
-In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition.
-For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired.
-Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning.
-Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.
-
-\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
-For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$.
-TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$.
-This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning.
-POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).
-As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
-In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.
-
-\section{Simple Linearization Procedure}
-The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks, and adding them only if they do not conflict with the originally required orderings.
-
-For a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
-$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type.
-For a grounded model, $f' = f$.
-The inferred preconditions and effects for a task are then defined as below:
-\begin{align*}
-& \forall t \in T_P : \PreS(t) := \Pre(t) \\
-& \forall t \in T_P : \AddS(t) := \Add(t) \\
-& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
-& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
-								& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
-& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
-								& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
-& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
-								& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
-\end{align*}
-
-From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1}.
-
-\begin{algorithm}\label{alg:Algorithm1}
-	\KwData{$(F, T_P, T_C, \delta, M)$}
-	\KwResult{$(F, T_P, T_C, \delta, M)$}
-
-	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
-	{
-
-		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}
-
-		$G \gets$ calculateTransitiveClosure($\singlePrec$) \\
-		\label{alg:StartBuildGraph}
-		\For{a $\in$ F}{  
-			\For{$t \in T_m$}{
-				\For{$t' \in T_m$}{
-					if $a \in \AddS(t)$ and $a \in \PreS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$  \\ 
-					if $a \in \AddS(t)$ and $a \in \DelS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \PreS(t')$, and $(t, t')$ not in $G$, add $(t', t)$ to $G$  \\ 
-					if $a \in \DelS(t)$ and $a \in \AddS(t')$, and $(t', t)$ not in $G$, add $(t, t')$ to $G$ \\  
-				}
-			} 
-			\label{alg:EndBuildGraph}	
-		}	 
-		\label{alg:TopSort}
-		$\singlePrec'\gets$ any linearization of $G$ \\
-		$m' = (tasks(m), \singlePrec', \alpha(t))$ \\
-		$M' = M' \cup  \{m'\}$ \\		
-	}
-	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
-	\caption{Calculation of linearized methods}
-\end{algorithm}
-
-\subsection{Theoretical Properties of Linearization Result}
-\begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes at most quadratic time, $\mathcal{O}( |M| * |F| * |T|^2)$. 
-\end{theorem}
-\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
-	Let $|T|$ = $|T_P| + |T_C|$.
-
-	The Floyd-warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,
-
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$, we can perform breadth-first search on the task decomposition sub-tree (where tasks are nodes, and edges indicate possible decomposition by methods) rooted at $t$.
-The size of a sub-tree has an upper limit of $T_C + T_P$ nodes.
-For each primitive task in the sub-tree, we can iterate over each fact to update $\PreS, \AddS, \DelS$ for the root $t$.
-Thus calculating  $\PreS, \AddS, \DelS$ for a single compound task has an upper limit of $(3 * |F| * |T_p|) + |T_C|$.
-This inference occurs for each compound task, so inference for all compound tasks takes $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$.
-
-	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
-Leading to $(M * F * (t_m)^2)$, where $t_m$ is the average number of sub-tasks per method.
-So it's at most $\mathcal{O}(|M| * |F| * |T|^2)$, since $t_m$ has an upper bound of $T$, where $T=T_p + T_C$.
-
-	Line~\ref{alg:TopSort} can be done via topological sort of the graph (which is known to be in $\mathcal{O}(V+E)$ in time and $\mathcal{O}(V)$ in space).
-In this case, the nodes of the graph are tasks, and the edges are orderings.
-So that's $M * (t_m+e_m)$, where $e_m$ is the number of \enquote{edges} in the new method, and has an upper bound of $e_m$ to find a topological sort for the sub-tasks of every method.
-That's approximately $\mathcal{O}(|M| * |T|)$, since both $t_m$ and $t_e$ are upper bounded by $T$, such that $T=T_p + T_C$.
-
-	So in total the main algorithm takes: \newline
-	$(|M| * |T|^3)$ +          % Floyd-Warshall
-	$(|M| * |F| * |T|)$  +    % GetPreEff
-	$\mathcal{O}(|M| * |F| * |T|^2)$ +  % desired orderings
-	$(|M| * |T|)$        % topological sort
-\end{proof}
-
-\begin{theorem}\label{thm:Soundness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a strict subset of $sol(P)$.
-\end{theorem}
-\begin{proof}
-	The new desired orderings for a method include all of the orderings already required by the method originally.
-The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph.
-This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one.
-Any solution to the linearized problem is then obviously a solution to the original problem.
-\end{proof}
-
-\begin{theorem}\label{thm:notCompleteness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then $sol(P')$ may be empty.
-\end{theorem}
-\begin{proof}
-	This algorithm linearizes all the methods to be totally ordered.
-Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents that are already ordered with respect to each other.
-This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered.
-Consider the simple example problem:
-
-	\begin{figure}
-		\caption{Diagram showing an example problem and its decomposition.}		
-		\begin{subfigure}{3.5cm}
-			\begin{align*}
-			F   = & \{a, b, c \}           \\
-			N_p = & \{A, B, C\}      \\
-			N_c = & \{AC, T_I\}            \\ 
-			M   = & \{  (T_I, \{AC, B\}), \\
-			&    (AC, \{A, C\})  \} \\
-			S_I = & \{ a \} 	             \\ 
-			\end{align*} 
-		\end{subfigure}		
-		\scalebox{0.7}{
-			\begin{subfigure}{7cm}
-				\begin{tikzpicture}[auto,node distance=1.5cm,
-				thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-				square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-				\node[] (InitState) {}; %{ $\mathbf{S_I = \{a\}}$ };
-
-				\node[main node] (Init) [right=3cm of InitState] {$T_I$};
-				\node[main node] (AC) [right=2cm of Init, below of=Init] {$AC$};
-
-				\node[main node] (A) [below left = 2em and 2em of AC] {$A$};
-				\node[main node] (B) [below left = 2em and 2em of Init] {$B$}; 
-				\node[main node] (C) [below right = 2em and 2em of AC] {$C$};
-
-		%		\action{A}{PrimitiveA,
-		%			width  = 2.5em, 
-		%			height = 2.5em, 
-		%			pre length = 2em,
-		%			eff length = 2em,
-		%			body = {below left = 2em and 2em of AC} 
-		%		};
-
-		%		\action{B}{PrimitiveB,
-		%			width  = 2.5em, 
-		%			height = 2.5em, 
-		%			pre length = 2em,
-		%			eff length = 2em,
-		%			body = {below left = 2em and 2em of Init} 
-		%		};
-
-		%		\action{C}{PrimitiveC,
-		%			width  = 2.5em, 
-		%			height = 2.5em, 
-		%			pre length = 2em,
-		%			eff length = 2em,
-		%			body = {below right = 2em and 2em of AC} 
-		%		};
-
-				\path[every node/.style={font=\sffamily\small}]
-				(Init) edge [->] node [left] {} (B)
-				(Init) edge [->] node [left] {} (AC)
-				(AC) edge [->] node [left] {} (A)
-				(AC) edge [->] node [left] {} (C);
-				\end{tikzpicture}
-			\end{subfigure}	
-		}
-	\end{figure}
-
-	\begin{figure}
-		\caption{The only possible solution $A, B, C$ for E.g.\ 1, requires the children of $AC$ and $B$ to be interleaved, meaning we cannot impose an order between them}
-		\scalebox{0.9}{
-			\begin{tikzpicture}[auto,node distance=3cm,
-			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
-			square node/.style={rectangle,draw,font=\sffamily\Large\bfseries}]
-
-			\node[] (Invis) [] {$S_I$};
-			\node[square node] (A) [right of=Invis] {$A$};
-			\node[square node] (B) [right of=A] {$B$};
-			\node[square node] (C) [right of=B] {$C$};
-
-			\path[every node/.style={font=\sffamily\small}]
-			(Invis) edge [->] node [left, label=a] {} (A)
-			(A) edge [->] node [left, label=b] {} (B)
-			(B) edge [->] node [left, label=c] {} (C);
-			\end{tikzpicture}		
-		}
-	\end{figure}
-
-	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
-	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$.
-This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution.
-	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
-
-	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete.
-Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
-	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
-\end{proof}
-
-We will now see that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} does not have to break cycles.
-\begin{theorem}\label{thm:SpecialCase}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if Algorithm~\ref{alg:Algorithm1} did not have to
-	cycle-break, then if $sol(P)$ is non-empty then $sol(P')$, will be non-empty as well.
-\end{theorem}
-\begin{proof}
-	Assume that there exists a solution in the PO domain.
-By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain.
-Assume this sequence is $(a_0, a_1, ..., a_n)$.
-We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
-	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state.
-The action $a_k$ could only be non-executable, if one or more of its preconditions was not met.
-Assume one of these unmet preconditions is for existence of the state variable $A$.
-	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution.
-So there must exist an action $a_i$, $0 < i < n$, that will add A.
-Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree.
-So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.
-
-	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc.
-We are assuming that all methods linearized without conflict, so $(t_i, t_k)$ should not be required.
-This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm.
-In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.
-
-	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution.
-Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
-\end{proof}
-
-There are several possible levels of \enquote{completeness} for a problem compilation.
-%\begin{enumerate}
-\begin{itemize}
-	\item all solutions remain 
-	\item at least one solution remains 
-	\item all optimal solutions remain
-	\item at least one optimal solution remains 	
-\end{itemize}
-%\end{enumerate}
-Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if no cycle-breaking is needed.
-If cycle-breaking is needed, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions.
-Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.
-
-\begin{theorem}\label{thm:newClass}
-	Problems $P$ that satisfy the criterion for linearization without cycle-breaking form a new class of decidable problems.
-\end{theorem}
-\begin{proof}
-	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.
-\end{proof}
-
-\section{Complex Linearization Procedure}
-
-The work by \cite{ConnyPreEff}, details a way to infer a subset of the mandatory preconditions and effects.
-
-\emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement.
-So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
-if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
-
-State-independent positive and negative effects (cf. their
-Def. 4) of a compound task c are facts that are added or
-deleted, resp., by the successful execution of a refinement of
-c, independent of the state in which the task is executed, i.e.
-$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
-$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$
-
-Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
-after every refinement of c but after at least one:
-$$ \RelPossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
-$$ \RelPossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
-if $E(c) \neq \emptyset and prec(c) := undef$ otherwise.
-
-The set of executability-enabling states of c is
-$E(c) = \{s \in 2F  \mid  \exists \text{t.o. refinement of c applicable in s} \}$.
-The set of resulting states of c w.r.t. some state $s \in 2^F$ is
-$R_s(c) = \{s' \in 2^F | \exists t.o. refinement appl. in s res. in s' \}$.
-
-So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
-with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.
-Then, the precondition-relaxed effects $\RelEffPlus$, $\RelEffMinus$, $\RelPossEffPlus$, $\RelPossEffMinus$. are defined
-just like the original ones but based on the precondition-
-relaxed variant of D.
-
-We can use these as an alternative input to Algorithm~\ref{alg:Algorithm1}.
-
-\section{Empirical Evaluation}
-
-To prove that our technique improves the solving time, we compare the runtime of a state-of-the-art planning system on the original problem vs.
-the transformed problem, for a number of different PO domains.
-All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
-The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
-Each problem has the standard IPC time limit of 30 minutes.
-Any grounding and pre-processing time needed is included as part of the 'solving' time.
-Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
-
-\subsection{Hardware and Planning Systems}
-The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
-Recent work by \cite{HTN2SAS} shows that the partial-order panda$_\pi$, actually achieved similar coverage and slightly lower IPC score than the best specialised TOHTN planner evaluated.
-%Lilotane by \cite{Lilotane} is an TOHTN solver and the IPC 2020 runner-up.
-The winner, HyperTensioN by \cite{hypertension} could not be tested due to lack of support for reading in optimisation metrics.
-
-We therefore test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} on the configuration of Greedy best first search with visited lists, and using RC to turn the problem into a classical planning problem.
-We try this search with 4 different heuristics: FF by \cite{FF}, Add by \cite{Add}, Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}.
-
-We compare the performance of these 4 planner settings on the original problem and the pre-processed problem, HTN2SAS, and the latest version of HyperTensioN and Lilotane.
-For panda$_{\pi}$, the same setting is used for re-runs.
-For TOHTN planners, re-runs use panda$_{\pi}$ on the best setting (Add heuristic).
-The comparison is done for grounded linearization variant and the lifted linearization variant 1.
-
-\subsection{Performance of Simple Linearization}
-
-\begin{table}[h]
-	\scalebox{0.45} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-				& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
-		\midrule 
-		Barman-BDI  \\ 
-		Monroe Fully Observ. \\ 
-		Monroe Part. Observ. \\ 
-		PCP\\ 
-		Rover  \\ 
-		Satellite  \\ 
-		Transport \\ 
-		UM-Translog \\ 
-		Woodworking \\ 
-		\midrule 
-		Monroe  \\ 
-		SmartPhone \\ 
-		Zenotravel \\ 
-		\midrule 
-		Coverage \\ 
-		Norm. coverage  \\ 
-		\bottomrule
-			\end{tabular} 	
-			}
-\end{table}
-
-\begin{table}[h]
-	\scalebox{0.45} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }   \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			IPC \\
-			\bottomrule
-			\end{tabular} 	
-	}
-\end{table}
-
-\subsection{Performance of Complex Linearization}
-
-\begin{table}[h]
-	\scalebox{0.45} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }    \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			Coverage \\ 
-			Norm. coverage  \\ 
-			\bottomrule
-			\end{tabular} 	
-	}
-\end{table}
-
-\begin{table}[h]
-	\scalebox{0.45} {
-		\begin{tabular}{lccccccccccccccccccccccccl} 
-			\toprule 
-			&& \multicolumn{2}{c}{rc2(Add)} & \multicolumn{2}{c}{rc2(Filter)} & \multicolumn{2}{c}{rc2(FF)} & \multicolumn{2}{c}{rc2(LMC)}  & \multicolumn{2}{c}{HTN2SAS} & \multicolumn{2}{c}{HyperTensioN} & \multicolumn{2}{c}{Lilotane} \\
-			\cmidrule(lr){3-4} \cmidrule(lr){5-6} \cmidrule(lr){7-8} \cmidrule(lr){9-10} \cmidrule(lr){11-12}  \cmidrule(lr){13-14} \cmidrule(lr){15-16}    
-			& max &PO & TO & PO & TO & PO & TO & PO &\multicolumn{2}{c}{ TO  }  \\ 
-			\midrule 
-			Barman-BDI  \\ 
-			Monroe Fully Observ. \\ 
-			Monroe Part. Observ. \\ 
-			PCP\\ 
-			Rover  \\ 
-			Satellite  \\ 
-			Transport \\ 
-			UM-Translog \\ 
-			Woodworking \\ 
-			\midrule 
-			Monroe  \\ 
-			SmartPhone \\ 
-			Zenotravel \\ 
-			\midrule 
-			IPC \\
-			\bottomrule
-		\end{tabular} 	
-	}
-\end{table}
-
-As we can see, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
-As we can see, the best planner is ? planner.
-
-\section{Related Work}
-% FROM (https://ojs.aaai.org/index.php/ICAPS/article/view/15944/15755) A Closer Look at Causal Links: Complexity Resultsfor Delete-Relaxation in Partial Order Causal Link (POCL) Planning
-Our linearization procedure is a pre-processing technique for the search space, is a compilation of an HTN planning problem class to a different class of problems, and can exploit specialised TO planners.
-
-The panda$_\pi$ grounder by \cite{Behnke2020Grounding} also prunes unreachable tasks, methods, etc.\.
-Because the panda$_{\pi}$ planner is a grounded planner, we can ground then linearize, or vice-versa to \enquote{stack} the reduction in search space.
-
-The main optimization of HyperTensioN by \cite{hypertension} is via the Pullup extension - which determines additional preconditions of methods and compound tasks by analysing the preconditions of possible child actions.
-Unlike ours, no approximation of effects are considered.
-
-The HTN2STRIPS planner by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} compiles HTN problems, both totally and partially ordered, to classical problems.
-The TOAD planner by \cite{HollerTOAD} compiles TOHTN problems into classical planning problems in order to allow the use of classical planning systems.
-% TOAD over-approximates the set of solutions to the HTN problem.
-In the empirical evaluation the paper performed, TOAD achieved higher coverage than the base version of HTN2STRIPS, and all systems submitted to the totally ordered track of the 2020 IPC.
-
-There exists totSAT planner by \cite{TOtoSAT} that compiles a totally ordered problem to SAT problem.
-There also exists 2 planners by \cite{POtoSAT, OptimalPOtoSAT} that compiles a partially ordered problem to a SAT problem.
-One searches for optimal plans, the other focuses on finding any solution as quickly as possible.
-Lilotane by \cite{Lilotane} directly encodes a lifted problem representation into a SAT problem.
-
-Another planner by \cite{Behnke_Speck_2021} converts TOHTN into Binary Decision Diagrams (BDDs), then use symbolic search on it.
-
-The BDD planner by \cite{Behnke_Speck_2021}, totSAT planner by \cite{TOtoSAT}, TOAD by \cite{HollerTOAD}, HyperTensioN by \cite{hypertension}, and Lilotane by \cite{Lilotane}, as discussed before, are all specialised TO planners.
-So are the TFD (Totally Ordered Fast Downward) and PFD (Partially Ordered Fast Downward) hierarchical planners by \cite{PDDL4J}.
-Note however that HTN2SAS achieved similar coverage than greedy search with panda$_\pi$, a partial-order planner.
-
-\section{Summary}
-
-The contributions of this paper are as follows:
-
-At least for the POHTN problems in the IPC domain, most of them are not undecideable.
-In another way, it is as if the POHTN domains are compressed TO domains - this linearization
-separates one back out.
-
-For another, this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here.
-Furthermore, there is demonstrably much more room for improvement.
-Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.
-
-We have a method that can increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques.
-Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems.
-Then $k+m$ (lifted or grounded) TOHTN problems exist now.
-And from empirical evaluation, $k$ may be close to $n$.
-
-We can identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all other criteria.
-
-\section{Future Work}
-
-\subsubsection{MAX-SAT Instead of Cycle-Break} 
-The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula.
-MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.
-
-Cycle-breaking considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$.
-Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, similar to the one described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
-Assuming no negative preconditons, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment).
-The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.
-
-\subsubsection{Adding a Plan as Additional Input to the Domain}
-Adding a plan as additional input to the PO domain having the
-semantics that this plan shall be in the solution set of the TO output
-model.
-This reduces the computational complexity of the decision problem from undecidable to something decidable.
-The specific complexity class of this will have to be proven in further work.
-% I assume the resulting problem is PSPACE-complete, but
-
-% References and End of Paper
-% These lines must be placed at the end of your paper
-\bibliography{bib}
-\end{document}
-
-\begin{document}\\
-\maketitle\\
-...\\
-\bibliography{bib}\\
-\end{document}\\
-
-\end{document}

### 2022-12-20 paper/04--otherLinearization.tex
further corrections

@@
  \begin{figure}[h]
- 	\caption{Example of Desired Additional Orderings}
- 	\label{fig:OrderingRules}
 	\scalebox{0.75}{
@@
 	}
+	 	\caption{Example of Desired Additional Orderings\label{fig:OrderingRules}}
 \end{figure}
@@
 \begin{figure}[h]
-	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
-	\label{fig:CycleBreaking}
 	\scalebox{0.75}{
@@
 			\end{tikzpicture}
-
 		\end{subfigure}
 	}
+	\caption{Example of Cycle-Breaking the Desired Additional Orderings\label{fig:CycleBreaking}\Psays{Ying, captions come in figures always below the graphics.
+Can you fix this?
+The captions are also not self-explanatory.
+E.g.
+in (a) you mention 'resulting', but it's completely unclear what you are referring to.
+Caption (b) is also not self-explanatory.}}
 \end{figure}

### 2022-12-20 paper/paper-mainfile.tex
further corrections

@@
 \usepackage{amssymb}
-\usepackage{mathbbol}
+\usepackage{todonotes}
+% \usepackage{mathbbol}
 \usepackage[noend]{algpseudocode}
@@
 
+\Psays{Ying, there are several unresolved references, can you please fix all of them? \includegraphics[width=\textwidth]{errors}}
+
+\Psays{There are quote a range of 'typical' errors throughout, see the list below}
+\begin{itemize}
+  \item Your quotes are wrong. You have to always use `6/9', ``66/99'', not '9/9'
+  \item Most citations are wrong. See my template for the rules.
+  \item You cite a paper by Erol twice, please fix (and remove the duplicate reference)
+  \item Gregor's AAAI'22 is missing page numbers.
+  \item Sometimes you have a dot that's not ending a sentence, yet you don't protect the next whitespace (see my template for an explanation)
+\end{itemize}
+
 \input{01--introduction}

### 2022-12-21 paper/05--theory.tex
some changes

@@
 
-We now discuss the implications of the above-described linearization procedure.
+We now discuss the implications of the above-described linearization procedure, starting by the runtime of the procedure.
+
+The procedure clearly runs in polynomial time, independent of which inference procedure is used for inferring compound tasks' preconditions and effects.
+Concretely, given a POHTN planning problem, the task of inferring a compound task's precondition and effects in a method using the simple inference takes time at most $\mathcal{O}(|\methods{}| \times M)$ with
+\begin{displaymath}
+	M =  \max_{(c, (T, \parOrd{}, \alpha)) \in \methods{}} |T|
+\end{displaymath}
+that is, $M$ is the number of tasks in the largest task network among all methods.
+This upper bound holds because at the worst case, the inductive inference procedure will visit all methods, and each method contains at most $M$ subtasks.
+Further, the complex inference procedure by \shortCite{ConnyPreEstimation} also has polynomial time complexity, as shown in their original work.
+
+The task of adding ordering constraints to a method $m = (c, (T, \parOrd{}, \alpha))$ takes time $\mathcal{O}(|T|^{2})$ because we need to check, for \emph{every} pair of $t, t' \in T$, whether an ordering constraint over them should be added.
+Further, since at most $\mathcal{O}(|T|^{2})$ ordering constraints will be added, the number of ordering constraints that will be removed for cycle-breaking will not exceed this number.
+Taken together, linearizing a POHTN planning problem can be done in polynomial time.
 
 \begin{theorem}\label{thm:Runtime}
-	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
+	Transforming a POHTN planning problem into a totally ordered one takes polynomial time, independent of which inference procedure is used.
 \end{theorem}
-\begin{proof}
-	Let $|T|$ = $|T_P| + |T_C|$.
+% \begin{proof}
+% 	Let $|T|$ = $|T_P| + |T_C|$.
 
-	To calculate $\PreS, \AddS, \DelS$ for each task $t$.
+% 	To calculate $\PreS, \AddS, \DelS$ for each task $t$.
 We explore it's compound sub-tasks until we collect all primitive tasks.
@@
 
-	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
+% 	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method.
 Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.
 
-	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.
+% 	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.
 
-	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
-	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
+% 	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time.
+% 	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.
 
-	So the algorithm takes polynomial time.
-\end{proof}
+% 	So the algorithm takes polynomial time.
+% \end{proof}
 

### 2022-12-22 paper/05--theory.tex
some changes

@@
 
-The procedure clearly runs in polynomial time, independent of which inference procedure is used for inferring compound tasks' preconditions and effects.
-Concretely, given a POHTN planning problem, the task of inferring a compound task's precondition and effects in a method using the simple inference takes time at most $\mathcal{O}(|\methods{}| \times M)$ with
+\paragraph{Runtime} The procedure runs in polynomial time, independent of which inference procedure is used for inferring compound tasks' preconditions and effects.
+Concretely, given a POHTN planning problem, inferring the precondition and effects of \emph{one} compound tasks using the simple inference takes time at most $\mathcal{O}(|\methods{}| \times M)$ with
 \begin{displaymath}
@@
 \end{displaymath}
-that is, $M$ is the number of tasks in the largest task network among all methods.
-This upper bound holds because at the worst case, the inductive inference procedure will visit all methods, and each method contains at most $M$ subtasks.
+% that is, $M$ is the number of tasks in the largest task network among all methods. 
+This upper bound holds because the inductive inference procedure visits all methods at the worst case, and each method contains at most $M$ subtasks.
+In fact, one can also observe that this number is also the upper bound for the runtime of inferring \emph{all} compound tasks' preconditions and effects.
+This is because after visiting all methods, the inductive procedure has naturally done processing (inferring) all compound tasks.
 Further, the complex inference procedure by \shortCite{ConnyPreEstimation} also has polynomial time complexity, as shown in their original work.
@@
 The task of adding ordering constraints to a method $m = (c, (T, \parOrd{}, \alpha))$ takes time $\mathcal{O}(|T|^{2})$ because we need to check, for \emph{every} pair of $t, t' \in T$, whether an ordering constraint over them should be added.
-Further, since at most $\mathcal{O}(|T|^{2})$ ordering constraints will be added, the number of ordering constraints that will be removed for cycle-breaking will not exceed this number.
+Additionally, since at most $\mathcal{O}(|T|^{2})$ ordering constraints will be inserted, the number of ordering constraints that will be removed for cycle-breaking will not exceed this number.
 Taken together, linearizing a POHTN planning problem can be done in polynomial time.
@@
 
-\begin{theorem}\label{thm:Soundness}
-	Given a POHTN planning problem $P$ and TOHTN problem
-	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
-	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
+\paragraph{Soundness} More importantly, the presented linearization approach ensures that any solution to the TOHTN planning problem $\Pi'$ obtained by linearizing a partially ordered one $\Pi$ is also a solution to $\Pi$.
+That is, the solution set of $\Pi'$ is a \emph{subset} of that of $\Pi$.
+
+\begin{theorem}
+	Let $\Pi$ be a POHTN planning problem, $\Pi'$ a TOHTN planning problem obtained from $\Pi$ by using the linearization approach, and $\mathcal{S}(\Pi)$ and $\mathcal{S}(\Pi')$ the set of all solutions to $\Pi$ and to $\Pi'$, respectively.
+Then, $\mathcal{S}(\Pi') \subseteq \mathcal{S}(\Pi)$.
+	\label{thm:Soundness}
 \end{theorem}
+
 \begin{proof}

### 2022-12-23 paper/paper-mainfile.tex
diagram

--- 2022-12-16 paper/paper-mainfile.tex
@@
 
+			\action{Prec}{SinglePrec,
+				width  = 2.5em, 
+				height = 2.5em, 
+				pre length = 1em,
+				eff length = 1em 
+			};
+
 			\action{Add}{SingleAdd,
@@
 				pre length = 1em,
-				eff length = 1em 
-			};
-
-			\action{Prec}{SinglePrec,
+				eff length = 1em,				
+				body = {left = 4em of Prec}
+			};
+
+			\action{Del}{SingleDelete,
 				width  = 2.5em, 
@@
 				body = {left = 4em of Add} 
-			};
-
-			\action{Del}{SingleDelete,
-				width  = 2.5em, 
-				height = 2.5em, 
-				pre length = 1em,
-				eff length = 1em,
-				body = {left = 4em of Prec} 
 			};
@@
 				eff length = 1em,
-				body = {right = 4em of first} 		
+				body = {right = 4em of B}	
 			};
@@
 				eff length = 1em,
-				body = {right = 4em of second} 	
-				%body = {below left = 2em and 2em of } 
+				body = {right = 4em of A} 
 			};
@@
 
+	\vspace{2em}
 	\scalebox{0.75}{
-		\begin{subfigure}{6cm} 
+		\begin{subfigure}{7cm} 
 		 %	\centering

### 2022-12-23 paper/01--introduction.tex

--- 2022-12-20 stuff/old-stuff/01-intro-inText.tex
@@
 \section{Introduction}
-% \input{01--intro.tex}
-Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
+
+Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},
 tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound.
@@
 A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications.
-If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.
+If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \emph{plan}.
 
@@
 In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.
-
-% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space.
-For some problems, such over-specification may remove all valid solutions.
 
@@
 Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case.
-% Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
 The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem.

### 2022-12-23 paper/06--evaluation.tex

--- 2022-12-20 paper/paper-mainfile.tex
@@
-%%%% ijcai22.tex
+\section{Empirical Evaluation}
 
-\typeout{IJCAI--22 Instructions for Authors}
+We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems.
+All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020.
+The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons.
+Each problem has the standard IPC time limit of 30 minutes.
+Any grounding and pre-processing time needed is included as part of the 'solving' time.
+Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.
 
-% These are the instructions for authors for IJCAI-22.
+\subsection{Hardware and Planning Systems}
+The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM.
+Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested.
+Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.
 
-\documentclass{article}
-\pdfpagewidth=8.5in
-\pdfpageheight=11in
-% The file ijcai22.sty is NOT the same as previous years'
-\usepackage{ijcai22}
+We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration.
+This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists.
+The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.
 
-% Use the postscript times font!
-\usepackage{times}
-\usepackage{soul}
-\usepackage{url}
-\usepackage[hidelinks]{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage[small]{caption}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{booktabs}
-\usepackage{algorithm}
-% \usepackage{algorithmic}
-\urlstyle{same}
+We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
 
-% the following package is optional:
-%\usepackage{latexsym}
+We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem.
+The same setting is used for re-runs.
+For other planners, panda$_\pi$ with rc2(Add) is used for re-runs.
+We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems.
+Re-runs use panda$_{\pi}$ with the best heuristic(Add).
+We test both Complex and Simple Inference for linearization.
+Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
 
-% See https://www.overleaf.com/learn/latex/theorems_and_proofs
-% for a nice explanation of how to define new theorems, but keep
-% in mind that the amsthm package is already included in this
-% template and that you must *not* alter the styling.
-\newtheorem{example}{Example}
-\newtheorem{theorem}{Theorem}
+The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
+As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
 
-% % % % % PACKAGES IMPORTED BY US % % % % %
-\usepackage{amsfonts}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{mathbbol}
-\usepackage[noend]{algpseudocode}
-\usepackage{paralist}
-\usepackage{booktabs}
-\usepackage{xcolor}
-\usepackage{subcaption}
-\usepackage{tikz}
-\usetikzlibrary{aiplans}
+The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.
 
-% Following comment is from ijcai97-submit.tex:
-% The preparation of these files was supported by Schlumberger Palo Alto
-% Research, AT\&T Bell Laboratories, and Morgan Kaufmann Publishers.
-% Shirley Jowell, of Morgan Kaufmann Publishers, and Peter F.
-% Patel-Schneider, of AT\&T Bell Laboratories collaborated on their
-% preparation.
+For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
+the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem.
+For each total-order planner, the column beneath it shows performance on the linearized problem.
+The IPC score has a maximum of 1 per domain, for the 12 domains in total.
 
-% These instructions can be modified and used in other conferences as long
-% as credit to the authors and supporting agencies is retained, this notice
-% is not changed, and further modification or reuse is not restricted.
-% Neither Shirley Jowell nor Peter F. Patel-Schneider can be listed as
-% contacts for providing assistance without their prior permission.
+The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
+achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and \ref{table:GroundedComplexIPC}.
+This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average.
+However, the slightly higher coverage does make it appear the complex inference pays off with \emph{better} linearized domains.
+E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.
 
-% To use for other conferences, change references to files and the
-% conference appropriate and use other authors, contacts, publishers, and
-% organizations.
-% Also change the deadline and address for returning papers and the length and
-% page charge instructions.
-% Put where the files are available in the appropriate places.
+Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
+When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable.
 
-% PDF Info Is REQUIRED.
-% Please **do not** include Title and Author information
-\pdfinfo{
-/TemplateVersion (IJCAI.2022.0)
-}
+\input{table--GroundedSimpleCoverage}
+\input{table--GroundedSimpleIPC}
+\input{table--LiftedSimpleCoverage}
+\input{table--LiftedSimpleIPC}
+\input{table--GroundedComplexCoverage}
+\input{table--GroundedComplexIPC}
+\input{table--FullyLinearizedProblems}
+\input{table--SimpleLinearizable}
+\input{table--ComplexLinearizable}
 
-\title{``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)}
+While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
+(Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)
 
-\author{Anonymous}
-
-% Single author syntax
-% \author{
-%     Author Name
-%     \affiliations
-%     Affiliation
-%     \emails
-%     pcchair@ijcai-22.org
-% }
-
-% Multiple author syntax (remove the single-author syntax above and the \iffalse ... \fi here)
-\iffalse
-\author{
-First Author$^1$
-\and
-Second Author$^2$\and
-Third Author$^{2,3}$\And
-Fourth Author$^4$
-\affiliations
-$^1$First Affiliation\\
-$^2$Second Affiliation\\
-$^3$Third Affiliation\\
-$^4$Fourth Affiliation
-\emails
-\{first, second\}@example.com,
-third@other.example.com,
-fourth@example.com
-}
-\fi
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-HTN planning is in general undecidable, yet there exist efficient planning algorithms.
-An important subclass is that of totally ordered HTN planning problems.
-Not only is this class decidable, but also easier to handle algorithmically since tasks cannot interleave anymore.
-Consequently, several specialized solvers exist, and dedicated tracks at the International Planning Competition (IPC) in both 2020 and 2023.
-We were able to show that almost all currently existing partially ordered planning benchmarks can be turned into totally ordered ones without sacrificing solvability.
-Establishing totally ordered problems in a preprocessing technique thus allows to use planning systems, heuristics, pruning techniques (etc.) that are only available for totally ordered problems.
-This allows solving problems more efficiently and with better-informed techniques, at the (little) cost of doing a preprocessing technique.
-We show that in only a very few cases linearization isn't possible, and in all others establishing a total order pays off \emph{significantly}, thus establishing our technique as a significant ingredient in the state of the art for solving partially ordered HTN problems.
-As a side contribution, we identify a new class of decidable (EXPTIME-complete) HTN problems, namely those where our preprocessing technique is guaranteed to be solvability-preserving.
-\end{abstract}
-
-\input{00--macros}
-
-\input{01--introduction}
-\input{02--formalism}
-\input{03--linearization-ground}
-\input{04--otherLinearization}
-\input{05--theory}
-\input{06--evaluation}
-\input{07--relatedWork}
-\input{08--futureWork}
-\input{09--conclusion}
-
-%% The file named.bst is a bibliography style file for BibTeX 0.99c
-\bibliographystyle{named}
-\bibliography{bib}
-
-\end{document}
+\input{table--POMethodBreak}

### 2022-12-23 paper/table--FullyLinearizedProblems.tex

\begin{table}
	\centering
	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
	\label{table:FullyLinearizedProblems}
	\scalebox{0.75} {
	\begin{tabular}{lcccl}
		\toprule
		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
		\midrule
		SmartPhone  & 4.0                   &  1     \\
		Transport   & 1144.9                & 40       \\
		UM-Translog & 1.1                    & 17   \\
		Woodworking & 2035              &   21    \\
				\bottomrule
	\end{tabular}
	}
\end{table}

### 2022-12-23 paper/table--POMethodBreak.tex

\begin{table}
	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain. Shows Results for Both Inference Methods.}\label{table:POMethodBreak}
	\begin{tabular}{lccl}
		\toprule
		Domain & Complex & Simple &  \\
		\midrule
		Transport & 1.0 & 0.0  \\
		UM-Translog & 0.8 & 0.0  \\
		Satellite & 1.0 & 0.0  \\
		Monroe Fully Observ. & 1.0 & 0.0  \\
		Rover & 1.0 & 0.0  \\
		Woodworking & 0.9 & 0.0  \\
		Monroe Part. Observ. & 1.0 & 0.0  \\
		PCP & 0.0 & 0.0  \\
		Barman-BDI & 1.0 & 0.0  \\
		SmartPhone & 0.1 & 0.1  \\
		Monroe & 0.8 & 0.0  \\
		Zenotravel & 1.0 & 0.0  \\
		\bottomrule
	\end{tabular}
\end{table}

### 2022-12-23 paper/table--SimpleLinearizable.tex

\begin{table}
	\centering
	\caption{These results are from using Simple Inference. Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
	\label{table:SimpleLinearizable}
		\scalebox{0.65} {
	\begin{tabular}{lcccl}
		\toprule
		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\
		\midrule
Barman-BDI & 4870.0 & 3717.1 & 28.6  \\
Monroe & 12127.3 & 3447.8 & 72.4  \\
Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\
Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\
PCP & 12.3 & 12.3 & 0.0  \\
Rover & 509.4 & 355.2 & 32.3  \\
Satellite & 70.6 & 36.1 & 50.9  \\
SmartPhone & 6.3 & 4.0 & 21.8  \\
Transport & 1144.9 & 1144.9 & 0.0  \\
UM-Translog & 1.5 & 1.5 & 0.0  \\
Woodworking & 1927.3 & 1927.3 & 0.0  \\
Zenotravel & 190.2 & 99.4 & 47.0  \\
		\bottomrule
	\end{tabular}
}
\end{table}

### 2022-12-23 stuff/old-stuff/01--intro.tex

Hierarchical Task Network (HTN) planning, as described by \shortCite{HTNSurvey}, is a hierarchical approach to planning where so-called \emph{compound tasks} are kept being refined until primitive ones (also called \emph{actions}) are obtained which form a \emph{plan}. Research on HTN planning has drawn increasing interests in the last decade due to its expressive power. More concretely, HTN planning can simulate the classes of formal languages ranging from star-free languages to (a strict subset of) context-sensitive languages, whereas non-hierarchical (i.e., classical) planning can only express a strict subset of star-free languages \cite{Hoeller2016Expressivity,Lin2022LTLExpressivity}. % As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
% tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound. HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks. A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications. If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.

One major problem faced by the HTN planning community is the high computational complexity of HTN planning problems. Specifically, \shortCite{Erol1996HTNComplexity} have shown that an HTN planning problem is undecidable in general, and thus, finding a solution to an HTN problem is still a challenge task even for the state-of-the-art HTN planner.

In this paper, we propose a novel approach which transforms a general HTN planning problem (where a compound task is refined into a \emph{partially ordered} set of subtasks) into a \emph{totally ordered} one which is a special form of HTN planning problems and in which a compound task can only be refined into a \emph{sequence} (i.e., a totally ordered set) of subtasks. More importantly, our approach assures that any solution to the transformed problem is also a solution to the original problem, and our approach works for both the grounded and the lifted formalism. Thus, by employing this approach (e.g., as a preprocessor), we could reduce the complexity of finding a solution to the original problem because, as proved by \shortCite{Alford2015TightHTNBounds}, it is \EXPTIME{}-complete to solve a totally ordered HTN planning problem, and specialized HTN planning techniques (e.g., heuristics and pruning techniques) for only totally ordered problems can also be deployed for solving the transformed problem.

Notably, our approach does \emph{not} guarantee that at least one solution will be preserved after the transformation. However, our empirical evaluation shown that it is rarely the case that none solutions are preserved. More specifically, there is only one domain in our benchmark set where problems become unsolvable after the transformation. Additionally, we will also present certain criteria which assert that at least one solution will be preserved if they are satisfied.

As a side contribution, our approach can also be exploited to create new total order HTN planning domains from partial order ones. This might be particularly useful by taking into account the upcoming 2023 International Planning Competition (IPC) on HTN planning.

% In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks. In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.

% % Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space. For some problems, such over-specification may remove all valid solutions.

% Many problems might be naturally more suited to being modelled as POHTN problems. However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions. For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages. On the other hand, TOHTN planning is not expressive enough to model undecideable problems. Where this is possible, it results in lower worst-case solving time. Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.

% Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case. % Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
% The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
% Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution. In fact, the state-of-the-art panda$_\pi$ planner and \cite{HTN2SAS} both use a compilation to classical planning, another decidable planning class.
% In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems. We prove that when certain criteria are met, it guarantees that at least one solution will be preserved. 
% Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion. Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.

### 2022-12-23 stuff/old-stuff/paper-mainfile--OLD.tex

\def\year{2022}\relax
%File: formatting-instructions-latex-2022.tex
%release 2022.1
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage[submission]{aaai23}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in}  % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in}  % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
% \usepackage{algorithm}
% \usepackage{algorithmic}
% \usepackage[noend]{algpseudocode}

%
% These are are recommended to typeset listings but not required. See the subsubsection on listing. Remove this block if you don't have listings in your paper.
\usepackage{newfloat}
\usepackage{listings}
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
%\floatstyle{ruled}
%\newfloat{listing}{tb}{lst}{}
%\floatname{listing}{Listing}

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{xcolor}
\usepackage{booktabs} 
% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb} 
\usepackage{mathbbol}
\usepackage{tikz}
\usetikzlibrary{aiplans}

\scheme{SinglePrec}{0}{
	text = {\textbf{A}},
	pre  = {a}
}

\scheme{SingleAdd}{0}{
	text = {\textbf{B}},
	effs = { a}
}

\scheme{SingleDelete}{0}{
	text = {\textbf{C}},
	effs = { {{$\neg$}a} }
}

\scheme{SinglePrecAlt}{0}{
	text = {\textbf{D}},
	pre  = {a}
}

\scheme{SingleAddAlt}{0}{
	text = {\textbf{E}},
	effs = { a}
}

\scheme{PrimitiveA}{0}{
	text = {\textbf{A}},
	pre  = {a},
	effs = { {{$\neg$}a}, {b} }
}

\scheme{PrimitiveB}{0}{
	text = {\textbf{B}},
	pre = {b},
	effs = {{{$\neg$}b}, {c}}
}

\scheme{PrimitiveC}{0}{
	text = {\textbf{C}},
	pre = {c},
	eff = {{$\neg$}c}
}

\nocopyright
%
% PDF Info Is REQUIRED.
% For /Title, write your title in Mixed Case.
% Don't use accents or commands. Retain the parentheses.
% For /Author, add all authors within the parentheses,
% separated by commas. No accents, special characters
% or commands are allowed.
% Keep the /TemplateVersion tag as is
\pdfinfo{
/Title (ORdering is half the battle -- Establishing Totally Ordered HTN
Planning Problems is Half the Job (to Getting them Solved More Efficiently))
%/Title (Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
%Planning Problems is Half the Job (to Getting them Solved More Efficiently))
/Author (Anonymous)
/TemplateVersion (2022.1)
}

% DISALLOWED PACKAGES
% \usepackage{authblk} -- This package is specifically forbidden
% \usepackage{balance} -- This package is specifically forbidden
% \usepackage{color (if used in text)
% \usepackage{CJK} -- This package is specifically forbidden
% \usepackage{float} -- This package is specifically forbidden
% \usepackage{flushend} -- This package is specifically forbidden
% \usepackage{fontenc} -- This package is specifically forbidden
% \usepackage{fullpage} -- This package is specifically forbidden
% \usepackage{geometry} -- This package is specifically forbidden
% \usepackage{grffile} -- This package is specifically forbidden
% \usepackage{hyperref} -- This package is specifically forbidden
% \usepackage{navigator} -- This package is specifically forbidden
% (or any other package that embeds links such as navigator or hyperref)
% \indentfirst} -- This package is specifically forbidden
% \layout} -- This package is specifically forbidden
% \multicol} -- This package is specifically forbidden
% \nameref} -- This package is specifically forbidden
% \usepackage{savetrees} -- This package is specifically forbidden
% \usepackage{setspace} -- This package is specifically forbidden
% \usepackage{stfloats} -- This package is specifically forbidden
% \usepackage{tabu} -- This package is specifically forbidden
% \usepackage{titlesec} -- This package is specifically forbidden
% \usepackage{tocbibind} -- This package is specifically forbidden
% \usepackage{ulem} -- This package is specifically forbidden
% \usepackage{wrapfig} -- This package is specifically forbidden
% DISALLOWED COMMANDS
% \nocopyright -- Your paper will not be published if you use this command
% \addtolength -- This command may not be used
% \balance -- This command may not be used
% \baselinestretch -- Your paper will not be published if you use this command
% \clearpage -- No page breaks of any kind may be used for the final version of your paper
% \columnsep -- This command may not be used
% \newpage -- No page breaks of any kind may be used for the final version of your paper
% \pagebreak -- No page breaks of any kind may be used for the final version of your paperr
% \pagestyle -- This command may not be used
% \tiny -- This is not an acceptable font size.
% \vspace{- -- No negative value may be used in proximity of a caption, figure, table, section, subsection, subsubsection, or reference
% \vskip{- -- No negative value may be used to alter spacing above or below a caption, figure, table, section, subsection, subsubsection, or reference

\setcounter{secnumdepth}{0} %May be changed to 1 or 2 if section numbers are desired.

% The file aaai22.sty is the style file for AAAI Press
% proceedings, working notes, and technical reports.
%

% Title

% Your title must be in mixed case, not sentence case.
% That means all verbs (including short verbs like be, is, using,and go),
% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
% articles, conjunctions, and prepositions are lower case unless they
% directly follow a colon or long dash

%Example, Single Author, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
% \iffalse

\newtheorem{theorem}{Theorem}

\newcommand{\Eff} {\ensuremath{\mathit{eff}}}  % example command without arguments
\newcommand{\Pre} {\ensuremath{\mathit{pre}}}  % (again)

\newcommand{\Add} {\ensuremath{\mathit{add}}}
\newcommand{\Del} {\ensuremath{\mathit{del}}}
\newcommand{\PreS} {\ensuremath{\mathit{pre^{*}}}}
\newcommand{\AddS} {\ensuremath{\mathit{add^{*}}}}
\newcommand{\DelS} {\ensuremath{\mathit{del^{*}}}}
\newcommand{\singlePrec} {\ensuremath{\mathit{ \mathord{\prec} }}}
\newcommand{\tasks} {\ensuremath{\mathit{tasks}}}

%\newcommand{\EffPlus} {\ensuremath{\mathit{eff^{+}_{*}}}}
%\newcommand{\EffMinus} {\ensuremath{\mathit{eff^{-}_{*}}}}
\newcommand{\PossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{+}_{*}}}}
\newcommand{\PossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{-}_{*}}}}

%\newcommand{\RelEffPlus} {\ensuremath{\mathit{\textit{eff}^{\emptyset +}_{*}}}}
%\newcommand{\RelEffMinus} {\ensuremath{\mathit{\textit{eff}^{\emptyset -}_{*}}}}
\newcommand{\RelPossEffPlus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset +}_{*}}}}
\newcommand{\RelPossEffMinus} {\ensuremath{\mathit{\textit{poss-eff}^{\emptyset -}_{*}}}}

\author {
    Submission
}
\affiliations{
    Anonymous
}
% \fi

%Example, Multiple Authors, ->> remove \iffalse,\fi and place them surrounding AAAI title to use it
\iffalse 
%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}
\author {
    % Authors
    Anonymous

}
\affiliations {
    % Affiliations
    Anonymous
}
\fi

\title{``Order is Half of Life'' -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved Efficiently)}

%\title{Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN
%	Planning Problems is Half the Job (to Getting them Solved More Efficiently)}

% REMOVE THIS: bibentry
% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
% \usepackage{bibentry}
% END REMOVE bibentry

\begin{document}
\input{00--macro.tex}
\maketitle

\begin{abstract} 
HTN planning is in general undecidable, yet there exist efficient
planning algorithms. An important subclass is that of totally ordered
HTN planning problems. Not only is this class decidable, but also easier
to handle algorithmically since tasks cannot interleave anymore.
Consequently, several specialized solvers exist, and dedicated tracks at
the International Planning Competition (IPC) in both 2020 and 2023. We
were able to show that almost all currently existing partially ordered
planning benchmarks can be turned into totally ordered ones without
sacrificing solvability. Establishing totally ordered problems in a
preprocessing technique thus allows to use planning systems, heuristics,
pruning techniques (etc.) that are only available for totally ordered
problems. This allows solving problems more efficiently and with
better-informed techniques, at the (little) cost of doing a
preprocessing technique. We show that in only a very few cases
linearization isn't possible, and in all others establishing a total
order pays off \emph{significantly}, thus establishing our technique as
a significant ingredient in the state of the art for solving partially
ordered HTN problems. As a side contribution, we identify a new class of
decidable (EXPTIME-complete) HTN problems, namely those where our
preprocessing technique is guaranteed to be solvability-preserving.
\end{abstract}

\section{Introduction}
% \input{01--intro.tex}
Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound. HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks. A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications. If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.

In totally ordered HTN planning, or TOHTN planning, methods specify a total order on the sub-tasks. In partially ordered HTN planning, or POHTN planning, methods might only specify a partial order on the sub-tasks.

% Certain kinds of problems might be naturally more suited to being modelled as a partially ordered problem, for example, the actions \enquote{deliver package 1 to city A} and \enquote{deliver package 2 to city B} -- these are essentially unrelated goals in a real transport scenario, and so modelling the problem to require that one task be completed before the other would be unnecessarily limiting the possible solution space. For some problems, such over-specification may remove all valid solutions.

Many problems might be naturally more suited to being modelled as POHTN problems. However, for \emph{solving} the problem, it is desirable to have additional constraints that reduces the search space, while still preserving at least some of the actual solutions. For example, \cite{ErolHTNExpressivity} proved that POHTN planning is expressive enough to model undecidable problems, such as the language intersection problem of two context-free languages. On the other hand, TOHTN planning is not expressive enough to model undecideable problems. Where this is possible, it results in lower worst-case solving time. Converting the problem to a TOHTN problem allows us to exploit that fact to solve the problem more quickly.

Another benefit of transforming a POHTN problem to a TOHTN problem is that the additional structure to the problem could allow us to deploy specialised algorithms and heuristics for the totally ordered case. % Also, heuristic design is comparably easy for total-order problems due to the missing interaction between tasks.
The drawback to this approach is that, due to the greater expressivity of POHTN planning, there may exist POHTN problems that cannot be solved when converted to a TOHTN problem. 
Fortunately, not every POHTN problem is guaranteed to be undecidable, and so could still be transformed while preserving at least one solution.
In this paper we present and investigate an algorithm for converting POHTN problems to TOHTN problems. We prove that when certain criteria are met, it guarantees that at least one solution will be preserved. 
Also, we obtain a new class of decidable problems, namely those that satisfy the above mentioned criterion. Finally, we show that, even when these criteria are not met, very few problems are rendered unsolvable by the transformation, and that it greatly reduces solving time for problems, with gains being bigger for more difficult problems.

\section{Hierarchical Planning Formalism}
\input{02--htn.tex}

\section{Linearizing Grounded HTN Problems}
\input{03--linearization-ground.tex}

% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other. This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.

% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }

% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed. If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$. This is true for all possible tasks by simple induction over the decomposition process.

% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.

% Specifically, let $\sigma$ be the set of parameters for the method. Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$. Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.

% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects. For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects. % This is illustrated in Figure~\ref{CompoundPreEffForLifted}.

% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$. The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded. Only one linearized lifted method per partially-ordered lifted method is produced.

% For a grounded method, there are no parameters in a task or method. Methods decompose to specific actions, actions have preconditions and effects on specific state variables. We can then use these to produce a linearized grounded method per grounded method.

% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
% \begin{align*}
% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
% & \forall t \in T_P : \AddS(t) := \Add(t) \\
% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
% \end{align*}

% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects. Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.

%State-independent positive and negative effects (cf. their Def. 4) of a compound task c are facts that are added or deleted, resp., by the successful execution of a refinement of c, independent of the state in which the task is executed, i.e.
%$$ \RelEffPlus := ( \bigcap_{s \in E(c)} \bigcap_{s' \in R_s(c)} s') \backslash  \bigcap_{s \in E(c)} s    $$
%$$ \RelEffMinus := \bigcap_{s \in E(c)}  (F \backslash \bigcap_{s' \in R_s(c)} s' ) $$

% Possible state-independent effects of a compound task $c$ are not guaranteed to hold (or not hold, resp.,)
% after every refinement of c but after at least one:
% $$ \PossEffPlus(c) := \bigcup_{s \in E(c)}  ( \bigcup_{s' \in R_s(c)}  s' \backslash s) $$
% $$ \PossEffMinus(c) := \bigcup_{s \in E(c)} ((\bigcup_{s' \in R_s(c)} (F \backslash s') \cap s ))$$
% if $E(c) \neq \emptyset$ and  $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

% The set of executability-enabling states of c is
% $E(c) = \{s \in 2F  \mid  \exists$ t.o. refinement of $c$ applicable in $s \}$.
% The set of resulting states of c w.r.t. some state $s \in 2^F$ is
% $R_s(c) = \{s' \in 2^F | \exists$ t.o. refinement appl. in $s$ res. in $s' \}$.

% So, the precondition-relaxation of a domain D = $(F, A, C, M)$ is the domain $D' = (F, A', C, M)$
% with $A' = \{(\emptyset, add , del ) \mid (prec, add , del ) \in A\}$.

% Then, the precondition-relaxed effects $\RelPossEffPlus$, $\RelPossEffMinus$. are defined just like the original ones but based on the precondition-relaxed variant of D.
% This means $\RelPossEffPlus$ and $\RelPossEffMinus$ has every effect that $\PossEffPlus$ and $\PossEffMinus$  do, respectively. But
% the precondition relaxation can make further refinements executable that produce
% effects that can not be achieved in the non-relaxed domain. 
% In other words, we can calculate a super-set, that might contain some false candidates, of the real preconditions and effects that might occur after any execution of $c$, i.e.\  $\PossEffMinus \subseteq \RelPossEffMinus$, and $\PossEffPlus  \subseteq \RelPossEffPlus$.

% \emph{Mandatory preconditions} of a compound task $c$ are facts that hold in every state for which there exists an executable refinement. So, they are required in every state in which a refinement of c shall be executed: prec(c) := $\cap_{s \in E(c)}  s$
% if $E(c) \neq \emptyset$ and $\Pre(c) := \ensuremath{\textit{undef}}$ otherwise.

% A fact $f \in F$ is an \emph{executability-relaxed precondition} of $c$ if and only if for all t.o. refinements (ignoring executability of the refinement) $\langle a_0 ... a_n \rangle$ of $c$ there exists an action $a_i$ with $f \in \prec(a_i)$ and there does not exist an action $a_j$ with $j < i$ and $f \in add(a_j)$, where $i, j \in \{0, ..., n\}$.

% There exists a polynomial-time algorithm for inferring the executability-relaxed preconditions and precondition-relaxed effects, see \cite{ConnyPreEstimation} for details.
% In this paper, we will be utilising both of these, as seen in the next section.
%the precondition-relaxed possible effects, which may hold after at least one refinement of c.

%A fact $f \in F$ is an executability-relaxed precondition of c if and only if for all t.o. refinements (ignoring ex-
%ecutability) 〈a0 . . . an〉 of c there exists an action ai with
%f ∈ prec(ai) and there does not exist an action aj with
%j < i and f ∈ add (aj ), where i, j ∈ {0 . . . n} (cf. Def. 10).
%The exploitation of the relaxed preconditions and effects
%is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates

\section{Linearization of Methods Using Any Set of Inferred Preconditions and Effects}

% \begin{algorithm}[h]
% 	\caption{Calculation of linearized methods}
% 	\label{alg:Algorithm1}
% 	\KwData{$(F, T_P, T_C, \delta, M)$}
% 	\KwResult{$(F, T_P, T_C, \delta, M)$}

% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
% 	{
% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
% 		$G \gets \singlePrec$ \\
% 		\label{alg:StartBuildGraph}
% 		\For{a $\in$ F}{  
% 			\For{$t \in T_m$}{
% 				\For{$t' \in T_m$}{
% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
% 				}
% 			} 
% 			\label{alg:EndBuildGraph}	
% 		}	
% 		\label{alg:StartCycleBreak}
% 		\While{$G$ has cycles in it}{
% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
% 		}
% 		\label{alg:EndCycleBreak}
% 		$\prec'$ = Any linearization of $G$ \\
% 		\label{alg:TopSort}
% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
% 		$M' = M' \cup  \{m'\}$ \\

% 	}
% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
% \end{algorithm}

From these inferred preconditions and effects $\PreS(t), \AddS(t), \DelS(t)$, (which may have been derived using the ground or lifted variant), we can run Algorithm~\ref{alg:Algorithm1} to get an linearized problem.
For an visual demonstration of what this algorithm is doing, see Figure~\ref{fig:OrderingRules} and \ref{fig:CycleBreaking}.% and \ref{fig:NotCycleBreaking}:

 \begin{figure}[h]
 	\caption{Example of Desired Additional Orderings}
 	\label{fig:OrderingRules}
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{first}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{second}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of first} 		
			};

			\path[every node/.style={font=\sffamily\small}]
			(first) edge [->,bend right] node [left]  {} (second);
			\end{tikzpicture}

			\caption{B adds a fact in preconditions of A -- so B before A}

		\end{subfigure}
	}  
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{A}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of } 
			};

			\action{B}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of A} 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{C deletes a fact in preconditions of A  -- so A before C}	
		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{A}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of } 
			};

			\action{B}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of A} 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->, bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{B adds a fact that C deletes -- so C before B}
		\end{subfigure}
	} 
\end{figure}

\begin{figure}[h]
	\caption{Example of Cycle-Breaking the Desired Additional Orderings}
	\label{fig:CycleBreaking}
	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
		 	\centering
			\caption{Resulting method ordering has a cycle}
			\label{fig:CycleBreaking1}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{B}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{A}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of first} 		
			};

			\action{C}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second} 	
				%body = {below left = 2em and 2em of } 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
			(A) edge [->,bend right] node [left]  {} (C)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}

		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{6cm} 
		 %	\centering
			\caption{Delete any random ordering to break it}
			\label{fig:CycleBreaking2}
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{B}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{A}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of first} 		
			};

			\action{C}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {right = 4em of second} 	
				%body = {below left = 2em and 2em of } 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A)
		%	(A) edge [->,bend right] node [left]  {} (C)
			(C) edge [->,bend right] node [left]  {} (B);
			\end{tikzpicture}

		\end{subfigure}
	}

%	\scalebox{0.75}{
%		\begin{subfigure}{7cm} 
%				\caption{Example of Not Needing to Cycle-Break the Desired Additional Orderings}
%			\label{fig:NotCycleBreaking}
%			\begin{tikzpicture}[auto,node distance=1.2cm,
%			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
%			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

%			\action{B}{SingleAddAlt,
%				width  = 2.5em, 
%				height = 2.5em, 
%				pre length = 1em,
%				eff length = 1em 
%			};

%			\action{A}{SinglePrecAlt,
%				width  = 2.5em, 
%				height = 2.5em, 
%				pre length = 1em,
%				eff length = 1em,
%				body = {right = 4em of first} 		
%			};

%			\path[every node/.style={font=\sffamily\small}]
%			(B) edge [->,bend right] node [left]  {} (A);
%			\end{tikzpicture}

%			\caption{Resulting method ordering has no cycle}
%			
%		\end{subfigure}
%	}   
\end{figure}

% We can use either sets of preconditions and effects (from either possible inference algorithm) as input to the next linearization phase. Since the effects and preconditions are guaranteed, it may find a linearization that leads to a problem whose solution is yet faster to find,
% or has better make-span than the simple inference. Specifically, the mandatory precondition-relaxed effects, $\RelEffPlus$, $\RelEffMinus$.

\section{Theoretical Properties of Linearization Result}

We now discuss the implications of the above-described linearization procedure.

\begin{theorem}\label{thm:Runtime}
	Given a problem $P = (F, T_P, T_C, \delta, M)$, Algorithm~\ref{alg:Algorithm1} takes polynomial time.
\end{theorem}
\begin{proof}  % ,  network of tasks it can decompose to as a tree of tasks whose edges are between a task and a task it can decompose to, since it excludes previously seen tasks. 
	Let $|T|$ = $|T_P| + |T_C|$.

	%The Floyd-Warshall algorithm to calculate transitive closure is used for each method's sub-tasks, resulting in a time complexity of $\mathcal{O}(|M| * |T|^3)$,

	To calculate $\PreS, \AddS, \DelS$ for each task $t$. We explore it's compound sub-tasks until we collect all primitive tasks. Then loop over $\PreS, \AddS, \DelS$ for the root $t$, over each fact, over each primitive task in the sub-tree. This is obviously polynomial in terms of $|T|$. %This provides an upper limit of $(3 * |F| * |T_p|) + T_C$. This inference occurs for each compound task, so $((3 * |F| * |T_P|) + |T_C|) * |T_C|$ time at most, or $\mathcal{O}(|F| * |T|^2)$. % we explore all poss (at most $|T_C|$)

	Lines~\ref{alg:StartBuildGraph}-\ref{alg:EndBuildGraph} of Algorithm~\ref{alg:Algorithm1} iterates over every method, which iterates over every fact, which iterates over every sub-task in that method, which iterates over every other sub-task in that method. Leading to at most $\mathcal{O}(|M| * |F| * |T|^2)$, since number of sub-tasks per method is upper bounded by $T$.

	Cycle-breaking, done by lines \ref{alg:StartCycleBreak} to \ref{alg:EndCycleBreak} can be done via depth-first search per cycle to break, which is also polynomial to $|T|$.

	Line~\ref{alg:TopSort} can be done via topological sort of a graph where sub-tasks are nodes, and orderings are edges, which is known to be in $\mathcal{O}(V+E)$ in time. % and $\mathcal{O}(V)$ in space.  
	The number of sub-tasks and edges are upper bounded by $T$, so approximately $\mathcal{O}(|M| * |T|)$.

	So the algorithm takes polynomial time. 
\end{proof}

\begin{theorem}\label{thm:Soundness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then the solution set of $P'$, denoted $sol(P')$ is a subset of $sol(P)$.
\end{theorem}
\begin{proof}
	The new desired orderings for a method include all of the orderings already required by the method originally. The algorithm then turns the tasks and new desired orderings between them into a directed graph, and the new ordering is produced by performing a topological sort on the nodes of that graph. This means we do not modify the sub-tasks a method produces, just the ordering between them, so the set of plans from the totally ordered method is just a subset of the plans possible from the partially ordered one. Any solution to the linearized problem is then obviously a solution to the original problem.
\end{proof}

\begin{theorem}\label{thm:notCompleteness}
	Given a POHTN planning problem $P$ and TOHTN problem
	$P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}
	then $sol(P')$ may be empty.
\end{theorem}
\begin{proof}
	This algorithm linearizes all the methods to be totally ordered. Since sub-tasks inherit the orderings of their parents, it's impossible to preserve a solution that requires the interleaving of sub-tasks if their respective parents are already ordered with respect to each other. This proves that the algorithm can remove some possible action sequences, assuming the original domain was not already totally ordered. Consider the simple example problem:
	The only decomposition for this problem results in the set of un-ordered actions $\{A, B, C\}$.
	If we consider that for the $3!$ linearizations of this set, the only executable one is $A, B, C$. This is impossible to achieve by linearized methods, since ordering either AB before C or C before AB will exclude the solution. 
	Even if we were to produce $k!$ methods for each partially ordered method with $k$ unordered sub-tasks, we would not be able to preserve any solution for this problem.
	This proves that the algorithm can remove all solutions, so Algorithm~\ref{alg:Algorithm1} is not complete. Note that incompleteness already follows from complexity theory as it's theoretically impossible to turn an arbitrary undecidable problem into a decidable one.
	Specifically, solutions that require interleaving of sub-tasks will not be preserved, as the example above demonstrates.
\end{proof}

% The exploitation of the relaxed preconditions and effects
% is possible because they possess subset properties with regard to the actual ones so that they do not contain false candidates.

\begin{description}
	\item[Linearization Criteria] If the linearization process does not find any desired ordering contradicting the existing ones for some method, or in other words, \emph{cycle-breaking} did not occur, that method is said to meet the linearization criteria. If all methods in a problem meet the linearization criteria, then the problem meets the linearization criteria as well. 
\end{description}

%IT ONLY WORKS IF *ALL* METHODS CAN BE CYCLE-BREAKED.

\begin{theorem} \label{thm:RelaxedPreconditions}
	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, \emph{only if $P$, the entire problem meets the linearization criteria},
	then we know executability-relaxed preconditions for any $c$ are indeed the only ones needed to execute any refinement of $c$.
\end{theorem}
\begin{proof}
%	At least in the case where the linearization criteria is met for all methods, we can be assured that the executability-relaxed preconditions actually work for us.

	For some method with at least two sub-tasks, $a$ and $b$,
	the desired orderings are to put $a$ with $f \in \Add(a)$ before $b$ with $f \in \Pre(b)$. We're assuming no cycle-breaking, so this was actually achieved. If such a precondition can't be met this way, (such an $a$ does not exist, or the method already enforces that $b$ executes before $a$) by definition it must be in the executability-relaxed preconditions calculated.

	Therefore, any precondition of $c$'s children that can't be met by placing other children of $c$ before it is part - so it is indeed a super-set of actual preconditions, assuming no cycle-breaking was needed.

	If even one partially ordered method did need cycle-breaking, than of course it means nothing - we may indeed need other preconditions to make refinements of $c$ executable. Then those results no longer hold.
\end{proof}

We use Theorem~\ref{thm:RelaxedPreconditions} as support for the following main result. We will now prove that our algorithm preserves at least one solution as long as Algorithm~\ref{alg:Algorithm1} uses simple inference or preconditions and possible effects from complex inference, and this criterion is met.

\begin{theorem}\label{thm:SpecialCase}
	Given a POHTN planning problem $P$ and TOHTN problem $P'$ obtained from $P$ by using Algorithm~\ref{alg:Algorithm1}, if $P$ meets the linearization criteria and $sol(P)$ is non-empty, then $sol(P')$ will be non-empty as well.
\end{theorem}
\begin{proof}	
	Assume that there exists a solution in the PO domain. By using the same decomposition sequence in the linearized domain, we can produce the same set of actions as in the PO solution, but with a linearization of the actions decided by the linearized domain. Assume this sequence is $(a_0, a_1, ..., a_n)$. We then prove by induction over the sequence $(a_0, a_1, ..., a_n)$ that it is executable.
	If $(a_0, a_1, ..., a_n)$ is not executable, that means there exists some action $a_k,  0 < k < n$ that is not executable in the corresponding state. The action $a_k$ could only be non-executable, if one or more of its preconditions was not met. Assume one of these unmet preconditions is for existence of the state variable $A$.
	The action $a_k$ must be executable in some linearization of $\{a_0, ..., a_n\}$, as we assumed it was a PO solution. So there must exist an action $a_i$, $0 < i < n$, that will add A. Actions $a_0$ and $a_k$ must have a shared parent p in a Task Decomposition Tree. So p has subtasks $t_0$ and $t_k$ that are parents of $a_0$ and $a_k$ respectively.

	The linearization of this method would have drawn an ordering $(t_i, t_k)$ due to the way the algorithm defines $prec^{*}, add^{*}$ etc. We are assuming that all methods meet the linearization criteria, so $(t_i, t_k)$ should not be required, either directly or via inheritance from parent tasks. This safely enforces $(a_k, a_0)$ ordering in the final TO plan, meaning $a_0$ is not the first action in the resulting total order imposed by the algorithm. In other words, if $a_k$’s precondition could be met by any action $a_i$, $a_i$ would be ordered in front of it.

	If $a_i$ does not exist then $a_k$ can never be executed for any linearization of $\{a_0, ...a_n\}$, contradicting the assumption that this was a PO solution. Since each action in the solution is executable, the entire sequence is executable linearization of actions produced by decomposition of initial task, i.e.\ the solution.
\end{proof}

There are several possible levels of \enquote{completeness} for a problem compilation.
%\begin{enumerate}
\begin{itemize}
	\item all solutions remain 
	\item at least one solution remains 
	\item all optimal solutions remain
	\item at least one optimal solution remains 	
\end{itemize}
%\end{enumerate}
Given what's proven in Theorem~\ref{thm:notCompleteness} and \ref{thm:SpecialCase}, Algorithm~\ref{alg:Algorithm1} guarantees at least one solution remains, if linearization criteria is met. Otherwise, Algorithm~\ref{alg:Algorithm1} makes no completeness guarantees at all -- it may remove all possible solutions. Finally, Algorithm~\ref{alg:Algorithm1} makes no decisions on any metric of optimality, so obviously cannot guarantee completeness that any optimal solutions remain.

\begin{theorem}\label{thm:newClass}
	Problems $P$ that satisfy the linearization criteria form a new class of decidable problems.
\end{theorem}
\begin{proof}
	A problem $P'$ obtained from applying Algorithm~\ref{alg:Algorithm1} to any arbitrary $P$ is a totally ordered problem, which are known to be decidable, as proven by \cite{Alford2015TightHTNBounds}.  
\end{proof}

\section{Empirical Evaluation}
We compare the runtime of several state-of-the-art planning systems on some transformed POHTN problems. All problems are taken from two benchmark sets prepared for the International Planning Competition (IPC) 2020. The first set \footnote{https://github.com/panda-planner-dev/ipc2020-domains/tree/master/partial-order} was used in the partially ordered track in the 2020 IPC benchmark, while the second set \footnote{https://github.com/panda-planner-dev/domains/tree/master/partial-order} went un-used for various reasons. Each problem has the standard IPC time limit of 30 minutes. Any grounding and pre-processing time needed is included as part of the 'solving' time. Since the pre-processing may \emph{potentially} remove all solutions, where the planning system can prove that the pre-processing renders a problem unsolvable, we use the remaining time to solve the original problem, called a \textit{re-run}.

\subsection{Hardware and Planning Systems}
The empirical evaluation was conducted on a machine with 30GiB of memory and 4 vCPUs, each with 2 GiB RAM. Recent work by \cite{HTN2SAS} shows that the PO panda$_\pi$, achieved similar coverage and slightly lower IPC score than the best TO planner tested. Also tested is HyperTensioN by \cite{hypertension} an TOHTN solver and the IPC 2020 winner, and Lilotane by \cite{Lilotane} another TOHTN solver and the IPC 2020 runner-up.

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration. This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists. The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.

% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }

%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}

We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. For other planners, panda$_\pi$ with rc2(Add) is used for re-runs. We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). We test both Complex and Simple Inference for linearization. Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.

The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.

The planner that has achieved the highest overall coverage is panda$_\pi$ with FF, and highest IPC score is panda$_\pi$ planner with Add heuristic, which reflects findings in previous papers.

For each partial-order planner, e.g. RC Add represents panda$_\pi$ using RC and Add heuristic,
the PO column shows it's performance on the original problem, and the TO column shows performance on the linearized problem. For each total-order planner, the column beneath it shows performance on the linearized problem.
The IPC score has a maximum of 1 per domain, for the 12 domains in total.

%The comparison is done for grounded  linearization variant and the lifted linearization variant 1. # \value{page}

The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}. This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average. However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains. E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.

Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.

%	&& \multicolumn{2}{c}{  \rotatebox{90}{rc2(Add)}} & 
%		\multicolumn{2}{c}{   \rotatebox{90}{rc2(Filter)}} & 
%		\multicolumn{2}{c}{  \rotatebox{90}{rc2(FF)}}
%		& \multicolumn{2}{c}{   \rotatebox{90}{rc2(LMC)}}  
%		& \multicolumn{2}{c}{  \rotatebox{90}{HyperTensioN}}
%		& \multicolumn{2}{c}{  \rotatebox{90}{Lilotane}} \\

%\todo{proven unsolvable should not be in superscripts}

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleCoverage}
	\scalebox{0.8} {
\begin{tabular}{lccccccl} 
	\toprule 
	& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO\\  
	\midrule 
	Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0}   \\ 
	Monroe Fully Observ.$^{2}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{25.0}   \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{14.0} & \textbf{14.0} & 14.0 & \textbf{15.0}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{14.0} & \textbf{14.0}   \\ 
	Rover & 6.0 & \textbf{20.0} & 4.0 & \textbf{19.0}   \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}   \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}   \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}   \\ 
	Woodworking$^{2}$ & 13.0 & \textbf{19.0} & 12.0 & \textbf{20.0}   \\ 
			\midrule 
	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
	SmartPhone$^{1}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
	Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}   \\ 
			\midrule 
	Coverage & 239.0 & \textbf{287.0} & 231.0 & \textbf{274.0}   \\ 
	Norm. coverage & 8.22 & \textbf{9.95} & 8.0 & \textbf{9.63}   \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

\begin{table}
	\centering
	\caption{IPC score achieved, using Simple Inference on Grounded Problems}
	\label{table:GroundedSimpleIPC}
	\scalebox{0.85} {
	\begin{tabular}{lccccccccl} 
	\toprule 
	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	& PO & TO & PO & TO  \\ 
	\midrule 
	Barman-BDI & 0.08 & \textbf{0.4} & 0.07 & \textbf{0.36}  \\

	Monroe Fully Observ.$^{2}$ & \textbf{0.56} & 0.45 & \textbf{0.46} & 0.41  \\ 
	Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.25 & \textbf{0.31} & 0.26   \\ 
	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.82} & \textbf{0.82}   \\ 
	Rover & 0.29 & \textbf{0.95} & 0.2 & \textbf{0.78}  \\ 
	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\

	Transport & 0.24 & \textbf{0.61} & 0.27 & \textbf{0.32}   \\ 
	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\ 
	Woodworking$^{2}$ & 0.38 & \textbf{0.58} & 0.36 & \textbf{0.57}  \\ 
	\midrule 
	Monroe & \textbf{0.77} & 0.69 & \textbf{0.75} & 0.71   \\ 
	SmartPhone$^{1}$ & \textbf{0.71} & \textbf{0.71} & \textbf{0.71} & \textbf{0.71}   \\ 
	Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}   \\

	\midrule 
	IPC score & 7.1 & \textbf{8.4} & 7.0 & \textbf{7.9}  \\

	\bottomrule 
		\end{tabular} 		
	}
\end{table}

\begin{table}
	\centering
	\caption{Coverage achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleCoverage}
	\scalebox{0.65} {
		\begin{tabular}{lccccccccccl} 
			\toprule 
			& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
			\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
			&PO & TO & PO & TO  \\ 
\midrule 
Barman-BDI & 3.0 & \textbf{10.0} & 3.0 & \textbf{10.0} & \textbf{17.0} & \textbf{17.0}  \\ 
Monroe Fully Observ.$^{7}$ & \textbf{25.0} & \textbf{25.0} & 22.0 & \textbf{23.0} & \textbf{25.0} & 18.0  \\ 
Monroe Part. Observ.$^{2}$ & \textbf{14.0} & 13.0 & \textbf{14.0} & 13.0 & 3.0 & \textbf{20.0}  \\ 
PCP$^{18}$ & \textbf{15.0} & \textbf{15.0} & \textbf{14.0} & \textbf{14.0} & 14.0 & 0.0  \\ 
Rover & 6.0 & \textbf{15.0} & 4.0 & \textbf{14.0} & \textbf{20.0} & \textbf{20.0}  \\ 
Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
Transport & 12.0 & \textbf{27.0} & 13.0 & \textbf{14.0} & 26.0 & \textbf{35.0}  \\ 
UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & 21.0  \\ 
Woodworking & \textbf{13.0} & 7.0 & \textbf{12.0} & 7.0 & 9.0 & 6.0  \\ 
\midrule 
Monroe & \textbf{96.0} & 92.0 & \textbf{92.0} & 90.0 & \textbf{100.0} & \textbf{100.0}  \\ 
SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{6.0} & 6.0 & 1.0  \\ 
Zenotravel & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\ 
\midrule 
Coverage & 240.0 & \textbf{263.0} & 231.0 & \textbf{243.0} & \textbf{272.0} & 268.0  \\ 
Norm. coverage & 8.23 & \textbf{9.45} & 8.0 & \textbf{8.83} & \textbf{9.61} & 8.58  \\ 
\bottomrule 
		\end{tabular}

	}
\end{table}

\begin{table}
	\centering
	\caption{IPC score achieved, using Simple Inference on Lifted Problems}
	\label{table:LiftedSimpleIPC}
	\scalebox{0.7} {
\begin{tabular}{lccccccccccl} 
	\toprule 
	& \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{RC FF} & HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5} 
	&PO & TO & PO & TO  \\  
\midrule 
Barman-BDI & 0.07 & \textbf{0.38} & 0.07 & \textbf{0.35} & \textbf{0.85} & 0.72  \\ 
Monroe Fully Observ.$^{7}$ & \textbf{0.56} & 0.52 & \textbf{0.47} & 0.45 & \textbf{0.95} & 0.54  \\ 
Monroe Part. Observ.$^{2}$ & \textbf{0.31} & 0.28 & \textbf{0.31} & 0.29 & 0.09 & \textbf{0.63}  \\ 
PCP$^{18}$ & \textbf{0.83} & \textbf{0.83} & \textbf{0.82} & \textbf{0.82} & 0.82 & 0.0  \\ 
Rover & 0.28 & \textbf{0.61} & 0.2 & \textbf{0.56} & \textbf{0.99} & 0.97  \\ 
Satellite & 0.9 & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
Transport & 0.24 & \textbf{0.6} & 0.27 & \textbf{0.32} & 0.61 & \textbf{0.78}  \\ 
UM-Translog$^{1}$ & \textbf{1.0} & 0.99 & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & 0.92  \\ 
Woodworking & \textbf{0.38} & 0.23 & \textbf{0.36} & 0.23 & 0.26 & 0.2  \\ 
\midrule 
Monroe & \textbf{0.77} & 0.74 & \textbf{0.76} & 0.73 & \textbf{1.0} & 0.96  \\ 
SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.86} & 0.79 & 0.14  \\ 
Zenotravel & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
\midrule 
IPC score & 7.1 & \textbf{8.2} & 7.0 & \textbf{7.6} & \textbf{9.4} & 7.9  \\ 
\bottomrule 
\end{tabular} 
	}
\end{table}

\begin{table}
	\centering
	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexCoverage}.
	\scalebox{0.8} {

\begin{tabular}{lccccccl} 
	\toprule 
	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO  \\ 
	\midrule 
	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\

	\midrule 
	Monroe & 96.0 & \textbf{100.0} & 92.0 & \textbf{100.0}  \\ 
	SmartPhone$^{3}$ & 5.0 & \textbf{7.0} & 5.0 & \textbf{7.0}  \\ 
	Zenotravel$^{2}$ & \textbf{5.0} & \textbf{5.0} & \textbf{5.0} & \textbf{5.0}  \\

		\midrule 
	Coverage & 245.0 & \textbf{290.0} & 233.0 & \textbf{271.0}  \\ 
	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
	\bottomrule 
\end{tabular} 
	}
\end{table}

\begin{table}
	\centering
	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexIPC}.
	\scalebox{0.8} { 
\begin{tabular}{lccccccl} 
			\toprule 
		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO  &PO & TO  \\ 
	\midrule 
	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\

	Monroe Fully Observ.$^{5}$ & \textbf{0.57} & 0.18 & \textbf{0.47} & 0.16  \\ 
	Monroe Part. Observ. & \textbf{0.31} & 0.1 & \textbf{0.31} & 0.11  \\ 
	PCP$^{17}$ & \textbf{0.82} & \textbf{0.82} & \textbf{0.83} & \textbf{0.83}  \\ 
	Rover & 0.41 & \textbf{0.84} & 0.2 & \textbf{0.69}  \\ 
	Satellite & 0.91 & \textbf{1.0} & 0.99 & \textbf{1.0}  \\ 
	Transport & 0.24 & \textbf{0.65} & 0.27 & \textbf{0.31}  \\ 
	UM-Translog$^{1}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
	Woodworking$^{1}$ & 0.38 & \textbf{0.57} & 0.35 & \textbf{0.54}  \\ 
	\midrule 
	Monroe & \textbf{0.77} & 0.48 & \textbf{0.75} & 0.48  \\ 
	SmartPhone$^{3}$ & 0.71 & \textbf{1.0} & 0.71 & \textbf{0.87}  \\ 
	Zenotravel$^{2}$ & \textbf{1.0} & \textbf{1.0} & \textbf{1.0} & \textbf{1.0}  \\ 
		\midrule 
	IPC score & 7.2 & \textbf{8.0} & 7.0 & \textbf{7.3}  \\ 
	\bottomrule 
\end{tabular}  
	}
\end{table}

\begin{table} 
	\centering  
	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
	\label{table:FullyLinearizedProblems}
	\scalebox{0.75} { 
	\begin{tabular}{lcccl} 
		\toprule
		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
		\midrule
		SmartPhone  & 4.0                   &  1     \\
		Transport   & 1144.9                & 40       \\
		UM-Translog & 1.1                    & 17   \\
		Woodworking & 2035              &   21    \\
				\bottomrule 
	\end{tabular} 
	}
\end{table}

\begin{table} 
	\centering
	\caption{These results are from using Simple Inference. Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
	\label{table:SimpleLinearizable} 
		\scalebox{0.65} { 
	\begin{tabular}{lcccl} 
		\toprule 
		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
		\midrule
Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
Monroe & 12127.3 & 3447.8 & 72.4  \\ 
Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
PCP & 12.3 & 12.3 & 0.0  \\ 
Rover & 509.4 & 355.2 & 32.3  \\ 
Satellite & 70.6 & 36.1 & 50.9  \\ 
SmartPhone & 6.3 & 4.0 & 21.8  \\ 
Transport & 1144.9 & 1144.9 & 0.0  \\ 
UM-Translog & 1.5 & 1.5 & 0.0  \\ 
Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
Zenotravel & 190.2 & 99.4 & 47.0  \\ 
		\bottomrule 
	\end{tabular} 
}
\end{table}

\begin{table} 
	\centering
	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
	\label{table:ComplexLinearizable} 
	\scalebox{0.65} { 
	\begin{tabular}{lcccl} 
		\toprule 
		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
		\midrule
			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
			Monroe & 12127.3 & 216.9 & 98.2  \\ 
			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
			PCP & 12.3 & 4.9 & 59.8  \\ 
			Rover & 509.4 & 134.8 & 72.4  \\ 
			Satellite & 70.6 & 10.7 & 77.9  \\ 
			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
			Transport & 1144.9 & 0.0 & 100.0  \\ 
			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
			Woodworking & 1927.3 & 476.0 & 85.5  \\
			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
			\bottomrule 
		\end{tabular} 
		}
\end{table}

While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too. (Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)

\begin{table} 
	\caption{For the Problems in Each Domain, Average Percentage of Partially-Ordered Methods Linearized Without Cycle-break per Problem, for each Domain. Shows Results for Both Inference Methods.}\label{table:POMethodBreak} 
	\begin{tabular}{lccl} 
		\toprule 
		Domain & Complex & Simple &  \\ 
		\midrule
		Transport & 1.0 & 0.0  \\ 
		UM-Translog & 0.8 & 0.0  \\ 
		Satellite & 1.0 & 0.0  \\ 
		Monroe Fully Observ. & 1.0 & 0.0  \\ 
		Rover & 1.0 & 0.0  \\ 
		Woodworking & 0.9 & 0.0  \\ 
		Monroe Part. Observ. & 1.0 & 0.0  \\ 
		PCP & 0.0 & 0.0  \\ 
		Barman-BDI & 1.0 & 0.0  \\ 
		SmartPhone & 0.1 & 0.1  \\ 
		Monroe & 0.8 & 0.0  \\ 
		Zenotravel & 1.0 & 0.0  \\ 
		\bottomrule 
	\end{tabular} 
\end{table}

%\begin{figure*}
%	\caption{Percentage of Problems Linearized Without Cycle-break for each Domain and each Inference Method}
%	\label{fig:ProblemsLinearizedWOCycleBreak}
%	\centering
%	\includegraphics[width=14cm]{figures/Lin_criteria_C_vs_S.jpg}
%\end{figure*}

%\begin{figure*}
%	\caption{For Grounded Problems, Average Percentage of Methods Linearized Without %Cycle-break for Each Domain and for Each Inference Method}
%	\label{fig:MethodsLinearizedWOCycleBreak}
%	\centering
%	\includegraphics[width=14cm]{figures/Lin_average_C_vs_S.jpg}
%\end{figure*}

\section{Related Work}
There exist other planners that also compile POHTN problems to decidable planning classes e.g. the planners by \cite{HTN2STRIPS} and HTN2SAS planner by \cite{HTN2SAS} convert POHTN to classical planning problems. To the best of my knowledge, this is the first work that focuses on converting POHTN to TOHTN problems.

\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
of actions has an executable linearization. Our criteria would work on a problem where the only method is for the initial task, and it’s sub-tasks are actions. That is essentially just ordering a partially ordered plan, so the criteria can also identify a proper subset of all partially ordered plans that can be linearized in polynomial time. It can also find a executable linearization for that subset in polynomial time.

\cite{NEBEL1994125} studied various questions regarding partially ordered plans, such as the complexity of plan existence, plan optimisation, possible or necessary truth of properties before or after plan steps, given various constraints on the types of tasks allowed.  \cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.

Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists. This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine. Thus their results are orthogonal to ours.

The paper by \citet{DeleteRelaxation, Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.

\section{Future Work}
%Encode Linearization Problem as a MAX-SAT Problem
The maximum satisfiability problem (MAX-SAT) is the problem of determining the maximum number of clauses, of a given Boolean formula in conjunctive normal form, that can be made true by an assignment of truth values to the variables of the formula. MAX-SAT is used over SAT as it may not be possible to satisfy all orderings implied by the inferred preconditions and effects.

The current linearization procedure considers each method in isolation, and sub-tasks have their inferred $\PreS, \AddS, \DelS$. Thus we can treat each sub-task as a \enquote{action}, and encode the method the same way as a classical plan, as described by \cite{RINTANEN201245}, but with the additional constraint that \enquote{actions} chosen from the method sub-tasks can only be selected once, unlike in the domain.
% Assuming no negative preconditions, the initial state has all state variables true, and goal state can be assumed to be empty (i.e.\ all state variables can have any assignment). The relative success (or failure) of this approach could also lend insight into what about the criteria causes the linearization to be successful.

%Adding a Plan as Additional Input to the Domain
%Adding a plan as additional input to the PO domain having the semantics that this plan shall be in the solution set of the TO output model. This reduces the computational complexity of the decision problem from undecidable.  % I assume the resulting problem is PSPACE-complete, but this needs to be proven

\section{Conclusion}

% The contributions of this paper are as follows:

This paper finds that, at least for the POHTN problems in the IPC domain, most of them are not undecidable. In other words, it is as if the POHTN domains are compressed TO domains - this linearization separates one of them back out.

We can also see this pre-processing technique leads to large gains in time/efficiency for a number of planners, at least for the problems tested here. Furthermore, there is demonstrably much more room for improvement. Though the criteria does not fire all the time, it's producing a linearization that is almost always solvable.

This method can also be used to increase the number of TOHTN problems available for purposes like comparing TOHTN planners or grounding techniques. Suppose there were $n$ POHTN problms and $m$ TOHTN problems, and this linearization could make those $n$ POHTN problems into $k$ solvable $TOHTN$ problems. Then $k+m$ (lifted or grounded) TOHTN problems exist now. And from empirical evaluation, $k$ may be close to $n$.

Finally, in this paper we identify a subset of decidable problems within POHTN problems, and this subset is orthogonal to all others discussed in other works.

% Use \bibliography{yourbibfile} instead or the References section will not appear in your paper
\bibliography{bib}
% \nobibliography{aaai22}

\end{document}

### 2022-12-23 paper/06--evaluation.tex
captions, ref, etc

@@
 The results table for both coverage and IPC score can be seen on page \pageref{table:GroundedSimpleIPC}--\pageref{table:GroundedComplexIPC}.
-As we can see from those figures, using complex inference results in ?  increase/decrease/similar, coverage and IPC score.
+As we can see from those figures, using complex inference results in [blank] increase/decrease/similar, coverage and IPC score.
 
@@
 
-While simple linearization can linearize almost none of the actaully partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
+While simple linearization can linearize almost none of the actually partially ordered methods, with complex linearization, we can successfully linearize a fair amount of the partially-ordered methods too.
 (Note that this does not result in a guaranteed solvability-preserving problem unless all methods conform to the criteria though.)

### 2022-12-23 paper/07--relatedWork.tex
captions, ref, etc

@@
 
-\cite{ErolHTNExpressivity} proved that it is NP-complete to decide whether a partially ordered set
+\cite{Erol1996HTNComplexity} proved that it is NP-complete to decide whether a partially ordered set
 of actions has an executable linearization.
@@
 
-The paper by \shortCite{DeleteRelaxation,Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{ErolHTNExpressivity}'s result (deciding whether a partially ordered
+The paper by \shortCite{DeleteRelaxation,Bercher2021POCLComplexities} generalised \cite{NEBEL1994125}'s as well as \cite{Erol1996HTNComplexity}'s result (deciding whether a partially ordered
 set of actions possesses an executable linearization) by showing that this problem does not become easier when one is allowed to insert delete-relaxed  actions.

### 2022-12-23 paper/07--relatedWork.tex
citations

@@
 \cite{KambhampatiModalTruth1996} studied related questions and criteria under different assumptions.
-In the paper by \cite{TanGruningerPOPlanComplexity}, the authors refine \cite{NEBEL1994125}'s results and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
+The work in \citep{TanGruningerPOPlanComplexity} refines the results of \cite{NEBEL1994125} and show the impact of the interaction of preconditions and effects thereby giving a more detailed picture for when finding a linearization for a partially-ordered plan is possible in polynomial time, and when it remains NP-hard.
 
-Criteria presented in \cite{NEBEL1994125} and \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
+Criteria presented by \cite{NEBEL1994125}, \cite{KambhampatiModalTruth1996} and  \cite{TanGruningerPOPlanComplexity} analyse cases where actions have singleton precondition and add lists.
 This is a less general case than our criteria can cover, but their criteria also correctly identifies some cases as linearizable in polynomial time that our criteria is unable to determine.

### 2022-12-23 paper/04--otherLinearization.tex
captions, ref, etc
delete 99 qote

@@
 	\scalebox{0.75}{
-		\begin{subfigure}{4.5cm}
+		\begin{subfigure}{4cm}
 			\begin{tikzpicture}[auto,node distance=1.2cm,
@@
 		\begin{subfigure}{7cm}
-		 	\centering
-			\caption{Resulting method ordering has a cycle}
-			\label{fig:CycleBreaking1}
+		 %	\centering
 			\begin{tikzpicture}[auto,node distance=1.2cm,
@@
 			\end{tikzpicture}
-
+			\caption{A method that has the orderings from Figure~\ref{fig:OrderingRules} has a cycle}
+			\label{fig:CycleBreaking1}
 		\end{subfigure}
@@
 		 %	\centering
-			\caption{Delete any random ordering to break it}
-			\label{fig:CycleBreaking2}
 			\begin{tikzpicture}[auto,node distance=1.2cm,
@@
 			\end{tikzpicture}
+			\caption{Delete any random ordering to break the cycle.}
+			\label{fig:CycleBreaking2}
 		\end{subfigure}
 	}
-	\caption{Example of Cycle-Breaking the Desired Additional Orderings\label{fig:CycleBreaking}\Psays{Ying, captions come in figures always below the graphics.
+	\caption{Example of Cycle-Breaking Until the Method No Longer Has Any Cycles \label{fig:CycleBreaking}\Psays{Ying, captions come in figures always below the graphics.
 Can you fix this?
